### 2017-10-20 daniel_thesis/ddd_fem.tex
added thesis, changed input file, fixed some formatting cuda code

\chapter{Coupling Discrete Dislocation Dynamics to Finite Element Methods}
\label{c:ddd_fem}
	\section{Superposition Scheme}
	\label{s:sup_sch}
		Coupling \kwd{ddd} to \kwdp{fem} \cite{analytical_integration_of_the_forces_induced_by_dislocations_on_a_surface_element} is important to properly simulate micromechanical tests because \kwd{ddd} provides us with a more precise set of inputs and greater granularity for solving the \kwd{fe} problem.
		\begin{figure}
			\centering
			\includegraphics[width=\linewidth]{fem_ddd.pdf}
			\caption[Coupling Discrete Dislocation Dynamics to Finite Element Methods.]{The \kwd{dl} ensemble in a volume $ V $ is bounded by surface $ S $. First, the traction field $ \sum_{\textrm{d}} \tns{\tilde{\sigma}}_{\textrm{d}} $ due to the \kwd{dl} ensemble is evaluated at the surface. Then, a traditional \kwd{fem} or \kwd{bem} calculates the image traction field $ \tns{\hat{\sigma}} \times \vec{n} $. Which is then fed back to the \kwd{ddd} problem to evolve the \kwd{dl} positions and repeat the cycle. Image edited from \cite{analytical_integration_of_the_forces_induced_by_dislocations_on_a_surface_element}.}
			\label{f:fem_ddd}
		\end{figure}

### 2017-10-20 daniel_thesis/glossary.tex
added thesis, changed input file, fixed some formatting cuda code

% Entries without acronyms
\newglossaryentry{bv}
{
	name={Burgers vector},
	description={Denoted as $\vec{b}$, it represents the lattice distortion caused by a \kwd{dl} in a crystal lattice. In \emph{edge} \kwdp{dl} the Burgers vector is perpendicular to the line direction ($ \vec{b} \perp t $); in \emph{screw} \kwdp{dl} it is parallel to the line direction ($ \vec{b} \parallel t $); in \emph{mixed} \kwdp{dl}, Burgers vector and line direction are neither perpendicular nor parallel to each other},
	symbol = {\ensuremath{\vec{b}}}
}

\newglossaryentry{dl}
{
	name={dislocation},
	description={Crystallographic defect which strongly influences many of a material's properties. It can consist of additional or missing partial crystallographic planes, and may come in three varieties: edge, screw and mixed. Mathematically it is a type of topological defect/soliton because it is a distinct, out of equillibrium---but stable---solution of the \kwd{pde} which in the trivial case yields the crystallographic structure of a material. Like any other soliton, it will not spontaneously decay to the ``trivial'' solution, which in this case would be a perfect crystal. Thus a dislocation preserves its identity by preserving its \kwd{bv}. Like other solitons, it can annihilate with another of opposite phase, which in this case would be an opposite \kwd{bv}}
}

\newglossaryentry{devmem}
{
	name = {device memory},
	description = {Graphics card memory visible only within GPU functions}
}

\newglossaryentry{atop}
{
	name = {atomic operation},
	description = {An operation on shared or global \kwd{devmem} which is guaranteed to be performed without interference from other threads. However, atomic operations don't act as memory fences and do not imply \kwd{thrsync} \cite{nvidia_atomics}}
}

\newglossaryentry{thrsync}
{
	name = {thread syncronisation},
	description = {Ensures all threads catch up to each other in some way or another. The function \mintinline{c}{__syncthreads()} ensures all threads in a \kwd{wrp} reach the same point. The function \mintinline{c}{__threadfence()} flushes all global memory and shared memory writes by a thread so the updated values are visible to other threads before continuing}
}

\newglossaryentry{cma}
{
	name = {coalesced memory access},
	description = {When all active threads in a \kwd{wrp} access contiguous global memory. Therefore cache lines can be very efficiently utilised}
}

\newglossaryentry{wrp}
{
	name = {warp},
	description = {Collection of threads with a maximum of 32 which execute concurrently on the same \kwd{sm} resources}
}

\newglossaryentry{wrpd}
{
	name = {warp divergence},
	description = {Due to the fact that all threads in a \kwd{wrp} must execute the same instruction concurrently, all program branches are executed regardless of branching condition. However, only those instructions for which a branching condition is met have an effect on the state of the thread's program. As a consequence, different threads in a \kwd{wrp} may meet different branching conditions, wasting all other branched instructions}
}

\newglossaryentry{tensor}
{
	name = {tensor},
	description = {Geometric object that represents linear relations between matrices, vectors, scalars and other tensors}
}

\newglossaryentry{dls}
{
	name = {dislocation line segment},
	description = {Discretisation of dislocations as straight line segments between two tracked nodes},
	plural={dislocation line segments}
}

% Entries with acronyms
% Syntax: \newdualentry[glossary options][acronym options]{label}{abbrv}{long}{description}
\newdualentry
{sm}
{SM}
{Streaming Multiprocessor}
{A differential equation which contains unkown multivariate functions and their partial derivatives. Solutions require knowledge of the boundary conditions the unkown functions are subject to. The types of PDEs and their boundary conditions can make it difficult or impossible to find well-behaved, analytical solutions. As a result, numerical methods such as \kwd{fem} are often used to solve them}

\newdualentry
{pde}
{PDE}
{Partial Differential Equation}
{A differential equation which contains unkown multivariate functions and their partial derivatives. Solutions require knowledge of the boundary conditions the unkown functions are subject to. The types of PDEs and their boundary conditions can make it difficult or impossible to find well-behaved, analytical solutions. As a result, numerical methods such as \kwd{fem} are often used to solve them}

\newdualentry
{fem}
{FEM}
{Finite Element Method}
{Also known as finite element analysis (FEA), they are a class of numerical methods for solving boundary value problems for \kwdp{pde} whose analytical solution might not meet the necessary uniqueness and existence requirements of a physical problem. These methods divide the domain of interest into smaller, simpler subdomains that can be described by a system of algebraic equations. These are then assembled into a larger system of coupled algebraic equations that approximately model the whole domain. Variational methods are then used to find an approximate solution by minimising an associated error function}

\newdualentry
{bem}
{BEM}
{Boundary Element Method}
{The 2D analogue of an \kwd{fem}, where only the domain boundaries are of interest}

\newdualentry
{fe}
{FE}
{Finite Element}
{One of the subdomains of a problem solved via \kwd{fem}}

\newdualentry
{be}
{BE}
{Boundary Element}
{One of the subdomains of a problem solved via \kwd{bem}}

\newdualentry
{se}
{SE}
{Surface Element}
{Special case of a \kwd{be}, where the boundary is a surface}

\newdualentry
{ddd}
{DDD}
{Discrete Dislocation Dynamics}
{The study of the dynamics of \kwdp{dl} as discrete entities made up of discrete nodes connected by line segments. They assume an infinite medium in which dislocations exist, evolve and interact. Due to their intermediate nature between atomistic and continuum models, they can explore time and length scales which are either too big for more fundamental approaches, and too small for \kwd{fem}}

### 2017-10-20 daniel_thesis/para_force_se.tex
added thesis, changed input file, fixed some formatting cuda code

\chapter{Parallelisation of the Analytical Forces Induced by Dislocations on Surface Elements}
\label{c:para_f_dln_se}
	%
	\section{Parallelisation on Graphics Processing Units}
	Efficient parallelisation requires \kwd{cma}, which means we have to be extremely careful when mapping CPU memory to device memory. The fact that threads work ``simultaneously'' means that in order to obtain good performance, the data which is to be ``simultaneously'' loaded into each thread must be contiguous. This maximises cache memory use and therefore reduces slow memory fetch operations to global or shared memory.

	The parallelisation was done only over the \kwdp{se} in order to avoid the undesirable and inefficient GPU branching that would occur under other schemes.

	The most natural form of parallelisation is to have blocks of $ 4n $ threads where $ n \leq 8 \in \mathbb{N}$. This also fits nicely into the 32 thread per warp paradigm.
	%
	\subsection{Data Mapping}
		%
		\begin{figure}
			\centering
			\includegraphics[width=\linewidth]{lrse_thread_map.pdf}
			\caption[Linear rectangular surface element mapping.]{Each linear rectangular \kwd{se} is mapped to one thread.}
			\label{f:lrse_map}
		\end{figure}
		%
		\subsubsection{Elements: Host $ \mapsto $ Device}
			%
			\begin{algorithm}
				\caption{Elements in host $ \mapsto $ device.}
				\label{a:ehd}
				\begin{algorithmic}[1]
					\Function{element\_host\_device\_map}{\hvar{\vec{X}[N][3\times E]}}
						\State{\Comment{Input, temporary, and output indices set to zero.}}
						\State{$ i,\, j,\, k \gets 0 $}
						\State{\Comment{\dvar{\vec{X}} accomodates all 3 coordinates of all $ N $ nodes in all $ E $ elements.}}
						\State{$ \dvar{\vec{X}} \gets $ malloc($ 3\times E\times N $)}
						\For{$(n = 0;\, n < N;\, n++)$} \Comment{Loop over nodes in element.}
							\State{\Comment{Set output index to point at the $ n\textsuperscript{th} $ node of the first coordinate of the first element.}}
							\State{$ k \gets j $}
							\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
								\State{\Comment{Set input index to point at the $ c\textsuperscript{th} $ coordinate of the first element of the $ n\textsuperscript{th} $ node.}}
								\State{$ i \gets c $}
								\For{$ (e = 0;\, e < E;\, e++) $} \Comment{Loop over elements.}
									\State{$ \dvar{\vec{X}[k + e]} \gets \hvar{\vec{X}[n][i]} $}
									\State{\Comment{Advance output index to point at the $ n\textsuperscript{th} $ node of the $ c\textsuperscript{th} $ coordinate of the first element.}}
									\State{$ i \gets i + 3 $}
								\EndFor
								\State{\Comment{Advance output index to point at the $ n\textsuperscript{th} $ node of the $ c\textsuperscript{th} $ coordinate of the first element.}}
								\State{$ k \gets k + E \times N $}
							\EndFor
							\State{\Comment{Advance temporary index to point at the $ (n+1)\textsuperscript{th} $ node of the first coordinate of the first element.}}
							\State{$ j \gets j + E $}
						\EndFor
						\State{\Return{\dvar{\vec{X}}}}
					\EndFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Elements: Device $ \mapsto $ Thread}
			\begin{algorithm}
				\caption{Elements in device $ \mapsto $ thread.}
				\label{a:edt}
				\begin{algorithmic}[1]
						\GPUFunction[element\_device\_thread\_map]{\dvar{\vec{X}[3\times E\times N]}, \tvar{\vec{X}[N][3]}}
						\State{\Comment{Thread, input indices.}}
						\State{$ \rvar{idx},\, i \gets \rvar{threadIdx}.x + \rvar{blockIdx}.x\times \rvar{blockDim}.x $}
						\For{$ (n = 0;\, n < N;\, n++) $}\Comment{Loop over nodes in element.}
							\For{$ (c = 0;\, c < 3;\, c++) $}\Comment{Loop over elements.}
								\State{$ \tvar{\vec{X}[n][c]} \gets \dvar{\vec{X}[i + c\times E\times N]}$}
							\EndFor
							\State{$ i \gets i + E $}
							\Comment{Advance input index to the $(n+1)\textsuperscript{th}$ node of element $i$.}
						\EndFor
						\State{\Return{\tvar{\vec{X}[n][c]}}}
					\EndGPUFunction
				\end{algorithmic}    	
			\end{algorithm}
		\subsubsection{Force: Thread $ \xmapsto{+} $ Device}
			\begin{algorithm}
				\caption{Force in thread $ \xmapsto{+} $ device.}
				\begin{algorithmic}[1]
						\GPUFunction[add\_force\_thread\_device]{\tvar{\vec{F_{n}}[N][3]}, \tvar{\vec{F_{e}}[3]}, \dvar{\vec{F_{n}}[3\times E\times N]},\newline{}\dvar{\vec{F_{e}}[3\times E]}, \rvar{idx}}
						\State{\Comment{Nodal force.}}
						\State{\Comment{Set output index to whatever parallelisation index is given to the function. In this case the same index we use for the main parallelisation.}}
						\State{$ i \gets \rvar{idx} $}
						\For{$ (n = 0;\, n < N;\, n++) $} \Comment{Loop over nodes.}
							\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
								\State{\Comment{Ensure nodal forces are correctly added and mapped from local thread memory to global device memory.}}
								\State{atomicAdd(\dvar{\vec{F_{n}}[i + c\times E\times N]}, \tvar{\vec{F_{n}}[n][c]})}
							\EndFor
							\State{\Comment{Displace output index to point at the first coordinate of the $ (n+1)\textsuperscript{th} $ node of the \rvar{idx}\textsuperscript{th} \kwd{se}.}}
							\State{$ i \gets i + E $}
						\EndFor
						\State{\Comment{Total force.}}	
						\State{$ i \gets \rvar{idx} $} \Comment{Reset output index.}
						\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
							\State{atomicAdd(\dvar{\vec{F_{e}}[i]}, \tvar{\vec{F_{e}}[c]})}
							\State{\Comment{Advance the output index to point at the $ (i+1)\textsuperscript{th} $ coordinate of the $ \rvar{idx}\textsuperscript{th} $ \kwd{se}.}}
							\State{$ i \gets i + E $}
						\EndFor
						\State{\Return{\dvar{\vec{F_{n}}}, \dvar{\vec{F_{e}}}}}
					\EndGPUFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Force (Parallelise over Dislocations): Thread $ \xmapsto{+} $ Device}
			\begin{algorithm}
				\caption{Force (parallelise over dislocations) in thread $ \xmapsto{+} $ device.}
				\begin{algorithmic}[1]
					\GPUFunction[dln\_add\_force\_thread\_device]{\tvar{\vec{F_{n}}[N][3]}, \tvar{\vec{F_{e}}[3]},\newline{}\dvar{\vec{F_{n}}[3\times E\times N]}, \dvar{\vec{F_{e}}[3\times E]}, $ k $}
						\State{\Comment{Nodal force.}}
						\State{\Comment{Set output index to correspond to whatever \kwd{se} we're on. By parallelising over dislocation lines, we must loop through \kwdp{se} in the main code, this is the value of $ k $ we provide. Multiply by 3 and $ N $ because each \kwd{se} has 3 coordinates and $ N $ nodes.}}
						\State{$ i \gets 3\times N\times k $}
						\State{$ j \gets 0 $} \Comment{Auxiliary index.}
						\For{$ (n = 0;\, n < N;\, n++) $} \Comment{Loop over nodes.}
							\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
								\State{\Comment{Ensure nodal forces are correctly added and mapped from local thread memory to global device memory.}}
								\State{atomicAdd(\dvar{\vec{F_{n}}[i + j + c]}, \tvar{\vec{F_{n}}[n][c]})}
							\EndFor
							\State{\Comment{Displace auxiliary index to point at the first coordinate of the $ (n+1)\textsuperscript{th} $ node of the $ k \textsuperscript{th}$ \kwd{se}.}}
							\State{$ j \gets j + 3 $}
						\EndFor
						\State{\Comment{Total force.}}
						\State{\Comment{Set auxiliary index to point at the first coordinate of the $ k\textsuperscript{th} $ \kwd{se}.}}
						\State{$ j \gets 3\times k $}
						\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
							\State{atomicAdd(\dvar{\vec{F_{e}}[j+c]}, \tvar{\vec{F_{e}}[c]})}
						\EndFor
						\State{\Return{\dvar{\vec{F_{n}}}, \dvar{\vec{F_{e}}}}}
					\EndGPUFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Nodal Force: Device $ \mapsto $ Host}
			\begin{algorithm}
				\caption{Nodal force in device $ \mapsto $ host.}
				\begin{algorithmic}[1]
					\Function{fx\_device\_host\_map}{\dvar{\vec{F_{n}}[3\times E\times N]}, \hvar{\vec{F_{n}}[N][3\times E]}}
						\State{$ i,~j \gets 0 $} \Comment{Set input and output indices to zero.}
						\For{$ n = 0;\, n < N;\, n++ $} \Comment{Loop over nodes.}
							\State{$ j \gets 0 $} \Comment{Reset output index to point at the first element.}
							\For{$ e = 0;\, e < E;\, e++ $} \Comment{Loop over elements.}
								\For{$ c = 0;\, c < 3;\, c++ $} \Comment{Loop over coordinates.}
									\State{$ \hvar{\vec{F_{n}}[n][j + c]} = \dvar{\vec{F_{n}}[i + e + c\times E\times N]} $}
								\EndFor
								\State{\Comment{Advance output index to point at the first coordinate of the $ (e+1)\textsuperscript{th} $ element.}}
								\State{$ j \gets j + 3 $}
							\EndFor
							\State{\Comment{Advance input index to point at the first coordinate of the $ (n+1)\textsuperscript{th} $ node of the first element.}}
							\State{$ i \gets i + E $}
						\EndFor
						\State{\Return{\hvar{\vec{F_{n}}}}}
					\EndFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Total Force: Device $ \mapsto $ Host}
			\begin{algorithm}
				\caption{Total force in device $ \mapsto $ host.}
				\begin{algorithmic}[1]
					\Function{ftot\_device\_host\_map}{\dvar{\vec{F_{e}}[3\times E]}, \hvar{\vec{F_{e}}[3\times E]}}
						\State{$ i \gets 0 $} \Comment{Set output index to zero.}
						\For{$ e = 0;\, e < E;\, e++ $} \Comment{Loop over elements.}
							\For{$ c = 0;\, c < 3;\, c++ $} \Comment{Loop over coordinates.}
								\State{$ \hvar{\vec{F_{e}}[i + c]} = \dvar{\vec{F_{e}}[e + c\times E]} $}
							\EndFor
							\State{\Comment{Advance the output index to point at the first coordinate of the $ (e+1)\textsuperscript{th} $ surface element.}}
							\State{$ i \gets i + 3 $}
						\EndFor
						\State{\Return{\hvar{\vec{F_{e}}}}}
					\EndFunction
				\end{algorithmic}
			\end{algorithm}
	\begin{subequations}\label{e:fcne}
		\begin{align}
			\vec{X}_{en}			&\coloneqq	\left[x_{en},\, y_{en},\, z_{en}\right]\\
			\vec{X}_{(1\to E)n}		&\mapsto 	\vec{X}_{n} \nn
			\vec{X}_{n}				&\coloneqq	\left[x_{1n},\, y_{1n},\, z_{1n},\ldots,x_{En},\, y_{En},\, z_{En}\right]\label{se:xn_arr}\\
			\vec{X}_{1\to N}		&\mapsto	\vec{X}^{\textrm{SE}}\nn
			\vec{X}^{\textrm{SE}}	&\coloneqq 
			\begin{aligned}
				&\left[x_{11},\, \ldots,\, x_{E1},\, x_{12},\, \ldots,\, x_{E2},\, \ldots,\, x_{1N},\, \ldots,\, x_{EN}, \right.\\
				&\left.\,y_{11},\, \ldots,\, y_{E1},\, y_{12},\, \ldots,\, y_{E2},\, \ldots,\, y_{1N},\, \ldots,\, y_{EN}, \right.\\
				&\left.\,z_{11},\, \ldots,\, z_{E1},\, z_{12},\, \ldots,\, z_{E2},\, \ldots,\, z_{1N},\, \ldots,\, z_{EN}  \right]
			\end{aligned}
		\end{align}
	\end{subequations}
	where $ e\equiv $~\kwd{se} label, $ n \equiv $~node label, $ E \equiv $~number of \kwdp{se} in the scope. $ N \equiv $~number of nodes in a \kwd{se}.

	Data-mapping according to \cref{a:fcne} and relabelling the nodes so they go from $ 0 \to N-1 $, the data from \cref{f:lrse_map} would be arranged in \kwd{devmem} like \cref{e:fcne_eg},
	\begin{align}\label{e:fcne_eg}
		\vec{X}^{\textrm{SE}} &= \begin{aligned}
			\left[\underbrace{h_{x},\, i_{x},\, f_{x},\, g_{x}}_{\mathbf{x_{0}}},\, 
			\underbrace{a_{x},\, b_{x},\, i_{x},\, h_{x}}_{\mathbf{x_{1}}},\, 
			\right.&\underbrace{i_{x},\, d_{x},\, e_{x},\, f_{x}}_{\mathbf{x_{2}}},\, 
			\underbrace{b_{x},\, c_{x},\, d_{x},\, i_{x}}_{\mathbf{x_{3}}},\\
			\ldots~y&\textrm{-coord}~\ldots,\\
			\ldots~z&\textrm{-coord}~\ldots]
		\end{aligned}
	\end{align}
	%

	In the GPU, each thread will cater to one \kwd{se} at a time. This means that each thread will have to extract the relevant data from the 1D array with length $ 3\times E\times N $ into four 1D arrays of length $ 3 $. The purpose of CNE mapping is to provide the \kwd{wrp} with \kwd{cma}. This is achieved via \cref{a:bcne}.

	Since \cref{a:bcne} is performed in a CUDA GPU, threads in a single block execute sequentially from,
	\begin{align}
		\rvar{threadIdx}.x &= 0 \to \rvar{threadIdx}.x = \rvar{blockDim}.x - 1\,,
	\end{align}
	while threads in different blocks execute in parallel. \Kwd{cma} is ensured by having each block load a cache line whose entries are contiguously accessed by the threads in the block. Using the same notation as \cref{a:fcne}, full cache line utilisation (optimal cache use) is achieved if cache lines can accomodate $ l $ entries given by \cref{e:opt_cache_len_bcne},
	\begin{align}
		\label{e:opt_cache_len_bcne}
		l =
		\begin{cases}
			a \times N \times E &,\, a > 0 \in \mathbb{N}\\
			&\textrm{or}\\
			\dfrac{1}{2^{a}} \times N \times E &,\, a \geq 0 \in \mathbb{N},\, N \times E \equiv 0\; (\bmod\; 2^{a})\,.
		\end{cases}
	\end{align}
	\Cref{f:fcne_eg} shows an example of \cref{a:bcne} up to the $ y $-coordinate.
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{node_bmap.pdf}
		\caption[Example of the backward coodinate-node-element-map.]{Minimum working complete example of the backward coodinate-node-element-map. The explicit calculations of global indices correspond to subsituting the values for ``idx'' and ``idxi'' as in \cref{a:bcne}. $\vec{X_{a}^{b}}$ denotes a 1D array of length three containing the $ xyz $-coordinates of node $ a $ of element $ b $. Each thread concerns itself with only one element at a time. The dash-dot and dashed boxes represent cache lines for a thread block, the dotted line represents a memory fetch, and the dashed lines in $ \vec{X^{E}} $ represent steps of $ E $ entries (the start of the data for the next node of the element type we're dealing with). The memory operations are not shown twice to minimuse redundancy.}
		\label{f:fcne_eg}
	\end{figure}
	% Start: Code for generating figure e:opt_cache_len_bcne
	%\begin{align}%\label{f:fcne_eg}
	%	\vec{X}^{\textrm{SE}} &= 
	%							\begin{aligned}
	%								\left[\overbrace{h_{x},\, i_{x},\, f_{x},\, g_{x}}^{\mathbf{x_{3}}},\, 
	%								\overbrace{a_{x},\, b_{x},\, i_{x},\, h_{x}}^{\mathbf{x_{4}}},\, 
	%								\right.&\overbrace{i_{x},\, d_{x},\, e_{x},\, f_{x}}^{\mathbf{x_{5}}},\, 
	%								\overbrace{b_{x},\, c_{x},\, d_{x},\, i_{x}}^{\mathbf{x_{6}}},\\
	%								\overbrace{h_{y},\, i_{y},\, f_{y},\, g_{y}}^{\mathbf{x_{3}}},\, 
	%								\overbrace{a_{y},\, b_{y},\, i_{y},\, h_{y}}^{\mathbf{x_{4}}},\, 
	%								&\overbrace{i_{y},\, d_{y},\, e_{y},\, f_{y}}^{\mathbf{x_{5}}},\, 
	%								\overbrace{b_{y},\, c_{y},\, d_{y},\, i_{y}}^{\mathbf{x_{6}}},\\
	%								\overbrace{h_{z},\, i_{z},\, f_{z},\, g_{z}}^{\mathbf{x_{3}}},\, 
	%								\overbrace{a_{z},\, b_{z},\, i_{z},\, h_{z}}^{\mathbf{x_{4}}},\, 
	%								&\left.\overbrace{i_{z},\, d_{z},\, e_{z},\, f_{z}}^{\mathbf{x_{5}}},\, 
	%								\overbrace{b_{z},\, c_{z},\, d_{z},\, i_{z}}^{\mathbf{x_{6}}}\right]
	%\end{align}
	%\begin{align}
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{0}^{0}}[0] \gets \vectorsym{X^{E}}[(0+0\times 2) + (0\times 4 \times 4) + (0\times 4)]\nonumber\\
	%			&\vectorsym{X_{0}^{1}}[0] \gets \vectorsym{X^{E}}[(1+0\times 2) + (0\times 4 \times 4) + (0\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{0}^{2}}[0] \gets \vectorsym{X^{E}}[(0+1\times 2) + (0\times 4 \times 4) + (0\times 4)]\nonumber\\
	%			&\vectorsym{X_{0}^{3}}[0] \gets \vectorsym{X^{E}}[(1+1\times 2) + (0\times 4 \times 4) + (0\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{2}^{0}}[0] \gets \vectorsym{X^{E}}[(0+0\times 2) + (0\times 4 \times 4) + (2\times 4)]\nonumber\\
	%			&\vectorsym{X_{2}^{1}}[0] \gets \vectorsym{X^{E}}[(1+0\times 2) + (0\times 4 \times 4) + (2\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{2}^{2}}[0] \gets \vectorsym{X^{E}}[(0+1\times 2) + (0\times 4 \times 4) + (2\times 4)]\nonumber\\
	%			&\vectorsym{X_{2}^{3}}[0] \gets \vectorsym{X^{E}}[(1+1\times 2) + (0\times 4 \times 4) + (2\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	%					
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{0}^{0}}[1] \gets \vectorsym{X^{E}}[(0+0\times 2) + (1\times 4 \times 4) + (0\times 4)]\nonumber\\
	%			&\vectorsym{X_{0}^{1}}[1] \gets \vectorsym{X^{E}}[(1+0\times 2) + (1\times 4 \times 4) + (0\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{0}^{2}}[1] \gets \vectorsym{X^{E}}[(0+1\times 2) + (1\times 4 \times 4) + (0\times 4)]\nonumber\\
	%			&\vectorsym{X_{0}^{3}}[1] \gets \vectorsym{X^{E}}[(1+1\times 2) + (1\times 4 \times 4) + (0\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{2}^{0}}[1] \gets \vectorsym{X^{E}}[(0+0\times 2) + (1\times 4 \times 4) + (2\times 4)]\nonumber\\
	%			&\vectorsym{X_{2}^{1}}[1] \gets \vectorsym{X^{E}}[(1+0\times 2) + (1\times 4 \times 4) + (2\times 4)]\nonumber\\
	%		\end{cases}\nonumber\\
	%	\textrm{Parallel execution}
	%		&\begin{cases}
	%			&\vectorsym{X_{2}^{2}}[1] \gets \vectorsym{X^{E}}[(0+1\times 2) + (1\times 4 \times 4) + (2\times 4)]\nonumber\\
	%			&\vectorsym{X_{2}^{3}}[1] \gets \vectorsym{X^{E}}[(1+1\times 2) + (1\times 4 \times 4) + (2\times 4)]\nonumber\\
	%		\end{cases}\nonumber
	%\end{align}
	% End: Code for generating figure e:opt_cache_len_bcne
	\subsubsection{Node Coordinate Element Map}
	%
	The node-coordinate-element (NCE) data mapping in \cref{e:fnce} is carried out by \cref{a:fnce}, each thread looks after a given \kwd{se}.
	\begin{algorithm}
		\caption{NCE data mapping.}
		\label{a:fnce}
		\begin{algorithmic}
			\ForAll{n nodes $ \in $ surface element}
			\ForAll{c coordinates $ \in [x,\, y,\, z] $}
			\ForAll{e surface elements $ \in $ surface mesh section}
			\State list.append(data of the $ n\textsuperscript{th}$ node with $ c\textsuperscript{th} $ coordinate of the $ e\textsuperscript{th} $ SE)
			\EndFor
			\EndFor
			\EndFor
		\end{algorithmic}
	\end{algorithm}
	\begin{subequations}\label{e:fnce}
		\begin{align}
			\vec{X}_{en}			&\coloneqq \left[x_{en},\, y_{en},\, z_{en}\right]\\
			\vec{X}_{(1\to E)n}		&\mapsto \vec{X}_{n} \nn
			\vec{X}_{n}				&\coloneqq \left[x_{1n},\ldots,\, x_{En},\, y_{1n},\ldots,\, y_{En},\, z_{1n},\ldots,\, z_{En}\right]\\
			\vec{X}_{1\to N}		&\mapsto \vec{X}^{\textrm{SE}}\nn
			\vec{X}^{\textrm{SE}}	&\coloneqq 
			\begin{aligned}
				\left[x_{11},\ldots,\, x_{E1},\, y_{11},\right.&\ldots,\, y_{E1},\, z_{11},\ldots,\, z_{E1}\\
				,&\ldots,\\
				x_{1M},\ldots,\, x_{EN},\, y_{1N},&\left.\ldots,\, y_{EN},\, z_{1N},\ldots,\, z_{EN}\right]
			\end{aligned}
		\end{align}
	\end{subequations}
	where $ e\equiv $~surface \textbf{e}lement, $ n \equiv $~\textbf{n}ode, $ E \equiv $~total number of \kwdp{se} in scope, $ N \equiv $~total number of nodes in each \kwd{se}.

	Data-mapping according to \cref{a:fnce} and relabelling the nodes so they go from $ 0 \to N-1 $, the data from \cref{f:lrse_map} would be arranged in \kwd{devmem} like \cref{e:fnce_eg},
	\begin{align}\label{e:fnce_eg}
		\vec{X}^{\textrm{SE}} &= \begin{aligned}
			&\left[\underbrace{h_{x},\, i_{x},\, f_{x},\, g_{x},\, 
				h_{y},\, i_{y},\, f_{y},\, g_{y},\, 
				h_{z},\, i_{z},\, f_{z},\, g_{z}}_{\mathbf{x_{0}}}\right.,\\
			&~\ldots~\mathbf{x_{1}},\, xyz\textrm{-coords}~\ldots,\\
			&~\ldots~\mathbf{x_{2}},\, xyz\textrm{-coords}~\ldots,\\
			&~\ldots~\mathbf{x_{3}},\, xyz\textrm{-coords}~\ldots]
		\end{aligned}
	\end{align}
	%
	\subsubsection{Resolving Data Write Conflicts}
	Data write conflicts can be a problem in parallel applications where global data is changed by multiple threads within the same clock tick. This can be avoided with \kwdp{atop}.
	%
	\subsection[Parallel Dislocation Line Segments to Surface Elements]{Resolving Parallel Dislocation Line Segments to Surface Elements}
	%
	Dealing with the special case when the \kwd{dls} $ \vec{t} $ is parallel to the \kwd{se} is relatively trivial when in a serial program. By the mean value theorem, we can slightly perturb $ \vec{t} $ by rotating it by a small angle around the midpoint of $ \vec{t} $ with respect to the axis of rotation defined by $ \vec{t} \times \vec{n} $. In contrast to serial code, program branches can have a serious effect on parallel performance due to \kwd{wrpd}. Due to the complexity of the force calculation and relative rarity of the edge case, there is no branching behaviour in the parallel code until \emph{after} the calculation is performed. Where \cref{a:plse_p} is performed.
	\begin{algorithm}
		\caption{Resolving cases when $ \vec{t} \parallel \vec{n} $ on GPUs.}
		\label{a:plse_p}
		\begin{algorithmic}
			\ForAll{surface elements \emph{and} line segments}
			\State $ \ldots $
			\If{$ \vec{t}_{\textrm{thread}} \parallel \vec{n}_{\textrm{thread}} $}
			\State $ \vec{x}_{\textrm{buffer}} \gets \vec{x}_{\textrm{thread}} $
			\State $ \vec{t}_{\textrm{buffer}} \gets \vec{t}_{\textrm{thread}} $
			\Else
			\State $ \vec{F}_{\textrm{total}} += \vec{F}_{\textrm{thread}} $
			\EndIf
			\EndFor
			\State return to serial code
			\If{$ \vec{x}_{\textrm{buffer}} \neq $ empty}
			\ForAll{surface elements \emph{and} line segments}
			\State perform calculation for $ \vec{t} \parallel \vec{n} $
			\EndFor
			\EndIf
		\end{algorithmic}
	\end{algorithm}
	\subsubsection{Implementation}
	The node mapping would be the same as \cref{a:fcne}. The parallelisation would be on individual packets of a \kwd{se} with a slightly rotated \kwd{dls}, as in a single iteration of the serial code where the \kwd{dls} is rotated. The forces would be averaged with \kwdp{atop} and \mintinline{c}{__syncthreads()} before they are added to the total nodal forces.

	\subsection{Test Case}
	\begin{figure}
		\includegraphics[width=\linewidth]{cuda_test.pdf}
		\caption[Test case for CUDA development.]{Test case for CUDA development. Dislocation line not shown in node separation as the parallelisation happens across surface elements. Not to perspective or scale.}
		\label{f:cuda_test}
	\end{figure}
	According to \cref{a:fcne} and the node labelling scheme of \cref{f:flrs} the data mapping would look like:
	\begin{align}\label{e:cuda_test}
		\vec{X}^{\textrm{SE}} = 
		\begin{split}
			\left[\overbrace{\underbrace{1,1,0,0}_{\mathbf{x_{3}}}, \underbrace{2,2,1,1}_{\mathbf{x_{4}}},
				\underbrace{1,1,0,0}_{\mathbf{x_{5}}}, \underbrace{2,2,1,1}_{\mathbf{x_{6}}}}^{x\textrm{-coord}},\right.\\
			\overbrace{\underbrace{0,1,1,0}_{\mathbf{x_{3}}}, \underbrace{0,1,1,0}_{\mathbf{x_{4}}},
				\underbrace{1,2,2,1}_{\mathbf{x_{5}}}, \underbrace{1,2,2,1}_{\mathbf{x_{6}}}}^{y\textrm{-coord}},\\
			\left.\overbrace{\underbrace{0,0,0,0}_{\mathbf{x_{3}}}, \underbrace{0,0,0,0}_{\mathbf{x_{4}}},
				\underbrace{0,0,0,0}_{\mathbf{x_{5}}}, \underbrace{0,0,0,0}_{\mathbf{x_{6}}}}^{z\textrm{-coord}}\right]
		\end{split}
	\end{align}
	In general the number of indices in the array would be $ 3 \times e \times n $ where $ e \equiv $~number of surface elements, $ n \equiv $~number of nodes per element and 3 is the number of spatial dimensions.
	\savearabiccounter

### 2017-10-20 daniel_thesis/standards.tex
added thesis, changed input file, fixed some formatting cuda code

\chapter{Best Practices}\label{c:best_practices}
	This chapter defines the best practices that will make improve the development and testing pipeline by defining rules and standards that facilitate collaboration.
	\section{Filesystem}\label{c:best_practices:s:filesystem}
		All files must be within \texttt{/project\_name}. 
		\begin{enumerate}
			\item All files must be within \texttt{/project\_name},\\
				  \texttt{\textasciitilde/} = \texttt{project\_name/}, \\
				  \texttt{\textasciitilde/\textasciitilde/} = \texttt{project\_name/src/} or \texttt{project\_name/dev/}.
			\item Release code must be within \texttt{\textasciitilde/src/}.
			\item Development code must be within \texttt{\textasciitilde/dev/}.
			\item Test data must be within \texttt{\textasciitilde/tests/}.
			\item Documentation must be within \texttt{\textasciitilde/\textasciitilde/doc/}.
			\item Examples must be within \texttt{\textasciitilde/\textasciitilde/exmp/}.
			\item External libraries must be within \texttt{\textasciitilde/lib/}.
			\item Generated images must be within \texttt{\textasciitilde/\textasciitilde/images/}.
			\item Old versions recordkeeping must be within \texttt{\textasciitilde/prv/va.b.c/}.
		\end{enumerate}
	%
	\section{Versioning}\label{c:best_practices:s:versioning}
		\begin{enumerate}
			\item Use a version control system like \href{https://github.com/}{GitHub} or \href{https://pastebin.com/}{PasteBin}.
			\item There must be a master branch that is only changed when the code is stable and bug free.
			\item Development branches should be exploited as seen fit without making things overly convoluted.
			\item Commits must be as bug free and regular as possible. When to commit is left to the developer's discresion.
			\item Commit messages should be as descriptive as possible.
			\item Versions should be specified as \texttt{va.b.c} where \texttt{a}, \texttt{b}, \texttt{c} = integers. The three levels are \texttt{a} = release version (usable, bug free code), \texttt{b} = beta version (code that is undergoing testing), \texttt{c} = alpha version (code that is under active development).
		\end{enumerate}
	%	 
	\section{Documentation}\label{c:best_practices:s:documentation}
		\subsection{Commenting}\label{c:best_practices:s:documentation:ss:commenting}
			Every codefile must be appropriately commented by meeting the following guidelines.
			\begin{enumerate}
				\item The start of each codefile must have a heading detailing the creator, date of creation and edit history (date and name of editor).
				\item Below the heading there must be a general explanation of the code. It must state any procedures, structures, objects and how they are to be utilised. Any backward or forward dependencies must be stated.
				\item Below the description and edit history any relevant literature must be mentioned (dois are preferred). Must be as detailed as possible, include equation numbers/ranges if necessary.
				\item The start of every procedure has an explanation of its purpose, inputs, outputs and inputs-outputs.
				\item Particularly complicated code blocks must have an in-depth explanation of what it does. Comment each line if necessary.
				\item Corrections or additions must be explicitly bounded by comments at the start and end of the change. Both bounding comments must have the author's name and the date. Below the starting comment, there should be an explanation of the change. Any punctual comments can be made as normal.
			\end{enumerate}
		\subsection{README}\label{c:best_practices:s:documentation:ss:readme}
			Every codefile must have an associated \textsc{readme} \texttt{.tex} document that documents the codefile's contents. It must meet the following guidelines as appropriate.
			\begin{enumerate}
				\item The name must be that of the file it documents (minus the extension of course).
				\item Description and overall explanation of the codefile's purpose.
				\item Overall flow chart or pseudo code describing the file's purpose.
				\item Document the codefile's procedures. This means describing and explaining their corresponding inputs, outputs, inputs-outputs, forwards and backwards dependencies, and flow charts or pseudo codes.
				\item Unit test designs and results for each procedure. If appropriate also include those of integral tests.
			\end{enumerate}
			The codefile may also be appended at the end of documentation if desired (the \texttt{minted} package is highly recommended).
	%
	\section{Modularisation}\label{c:best_practices:s:modularisation}
		\begin{enumerate}
			\item Code repetition must be kept to a \emph{strict} minimum. Any piece of code that will be reused must be modularised.
			\item Procedures must be as self-sufficient as possible \emph{without} repeating code. If repeating code is necessary, replace it with a procedure that is to be repeatedly called instead. Minimising repeated code $\ggg$ procedure self-sufficiency.
		\end{enumerate}
	%
	\section{Coding Style}\label{c:best_practices:s:naming_conventions}
		All names must meet the following guidelines.
		\begin{enumerate}
			\item Indent appropriately. Four space tabs are a good compromise between code necking and readability.
			\item Minimise the use of nested code blocks, use intrisics, libraries or create procedures instead.
			\item Break up lines that are uncomfortably long, typically anything over 80--100 characters.
			\item Names should be appropriately descriptive and human readable.
			\item All code and names must be systematic and logical.
			\item the use of upper cases should be reserved for parameters (\texttt{const} variables in C).
			\item Delimit words with ``\texttt{\_}'' \emph{not} case changes.
			\item Long and descriptive $\ggg$ short and cryptic.
		\end{enumerate}
		\subsection{Filenames}\label{c:best_practices:s:naming_conventions:ss:filenames}
			\begin{enumerate}
				\item If old versions are to be kept, the old \emph{stable} versions of file must have the date of last modification appended \emph{suffixed} after the file extension in the \texttt{\_yyyymmdd} format. For example, if the stable version of the release code \texttt{hello\_world\_parallel.c} was last modified on April 25, 2017 it should be archived as\\ \texttt{hello\_world\_parallel.c\_20170425}.
			\end{enumerate}
		\subsection{Variables, Structures and Objects}\label{c:best_practices:s:naming_conventions:ss:variables_structures_objects}
			\begin{enumerate}
				\item Only counters and indices can be single letter variables.
				\item Structure and object \emph{definitions} are \emph{suffixed} with \texttt{\_s} and \texttt{\_o} respectively.
				\item Inputs, outputs and input-outputs to procedures must be \emph{prefixed} with \texttt{i\_}, \texttt{o\_} and \texttt{io\_} respectively.
			\end{enumerate}
		\subsection{Procedures}\label{c:best_practices:s:naming_conventions:ss:procedures}
			\begin{enumerate}
				\item Functions and subroutines must be \emph{prefixed} with \texttt{f\_} and \texttt{s\_} respectively.
			\end{enumerate}

### 2017-10-20 daniel_thesis/toc.tex
added thesis, changed input file, fixed some formatting cuda code

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\begin{romanpages}
	\tableofcontents
	%
	\phantomsection
	\addcontentsline{toc}{chapter}{List of Figures} % Add table index to the table of contents (toc).
	\listoffigures
	%
	\phantomsection
	\addcontentsline{toc}{chapter}{List of Tables} % Add table index to the table of contents (toc).
	\listoftables
	%
	\phantomsection
	\addcontentsline{toc}{chapter}{List of Algorithms} % Add table index to the table of contents (toc).
	\listofalgorithms
	%
	\printglossary[type=\acronymtype,title={Nomenclature}]
\end{romanpages}

### 2017-10-20 nodalForce/cuda_nodal_surface_force_linear_rectangle.cu

@@ -1332,7 +1332,7 @@ __device__ void add_force_thread_device(double i_nodal_force[][3], double *i_tot
   // Total force per surface element.
   // Loop over coordinates.
   idxf = idx;
-  for (int i= 0; i < 3; i++){
+  for (int i = 0; i < 3; i++){
     atomicAdd(&o_g_ftot_arr[idxf], i_total_force[i]);
     // Advance the output index to point at the (i+1)'th coordinate of the idx'th surface element.
     idxf += i_n_se;
@@ -1417,7 +1417,7 @@ void dln_fx_device_host_map(double *i_g_fx_arr, double *o_fx_arr[], int i_n_se, 
     }
     // Advance the input index to point at the first coordinate of the (i+1)'th node of the first element.
     idxi += 3;
-    idxf = 0;
+    idxf  = 0;
   }
 }
 

### 2017-10-23 nodalForce/cuda_nodal_surface_force_linear_rectangle.cu
fixed general device-thread map to use coalesced memory access

@@ -1243,6 +1243,17 @@ __device__ void element_device_thread_map(double *i_g_elem_arr, double o_x[][3],
   int n_elem_n_nodes = i_n_nodes*i_n_elem_scope;
   int idx  = threadIdx.x + blockIdx.x * blockDim.x;
   int idxi = idx;
+  // The lhs of this loop is not ideal due to the row-order of C but the rhs allows fully coalesced memory access of global memory.
+  // Loop over nodes.
+  for (int i = 0; i < 3; i++){
+    // Loop over coordinates.
+    for (int j = 0; j < i_n_nodes j++){
+      o_x[j][i] = i_g_elem_arr[idxi + i_n_elem_scope];
+    }
+    // Advance the global array index to point at the i'th coordinate of the first node of the idx'th element.
+    idxi += n_elem_n_nodes;
+  }
+  /*
   // Loop over nodes.
   for (int i = 0; i < i_n_nodes; i++){
     // Loop over coordinates.
@@ -1253,6 +1264,7 @@ __device__ void element_device_thread_map(double *i_g_elem_arr, double o_x[][3],
     // Advance the input index to point at the first coordinate of the (i+1)'th node of the idx'th element.
     idxi += i_n_elem_scope;
   }
+  */
 }
 
 __device__ void se_device_thread_map(double *i_g_se_arr,

### 2017-10-23 nodalForce/cuda_nodal_surface_force_linear_rectangle.cu
fixed general device-thread map to use coalesced memory access

@@ -1244,11 +1244,11 @@ __device__ void element_device_thread_map(double *i_g_elem_arr, double o_x[][3],
   int idx  = threadIdx.x + blockIdx.x * blockDim.x;
   int idxi = idx;
   // The lhs of this loop is not ideal due to the row-order of C but the rhs allows fully coalesced memory access of global memory.
-  // Loop over nodes.
+  // Loop over coordinates.
   for (int i = 0; i < 3; i++){
-    // Loop over coordinates.
+    // Loop over nodes.
     for (int j = 0; j < i_n_nodes j++){
-      o_x[j][i] = i_g_elem_arr[idxi + i_n_elem_scope];
+      o_x[j][i] = i_g_elem_arr[idxi + j*i_n_elem_scope];
     }
     // Advance the global array index to point at the i'th coordinate of the first node of the idx'th element.
     idxi += n_elem_n_nodes;

### 2017-10-24 daniel_thesis/force_lin_rect_se.tex

\chapter{Analytical Forces Induced by Dislocations on Linear Rectangular Surface Elements}
\label{c:lin_rect}
	%
	\section{Forces Exerted by a Dislocation Line Segment on Linear Rectangular Surface Elements}
	\label{s:f_lin_rect}
		%
		\begin{figure}
			\centering
			\includegraphics[width=\linewidth]{force_calc_linear_rectangle.pdf}
			\caption[Diagram of the analytical force calculation on linear rectangular surface elements.]{Diagram of the line integral method used to find analytical expressions for the forces exerted by \kwdp{dl} on linear rectangular \kwdp{se} \cite{analytical_integration_of_the_forces_induced_by_dislocations_on_a_surface_element}.
				\textit{1}) For any given point $ \vec{x} $ on the \kwd{se} and any given point $ \vec{x'}$ on the \kwd{dls}, define distance $ R_{a} $.
				\textit{2}) Integrate from $ x_{1} \to x_{2} $ along line direction $ \vec{t} $.
				\textit{3}) Integrate from $ r_{1} \to r_{2} $ along vector $ \vec{p} $.
				\textit{4}) Integrate from $ s_{1} \to s_{2} $ along vector $ \vec{q} $.}
			\label{f:flrs}
		\end{figure}
		\subsection{Resolving Singularities when Dislocation Line Segments are Parallel to Surface Elements}
		\label{ss:par_dln_se}
			%
			\begin{figure}
				\centering
				\includegraphics[width=\linewidth]{ftot_rotation_lin_rect.pdf}
				\caption[Avoiding singularities by rotating dislocation line segments.]{Effects of rotating a single \kwd{dls} on the forces exerted by it on a linear rectangular \kwd{se}. The specific values of this function are not known \emph{a priori}, all that is known is that it must be periodic ($ T = 2\pi$) and have finite maximum and minimum values. The singularity is avoided by perturbing the angle $ \theta = 0 \to \theta = \pm \epsilon\,\, \epsilon \gtrsim 0 $.}
				\label{f:rflrs}
			\end{figure}
		%
\savearabiccounter

### 2017-10-24 daniel_thesis/force_quad_triang_se.tex

\chapter{Analytical Forces Induced by Dislocations on Quadratic Triangular Surface Elements}
\label{c:quad_triang}
	\section{Forces Exerted by a Dislocation Line Segment on Quadratic Triangular Surface Elements}
	\label{s:f_quad_triang}
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{force_calc_quad_triangle.pdf}
		\caption[Diagram of the analytical force calculation on quadratic triangular surface elements.]{Diagram of the line integral method used to find analytical expressions for the forces exerted by \kwdp{dl} on quadratic triangular \kwdp{se}.}
		\label{f:fqts}
	\end{figure}
\savearabiccounter

### 2017-10-24 daniel_thesis/preface.tex

\addtocounter{chapter}{-1}
\chapter{Preface}
\label{c:pre}
%
\section{Notation}
\label{s:nota}
%
For the sake of clarity the following notation conventions have been used:
\begin{itemize}
	\item \Kwdp{tensor} are denoted by sans serif bold italics, $ \tns{T} $.
	\item Matrices are denoted by serif bold roman, $ \mtx{M} $.
	\item Vectors are denoted by serif bold italics, $ \vec{V} $.
	\item Scalars are denoted by serif italics, $ S $.
	\item Host variables are denoted by $\hvar{a}$.
	\item Global device variables are denoted by $\dvar{a}$.
	\item Thread variables are denoted by $\tvar{a}$.
\end{itemize}
\section{Conventions}
All angles are given in radians unless stated otherwise. All pseudo-code is C-style and assuming C conventions (row-order, 0-start indexing, memory allocation).

Elements, be they \kwdp{se}, \kwdp{fe}, \kwdp{dls} or else, are denoted by $ e $ and their total as $ E $. Similarly nodes are denoted by $ n $ and their total $ N $. Parallel indices are denoted by $ \rvar{idx} $ to distinguish them from regular indices/counters $i,~j,~k$. For disambiguation purposes the exponential function will de denoted as $ \exp(x) $.
\section{Typesetting}
\label{s:typeset}
%
This document was typeset using a custom-made \LaTeX{} document class created by the author, compiled with \hologo{XeLaTeX}, and the bibliography was produced with \hologo{BibTeX}. The custom document class can be found in \href{https://github.com/dcelisgarza/latex_templssaates}{https://github.com/dcelisgarza/latex\_templates}.
\section{Diagrams}
\label{s:diag}
%
All diagrams are vector graphics drawn using the open-source image editing software \href{https://inkscape.org/en/}{InkScape} for its ease of use, elegant simplicity, high quality outputs, and ``Draw~Freely'' philosophy.
\savearabiccounter

### 2017-10-24 daniel_thesis/talks.tex

\chapter{Talks}
	\section{Durham July 12--14 2017}
		Bridging the gap between the microscopic and macroscopic world is an on-going challenge for science and technology. If we hope to understand complex emergent phenomena we need to study systems that blur the line between micro and macro. In materials science, one such area is the study of extended defects called dislocations; whose nucleation and movement mediate the permanent deformation of materials. These large, high energy defects present very complex and long ranged interactions with each other, crystal boundaries, impurities, free surfaces, and themselves. As such, their dynamics are difficult to study experimentally. So we make justified assumptions and simplifications and create models that let us study them in detail. However if our models are to prove useful in real applications, they must be continually refined and improved by weakening assumptions and removing simplifications. Unfortunately, with increased refinement comes increased computational cost and new challenges. Therefore, finding faster alternatives that do not sacrifice accuracy is of the utmost importance---better yet if the alternatives are more accurate or exact. With the advent of increasingly accessible graphics processor units (GPUs) typically used in video gaming, the power of parallel processing is no longer exclusive to researchers with access to supercomputers. In this talk we will discuss the GPU implementation of exact solutions for the forces dislocations exert on the surfaces of materials.

### 2017-11-16 daniel_thesis/ddd_fem.tex
Updated thesis folder with extra documentation work I've done. Aligned some stuff in the code to make it look pretty.

@@
 		\end{figure}
+	\section{Extracting Surface Nodes}
+		The \kwd{fem} coupler arranges the nodes starting on the $ xz $-plane where $ y = 0, \ldots, n \mathrm{d}y,~n\in \mathbb{N} $.
+However in order to couple \kwd{ddd} to \kwd{fem} we only require the surface nodes where displacements are not calculated.
+Because we're working with rectangular prisms, we can easily pick out the surface nodes using a search algorithm with a logical mask.
+MATLAB and Fortran provide vector intrinsics that allow one to do so.
+\Cref{f:fem_surf_nodes} illustrates only the surface nodes according to our implementation's node arrangement---which is the $ xz $-plane going from $ y = y_{\textrm{min}} \to y = y_{\textrm{max}} $.
+		\begin{figure}
+			\centering
+			\begin{subfigure}[t]{0.45\linewidth}
+				\centering
+				\includegraphics[width=\linewidth]{fem_surf_nodes.pdf}
+				\caption[Surface nodes of our \kwd{fe} model.]{Arrangement of the surface nodes of our \kwd{fe} model.}
+				\label{f:fem_surf_nodes}
+			\end{subfigure}
+			~
+			\begin{subfigure}[t]{0.45\linewidth}
+				\centering
+				\includegraphics[width=\linewidth]{fe_numbering.pdf}
+				\caption[Single finite element node numbering.]{Single \kwd{fe} node numbering.}
+				\label{f:fe_numbering}
+			\end{subfigure}
+		\caption[Coupling Discrete Dislocation Dynamics to Finite Element Methods.]{Coupling Discrete Dislocation Dynamics to Finite Element Methods.}
+		\label{f:fem_node_arr}
+		\end{figure}
+		However, due to the nature of the analytical solutions in \cref{c:lin_rect}, we need all the surface nodes of the rectangular faces for which there are no displacements.
+This means that edge nodes are shared between 2 adjacent faces and corner nodes between 3 adjacent faces.
+In order to properly apply the logical mask to find \emph{only} the surface nodes need to know that each \kwdp{fe}' nodes are numbered according to \cref{f:fe_numbering}.
+
+		Using \cref{f:fem_node_arr} one can work out which nodes are of interest to whichever surface is being extracted.
+The ordering of the nodes in the final array will depend on the definition of the problems in \cref{c:lin_rect,c:quad_triang}.
+
+		Node selection remains an expensive operation and minimising array indexing is of the utmost importance for the best perfomance.
+Selecting nodes in the traditional sense, i.e.
+with code branching such as \texttt{if statements} or \texttt{case selection} is unmantainable, verbose and very prone to mistakes.
+The issue was solved by introducing an auxiliary matrix which defines various parameters that aid node selection and greatly reduces code size, improves readability, and eliminates the need for code branching.
+The matrix can be constructed utilising \cref{f:fem_node_arr} in order to know which nodes correspond to which \kwd{fe} planes.
+The $ p\textsuperscript{th} $ column of the matrix\footnote{MATLAB uses column-major ordering, so this gives us the best performance for vectorised code.} corresponds to the $ p\textsuperscript{th} $ plane (according to an arbitrary plane numbering) and is defined as the following column vector,
+		\begin{align}
+			\vec{V_{p}}^{\mathsf{T}} =
+				\begin{bmatrix}
+					L_{1p} & L_{2p} & \cdots & L_{Np} & A_{p} & C_{p}
+				\end{bmatrix}\,,
+		\end{align}	
+		where $ L_{np} \equiv $ the numeric label for node $ n $ as given by \cref{f:fem_node_arr}, $ A_{p} \equiv $ the area of the plane, and $ C_{p} \equiv$ the numeric label of the orthogonal coordinate to the plane $ C_{p} = 1, ~2, ~3 $ for the $ x, ~y, ~z $ coordinates respectively.
+$ A_{p} $ lets us segment our output and transitional arrays so that the only data being modified is that which corresponds to the correct plane and $ C_{p} $ lets us know which coordinate we must use in our selection criteria.
+The information codified in this matrix allows us to index and process only the necessary columns to extract the surface nodes we're interested in.
+The advantage of this setup over a naïve implementation is that it can be relatively easily expanded, maintained, and is general enough that it lends itself to a variety of selection criteria.

### 2017-11-16 analytic_traction.m

@@ -1,11 +1,11 @@
-function [nodal_force, total_force, x3x6] = analytic_traction(      ...
-                fem_nodes, fem_node_cnct, dln_nodes, dln_node_cnct, ...
-                fem_dim  , fem_planes   , n_nodes  , mu, nu, a    , ...
+function [nodal_force, total_force, x3x6] = analytic_traction(     ...
+                fem_nodes, fem_node_cnct, dln_nodes, dln_node_cnct,...
+                fem_dim  , fem_planes   , n_nodes  , mu, nu, a    ,...
                 use_gpu  , para_scheme)
     %%===================================================================%%
     %---------------------------------------------------------------------%
     % Written by famed MATLAB hater and fan of compiled languages,
-    % Daniel Celis Garza, in 12/11/17--16/11/17. 
+    % Daniel Celis Garza, in 12/11/17--16/11/17.
     %---------------------------------------------------------------------%
     % Couples analytical forces to the surfaces of a rectangular
     % cantilever whose nodes are labelled as follows:
@@ -13,16 +13,16 @@ function [nodal_force, total_force, x3x6] = analytic_traction(      ...
     % 4. ----- .3
     %  |\       |\
     %  | \      | \
-    % 1. -\---- .2 \ 
+    % 1. -\---- .2 \
     %   \  \     \  \
     %    \ 8. ----\- .7
     %     \ |      \ |
     %      \|       \|
     %      5. ----- .6
     % ^z
-    % |  y      
-    % | /         
-    % |/           
+    % |  y
+    % | /
+    % |/
     % |------>x
     %
     %=====================================================================%
@@ -43,13 +43,13 @@ function [nodal_force, total_force, x3x6] = analytic_traction(      ...
     % columns. Describes the node connectivity of the dislocation ensemble,
     % associated Burgers' vectors and slip planes.
     %
-    % fem_dim := [dim_x; dim_y; dim_z], finite element model dimensions. 
-    % dim_x := dimension in x-direction, dim_y := dimension in y-direction, 
+    % fem_dim := [dim_x; dim_y; dim_z], finite element model dimensions.
+    % dim_x := dimension in x-direction, dim_y := dimension in y-direction,
     % dim_z := dimension in z-direction.
     %
[…]

### 2017-11-16 extract_node_planes.m

@@ -1,15 +1,15 @@
 function node_plane = extract_node_planes(fem_nodes     , fem_node_cnct,...
-                                          surf_node_util, fem_planes    ,...
+                                          surf_node_util, fem_planes   ,...
                                           n_elem        , n_nodes)
     %%====================================================================%%
     %---------------------------------------------------------------------%
     % Written by famed MATLAB hater and fan of compiled languages,
-    % Daniel Celis Garza, in 13/11/17. 
+    % Daniel Celis Garza, in 13/11/17.
     %
     % This code has been optimised as much as I can and has been thoroughly
     % tested as of 15/11/17.
     %---------------------------------------------------------------------%
-    % 
+    %
     % Extracts a single node plane according to given filtering criteria
     % and puts it into a 2D array arranged in xyz-coordinates like so.
     %
@@ -41,12 +41,12 @@ function node_plane = extract_node_planes(fem_nodes     , fem_node_cnct,...
     % the model.
     %
     % surf_node_util := dimension(n_nodes+2, 6). Each column is laid out as
-    % follows: 
-    %   [node_label_initial; ... ; node_label_final; 
-    %    plane_area; coordinate_number]. 
+    % follows:
+    %   [node_label_initial; ... ; node_label_final;
+    %    plane_area; coordinate_number].
     % Each row corresponds to one plane.
     %
-    % fem_planes := dimension(:). Contains the planes whose nodes are to be 
+    % fem_planes := dimension(:). Contains the planes whose nodes are to be
     % extracted.
     %
     % n_elem := total number of elements to be extracted.
@@ -64,14 +64,14 @@ function node_plane = extract_node_planes(fem_nodes     , fem_node_cnct,...
     % node, plane_area is the total number of nodes in a plane and is found
     % in surf_node_utils.
     %
-    % tmp_nodes := dimension(n_nodes, 3). Contains the xyz-coordinates of 
+    % tmp_nodes := dimension(n_nodes, 3). Contains the xyz-coordinates of
     % all nodes with the labels specified by node_label.
     %
     % mask := same dimension as tmp_nodes. Logical mask whose entries are 1
-    % only when a given condition is met. It is used to index tmp_nodes to 
+    % only when a given condition is met. It is used to index tmp_nodes to
     % find only the nodes that correspond to a given plane.
     %
[…]

### 2017-11-17 daniel_thesis/ddd_fem.tex
Updating documentation.

@@
 			\centering
-			\begin{subfigure}[t]{0.45\linewidth}
+			\begin{subfigure}[b]{0.45\linewidth}
 				\centering
@@
 			~
-			\begin{subfigure}[t]{0.45\linewidth}
+			\begin{subfigure}[b]{0.45\linewidth}
 				\centering
@@
 The $ p\textsuperscript{th} $ column of the matrix\footnote{MATLAB uses column-major ordering, so this gives us the best performance for vectorised code.} corresponds to the $ p\textsuperscript{th} $ plane (according to an arbitrary plane numbering) and is defined as the following column vector,
-		\begin{align}
+		\begin{align}\label{e:surf_node_util_vec}
 			\vec{V_{p}}^{\mathsf{T}} =
@@
 $ A_{p} $ lets us segment our output and transitional arrays so that the only data being modified is that which corresponds to the correct plane and $ C_{p} $ lets us know which coordinate we must use in our selection criteria.
-The information codified in this matrix allows us to index and process only the necessary columns to extract the surface nodes we're interested in.
+Using our particular node labelling scheme (with dimensions $ \Delta x,~ \Delta y,~ \Delta z $ respectively in the $ x,~ y,~ z $ directions), the matrix is defined as
+		\begin{align}\label{eq:surf_node_util}
+			\mtx{V} = 
+				\begin{bmatrix}
+					5 & 2 & 6 & 1 & 5 & 4\\
+					1 & 6 & 5 & 2 & 6 & 3\\
+					8 & 3 & 7 & 4 & 1 & 8\\
+					4 & 7 & 8 & 3 & 2 & 7\\
+					\Delta y \Delta z & \Delta y \Delta z & \Delta x \Delta z & \Delta x \Delta z & \Delta x \Delta y & \Delta x \Delta y\\
+					1 & 1 & 2 & 2 & 3 & 3
+				\end{bmatrix}\,.
+		\end{align}
+		The information codified in \cref{eq:surf_node_util} lets us index and process only the necessary columns to extract the surface nodes we're interested in.
 The advantage of this setup over a naïve implementation is that it can be relatively easily expanded, maintained, and is general enough that it lends itself to a variety of selection criteria.
+The columns from left to right (1 to 6) represent:
+		\begin{inparaenum}[{face} 1 $ \equiv $]
+			\item $ \min(x),~ yz $-plane;
+			\item $ \max(x),~ yz $-plane;
+			\item $ \min(y),~ xz $-plane;
+			\item $ \max(y),~ xz $-plane;
+			\item $ \min(z),~ xy $-plane;
+			\item $ \max(z),~ xy $-plane.
+		\end{inparaenum}
+
+		It is important to make sure the nodes are extracted in a self consistent manner because the problem definition in \cref{c:lin_rect,c:quad_triang} assumes a specific node ordering.
+In particular, the labelling chirality must remain the same.
+This is due to the fact that the problems in \cref{c:lin_rect,c:quad_triang} utilise internal coordinates derived from a set of basis vectors, and scalar projections onto them.
+If the relationship between the vectors is kept, but the chirality is different (opposite) the calculated quantities will have the wrong sign.
+If however the relationship between the vectors is different to the problem formulation, the program will crash due to division by 0.
+Self-consistency was achieved by placing an imaginary observer inside the \kwd{fe} model facing the $ \min(x),~ yz $-plane (face 1) and rotating it to view all 6 planes according to \cref{f:surf_node_plane}.
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.75\linewidth]{surf_node_plane.pdf}
+			\caption[Self-consistent, chirality preserving surface planes.]{Self-consistent, chirality preserving surface planes.
+Plane and node numbering according to the columns of \cref{eq:surf_node_util} and \cref{f:fem_node_arr}.}
+			\label{f:surf_node_plane}
+		\end{figure}

### 2017-11-17 daniel_thesis/para_force_se.tex
fixed general device-thread map to use coalesced memory access and updated thesis to reflect this
Updating documentation.

@@
 						\State{$ \rvar{idx},\, i \gets \rvar{threadIdx}.x + \rvar{blockIdx}.x\times \rvar{blockDim}.x $}
+						\For{$ (c = 0;\, c < 3;\, c++) $}\Comment{Loop over elements.}
 							\For{$ (n = 0;\, n < N;\, n++) $}\Comment{Loop over nodes in element.}
-							\For{$ (c = 0;\, c < 3;\, c++) $}\Comment{Loop over elements.}
-								\State{$ \tvar{\vec{X}[n][c]} \gets \dvar{\vec{X}[i + c\times E\times N]}$}
+								\State{$ \tvar{\vec{X}[n][c]} \gets \dvar{\vec{X}[i + n\times E]}$}
 							\EndFor
-							\State{$ i \gets i + E $}
+							\State{$ i \gets i + E\times N $}
 							\Comment{Advance input index to the $(n+1)\textsuperscript{th}$ node of element $i$.}
@@
 	In general the number of indices in the array would be $ 3 \times e \times n $ where $ e \equiv $~number of surface elements, $ n \equiv $~number of nodes per element and 3 is the number of spatial dimensions.
+	%
+	\section{Thread Block Size Optimisation}
+	\href{http://docs.nvidia.com/cuda/cuda-c-best-practices-guide/index.html#memory-optimizations}{http://docs.nvidia.com/cuda/cuda-c-best-practices-guide/index.html\#memory-optimizations}
+	\href{http://docs.nvidia.com/cuda/cuda-c-best-practices-guide/index.html#execution-configuration-optimizations}{http://docs.nvidia.com/cuda/cuda-c-best-practices-guide/index.html\#execution-configuration-optimizations}
 	\savearabiccounter

### 2017-11-17 analytic_traction.m

@@ -53,11 +53,11 @@ function [nodal_force, total_force, x3x6] = analytic_traction(     ...
     % exerted by dislocations on free surfaces. The faces re det_fined by the
     % areas made up of the following nodes in the diagram:
     % min(x), yz-plane, nodes [5, 1, 8, 4], face 1
-	% max(x), yz-plane, nodes [2, 6, 3, 7], face 2
+    % max(x), yz-plane, nodes [2, 6, 3, 7], face 2
     % min(y), xz-plane, nodes [6, 5, 7, 8], face 3
-	% max(y), xz-plane, nodes [1, 2, 4, 3], face 4
-	% min(z), xy-plane, nodes [5, 6, 1, 2], face 5
-	% max(z), xy-plane, nodes [4, 3, 8, 7], face 6.
+    % max(y), xz-plane, nodes [1, 2, 4, 3], face 4
+    % min(z), xy-plane, nodes [5, 6, 1, 2], face 5
+    % max(z), xy-plane, nodes [4, 3, 8, 7], face 6.
     % The node ordering for each face ensures self-consistency in the force
     % calculation according to the labelling scheme in S. Queyreau,
     % J. Marian, B.D. Wirth, A. Arsenlis, MSMSE, 22(3):035004, (2014).

### 2017-11-20 daniel_thesis/ddd_fem.tex
Lit review disguised as documentation and chapters of the thesis.

@@
 The matrix can be constructed utilising \cref{f:fem_node_arr} in order to know which nodes correspond to which \kwd{fe} planes.
-The $ p\textsuperscript{th} $ column of the matrix\footnote{MATLAB uses column-major ordering, so this gives us the best performance for vectorised code.} corresponds to the $ p\textsuperscript{th} $ plane (according to an arbitrary plane numbering) and is defined as the following column vector,
+The $ p\textsuperscript{th} $ column of the matrix\footnote{MATLAB uses column-major ordering, so this gives us the best performance for vectorised code.} corresponds to the $ p\textsuperscript{th} $ plane (according to an arbitrary plane numbering) and is defined as,
 		\begin{align}\label{e:surf_node_util_vec}
@@
 		\end{align}	
-		where $ L_{np} \equiv $ the numeric label for node $ n $ as given by \cref{f:fem_node_arr}, $ A_{p} \equiv $ the area of the plane, and $ C_{p} \equiv$ the numeric label of the orthogonal coordinate to the plane $ C_{p} = 1, ~2, ~3 $ for the $ x, ~y, ~z $ coordinates respectively.
+		where $ L_{np} $ is the numeric label for node $ n $ as given by \cref{f:fem_node_arr}, $ A_{p} $ is the area of the plane, and $ C_{p} $ is the numeric label of the orthogonal coordinate to the plane $ C_{p} = 1, ~2, ~3 $ for the $ x, ~y, ~z $ coordinates respectively.
 $ A_{p} $ lets us segment our output and transitional arrays so that the only data being modified is that which corresponds to the correct plane and $ C_{p} $ lets us know which coordinate we must use in our selection criteria.
-Using our particular node labelling scheme (with dimensions $ \Delta x,~ \Delta y,~ \Delta z $ respectively in the $ x,~ y,~ z $ directions), the matrix is defined as
-		\begin{align}\label{eq:surf_node_util}
+Using our particular node labelling scheme (with dimensions $ \Delta x,~ \Delta y,~ \Delta z $ respectively in the $ x,~ y,~ z $ directions), the matrix is defined as,
+		\begin{align}\label{e:surf_node_util}
 			\mtx{V} = 
@@
 		\end{align}
-		The information codified in \cref{eq:surf_node_util} lets us index and process only the necessary columns to extract the surface nodes we're interested in.
+		The information codified in \cref{e:surf_node_util} lets us index and process only the necessary columns to extract the surface nodes we're interested in.
 The advantage of this setup over a naïve implementation is that it can be relatively easily expanded, maintained, and is general enough that it lends itself to a variety of selection criteria.
@@
 
-		It is important to make sure the nodes are extracted in a self consistent manner because the problem definition in \cref{c:lin_rect,c:quad_triang} assumes a specific node ordering.
+		It is important to make sure the nodes are extracted in a self consistent manner because the problem definitions in \cref{c:lin_rect,c:quad_triang} assume a specific node ordering.
 In particular, the labelling chirality must remain the same.
@@
 			\caption[Self-consistent, chirality preserving surface planes.]{Self-consistent, chirality preserving surface planes.
-Plane and node numbering according to the columns of \cref{eq:surf_node_util} and \cref{f:fem_node_arr}.}
+Plane and node numbering according to the columns of \cref{e:surf_node_util} and \cref{f:fem_node_arr}.}
 			\label{f:surf_node_plane}

### 2017-11-20 daniel_thesis/force_lin_rect_se.tex
Lit review disguised as documentation and chapters of the thesis.

@@
 		%
+		Coupling \kwd{ddd} to \kwd{fem} requires the traction field $ \tns{\sigma^{\infty}}(\vec{x}) \cdot \vec{n}(\vec{x}) $ to be distributed among the set of relevant discrete nodes of a \kwd{fe} or \kwd{be} model.
+This is usually achieved as follows,
+		\begin{align}\label{e:ddd_fem_force}
+			\vec{F}^{(n)} = \int_{S^{e}} \left[\tns{\sigma^{\infty}}(\vec{x}) \cdot \vec{n}(\vec{x})\right] L_{n}(\vec{x})\; \rvar{d}S_{e}\,,
+		\end{align}
+		where $ \rvar{d}S_{e} $ is the infinitesimal surface element with surface area $ S_{e} $.
+$ L_{n}(\vec{x}) $ are so-called shape functions (interpolation functions) that distribute  the traction field among the surface element's nodes.
+
+		The problematic singularity associated with the classical Volterra dislocation is avoided by using the non-singular formulation of \citet{a_non-singular_continuum_theory_of_dislocations}.
+The stress field of a dislocation in a homogenous infinite linear elastic domain can be calculated as a contour integral along the loop \cite{mura_t},
+		\begin{align}\label{e:field_stress}
+			\sigma_{ij}^{\infty}(\vec{x}) = C_{ijkl} \oint \epsilon_{lnh} C_{pqmn} \dfrac{\partial G_{kp}(\vec{x} - \vec{x'})}{\partial x_{q}} b_{m} \rvar{d}x'_{h}\,,
+		\end{align}
+		where $ C_{ijkl} $ is the elastic stiffness matrix, $ \epsilon_{lnh} $ the permutation operator, \kwds{bv} the \kwd{bv}, $ \vec{x'} $ the coordinate that spans the dislocation, and $ G_{kp}(\vec{x} - \vec{x'}) $ is Green's function of elasticity \cite{mura_t}.
+$ G_{kp}(\vec{x} - \vec{x'}) $ is defined as the displacement component in the $ x_{k} $ direction at point $ \vec{x} $ due to a force applied in the $ x_{p} $ direction at point $ \vec{x'} $.
+The traditional singularity comes from taking the \kwd{bv} distribution as a delta function.
+\citet{a_non-singular_continuum_theory_of_dislocations} proposed an alternative definition of $ G_{kp}(\vec{x} - \vec{x'}) $ which has a wider isotropic spread mainly localised in a radius $ a $ around the dislocation core,
+		\begin{align}\label{e:elastic_green_func}
+			G_{ij}(\vec{x} - \vec{x'}) = \dfrac{1}{8\pi \mu}\left[ \delta_{ij} \partial_{pp} - \dfrac{1}{2(1-\nu)} \partial_{ij} \right] R_{a}\,,
+		\end{align}
+		where $ \mu $, $ \nu $ are the isotropic shear modulus and Poisson's ratio respectively, $ \delta_{ij} $ is the Kronecker Delta, $ \partial_{x_{1} \ldots\, x_{n}} \equiv \dfrac{\partial^{n}}{\partial x_{1} \ldots\, \partial x_{n}}$.
+$ R_{a} $ is the defined as,
+		\begin{subequations}
+			\begin{align}\label{e:ra}
+				R_{a}(\vec{x}) &= R(\vec{x}) * w(\vec{x}) = \int R(\vec{x} - \vec{x'}) w(\vec{x'}) \rvar{d}^{3}\vec{x'}\nn
+							   &= \sqrt{R^{2} + a^{2}}\\
+				w(\vec{x}) 	   &= \dfrac{15 a^{4}}{8\pi (R^{2} + a^{2})^{7/2}}\,,
+			\end{align}
+		\end{subequations}
+		 where $ w(\vec{x}) $ is a \kwd{bv} distribution in \cite{a_non-singular_continuum_theory_of_dislocations}.
+To keep in line with the definition of \cref{e:field_stress}, where the displacement component is in the $ x_{k} $ direction, $ R_{a} = \sqrt{R_{k}^{2} + a^{2}} $.
+
+		 For two dislocation nodes (1, 2) connected by straight line segments \cref{e:field_stress} becomes,
+		 \begin{align}
+			 \tns{\sigma}^{(12)}(\vec{x}) =
+			 \begin{split} 
+				&-\dfrac{\mu}{8\pi} \int\limits_{\vec{x}_{1}}^{\vec{x}_{2}} \left( \dfrac{2}{R_{a}^{3}} + \dfrac{3 a^{2}}{R_{a}^{5}} \right) \left[ \left( \vec{R} \times \vec{b} \right) \otimes \rvar{d}\vec{x'} + \rvar{d}\vec{x'} \otimes \left( \vec{R} \times \vec{b} \right) \right]\\
+				%
+				&+ \dfrac{\mu}{4\pi (1 - \nu)} \int\limits_{\vec{x}_{1}}^{\vec{x}_{2}} \left( \dfrac{1}{R_{a}^{3}} + \dfrac{3 a^{2}}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right)\cdot \rvar{d}\vec{x'} \right] \mtx{I}_{2}\\
+				%
+				&- \dfrac{\mu}{4\pi (1 - \nu)} \int\limits_{\vec{x}_{1}}^{\vec{x}_{2}} \dfrac{1}{R_{a}^{3}} \left[ \left(\vec{b} \times \rvar{d}\vec{x'}\right) \otimes \vec{R} + \vec{R} \otimes \left(\vec{b} \times \rvar{d}\vec{x'}\right) \right]\\
+				&+ \dfrac{\mu}{4\pi (1 - \nu)} \int\limits_{\vec{x}_{1}}^{\vec{x}_{2}} \dfrac{3}{R_{a}^{5}} \left[ \left( \vec{R} \times \vec{b} \right) \cdot \rvar{d}\vec{x'} \right]\vec{R} \otimes \vec{R}
+			 \end{split}
+		 \end{align}
 		\begin{figure}

### 2017-11-20 daniel_thesis/para_force_se.tex
Lit review disguised as documentation and chapters of the thesis.

@@
 	\end{subequations}
-	where $ e\equiv $~\kwd{se} label, $ n \equiv $~node label, $ E \equiv $~number of \kwdp{se} in the scope. $ N \equiv $~number of nodes in a \kwd{se}.
+	where $ e $ is the \kwd{se} label, $ n $ the node label, $ E $ the number of \kwdp{se} in the scope. $ N $ the number of nodes in a \kwd{se}.
 
@@
 	\end{subequations}
-	where $ e\equiv $~surface \textbf{e}lement, $ n \equiv $~\textbf{n}ode, $ E \equiv $~total number of \kwdp{se} in scope, $ N \equiv $~total number of nodes in each \kwd{se}.
+	where $ e $ is the surface \textbf{e}lement, $ n $ the \textbf{n}ode, $ E $ the total number of \kwdp{se} in scope, $ N $ the total number of nodes in each \kwd{se}.
 
@@
 	\end{align}
-	In general the number of indices in the array would be $ 3 \times e \times n $ where $ e \equiv $~number of surface elements, $ n \equiv $~number of nodes per element and 3 is the number of spatial dimensions.
+	In general the number of indices in the array would be $ 3 \times e \times n $ where $ e $ is the number of surface elements, $ n $ the number of nodes per element and 3 the number of spatial dimensions.
 	%

### 2017-11-30 analytic_traction.m
Figured out the mapping issue from the analytical force calculation to matlab nodal forces. Will proceed to implement mapping and split functions up.

@@ -1,7 +1,7 @@
 function [x3x6_lbl, x3x6] = analytic_traction(...%Stop,Sbot,Sleft,Sright,Sfront,Sback,gammaMixed,     ...
-                fem_nodes, fem_node_cnct, dln_nodes, dln_node_cnct,...
-                fem_dim  , fem_planes   , n_nodes  , mu, nu, a    ,...
-                use_gpu  , para_scheme, surf_node_util)
+                fem_nodes, fem_node_cnct, dln_nodes  , dln_node_cnct,...
+                fem_dim  , fem_planes   , n_nodes    , gamma       ,...
+                mu, nu, a, use_gpu      , para_scheme, surf_node_util)
 %             nodal_force, total_force, 
     %%===================================================================%%
     %---------------------------------------------------------------------%
@@ -168,6 +168,13 @@ function [x3x6_lbl, x3x6] = analytic_traction(...%Stop,Sbot,Sleft,Sright,Sfront,
 
     [x3x6_lbl, x3x6] = extract_node_planes(fem_nodes, fem_node_cnct, surf_node_util, fem_planes, n_se, n_nodes);
     clear surf_node_util;
+    
+    for i = 1: size(gamma, 1)
+        idx = 3*find(x3x6_lbl == gamma(i));
+            [x3x6(idx-2); x3x6(idx-1); x3x6(idx)]
+            [sum(x3x6(idx-2)); sum(x3x6(idx-1)); sum(x3x6(idx))]
+%         end %for
+    end %for
 
 %     %% Force calculation.
 %     % Allocating nodal and total force arrays

### 2017-11-30 checkFTilda.m

@@ -25,17 +25,15 @@ for mx=min_mx:stp_mx:max_mx
         w,h,d,my,mz,mel] = finiteElement3D(dx,dy,dz,mx,MU,NU,loading);
     %% Testing the backward map
         snodes = [Sleft];
-        mx
-        my
-        mz
+        gamma = [gammat(:,1); gammaMixed(:,1)];
         [x3x6_lbl, x3x6] = analytic_traction(...%Stop,Sbot,Sleft,Sright,Sfront,Sback,gammaMixed,     ...
                 xnodes, nc, rn, links,...
-                [mx; my; mz]  , [1;2;3;4;5;6]   , 4  , MU, NU, a    ,...
+                [mx; my; mz]  , [1;2;3;4;5;6]   , 4  , gamma, MU, NU, a    ,...
                 1  , 1);
-            size(x3x6_lbl)
-            size(x3x6)
-            clear x3x6;
-            clear x3x6_lbl;
+%             size(x3x6_lbl)
+%             size(x3x6)
+%             clear x3x6;
+%             clear x3x6_lbl;
       %%
 %     % FRONT FACE
 %     fmidpoint_element = zeros(mx*mz,3);

### 2018-11-28 daniel_thesis/para_force_se.tex

@@
 	Efficient parallelisation requires \kwd{cma}, which means we have to be extremely careful when mapping CPU memory to device memory.
-The fact that threads work ``simultaneously'' means that in order to obtain good performance, the data which is to be ``simultaneously'' loaded into each thread must be contiguous.
+The fact that threads work ``simultaneously''\footnote{Not quite but essentially simultaneously.} means that in order to obtain good performance, data which is to be ``simultaneously'' loaded into each thread must be contiguous.
 This maximises cache memory use and therefore reduces slow memory fetch operations to global or shared memory.

### 2018-11-28 daniel_thesis/ddd_fem.tex

@@
 		Coupling \kwd{ddd} to \kwdp{fem} \cite{analytical_integration_of_the_forces_induced_by_dislocations_on_a_surface_element} is important to properly simulate micromechanical tests because \kwd{ddd} provides us with a more precise set of inputs and greater granularity for solving the \kwd{fe} problem.
+This can be achieved by using a so-called superposition scheme \cref{f:fem_ddd} that enables the independent solution of both problems, whilst feeding information from one to the other in a continuous feedback loop.
 		\begin{figure}
@@
 				\includegraphics[width=\linewidth]{fem_surf_nodes.pdf}
-				\caption[Surface nodes of our \kwd{fe} model.]{Arrangement of the surface nodes of our \kwd{fe} model.}
+				\caption[Surface nodes of our \kwd{fe} model.]{Arrangement of the surface nodes of our \kwd{fe} model.
+\kwd{fe} nodes are arranged in chunks of $ \Delta x \Delta z $ nodes in our implementation, but we only want the surface nodes.}
 				\label{f:fem_surf_nodes}
@@
 				\includegraphics[width=\linewidth]{fe_numbering.pdf}
-				\caption[Single finite element node numbering.]{Single \kwd{fe} node numbering.}
+				\caption[Single finite element node numbering.]{Single \kwd{fe} node numbering.
+It is necessary to know which \kwd{fe} plane corresponds to which node labels.
+This lets us design the auxiliary matrix that selects nodes according to the planes we want to extract.}
 				\label{f:fe_numbering}
 			\end{subfigure}
-		\caption[Coupling Discrete Dislocation Dynamics to Finite Element Methods.]{Coupling Discrete Dislocation Dynamics to Finite Element Methods.}
+		\caption[Finite Element node arrangement for coupling to Discrete Dislocation Dynamics.]{\kwd{fe} node arrangement for coupling to \kwd{ddd}.}
 		\label{f:fem_node_arr}
@@
 		\end{figure}
+		\section{Mapping Forces}
+		\begin{algorithm}
+			\caption{If $ \vec{\hat{F}} $'s columns are arranged the same way as $ \vec{\gamma_{t}} $.}
+			\begin{algorithmic}[1]
+				\State\Comment{Loop through the array containing the node labels of the relevant surface nodes.}
+				\For{$ i = 0;\, i < \rvar{length}(\vec{\gamma_{t}});\, i++$}
+					\State\Comment{Save the global node label for the current iteration.}
+					\State $ n \gets \vec{\gamma_{t}}[i] $
+					\State\Comment{Use the node label to find a vector with the linear location of all surface nodes whose labels correspond to the node whose forces we want to pass on to the \kwd{fem} coupler.}
+					\State $ \vec{L} \gets \rvar{find}(\mtx{N_{L}} == n) $
+					\State\Comment{Loop over coordinates.}
+					\For{$ k = 0;\, k < 3;\, k++ $}
+						\State\Comment{Use global node label vector to index the force array from the analytical force calculation due to dislocations on surface nodes.
+Multiplied by 3 because there are three coordinates per node.
+We sum the forces from the analytical calculation because the same global node can be part of multiple surface elements.
+We add $ k $ because the $ x,~y,~z $ coordinates are consecutively stored in $ \mtx{F_{n}} $.}
+						\State $ \mtx{\tilde{F}}[3\times \vec{L} + k] \gets \mtx{\tilde{F}}[3\times \vec{L} + k] + \sum\mtx{F_{n}}[3\times \vec{L} + k]  $
+					\EndFor
+				\EndFor
+			\end{algorithmic}
+		\end{algorithm}
+
+%	\begin{algorithm}
+%		\begin{algorithmic}[1]
+%			content...
+%		\end{algorithmic}
+%	\end{algorithm}
+
+	$ \vec{\hat{F}} $ only cares about the global node numbers, of which there are $ M $.
+The columns of $ \mtx{N_{L}},~ \mtx{F_{N}} $ represent the 4 nodes of a \kwd{se}, the rows represent the \kwd{se} they are part of.
+The column vector $ \vec{x} $ represents the $ x,~y~z $-coordinates of the node-element or global node corresponding to their subscript.
+The column vector $ \vec{\gamma_{t}} $ is the list of global nodes for which the forces induced by dislocations must be calculated.
+	\begin{align}
+		\mtx{N_{L}} &=	\begin{bmatrix}
+							4 & 5 & 1 & 2\\
+							5 & 6 & 2 & 3\\
+							7 & 8 & 4 & 5\\
+							8 & 9 & 5 & 6\\
+						\end{bmatrix}\\
+		\mtx{F_{n}} &=	\begin{bmatrix}
+							\vec{x_{11}} & \vec{x_{12}} & \vec{x_{13}} & \vec{x_{14}}\\
+							\vec{x_{21}} & \vec{x_{22}} & \vec{x_{23}} & \vec{x_{24}}\\
+							\vec{x_{31}} & \vec{x_{32}} & \vec{x_{33}} & \vec{x_{34}}\\
+							\vec{x_{41}} & \vec{x_{42}} & \vec{x_{43}} & \vec{x_{44}}\\
+						\end{bmatrix}\\
+		\vec{\hat{F}}^{\mathsf{T}} &= 	\begin{bmatrix}
+											\vec{x_{1}}^{\mathsf{T}} & \vec{x_{2}}^{\mathsf{T}} & \ldots & \vec{x_{M}}^{\mathsf{T}}
+										\end{bmatrix}\\
+		\vec{x_{en}}^{\mathsf{T}} &=	\begin{bmatrix}
+											x_{en} & y_{en} & z_{en}
+										\end{bmatrix}
+	\end{align}

### 2020-09-18 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/paper/main.tex
Added overleaf papers to wip

\documentclass[11pt]{iopart}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage[noabbrev]{cleveref}
% Let us use amsmath.
\expandafter\let\csname equation*\endcsname\relax
\expandafter\let\csname endequation*\endcsname\relax
% Let us use amsmath.
\usepackage{amsmath,isomath,amssymb,bm}
\usepackage[section]{placeins}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{comment}
\usepackage[sort&compress,numbers]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode} % Package for algorithm typesetting (pseudo-code).
\usepackage{lmodern}
\graphicspath{{./images/}}
\input{macros.tex}

\begin{document}
    %% Title, authors and addresses
    \title{Accurate evaluation of dislocation tractions}
    \author[]{Daniel Celis-Garza, Edmund Tarleton}

    \ead{edmund.tarleton@materials.ox.ac.uk}

    \address{Department of Materials, University of Oxford, Parks Road, OX1 3PH, UK}
    \begin{abstract}
        %% Text of abstract
        Dislocations generate tractions on the surface of a finite volume. Traditionally the dislocation tractions are integrated numerically over a finite element face to obtain the nodal forces; as required when using superposition to couple discrete dislocation plasticity and the finite element method. Here we implement analytic finite element nodal forces obtained using closed form expressions for the traction integrals. We compare the behaviour of the errors which arise when using numerical integration, provide insight into how and why they occur and give recommendations on avoiding numerical issues when implementing the analytic solution. Evaluating the tractions analytically in a large scale discrete dislocation plasticity simulations of a microcantilever showed a clear difference in the simulated load-displacement curve while the dislocation structure was unchanged.
    \end{abstract}

  %%
  %% Start line numbering here if you want
  %%
    %\linenumbers

%% main text
\section{Introduction}\label{s:intro}
Coupling discrete dislocation dynamics (DDD) to the finite element method (FEM) allows micromechanical tests to be simulated \cite{Groh2009}. Virtual experiments are essential for interpreting experimental data and relating the measured mechanical response to dislocation mechanisms \cite{0965-0393-6-6-007,doi:10.1080/14786430500341250,tarleton2015discrete,YU2018}. One of the most popular methods for coupling DDD and FEM is the superposition method \cite{superposition_scheme0,superposition_scheme1,superposition_scheme2}.
%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fem_ddd.pdf}
\caption[Superposition Model for DDD-FEM coupling.]{The superposition used to couple DDD and FEM. The volume $V$ is bounded by a surface $S = S_{T} \cup S_{U}$ and contains a dislocation ensemble and is subjected to tractions $\vec{T}$ on $S_{T}$ and $\vec{u}$ on $S_{u}$. First, the traction, $\vec{\tilde{T}}$, and displacement, $\vec{\tilde{U}}$, fields due to the dislocations in the infinite domain (DDD) are evaluated on the boundaries $S_{T}$ and $S_{U}$ respectively. Then an elastic boundary value problem can be solved with FEM to calculate the corrective elastic fields required to satisfy the boundary conditions $\vec{\hat{T}} = \vec{T} - \vec{\tilde{T}}$ and $\vec{\hat{u}} = \vec{U} - \vec{\tilde{U}}$.}
\label{f:superposition_scheme}
\end{figure}
%        
The superposition scheme works by decomposing the problem into separate DDD and FE problems as in \cref{f:superposition_scheme}. A linear-elastic solid $V$ bounded by a surface $S$ is subjected to traction boundary conditions, $\vec{T}$, on $S_{T}$ and displacement boundary conditions, $\vec{U}$, on $S_{U}$. The ($\tilde{~}$) fields are those generates by the dislocations in an infinite solid and are obtained by evaluating analytic solutions in a DDD simulation \cite{Cai2006}. Formally the dislocation field satisfies
%
\begin{align}
&\left.
\begin{array}{l}
\nabla\cdot{\bm{\tilde{\sigma}}} = 0\\
\bm{\tilde{\sigma}} = \bm{C}:\tilde{\bm{\varepsilon}}\\
\tilde{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla\tilde{\bm{u}}+(\nabla\tilde{\bm{u}})^T\right)
\end{array}
\right\}\textrm{in V}\\
%
&\tilde{\bm{\sigma}}\cdot\bm{n} = \tilde{\bm{T}} \textrm{ on } S_T\\
%
&\left. 
\begin{array}{l}
\tilde{\bm{u}} = \tilde{\bm{U}} \quad t>0\\ 
\tilde{\bm{u}} = \bm{0} \quad t=0 
\label{eq:utildebc}
\end{array}
\right\} \textrm{ on } S_U. 
\end{align}
%
As the dislocation fields do not vanish on $S$ the dislocations load the volume by generating tractions, $\tilde{\bm{T}}$, on $S_T$ and displacements, $\tilde{\bm{U}}$, on $S_U$ this additional loading deforms $V$ generating an additional ``image'' stress which the dislocations then feel. Therefore corrective ($\hat{~}$) fields must be superimposed to satisfy the desired boundary conditions. The corrective field which accounts for both the applied and image stress is obtained numerically by solving the elastic boundary value problem
%
\begin{align}
&\left.
\begin{array}{l}
\nabla\cdot{\bm{\hat{\sigma}}} = 0\\
\bm{\hat{\sigma}} = \bm{C}:\hat{\bm{\varepsilon}}\\
\hat{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla\hat{\bm{u}}+(\nabla\hat{\bm{u}})^{T}\right)
\end{array}
\right\}\textrm{in V}\\
%
&\hat{\bm{\sigma}}\cdot\bm{n} = \bm{T} - \tilde{\bm{T}} \textrm{ on } S_T\label{eq:thatbc}\\
%
&\hat{\bm{u}} = \bm{U} - \tilde{\bm{U}} \textrm{ on } S_U \label{eq:uhatbc}
\end{align}
%
once the solution to both problems are known, then their superposition solves the desired mixed boundary value problem:
%
\begin{align}
&\left.
\begin{array}{l}
\nabla\cdot\bm{\sigma}=\nabla\cdot\left(\bm{\hat{\sigma}} +\bm{\tilde{\sigma}}\right) = 0\\
\bm{\sigma} =\bm{\hat{\sigma}}+\bm{\tilde{\sigma}}= \bm{C}:\left(\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}\right)=\bm{C}:{\bm{\varepsilon}}\\
\bm{\varepsilon}=\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla(\hat{\bm{u}}+\tilde{\bm{u}})+\left(\nabla(\hat{\bm{u}}+\tilde{\bm{u}})\right)^T\right) =\frac{1}{2}\left(\nabla\bm{u}+(\nabla\bm{u})^{T}\right)
\end{array}
\right\}\textrm{in V}\\
%
&\bm{\sigma}\cdot\bm{n} = \bm{T}  \textrm{ on } S_T\\
%
&\left. 
\begin{array}{l}
\bm{u} = \bm{U} \quad t>0\\ 
\bm{u} = \bm{0} \quad t=0
\end{array}
\right\} \textrm{ on } S_U 
\label{eq:ubc}
\end{align}

The method is not without problems however. As a dislocation segment moves closer to the surface, its ($\tilde{~}$) field diverges and starts causing numerical problems \cite{boundary_problems_in_dd}. This can be partially solved by using a non-singular formulation such as that proposed by \citet{Cai2006} however the gradients in the dislocation field are difficult to accurately capture when a dislocation approaches $S$. Another problem with this method is the computational cost when simulating a heterogeneous solid as it requires calculating polarisation stresses due to the difference in the elastic constants in a secondary phase \cite{superposition_scheme0,boundary_problems_in_dd,ddd_precipitate}. A modified superposition scheme \cite{ODay2004} can overcome this by dividing the problem into separate DDD/FEM problems coupled through 1 elastic FE problem. This requires accurate evaluation of $\tilde{T}$ on the domain boundaries which can only be captured with a fine FE mesh. This in turn will increase the computational cost. In order to simulate polycrystalline or composite materials using superposition requires methods to accurately evaluate both $\tilde{\bm{U}}$ and $\tilde{\bm{T}}$. The displacements can be evaluated analytically \cite{ddd_disp} and this paper investigates the evaluation of the dislocation tractions analytically.

The relative simplicity of the superposition method has made it a popular choice for coupling DDD and FEM since all it requires is the evaluation of FE nodal forces and displacements on the boundary. Furthermore, analytic expressions for the stress field produced by a finite straight dislocation line segment, has allowed \citet{Queyreau} to use a non-singular formulation to obtain a closed-form solution for the tractions generated by a segment on the surface of a finite element. They used integration by parts giving rise to a number of recursion relations that can be used to construct the full solution from a small set of seed functions.

\section{Theory}\label{s:theory}

The force exerted by a dislocation ensemble on a node $a$ belong to element $e$ is given by, 
%
\begin{align}
	\vec{F}^{a} = \int_{S^{e}} \left[\tilde{\bm{\sigma}}(\vec{x}) \cdot \vec{n}\right] N^{a}(\vec{x})\; \mathrm{d}S\,,
	\label{e:ddd_fem_force}
\end{align}
%
where $\mathrm{d}S^{e}$ is the surface of element $e$ with surface area $S^{e}$ and $N^{a}$ is the finite element shape function for node $a$ which is bi-linear in this paper. In the parent element (shown in figure  \ref{f:2d_gaussian_quad}) the shape functions are,

\begin{align}
    \label{e:shape_function}
    N^{1} &= \dfrac{1}{4}(1-s_1)(1-s_2)\\
    N^{2} &= \dfrac{1}{4}(1+s_1)(1-s_2)\nonumber\\
    N^{3} &= \dfrac{1}{4}(1+s_1)(1+s_2)\nonumber\\
    N^{4} &= \dfrac{1}{4}(1-s_1)(1+s_2)\nonumber\,.
\end{align}

Usually Gauss quadrature is used to evaluate the surface integral in equation (\ref{e:ddd_fem_force}) numerically. The 1D Gauss quadrature is,
%
\begin{align}
\label{e:gauss_leg}
    \int\limits_{-1}^{1} f(s)\;\mathrm{d}s \approx \sum\limits_{i=1}^{n} w_{i} f(s_{i}) \quad \textrm{where}\quad
    %
    w_{i} = \dfrac{2}{\left(1-s_{i}^{2}\right) \left[P_{n}^{'}\left(s_{i}\right)\right]^{2}},
\end{align}
%
is the weighting of the Gauss point $s_{i}$ which is the $i\textsuperscript{th}$ root of $P_{n}$; the $n\textsuperscript{th}$ Legendre polynomial normalised so $P_{n}(1) = 1$. $P_{n}^{'}$ is the first order derivative of $P_{n}$.

The method is very accurate for functions that can be approximated by polynomials, but unsuitable for functions with singularities and near singularities \cite{gauss_leg, gauss_leg_sing}. We use a non-singular formulation for the forces \cite{Cai2006}, but the singularity is avoided by adding a small cut off radius to account for the dislocation core. However if the integration point falls close to or within the dislocation core, numerical integration can still generate large errors.

For rectangular surface elements we must transform from the parent element in $(s_1,\,s_2)$ in equation (\ref{e:gauss_leg}) to the real element coordinate system $(x,y,z)$ shown in \cref{f:force_lin_rect}. Evaluating equation (\ref{e:ddd_fem_force}) in the parent element and mapping to the real element gives the force on node $a$,
%
\begin{align}
    \label{e:gauss_leg_ddd_fem_force}
	\vec{F}^{a} \approx \sum\limits_{i=1}^{Q} w_{i} \sum\limits_{j=1}^{Q} w_{j} [\tns{\sigma}(r_{i}, s_{j})\cdot \vec{n}] N^{a}(r_{i}, s_{j}) \det(\mtx{J})\,.
\end{align}
%
Where the sum is over the $Q$ quadrature points and $J_{ij}=dx_{i}/ds_{j}$ is the element Jacobian defining the transformation from $(s_1,\,s_2) \mapsto (x,\,y)$; as the real element is rectangular with surface area $S^e$, $\det(\mtx{J})=S^e/4$. \Cref{f:2d_gaussian_quad} contains examples of how the Gauss points are distributed on the surface.
%
\begin{figure}[htb]
    \centering
    \includegraphics[width=\linewidth]{2d_gaussian_quad.pdf}
    \caption{Examples of 2D Gauss-Legendre quadrature of the parent element with $Q = 1,\, 2,\, 3,\, 4$. The point size represents the weight $w$ of the integration point. The parent elements are centred at the origin and $s_1,\, s_2 \in [-1,\,1]$ with node anticlockwise node numbering.}
    \label{f:2d_gaussian_quad}
\end{figure}
%        
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{images/force_calc_linear_rectangle.pdf}
    \caption{Diagram of the parametric line integrals solved by \citet{Queyreau} to find the forces on linear rectangular surface elements.}
    \label{f:force_lin_rect}
\end{figure}
%

Equation \ref{e:ddd_fem_force} is actually a triple vector integral. It involves integrating over the surface element and along the dislocation line segment, as shown in \cref{f:force_lin_rect}. Using the isotropic Burgers vector distribution proposed in \cite{Cai2006}, the dyadic form of the stress tensor produced by a straight finite dislocation segment bounded by nodes at $\mathbf{x_1}$ and $\mathbf{x_2}$ is \cite{Queyreau},
%
\begin{align}
    \label{e:stress}
    \tns{\sigma}(\vec{x}) = & 
            - \dfrac{\mu}{8\pi} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{2}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \otimes \mathrm{d}\vec{x'} + \mathrm{d}\vec{x'} \otimes \left(\vec{R} \times \vec{b}\right) \right]\\
            %
            &+ \dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{1}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \cdot \mathrm{d}\vec{x'} \right]\vec{I_2}\nonumber\\
            %
            &-\dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}}  \dfrac{1}{R_{a}^{3}} \left[ \left(\vec{b} \times \mathrm{d}\vec{x'}\right) \otimes \vec{R} + \vec{R} \otimes \left(\vec{b} \times \mathrm{d}\vec{x'}\right) \right]\nonumber\\
            %
            &+ \dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \dfrac{3}{R_{a}^{5}} \left[ \left(\vec{R} \times \vec{b}\right) \cdot \mathrm{d}\vec{x'} \right]\vec{R}\otimes\vec{R}\nonumber,
\end{align}
where
\begin{align}
    \vec{R} &= \vec{x} - \vec{x'} = y \vec{l} + r \vec{p} + s \vec{q}\\
    %
    R_a &= \sqrt{\vec{R} \cdot \vec{R} + a^2}\\
    %
    \mathrm{d}\vec{x'} &= -\mathrm{d} y \vec{l}
\end{align}
%
The vectors $\vec{p}$ and $\vec{q}$ are aligned with the edges of the rectangular finite element, $\vec{n} = \vec{p} \times \vec{q}$ is the element surface normal (pointing away from the dislocation), and $\vec{l}$ is parallel to the dislocation line segment as shown in figure \ref{f:force_lin_rect}. Then (provided $\vec{l}$ is not parallel to $\vec{p}$ or $\vec{q}$) $\vec{R}$ can be expressed in terms of $(\vec{l},~\vec{p},~\vec{q})$ with coefficients
%
\begin{align}
     y = \dfrac{\vec{R}\cdot \vec{n}}{\vec{l}\cdot \vec{n}} \label{se:problem},\quad
    %
     r = \dfrac{\vec{R}\cdot (\vec{q} \times \vec{l})}{\vec{p}\cdot (\vec{q} \times \vec{l})}, \quad
    %
     s = \dfrac{\vec{R}\cdot (\vec{p} \times \vec{l})}{\vec{q}\cdot (\vec{p} \times \vec{l})}\,.
\end{align}
%
Substituting (\ref{e:stress}) and (\ref{e:shape_function}) into (\ref{e:ddd_fem_force}) yields four long and messy equations (one for each FE node) that were elegantly solved by \citet{Queyreau} by utilising the fact that the triple integrals all had the form,
%
\begin{align}
    H_{ijkl} &= \int\limits_{r_{1}}^{r_{2}}\int\limits_{s_{1}}^{s_{2}}\int\limits_{y_{1}}^{y_{2}} \dfrac{r^i s^j y^k}{R_{a}^{m}}\label{e:triple_int}\\
    \textrm{when }m &= 5 \textrm{ then } i,\, j \in [0,\,3],~k \in [0,\,2]\nonumber\\
    \textrm{when }m &= 3 \textrm{ then } i,\, j \in [0,\,2],~k \in [0,\,1]\nonumber\\
    \textrm{when }m &= 1 \textrm{ then } i = j = k = 0\nonumber.
\end{align}
%
Using partial differentiation and integration by parts, they found a series of recurrence relations that lead to double and single integrals with a similar form to equation (\ref{e:triple_int}). Together they are used to construct a full solution. The recurrence relations stop working when $i = j = k = 0 \textrm{ and } m = 1,\, 3$. At which point, direct integration of the resulting single and double integrals (the last triple integrals all cancel out in the global calculation) yields six seed functions that are used as the starting point for the recurrence relations. Three of them are logarithms and three either arctangents or---if a discriminant is negative---hyperbolic arctangents. The details of the procedure can be found in \cite{Queyreau}.

Although exact, the use of arctangents/hyperbolic arctangents and logarithmic functions, compounded by the large number of recurrence relations is prime territory for error propagation and numerical problems (see \cref{s:method}). This is particularly egregious when using general purpose compilers instead of high-performance or scientific computing compilers where mathematical functions are implemented more precisely.

\section{Methodology}\label{s:method}
Numerical integration of tractions can produces unexpected behaviour such as force hot spots (see \cref{f:err_basic_cantilever}) and sign inversions as a dislocation approaches a surface. During a large simulation, these effects are hard to spot. \citet{Queyreau} identified that for a given number of quadrature points, the error is dependent on the dislocation character but always increases rapidly as the distance between the segment and element surface decrease (see \cref{f:rel_err_perp_edge,f:rel_err_par_edge}).
%
\begin{figure}[htb]
		\centering
		\subfloat[$60 \times 16$ elements ($x \times y$).]
		{
		    { \includegraphics[width=0.45\linewidth]{eta_mx=60_face=1.pdf} }
		}
		~
		\subfloat[$120 \times 36$ elements ($x \times y$).]
		{
		    { \includegraphics[width=0.45\linewidth]{eta_mx=120_face=1.pdf} }
		}
\caption{Relative error ($\vec{F}^{\eta}$) in the nodal force obtained using numerical integration with one quadrature point $Q = 1$, and the analytic solution. The $xz$-face of a rectangular cantilever with plane normal, $\vec{n} = \left[0\,\overline{1}\,0\right]$. The dislocation is of pure edge character with $\vec{b} = [1\,0\,\overline{1}]$, and line direction, $\vec{l} = \left[\overline{1}\,2\,\overline{1}\right]/\sqrt{6}$ which pierces both $xz$-faces. The dislocation has its centre at the centroid of the cantilever. %The absolute difference cutoff was set to $10^{-9}$ to avoid post-processing artefacts arising from truncation and roundoff errors in floating point arithmetic.
}
\label{f:err_basic_cantilever}
\end{figure}
%
Expanding the test cases reveals just how problematic numerical integration of the tractions can be when a dislocation approaches a surface. The two basic test cases, an orthogonal and parallel edge segment, are shown in \cref{f:gauss_quad_test}.

The symmetry of the simple test cases can also influence how solution is as the stress fields exhibit symmetries about the dislocation line. If the dislocation is centered at the center of the element and orthogonal to it then the numerical solution becomes more accurate. However isolated test cases are far from typical simulation scenarios. A single quadrature point is often used to evaluate tractions due to the low computational cost and works well for segments which are not close to the surface. This is therefore the benchmark against which we measure the cost-benefit of implementing and utilising the analytic solutions. It should also be noted that by using a single Gauss point, one can use the same FE mesh as for the Gauss points, simplifying the implementation. %If the nodes represent the midpoint of the surface element and all we care about are the total force on it, one can make the shape functions in equation \ref{e:gauss_leg_ddd_fem_force} equal to 1 and evaluate the equation once. The latter statement also applies for multiple gauss nodes, but they would have to be centered around the midpoint. Also, the gauss nodes need not be calculated for each surface element, they can be calcaulated once and then rotated, translated and scaled accordingly.
%		
\begin{figure}
	\centering
    \includegraphics[width=0.8\linewidth]{images/test_gauss_quad.pdf}
    \caption{Simple test cases for an edge segment and surface element perpendicular (a) and parallel (b). The perpendicular dislocation is centered at the midpoint of the surface element, node $\mathbf{x_1}$ is separated by a perpendicular distance $\mathbf{x_1}^z$ to prevent the dislocation from intersecting the surface. On the right, the parallel dislocation runs along the$x$-axis at half the height of the surface element. The nodes of each dislocation line segment are kept at a perpendicular distance of at least one core radius away from the surface element.}
    \label{f:gauss_quad_test}
\end{figure}

\citet{Queyreau} found the analytic solution is approximately 10 times more computationally expensive than its numerical counterpart for 1 quadrature point. The implementation of the analytic solution is also much more involved. One issue is the calculation of the $y$-coordinate in the local coordinate frame as shown in \cref{f:force_lin_rect} and equation (\ref{se:problem}), if $\vec{l} \perp \vec{n}$, we get a singularity. As mentioned in \cite{Queyreau}, an easy fix is to rotate the line segment about its midpoint around the $\vec{l} \times \vec{n}$ axis and use the mean values either side as the true result. An example of what this looks like in terms of forces can be seen in \cref{f:rotate} (we removed the singularity to keep the graph smooth).
%
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect.pdf}
    \caption{Example of the components of the total force on a surface element (the force summed over all four FE nodes) as a dislocation segment parallel to the surface element ($\theta = 0$) is rotated about its midpoint around the axis defined by $\vec{l}\times\vec{n}$. The force is smooth but not necessarily antisymmetric about the neighbourhood of $\theta=0$.}
    \label{f:rotate}
\end{figure}

The specific shape of the curves will vary depending on the element/segment configuration, but is smooth and well-behaved about singularity. For our purposes, we used 4 perturbations each of $1\,\deg$, in the clockwise and anti-clockwise directions (8 rotations in total) w.r.t. the parallel position.

However, the check for orthogonality is dependent on the length scales involved in the simulation, we found that machine precision plays an important part in deciding how strict the tolerance should be. If,
%
\begin{align}
    \lvert\vec{l}\cdot\vec{n}\rvert \lesssim \dfrac{\max\left(\lvert\vec{R}\cdot\vec{n}\rvert\right)}{10^8}\,,
\end{align}
%
it is advisable to treat the segment as parallel to the surface element. In our case the numerator on the RHS is simply the cantilever's largest dimension. $10^8$ is used instead of actual machine precision $\sim10^{15}$ because the seed functions and large number of recurrence relations of the solution propagate errors. Smaller tolerances lead to these errors growing so much that the simulation can be impacted; this is a problem when such dislocations move slightly during a simulation and become nearly parallel with the surface, which are detected if the tolerance is too small, yet the limited numerical precision leads to round off and truncation errors during the calculation. Ironically tolerances which are too large can cause the perturbations to rotate the dislocation segment closer to the singularity also producing erroneous results. Larger than necessary tolerances can also slow down the calculation by detecting dislocations that are far enough from the special case that they can be treated like non-parallel segments.

In general one does not want a dislocation segment to intersect the surface when it is being rotated. Naively one would calculate the maximum rotational angle, $\theta_{\textrm{max}}$, to be,
%
\begin{align}
    \theta_{\textrm{max}} &= \arctan\left(\dfrac{2 d}{\left\lvert\mathbf{x_2} - \mathbf{x_1}\right\rvert}\right)\,,
\end{align}
%
where $d$ is the minimum orthogonal distance from the dislocation to the surface element (collision distance), and $\mathbf{x_1},\,\mathbf{x_2}$ are the dislocation segment node coordinates. However, $\theta_\textrm{max}$ might be too small (due to numerical precision) in cases when the segment length is too small compared to the distance to a surface element or when the segment length is much greater than $d$. Fine tuning the angle is a task that involves knowing the minimum collision distance, minimum segment length, dislocation core radius, and the compiler's implementation of mathematical functions. Given the rarity of such cases and their comparatively low impact, we chose our perturbation such that we safely avoid this problem.

Furthermore, the chirality and self-consistency of the  FE nodes must be accounted for such that they are in the proper order regardless of the element face they belong to. Here we use 8  node linear hexahedral (brick) elements with the node numbering shown in \cref{f:fe_numbering}. The node ordering for the various surfaces are obtained by placing an observer inside the element and noting the nodes for the faces of the element, these are shown in \cref{f:surface_nodes}.
%
\begin{figure}
    \centering
    \subfloat[Node numbering for our FE voxels.\label{f:fe_numbering}]
		{
		    { \includegraphics[width=0.375\linewidth]{images/fe_numbering.pdf} }
		}
		\hfill
		\subfloat[Surface nodes selected for each face.\label{f:surface_nodes}]
		{
		    { \includegraphics[width=0.525\linewidth]{images/surf_node_plane.pdf} }
		}
    \caption{Surface element nodes must be self-consistent so the forces have the correct sign.}
\end{figure}
%
The total force on a given node must include the force contributions from every element in which said node appears, see \cref{f:shared_node}.
%
\begin{figure}[htb]
    \centering
    \includegraphics[width=\linewidth]{images/lrse_thread_map.pdf}
    \caption{FE nodes are shared by either 4 element faces or 3 if it is a corner node. The total force on a given node is the summation of the force contributions from each element it belongs to.}
    \label{f:shared_node}
\end{figure}
%
The specifics of the mapping depend on the global FE node numbering. Using \cref{f:shared_node} as our reference labels for elements and nodes, $e$ and $n$ respectively, we can give a concrete example of how this is done by defining,
\begin{subequations}
    \begin{align}
            \vec{x_{e,n}} &\equiv	\begin{bmatrix}
    									x_{e,n} & y_{e,n} & z_{e,n}
    								\end{bmatrix}^{\mathsf{T}}, \quad
    		\vec{x_{n}} \equiv	\begin{bmatrix}
    								x_{n} & y_{n} & z_{n}
    							\end{bmatrix}^{\mathsf{T}}\\
    		\begin{split}
        		\mtx{N_{L}} &=	\begin{bmatrix}
        							l_{1,1} & l_{1,2} & l_{1,4} & l_{1,5}\\
        							l_{2,2} & l_{2,3} & l_{2,5} & l_{2,6}\\
        							l_{3,5} & l_{3,6} & l_{3,8} & l_{3,9}\\
        							l_{4,4} & l_{4,5} & l_{4,7} & l_{4,8}\\
        						\end{bmatrix}
    		\end{split}
            , \quad
            \vec{\gamma} =   \begin{bmatrix}
                            l_1\\
                            l_2\\
                            \vdots\\
                            l_9
                        \end{bmatrix}\\
    		\begin{split}
    		    \mtx{F_{e}} &=	\begin{bmatrix}
        							\vec{x_{1,1}} & \vec{x_{1,2}} & \vec{x_{1,4}} & \vec{x_{1,5}}\\
        							\vec{x_{2,2}} & \vec{x_{2,3}} & \vec{x_{2,5}} & \vec{x_{2,6}}\\
        							\vec{x_{3,5}} & \vec{x_{3,6}} & \vec{x_{3,8}} & \vec{x_{3,9}}\\
        							\vec{x_{4,4}} & \vec{x_{4,5}} & \vec{x_{4,7}} & \vec{x_{4,8}}\\
    						    \end{bmatrix}
    		\end{split}
    		,\quad
    		\vec{\tilde{F}} = 	\begin{bmatrix}
    								\vec{x_{1}}\\
    								\vec{x_{2}}\\
    								\vdots\\
    								\vec{x_{9}}
    							\end{bmatrix}\,.\label{e:force_imp}
    \end{align}
\end{subequations}
Where $\vec{x_{e,n}}$ is a $3\times1$ column vector corresponding to the $x,~y,~z$ dislocation induced forces on node $n$ on the surface element $e$. There are four of these per rectangular surface element, where a given node, $n$, can appear in multiple surface elements (e.g. node 5 in \cref{f:shared_node} is shared by all 4 surface elements), all of which independently contribute to the total force on said node. $\vec{x_n}$ is a $3\times1$ column vector corresponding to the total $x,~y,~z$ dislocation induced forces on node $n$. These are used to shorten the definition of equation (\ref{e:force_imp}) and are not explicitly defined in the implementation, rather they give the force matrices $\mtx{F_{e}}$ and $\vec{\tilde{F}}$ a specific row order. $\mtx{N_{L}}$ is crucial for the correct implementation of this analytical solution in traditional FE codes. It is the $E\times4$ matrix corresponding to the global label of each node in a given surface element. Each row of the matrix represents a surface element and each column represents a node in the surface element. We cannot na\"ively add the columns together as that would give the total force acting on the element as a whole, not each FE node individually. We chose to arrange the columns in accordance to \cref{f:force_lin_rect} as it makes it easier to implement the solution, but the only thing that matters is that the basis vectors $\vec{n},\,\vec{p},\,\vec{q}$ are calculated appropriately. $\vec{\gamma}$ is the vector with the FE node labels, which makes mapping force to node possible. $\mtx{F_{e}}$ is the $3E \times 4$ matrix where the forces acting on each of the four nodes (column) in a particular surface element (each element corresponds to three consecutive rows because there are three dimensions) are stored. $\vec{\tilde{F}}$ is the $3N\times1$ column vector where the total forces on each node are stored (each node has three rows because there are three dimensions). This is easily generalisable to $E$ elements and $N$ nodes.

The following algorithm illustrates how the total force on each node is obtained. The resulting force vector is later used in eq. (\ref{eq:thatbc}) as $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
    \begin{algorithm}
		\caption{Assuming $ \vec{\tilde{F}} $ is arranged the same way as $ \vec{\gamma} $ and indexing starts at 0.}
		\begin{algorithmic}[1]
		\label{a:tot_force}
			\State\Comment{Loop through the array containing the node labels of the relevant surface nodes.}
			\For{$ i = 0;\, i < \rvar{length}(\vec{\gamma});\, i++$}					\State\Comment{Save the global node label for the current iteration.}
				\State $ n \gets \vec{\gamma}[i] $
				\State\Comment{Use the node label to find a vector, $\vec{L}$, with the linearised indices in $\mtx{N_{L}}$ where node $n$ appears as part of a surface element whose tractions we are calculating.}
				\State $ \vec{L} \gets \rvar{find}(\mtx{N_{L}} == n) $
				\State\Comment{Loop over coordinates.}
				\For{$ k = 0;\, k < 3;\, k++ $}
					\State\Comment{Use global node label vector to index the force array from the analytical force calculation. Multiplied by 3 because there are three coordinates per node. We sum the forces from the analytical calculation because the same global node can be part of multiple surface elements. We add $ k $ because the $ x,~y,~z $ coordinates are consecutively stored in $ \mtx{F_{e}} $.}
						\State $ \vec{\tilde{F}}[3n + k] \gets \vec{\tilde{F}}[3n + k] + \sum\mtx{F_{e}}[3\vec{L} + k]  $
				\EndFor
			\EndFor
		\end{algorithmic}
	\end{algorithm}
Our implementation does not strictly follow \cref{a:tot_force} because we also memoise a generalised version of $\vec{L}$ upon simulation initialisation instead of finding one at every iteration, reducing computational time but requiring us to account for nodes without traction boundary conditions. Our indexing also starts at 1, so the algorithm further adjusted for this.

\section{Results}

\begin{figure}[t]
	\centering
    \subfloat[Segment starts a single dislocation core radius away.]
		{
		    {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=5.pdf}}
		}
		~
    \subfloat[Segment starts 3 dislocation core radii away.]
		{
		    {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=15.pdf}}
		}

    \subfloat[Segment starts 201 dislocation core radii away.]
		{
		    {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=1005.pdf}}
		}
		~
    \subfloat[Segment starts 20001 dislocation core radii away.]
		{
		    {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.47\linewidth]{perp_e_xz=100005.pdf}}
		}
    \caption{Log-log plot of the relative error as a function of dislocation segment length for a perpendicular edge dislocation (\cref{f:gauss_quad_test}a). $x^{1}_{z}$ is the $z$-coordinate of node $\mathbf{x_1}$. $\vec{b} = [1 0 0]$, line direction, $\vec{l} = [0 0 1]$, and dislocation core radius, $a = 5b$, the surface element's normal and size are, $\vec{n} = [0 0 1]$, $L = 1000b$, respectively. $Q$ is the number of quadrature points per dimension.}
    \label{f:rel_err_perp_edge}
\end{figure}

Isolated test cases were useful in order to gain insight into the differences between the numerical and analytical approaches. When the stress field on the surface element is highly symmetric numerical integration works well; showing good convergence with increasing number of quadrature points. \Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5b$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 quadrature points, for all segment lengths tested. However, as stated in \cref{s:theory}, the limitations of Gauss quadrature are also evident. \Cref{f:rel_err_perp_edge,f:rel_err_par_edge} showcase the problem with numerical integration to compute integrals of rational functions close to a pole. The comparatively large relative errors with $Q = 11$, compared to fewer quadrature points, as the dislocation nears the element face makes it hard to globally minimise the error by picking a specific number of quadrature points while maintaining a feasible computational cost.

Gauss quadrature fails to capture the $1/R_a$ nature of the stress tensor, especially when a segment is close to a heavily weighted quadrature point. When the dislocation node $\mathbf{x_{1}}$ is close to the surface element (see \cref{f:gauss_quad_test}), 11 Gauss points ($Q=11$) performs worse than with $Q=2$, as shown in \cref{f:rel_err_perp_edge} (a) and (b). This is because When $Q$ is odd a Gauss point is at the element center, as shown in \Cref{f:2d_gaussian_quad}, directly in front of the dislocation segment.

The limitations of Gauss quadrature become evident when the dislocation line segment is parallel to a surface element. \Cref{f:rel_err_par_edge} shows the relative errors for a parallel edge dislocation. In this configuration the forces due to a screw dislocations vanish as the stress field is antisymmetric.
%
\begin{figure}[t]
	\centering
    \includegraphics[width=0.8\linewidth]{par_e_z.pdf}
\caption{Log-log plot of the relative error as a function of distance from the surface element for a parallel edge dislocation (\cref{f:gauss_quad_test}b). Burgers vector, $\bm{b} = [0 1 0]$, line direction, $\bm{l} = [1 0 0]$, dislocation core and surface element parameters are the same as \cref{f:rel_err_perp_edge}. The dislocation length is fixed to $10^{6}\, b,\, x\in\left[-0.5\times10^{6},\, 0.5\times10^{6} \right]$ and bisects the surface element along the $[1 0 0]$ direction. The whole dislocation was segmented into $10^4$ pieces of length $100\, b$ to prevent the dislocation from intersecting the surface element when they were rotated to avoid the singularity. The relative error at large distances ($>10^6 b$) converges to one due to artifacting when dividing two very small double precision numbers. The absolute error always goes towards zero with increasing distance from the surface.}
\label{f:rel_err_par_edge}
\end{figure}
%
In \cref{f:rel_err_par_edge}, we observe the relative errors decrease and then converge to $\sim 1$ as the distance grows larger. The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, which results in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim1$ when done with limited precision. Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$. The absolute error \textit{always} decreases as the distance from the surface element increases, but absolute errors are not as useful tools of comparison. However, when the segment is close to the surface, the relative errors are large ($\gg1$) unless using a large number of quadrature points, for example \cref{f:gauss_quad_test}(a) shows that $Q\geq100$ are required when the distance $x^1_z = 15b$.

For a parallel segment, Gauss quadrature performs far worse than for a perpendicular segment, as shown in figure \ref{f:rel_err_par_edge}. This is because numerical quadrature is only accurate for integrating functions that can be approximated by polynomials. Whereas the dislocation stress field \cite{Cai2006} decays as $1/R_{a}$. This makes numerical quadrature unsuitable as (\ref{e:gauss_leg_ddd_fem_force}) fails to accurately capture the stress, which varies rapidly across the element surface for small $R_a$. The relevant components of the stress tensor for a perpendicular edge segment which is not penetrating the surface are shown in \cref{f:sigma_perp_edge}. The $\sigma_{xz}$ and $\sigma_{zz}$ components are antisymmetric and the resultant forces vanish which is captured when numerically integrating with small $Q$, while $\sigma_{yz}$ does not but can be accurately integrated with sufficiently large $Q$.

    \begin{figure}[t]
        \centering
        \subfloat[$\sigma_{xz}$.\label{sf:xzeperp}]
			{
			    {\includegraphics[width=0.3\linewidth]{images/xz_eperp_5_000000.pdf}}
			}
        ~
        \subfloat[$\sigma_{yz}$.\label{sf:yzeperp}]
			{
			    {\includegraphics[width=0.3\linewidth]{images/yz_eperp_5_000000.pdf}}
			}
        ~
        \subfloat[$\sigma_{zz}$.\label{sf:zzeperp}]
			{
			    {\includegraphics[width=0.3\linewidth]{images/zz_eperp_5_000000.pdf}}
			}
        \caption{Relevant stress components to \cref{f:rel_err_perp_edge}. The antisymmetry of $\sigma_{xz}$ and $\sigma_{zz}$ makes them vanish when integrating. $\sigma_{yz}$ does not vanish, but its symmetry means Gauss quadrature works if sufficient quadrature points are used.}
        \label{f:sigma_perp_edge}
    \end{figure}

It is evident that symmetry plays a role in the accuracy of numerical integration. If a stress field has the appropriate symmetry, as in \cref{f:sigma_perp_edge}, Gauss quadrature will be accurate given enough quadrature points. However, when the segment is translated off-centre, this breaks the symmetry and the symmetric weighting of the Gauss quadrature scheme fails to accurately integrate the stress fields when the segment is close to the surface. The latter case is of course much more common in a simulation than the former, so in reality the errors between analytical and numerical solutions are larger than what is led on by these contrived cases. The error convergence with higher numbers of quadrature points is consistent with the findings of \cite{Queyreau}.

The isolated tractions are only part of the story however, as they are used to calculate the image forces as a result of the boundary. We therefore also compare image forces calculated from numeric ($Q = 1$) tractions and analytic traction calculations affect the image forces to see the extent to which higher accuracy tractions affect the FE part of the simulation. To do so we compare the traction + FEM calculation to analytic solutions by \citet{Head}.

In a DDP simulation it is rare to find a dislocation segment so close to a quadrature point that the errors spike so dramatically. However, numerical integration with small $Q$ produces noticeable errors over a wide range of distances and segment lengths. Simulations usually contain a large number of dislocations which are parallel or near-parallel and close to surface elements. \Cref{f:rel_err_par_edge} shows it is not possible to accurately compute the tractions and nodal forces using Gauss quadrature even with a large number of quadrature points.

It is worth noting that rotational perturbation required for the analytic solution to be non-singular when a dislocation segment is parallel to a surface element can introduce small erroneous force components if the rotation is too large. If the rotational perturbations were small enough and floating point arithmetic exact, these erroneous forces would cancel when averaged over two opposite rotations. We found that a maximum rotation angle of $\pm0.5^\circ$ makes these erroneous force components negligible.

\begin{figure}[t]
        \centering
        \includegraphics[width=0.7\linewidth]{images/load_disp.pdf}
        \caption{Load-displacement curve. When the tractions are evaluated analytically the curve is less noisy compared to numerical integration. As expected the yield point remains the same in both cases.}
        \label{f:load_disp_curve}
\end{figure}

The purpose of the cantilever simulation showed herein is not to be have an exactly physical when it comes to dislocation structure. Our initial source sizes and structure are somewhat unphysical, i.e. square sources with segment lengths on the order of the FE mesh courseness. There are also known issues with junction formation when multiple active slip systems are used in a single simulation. However, we are investigating not only the results but also the robustness and numerical stability of a fully integrated implementation of analytical solutions to dislocation tractions. By throwing the worst case scenario at both numerical and analytic traction calculations, we ensure both numerical and analytic solutions work even when the multiscale nature of the problem causes serious floating point arithmetic errors.

A full discrete dislocation plasticity simulation of a microcantilever bend test demonstrates the benefits of using the analytic solution over numerical integration. The FE nodal forces were evaluated using Gauss quadrature with a single integration point for one simulation, and analytical tractions for the other. The simulations were otherwise identical with a finite element size of $0.25\mu\textrm{m}$ and sixty initial sources equally distributed on the 12 $\{1\bar{1}0\}\langle111\rangle$ bcc slip systems randomly distributed inside the region occuping the central $70\%$ of the cantilever ensuring the simulation proceeded at an acceptable rate and avoiding dislocations from exiting the fixed end, which can lead to problems due to the necessary FEM boundary conditions. The beam was fixed at $x=0$ and displaced by $U_{z}=-0.15~\mu\textrm{m}$ at $x=L=15~\mu\textrm{m}$. The material parameters were those of bcc tungsten, $\mu = 145\,\textrm{GPa}$ and $\nu = 0.28$. The analytic solution significantly reduced the noise in the load displacement curve as shown in \cref{f:load_disp_curve}.

The inset in \cref{f:load_disp_curve} shows the yield point remains the same, but the reaction forces diverge from each other as the simulation progresses. It should be noted that the dislocation structure was unchanged and so the change in the mechanical response is due entirely to the accuracy of the force calculation. The fluctuations are due to dislocations approaching a free surface and generating a large traction which is suddenly removed when the segment exits. These events are difficult to capture accurately when using numerical integration.

The dislocation structure did not change much in either case. In fact, when looking at it from the zoom level of \cref{f:dln_struc}, they both appear identical. There are however, many small differences in node position. Surprisingly, depending on the specific simulation, we have found between $10--20\%$ less dislocation segments when the analytic solution is used. Meaning the numerical solution systematically underestimates the average contribution of every single dislocation segment, with occasional massive spikes in force when a dislocation nears a gauss point. We expect these differences to get larger as simulation runtime increases. This is a fundamental and practically unavoidable problem of the numerical solution.

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.7\linewidth]{images/analytic_struct.pdf}
        \caption{Final dislocation structure using analytic tractions.}
        \label{f:dln_struc}
    \end{figure}

There are a few things that determine whether the numerical solutions are good enough for a given problem. When primarily investigating larger scale features of a dislocation structure---such as larger scale investigation of dislocation forresting around inclusions---Gauss quadrature is quite suitable. However, if one is interested in investigating the finer details of a dislocation structure---such as the nuanced interactions with closly packed inclusions---the analytic method is best. Furthermore, when investigating load-displacement curves, the analytical solutions provide a much better description for a relatively small increase in computational cost \cite{Queyreau}. That being said, the cost is nowhere near rate limiting, segment-segment forces and topological changes quickly become much more expensive as they both have worse asymptotic scaling, and topological changes also quickly become memory bound. An accurate description of load-displacement curves should also implement the exact displacement boundary conditions obtained by \citet{ddd_disp}.

\section{Acknowledgements}

We would like to thank Prof. Sylvain Queyreau and Lawrence Livermore National Laboratory for their invaluable input. This work was supported by the Consejo Nacional de Ciencia y Tecnologia, Fondo Sectorial CONACYT-Secretaria de Energia-Sustentabilidad Energetica Cuarto Periodo [291129]. This work was supported by the Engineering and Physical Sciences Research Council Centre for Doctoral Training in the Science and Technology of Fusion Energy EP/L01663X/1 and Fellowship grant EP/N007239/1.
  %% References
  %%
  %% Following citation commands can be used in the body text:
  %% Usage of \cite is as follows:
  %%   \cite{key}          ==>>  [#]
  %%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
  %%   \citet{key}         ==>>  Author [#]

  %% References with bibTeX database:
  \newcommand{\newblock}{}
  \bibliographystyle{unsrtnat}
  \bibliography{references.bib}

  %% Authors are advised to submit their bibtex database files. They are
  %% requested to list a bibtex style file in the manuscript if they do
  %% not want to use model1-num-names.bst.

  %% References without bibTeX database:

  % \begin{thebibliography}{00}

  %% \bibitem must have the following form:
  %%   \bibitem{key}...
  %%

  % \bibitem{}

  % \end{thebibliography}
\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2020-09-21 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/paper/main.tex
Image forces edge perp. Add head's paper.

@@
 \usepackage{booktabs}
-\usepackage[noabbrev]{cleveref}
 % Let us use amsmath.
@@
 \usepackage{amsmath,isomath,amssymb,bm}
+\usepackage[noabbrev]{cleveref}
 \usepackage[section]{placeins}
@@
 \address{Department of Materials, University of Oxford, Parks Road, OX1 3PH, UK}
+
 \begin{abstract}
@@
 \begin{align}
-&\left.
+     & \left.
     \begin{array}{l}
-\nabla\cdot{\bm{\tilde{\sigma}}} = 0\\
-\bm{\tilde{\sigma}} = \bm{C}:\tilde{\bm{\varepsilon}}\\
+        \nabla\cdot{\bm{\tilde{\sigma}}} = 0                  \\
+        \bm{\tilde{\sigma}} = \bm{C}:\tilde{\bm{\varepsilon}} \\
         \tilde{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla\tilde{\bm{u}}+(\nabla\tilde{\bm{u}})^T\right)
     \end{array}
-\right\}\textrm{in V}\\
+    \right\}\textrm{in V}                                                \\
     %
-&\tilde{\bm{\sigma}}\cdot\bm{n} = \tilde{\bm{T}} \textrm{ on } S_T\\
+     & \tilde{\bm{\sigma}}\cdot\bm{n} = \tilde{\bm{T}} \textrm{ on } S_T \\
     %
-&\left. 
+     & \left.
     \begin{array}{l}
-\tilde{\bm{u}} = \tilde{\bm{U}} \quad t>0\\ 
+        \tilde{\bm{u}} = \tilde{\bm{U}} \quad t>0 \\
         \tilde{\bm{u}} = \bm{0} \quad t=0
@@
 \begin{align}
-&\left.
+     & \left.
     \begin{array}{l}
-\nabla\cdot{\bm{\hat{\sigma}}} = 0\\
-\bm{\hat{\sigma}} = \bm{C}:\hat{\bm{\varepsilon}}\\
+        \nabla\cdot{\bm{\hat{\sigma}}} = 0                \\
+        \bm{\hat{\sigma}} = \bm{C}:\hat{\bm{\varepsilon}} \\
         \hat{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla\hat{\bm{u}}+(\nabla\hat{\bm{u}})^{T}\right)
     \end{array}
-\right\}\textrm{in V}\\
+    \right\}\textrm{in V}                                                                        \\
     %
-&\hat{\bm{\sigma}}\cdot\bm{n} = \bm{T} - \tilde{\bm{T}} \textrm{ on } S_T\label{eq:thatbc}\\
+     & \hat{\bm{\sigma}}\cdot\bm{n} = \bm{T} - \tilde{\bm{T}} \textrm{ on } S_T\label{eq:thatbc} \\
     %
-&\hat{\bm{u}} = \bm{U} - \tilde{\bm{U}} \textrm{ on } S_U \label{eq:uhatbc}
+     & \hat{\bm{u}} = \bm{U} - \tilde{\bm{U}} \textrm{ on } S_U \label{eq:uhatbc}
 \end{align}
@@
 \begin{align}
-&\left.
+     & \left.
     \begin{array}{l}
-\nabla\cdot\bm{\sigma}=\nabla\cdot\left(\bm{\hat{\sigma}} +\bm{\tilde{\sigma}}\right) = 0\\
-\bm{\sigma} =\bm{\hat{\sigma}}+\bm{\tilde{\sigma}}= \bm{C}:\left(\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}\right)=\bm{C}:{\bm{\varepsilon}}\\
+        \nabla\cdot\bm{\sigma}=\nabla\cdot\left(\bm{\hat{\sigma}} +\bm{\tilde{\sigma}}\right) = 0                                                         \\
+        \bm{\sigma} =\bm{\hat{\sigma}}+\bm{\tilde{\sigma}}= \bm{C}:\left(\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}\right)=\bm{C}:{\bm{\varepsilon}} \\
         \bm{\varepsilon}=\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla(\hat{\bm{u}}+\tilde{\bm{u}})+\left(\nabla(\hat{\bm{u}}+\tilde{\bm{u}})\right)^T\right) =\frac{1}{2}\left(\nabla\bm{u}+(\nabla\bm{u})^{T}\right)
     \end{array}
-\right\}\textrm{in V}\\
+    \right\}\textrm{in V}                                 \\
     %
-&\bm{\sigma}\cdot\bm{n} = \bm{T}  \textrm{ on } S_T\\
+     & \bm{\sigma}\cdot\bm{n} = \bm{T}  \textrm{ on } S_T \\
     %
-&\left. 
+     & \left.
     \begin{array}{l}
-\bm{u} = \bm{U} \quad t>0\\ 
+        \bm{u} = \bm{U} \quad t>0 \\
         \bm{u} = \bm{0} \quad t=0
@@
     \label{e:shape_function}
-    N^{1} &= \dfrac{1}{4}(1-s_1)(1-s_2)\\
-    N^{2} &= \dfrac{1}{4}(1+s_1)(1-s_2)\nonumber\\
-    N^{3} &= \dfrac{1}{4}(1+s_1)(1+s_2)\nonumber\\
-    N^{4} &= \dfrac{1}{4}(1-s_1)(1+s_2)\nonumber\,.
+    N^{1} & = \dfrac{1}{4}(1-s_1)(1-s_2)             \\
+    N^{2} & = \dfrac{1}{4}(1+s_1)(1-s_2)\nonumber    \\
+    N^{3} & = \dfrac{1}{4}(1+s_1)(1+s_2)\nonumber    \\
+    N^{4} & = \dfrac{1}{4}(1-s_1)(1+s_2)\nonumber\,.
 \end{align}
@@
     \tns{\sigma}(\vec{x}) = &
-            - \dfrac{\mu}{8\pi} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{2}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \otimes \mathrm{d}\vec{x'} + \mathrm{d}\vec{x'} \otimes \left(\vec{R} \times \vec{b}\right) \right]\\
+    - \dfrac{\mu}{8\pi} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{2}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \otimes \mathrm{d}\vec{x'} + \mathrm{d}\vec{x'} \otimes \left(\vec{R} \times \vec{b}\right) \right]  \\
     %
-            &+ \dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{1}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \cdot \mathrm{d}\vec{x'} \right]\vec{I_2}\nonumber\\
+                            & + \dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{1}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \cdot \mathrm{d}\vec{x'} \right]\vec{I_2}\nonumber                  \\
     %
-            &-\dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}}  \dfrac{1}{R_{a}^{3}} \left[ \left(\vec{b} \times \mathrm{d}\vec{x'}\right) \otimes \vec{R} + \vec{R} \otimes \left(\vec{b} \times \mathrm{d}\vec{x'}\right) \right]\nonumber\\
+                            & -\dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}}  \dfrac{1}{R_{a}^{3}} \left[ \left(\vec{b} \times \mathrm{d}\vec{x'}\right) \otimes \vec{R} + \vec{R} \otimes \left(\vec{b} \times \mathrm{d}\vec{x'}\right) \right]\nonumber \\
     %
-            &+ \dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \dfrac{3}{R_{a}^{5}} \left[ \left(\vec{R} \times \vec{b}\right) \cdot \mathrm{d}\vec{x'} \right]\vec{R}\otimes\vec{R}\nonumber,
+                            & + \dfrac{\mu}{4\pi(1-\nu)} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \dfrac{3}{R_{a}^{5}} \left[ \left(\vec{R} \times \vec{b}\right) \cdot \mathrm{d}\vec{x'} \right]\vec{R}\otimes\vec{R}\nonumber,
 \end{align}
@@
 \begin{align}
-    \vec{R} &= \vec{x} - \vec{x'} = y \vec{l} + r \vec{p} + s \vec{q}\\
+    \vec{R}            & = \vec{x} - \vec{x'} = y \vec{l} + r \vec{p} + s \vec{q} \\
     %
-    R_a &= \sqrt{\vec{R} \cdot \vec{R} + a^2}\\
+    R_a                & = \sqrt{\vec{R} \cdot \vec{R} + a^2}                     \\
     %
-    \mathrm{d}\vec{x'} &= -\mathrm{d} y \vec{l}
+    \mathrm{d}\vec{x'} & = -\mathrm{d} y \vec{l}
 \end{align}
@@
 \begin{align}
-    H_{ijkl} &= \int\limits_{r_{1}}^{r_{2}}\int\limits_{s_{1}}^{s_{2}}\int\limits_{y_{1}}^{y_{2}} \dfrac{r^i s^j y^k}{R_{a}^{m}}\label{e:triple_int}\\
-    \textrm{when }m &= 5 \textrm{ then } i,\, j \in [0,\,3],~k \in [0,\,2]\nonumber\\
-    \textrm{when }m &= 3 \textrm{ then } i,\, j \in [0,\,2],~k \in [0,\,1]\nonumber\\
-    \textrm{when }m &= 1 \textrm{ then } i = j = k = 0\nonumber.
+    H_{ijkl}        & = \int\limits_{r_{1}}^{r_{2}}\int\limits_{s_{1}}^{s_{2}}\int\limits_{y_{1}}^{y_{2}} \dfrac{r^i s^j y^k}{R_{a}^{m}}\label{e:triple_int} \\
+    \textrm{when }m & = 5 \textrm{ then } i,\, j \in [0,\,3],~k \in [0,\,2]\nonumber                                                                         \\
+    \textrm{when }m & = 3 \textrm{ then } i,\, j \in [0,\,2],~k \in [0,\,1]\nonumber                                                                         \\
+    \textrm{when }m & = 1 \textrm{ then } i = j = k = 0\nonumber.
 \end{align}
@@
 This is particularly egregious when using general purpose compilers instead of high-performance or scientific computing compilers where mathematical functions are implemented more precisely.
+
+In simulations, the tractions are manifested in the reaction forces calculated by the FE solver at FE nodes.
+In order to validate and compare the differences in tractions have on dislocation plasticity simulations we compare the analytic expressions for infinite dislocations in inhomogenous media by \citet{head1953edge}.
+The original paper has a few typos that have been replicated in other sources so we write the correct expressions for an edge dislocation parallel to a surface described by the line $x = 0$, where the dislocation coordinates are $(a,~c)$ and we are looking at the $xy$-plane where $\vec{b}$ is perpendicular to the surface in \cref{e:imageStressAnalyticEdge1} and parallel to the surface in \cref{e:imageStressAnalyticEdge2}.
+\begin{subequations}
+    \begin{align}\label{e:imageStressAnalyticEdge1}
+        \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}\right.
+\\\nonumber
+                                & \left.
++\dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a x \dfrac{3 (x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                                   \\
+        \sigma_{yy} = D (y - c) & \left\{\dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}                                                 \right.
+\\\nonumber
+                                & \left.
+-\dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a (2 a - x) \dfrac{(x + a)^2 + (3 x + 2 a) (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                   \\
+        \sigma_{xy} = D         & \left\{(x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} \right.
+\\\nonumber
+                                & \left.
+-(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 2 a \dfrac{6 x (x + a) (y - c)^2 - (x - a) (x + a)^3 - (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\},
+    \end{align}
+\end{subequations}
+
+\begin{subequations}
+    \begin{align}\label{e:imageStressAnalyticEdge2}
+        \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}\right.
+\\\nonumber
+                                & \left.
++\dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a x \dfrac{3 (x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                                   \\
+        \sigma_{yy} = D (y - c) & \left\{\dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}                                                 \right.
+\\\nonumber
+                                & \left.
+-\dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a (2 a - x) \dfrac{(x + a)^2 + (3 x + 2 a) (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                   \\
+        \sigma_{xy} = D         & \left\{(x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} \right.
+\\\nonumber
+                                & \left.
+-(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 2 a \dfrac{6 x (x + a) (y - c)^2 - (x - a) (x + a)^3 - (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\},
+    \end{align}
+\end{subequations}
 
@@
 \begin{align}
-    \theta_{\textrm{max}} &= \arctan\left(\dfrac{2 d}{\left\lvert\mathbf{x_2} - \mathbf{x_1}\right\rvert}\right)\,,
+    \theta_{\textrm{max}} & = \arctan\left(\dfrac{2 d}{\left\lvert\mathbf{x_2} - \mathbf{x_1}\right\rvert}\right)\,,
 \end{align}
@@
     \begin{align}
-            \vec{x_{e,n}} &\equiv	\begin{bmatrix}
+        \vec{x_{e,n}} & \equiv	\begin{bmatrix}
             x_{e,n} & y_{e,n} & z_{e,n}
@@
             x_{n} & y_{n} & z_{n}
-    							\end{bmatrix}^{\mathsf{T}}\\
+        \end{bmatrix}^{\mathsf{T}}            \\
         \begin{split}
             \mtx{N_{L}} &=	\begin{bmatrix}
-        							l_{1,1} & l_{1,2} & l_{1,4} & l_{1,5}\\
-        							l_{2,2} & l_{2,3} & l_{2,5} & l_{2,6}\\
-        							l_{3,5} & l_{3,6} & l_{3,8} & l_{3,9}\\
-        							l_{4,4} & l_{4,5} & l_{4,7} & l_{4,8}\\
+                l_{1,1} & l_{1,2} & l_{1,4} & l_{1,5} \\
+                l_{2,2} & l_{2,3} & l_{2,5} & l_{2,6} \\
+                l_{3,5} & l_{3,6} & l_{3,8} & l_{3,9} \\
+                l_{4,4} & l_{4,5} & l_{4,7} & l_{4,8} \\
             \end{bmatrix}
@@
         \vec{\gamma} =   \begin{bmatrix}
-                            l_1\\
-                            l_2\\
-                            \vdots\\
+            l_1    \\
+            l_2    \\
+            \vdots \\
             l_9
-                        \end{bmatrix}\\
+        \end{bmatrix}                          \\
         \begin{split}
             \mtx{F_{e}} &=	\begin{bmatrix}
-        							\vec{x_{1,1}} & \vec{x_{1,2}} & \vec{x_{1,4}} & \vec{x_{1,5}}\\
-        							\vec{x_{2,2}} & \vec{x_{2,3}} & \vec{x_{2,5}} & \vec{x_{2,6}}\\
-        							\vec{x_{3,5}} & \vec{x_{3,6}} & \vec{x_{3,8}} & \vec{x_{3,9}}\\
-        							\vec{x_{4,4}} & \vec{x_{4,5}} & \vec{x_{4,7}} & \vec{x_{4,8}}\\
+                \vec{x_{1,1}} & \vec{x_{1,2}} & \vec{x_{1,4}} & \vec{x_{1,5}} \\
+                \vec{x_{2,2}} & \vec{x_{2,3}} & \vec{x_{2,5}} & \vec{x_{2,6}} \\
+                \vec{x_{3,5}} & \vec{x_{3,6}} & \vec{x_{3,8}} & \vec{x_{3,9}} \\
+                \vec{x_{4,4}} & \vec{x_{4,5}} & \vec{x_{4,7}} & \vec{x_{4,8}} \\
             \end{bmatrix}
@@
         \vec{\tilde{F}} = 	\begin{bmatrix}
-    								\vec{x_{1}}\\
-    								\vec{x_{2}}\\
-    								\vdots\\
+            \vec{x_{1}} \\
+            \vec{x_{2}} \\
+            \vdots      \\
             \vec{x_{9}}
@@
 In \cref{f:rel_err_par_edge}, we observe the relative errors decrease and then converge to $\sim 1$ as the distance grows larger.
-The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, which results in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim1$ when done with limited precision.
+The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, which results in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim 1$ when done with limited precision.
 Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$.

### 2020-09-21 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/HeadVsFEM_ReactionForce.m
Fixed numeric traction as it was using the old function signature.

@@ -412,7 +412,7 @@ ylabel('b')
 hold on
 plot(x1, z1, '.', 'color', 'black', 'MarkerSize', 10)
 hold off
-%%
+
 
 figCounter = figCounter + 1;
 figure(figCounter)
@@ -645,7 +645,8 @@ function [txx, tyy, txy] = imageStressAnalyticEdgePar(mu, b, nu, x, y, a, c)
 
     txx = ...%xma .* (xma2 - ymc2) ./ den1 + ...
     -xpa .* (xpa2 - ymc2) ./ den2 + ...
-        2 .* a .* (3 .* xpa2 .* xpa2 - 6 .* x .* xpa .* ymc2 - ymc2 .* ymc2) ./ den3;
+        2 .* a .* ((3*x + a) .* xpa2 .* xpa - 6 .* x .* xpa .* ymc2 - ymc2 .* ymc2) ./ den3;
+    %%%
     txx = D .* txx;
 
     tyy = ...%xma .* (xma2 + 3.*ymc2) ./ den1 + ...

### 2020-09-21 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/STATIC_FEMcoupler.m

@@ -56,12 +56,13 @@ function [uhat, fend, Ubar, ftilda] = FEMcoupler(rn, links, maxconnections, a, M
     uhat(fixedDofs) = u(fixedDofs); % - utilda(fixedDofs);
 
     fhat = zeros(3 * (mno), 1);
+    ftilda = zeros(3 * (mno), 1);
 
     % gamma=[gammat;gammaMixed];
     gamma = gammat;
 
     %ftilda = zeros(3*mno,1);
-    ftilda = traction(gamma, segments, xnodes, mno, a, MU, NU);
+    ftilda = traction(gamma, segments, xnodes, a, MU, NU, ftilda);
 
     %%
     %ftilda=zeros(3*mno,1); %ET uncomment later!

### 2020-09-23 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/paper/main.tex
Head's correct equations.
Reformat equations.
Clarity
Added a bunch of things to do.

@@
 This is particularly egregious when using general purpose compilers instead of high-performance or scientific computing compilers where mathematical functions are implemented more precisely.
+These issues must be taken into account when using analytic tractions in the form of numeric tolerances.
 
@@
 In order to validate and compare the differences in tractions have on dislocation plasticity simulations we compare the analytic expressions for infinite dislocations in inhomogenous media by \citet{head1953edge}.
-The original paper has a few typos that have been replicated in other sources so we write the correct expressions for an edge dislocation parallel to a surface described by the line $x = 0$, where the dislocation coordinates are $(a,~c)$ and we are looking at the $xy$-plane where $\vec{b}$ is perpendicular to the surface in \cref{e:imageStressAnalyticEdge1} and parallel to the surface in \cref{e:imageStressAnalyticEdge2}.
+The original paper has a few typos that have been replicated in other sources so we write the correct expressions for an edge dislocation parallel to a surface described by the line $x = 0$, where the dislocation coordinates are $(a,~c)$ and we are looking at the $xy$-plane where $\vec{b}$ is perpendicular to the surface in \cref{e:imageStressAnalyticEdge1},
 \begin{subequations}
     \begin{align}\label{e:imageStressAnalyticEdge1}
-        \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}\right.
+        \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} + \dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2}\right.
 \\\nonumber
                                 & \left.
-+\dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a x \dfrac{3 (x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                                   \\
-        \sigma_{yy} = D (y - c) & \left\{\dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}                                                 \right.
++ 4 a x \dfrac{3 (x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\}\,,                                                                                               \\
+        \sigma_{yy} = D (y - c) & \left\{\dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} - \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2}                                                 \right.
 \\\nonumber
                                 & \left.
--\dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a (2 a - x) \dfrac{(x + a)^2 + (3 x + 2 a) (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                   \\
-        \sigma_{xy} = D         & \left\{(x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} \right.
++ 4 a (2 a - x) \dfrac{(x + a)^2 + (3 x + 2 a) (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\}\,,                                                                             \\
+        \sigma_{xy} = D         & \left\{(x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} - (x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2}\right.
 \\\nonumber
-                                & \left.
--(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 2 a \dfrac{6 x (x + a) (y - c)^2 - (x - a) (x + a)^3 - (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\},
+                                & \left. + 2 a \dfrac{6 x (x + a) (y - c)^2 - (x - a) (x + a)^3 - (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\}\,.
+    \end{align}
+\end{subequations}
+The case where the Burgers vector lies parallel to the surface is found in \cref{e:imageStressAnalyticEdge2}.
+\begin{subequations}
+    \begin{align}\label{e:imageStressAnalyticEdge2}
+        \sigma_{xx} = D         & \left\{ (x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} -(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} \right.     \\\nonumber
+                                & \left. + 2 a \dfrac{(3 x + a) (x + a)^3 - 6 x (x + a) (y - c)^2 - (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\}\,,                                     \\
+        \sigma_{yy} = D         & \left\{ (x - a) \dfrac{(x - a)^2 + 3 (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} - (x + a) \dfrac{(x + a)^2 + 3 (y - c)^2}{[(x + a)^2 + (y - c)^2]^2}\right. \\\nonumber
+                                & \left. - 2 a \dfrac{(x - a) (x + a)^3 - 6 x (x + a) (y - c)^2 + (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\}\,,                                       \\
+        \sigma_{xy} = D (y - c) & \left\{\dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} - \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} \right.                     \\\nonumber
+                                & \left. + 4 a x \dfrac{3 (x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\}\,.
     \end{align}
@@
 
-\begin{subequations}
-    \begin{align}\label{e:imageStressAnalyticEdge2}
-        \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}\right.
-\\\nonumber
-                                & \left.
-+\dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a x \dfrac{3 (x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                                   \\
-        \sigma_{yy} = D (y - c) & \left\{\dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2}                                                 \right.
-\\\nonumber
-                                & \left.
--\dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 4 a (2 a - x) \dfrac{(x + a)^2 + (3 x + 2 a) (y - c)^2}{[(x + a)^2 + (y - c)^2]^3}\right\},                   \\
-        \sigma_{xy} = D         & \left\{(x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} \right.
-\\\nonumber
-                                & \left.
--(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} + 2 a \dfrac{6 x (x + a) (y - c)^2 - (x - a) (x + a)^3 - (y - c)^4}{[(x + a)^2 + (y - c)^2]^3}\right\},
-    \end{align}
-\end{subequations}
+% TODO #27
 
@@
 It should also be noted that by using a single Gauss point, one can use the same FE mesh as for the Gauss points, simplifying the implementation.
-%If the nodes represent the midpoint of the surface element and all we care about are the total force on it, one can make the shape functions in equation \ref{e:gauss_leg_ddd_fem_force} equal to 1 and evaluate the equation once.
-The latter statement also applies for multiple gauss nodes, but they would have to be centered around the midpoint.
-Also, the gauss nodes need not be calculated for each surface element, they can be calcaulated once and then rotated, translated and scaled accordingly.
 %		
@@
 
-For a parallel segment, Gauss quadrature performs far worse than for a perpendicular segment, as shown in figure \ref{f:rel_err_par_edge}.
+For a segment parallel to a surface, Gauss quadrature performs far worse than for a perpendicular segment, as shown in figure \ref{f:rel_err_par_edge}.
 This is because numerical quadrature is only accurate for integrating functions that can be approximated by polynomials.
@@
 We therefore also compare image forces calculated from numeric ($Q = 1$) tractions and analytic traction calculations affect the image forces to see the extent to which higher accuracy tractions affect the FE part of the simulation.
-To do so we compare the traction + FEM calculation to analytic solutions by \citet{Head}.
+To do so we compare the traction + FEM calculation to analytic solutions by \citet{head1953edge}.
+
+% TODO #28
 
@@
 
+% TODO #23
 \begin{figure}[t]
@@
 
+% TODO #22 
 A full discrete dislocation plasticity simulation of a microcantilever bend test demonstrates the benefits of using the analytic solution over numerical integration.
@@
 
+% TODO #24
 \begin{figure}[t]

### 2020-09-23 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/HeadVsFEM_ReactionForce.m

@@ -26,6 +26,7 @@ dz = 1000;
 figCounter = 0;
 cntr = 0;
 
+% TODO #25
 for j = 15
     mx = j;
 
@@ -286,7 +287,7 @@ end
 % end
 
 %%
-
+% TODO #26
 figCounter = figCounter + 1;
 figure(figCounter)
 contourf(X, Z, sxxA);

### 2020-09-25 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m
Add screw dislocations and make graphs. Fixes #26 and #27

@@ -29,52 +29,52 @@ cntr = 0;
 
 for j = 20
     mx = j;
-
+    
     gridSize = mx;
     x = linspace(0, dx, gridSize);
     y = linspace(0.5 * dy, 0.5 * dy, gridSize);
     z = linspace(0, dz, gridSize);
     [X, Z] = meshgrid(x, z);
     Y = meshgrid(y);
-
+    
     clear x y z;
-
+    
     loading = 1;
     vertices = [0, 0, 0; ...
-                dx, 0, 0; ...
-                0, dy, 0; ...
-                dx, dy, 0; ...
-                0, 0, dz; ...
-                dx, 0, dz; ...
-                0, dy, dz; ...
-                dx, dy, dz];
-
+        dx, 0, 0; ...
+        0, dy, 0; ...
+        dx, dy, 0; ...
+        0, 0, dz; ...
+        dx, 0, dz; ...
+        0, dy, dz; ...
+        dx, dy, dz];
+    
     plim = 12 / amag; %12microns
     [xnodes, mno, nc, n, D, kg, K, L, U, Sleft, Sright, Stop, Sbot, ...
-            Sfront, Sback, Smixed, gammat, gammau, gammaMixed, fixedDofs, freeDofs, ...
-            w, h, d, my, mz, mel] = STATIC_finiteElement3D(dx, dy, dz, mx, MU, NU, loading);
-
+        Sfront, Sback, Smixed, gammat, gammau, gammaMixed, fixedDofs, freeDofs, ...
+        w, h, d, my, mz, mel] = STATIC_finiteElement3D(dx, dy, dz, mx, MU, NU, loading);
+    
     gamma_dln = [gammat(:, 1)];
-
+    
     % Set surface node labels for surface node extraction.
     n_nodes = 4;
     surf_node_util = zeros(n_nodes + 2, 6);
     xy = mx * my;
     xz = mx * mz;
     yz = my * mz;
-
+    
     f_hat = zeros(3 * mno, 1);
     [x3x6_lbl, x3x6, n_se] = extract_surface_nodes(xnodes, nc, [mx; my; mz], ...
[…]

### 2020-09-25 src/wip/DanielCelisGarza/Hardware accelerated_dislocation_plasticity_analytic_tractions/paper/main.tex

\documentclass[12pt]{iopart}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage[noabbrev]{cleveref}
% Let us use amsmath.
\expandafter\let\csname equation*\endcsname\relax
\expandafter\let\csname endequation*\endcsname\relax
% Let us use amsmath.
\usepackage{amsmath,isomath,amssymb,bm,mathtools}
\usepackage[section]{placeins}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{comment}
\usepackage[sort&compress,numbers]{natbib}
\usepackage{paralist}
\usepackage{siunitx}
\usepackage{minted}
\usepackage{lmodern}
\graphicspath{{./images/}}
\input{macros.tex}

\begin{document}
    %% Title, authors and addresses
    \title{Hardware accelerated dislocation plasticity: analytic tractions}
    \author[]{Daniel Celis-Garza, Edmund Tarleton}

    \ead{edmund.tarleton@materials.ox.ac.uk}

    \address{Department of Materials, University of Oxford, Parks Road, OX1 3PH, UK}
    \begin{abstract}
        %% Text of abstract
    \end{abstract}

  %%
  %% Start line numbering here if you want
  %%
    %\linenumbers

%% main text
    \section{Introduction}\label{s:intro}
    % The implementation of solutions to computable problems tend to either be memory or computationally bound. Memory bound solutions are those whose runtime is limited by the amount of memory required to store data. Conversely, computationally bound ones are limited by arithmetic computations. The objective of program optimisation is to find the best compromise between the two. However, the solution to some problems simply cannot be implemented in a manner that is primarily limited by one or the other but both at the same time and in non-trivial ways.
	%
% 	\begin{figure}[t]
% 		\centering
% 		\includegraphics[width=\linewidth]{gpu_parallel.png}
% 		\caption[CUDA runtime schematic.]{CUDA runtime schematic. Repetitive but computationally intensive tasks can be offloaded to the GPU. Both GPU and CPU are completely independent from each other and can work on different parts of the code at the same time, care must be taken to ensure proper syncronisation. Image taken from \cite{nvidia}.}
% 		\label{f:cuda}
% 	\end{figure}

	Central Processing Units (CPUs) are designed not only to perform mathematical operations but logical ones that control program flow. They are tailored to perform the wide variety of operations required by an operating system. These include program scheduling (load balancing), instantiation (program loading, unloading, loops, recusion instances) \& branching (if/case statements, go to's), memory operations (fetching, storing, allocation), input/output (IO), and program monitoring (program counters, recursion counters). Modern CPUs have a degree of parallelism that allows them to increase their total throughput while operating close to optimum conditions \cite{cpu_arch}.

	Given the limited scope of the first computers, the general purpose of CPUs was enough to cover their needs. With the advent of personal computers, the demands on CPUs drastically increased. For industrial users these revolved around data acquisition, filtering and preprocessing \cite{fpga, preproc, filtering}. On the other hand, the domestic market demanded ever increasing levels of abstraction and usability in the form of Graphical User Interfaces (GUIs) such as windows, cursors and their accompanying sound effects. Manufacturers identified this and moved to provide specialised modules that freed CPU resources and improved user experience by accelerating different processes through hardware means \cite{gpu1, gpu2, gpu3, sound}. These modules include Sound Cards (SCs), Field Programmable Gate Arrays (FPGAs), Graphics Processing Units (GPUs), Application Specific Integrated Circuits (ASICs), Cryptographic Accelerators, Regular Rxpression (RegEx) Accelerators, among others. They are collectively dubbed ``hardware accelerators''.

	Graphics Processing Units were originally intended to offload the very data-intensive but computationally simple operations needed for 3D gaming and rendering \cite{gpu1,gpu2,gpu3}. Graphics processing was seen as a prime candidate for hardware acceleration because the operations on each pixel are largely the same across the screen. Due to their original purpose as gaming and rendering accelerators, they were never designed to operate on higher than single precision data. In fact, single precision (32-bit precision) is still good enough to encode 32-bit colour depth (8-bit channel per RGB colour + 8-bit alpha channel), which only the most high-end monitors support \cite{monitor}. It is also worth noting that because the same operations apply to different pieces of (mostly) independent data, they can all be performed at the same time, often trivially reducing the order of polynomial complexity algorithms.

	As previously mentioned, GPU parallelism frees up enormous amounts of CPU processing power that can be put to good use running other programs or performing complementary serial processes, while the GPU works concurrently on its dataset. Parallelism has been used by the scientific community for years, but the focus has mainly been on CPU parallelism \cite{cpu_par}. Consequently, its scope was lagerly limited to the use of computational clusters. The two main reasons for this were the fact that GPUs lacked support for higher precision arithmetic, and the very limited to non-existent support for scientific computing in GPU programming languages such as OpenGL \cite{gpu_comp}. It wasn't until the development of the OpenCL and OpenACC standards that GPUs caught the attanetion of the scientific community as a viable way of exploiting parallelisation without access to a computing cluster. However, OpenCL is very bare bones and requires specialist knowledge not only of the problem at hand, but also of the GPU and CPU architectures \cite{opencl}. OpenACC is similar to OpenMP (originally an extension of OpenMP) in that it is pragma based, greatly limiting its scope due to pragmas' inherent rigidity and their implementation require significan work by compiler manufacturers, limiting its adoption \cite{openacc}.

	Recently however, a third option has become increasingly viable. NVidia's Computer Unified Device Architecture (CUDA) framework provides the best aspects of both OpenCL and OpenACC. The tradeoff is that it only works on NVidia GPUs and is a closed source product. However, the accessibility and flexibility of CUDA provides anyone familiar with C/C++ the means to develop a GPU application with little issue. NVidia is also strongly backing scientific research by adding double precision support on their GPUs and specialised matrix operation cores. They have also worked to provide parallel equivalents of well known serial libraries---such as cuBLAS \& cuFFT---for scientific computing. They have additionally developed a wide range of specialist graphics cards tailor-made for scientific purposes. As such, they are the leaders in GPU computing in scientific communities \cite{nvidia}.

	NVidia's hardware and software has already been extensively used in scientific computing. Examples include image processing, machine learning, cosmology, civil engineering, etc. 
	%
	\subsection{Hurdles for Parallelisation}
	%
	\begin{figure}[t]
		\centering
		\includegraphics[width=\linewidth]{mem_access.pdf}
		\caption[Memory access pattern example.]{Arrows represent fetch requests by single threads in a GPU. Data should be arranged in such a way that all threads in a warp (collections of 32 threads) access contiguous memory locations to reduce time-consuming memory fetch operations. This is often unintuitive but extremely important, especially on scientific computing cards which are optimised for long computational times and low memory fetch frequency.}
		\label{f:mem_access}
	\end{figure}

	The difficulty in parallelisation varies tremendously from problem to problem. Problems where data is uncorrelated and independent---such as sampling well-behaved probability distributions---are almost trivially parallelisable. Problems where data is correlated or strongly dependent on its neighbours---such as Dislocation Dynamics---require a more careful approach \cite{parallel_algs}.

	The largest hurdle when implementing parallel algorithms is often the efficient use of data. In order to obtain good parallel performance, a lot of thought has to be placed on data access patterns, data read/write conflicts, and memory allocation and transfer \cite{nvidia}. For best performance, all this must be analysed on a case by case basis. If done incorrectly, the performance of a parallel application may be lower than the serial version. One must consider a wide range of parameters to successfully parallelise a problem. Among these are GPU architecture, problem size, computational and memory complexity, code branching, required arithmetic precision, and error tolerances \cite{nvidia, gpu_rev}.

	Efficient parallelisation of many problems requires ``coalesced memory access'' as shown in \cref{f:mem_access}, which means we have to be extremely careful when mapping CPU memory to global GPU (device) memory. The fact that threads work ``simultaneously''\footnote{Not quite but essentially simultaneously. See \cite{nvidia} for details.} means that in order to obtain good performance, data which is to be ``simultaneously'' loaded into each thread must be contiguous. This maximises cache memory use and therefore reduces slow memory fetch operations to global or shared memory.

	Special cases, such as having a parallel dislocation line segment to a surface as discussed in \cref{s:anal_forces}, must be treated carefully due to the way code branching works in GPUs. There are various ways of doing so:
	\begin{inparaenum}[\itshape 1\upshape)]
		\item if the special case is inexpensive, it can be treated within the same GPU function;
		\item if the special case is expensive and always known (certain boundary conditions in FEM), it can be placed in its own GPU function that treats it separately;
		\item if the special case is expesive and found at runtime it may be asynchronously treated by the CPU or buffered into its own GPU function to be executed at a later time.			
	\end{inparaenum}

	\begin{figure}[t]
		\centering
		\includegraphics[width=\textwidth]{async.pdf}
		\caption[GPU and CPU asynchronous execution.]{GPU and CPU code run independent of each other. Leads to state ambiguities if both sides need to talk to each other \cite{nvidia}.}
		\label{f:async_gpu_cpu}
	\end{figure}
	One of the advantages of GPU-CPU independence is that both can work concurrently on the problem. If both systems have to talk to each other, then one must tread carefully, ensuring proper syncronisation and data mapping before moving (see \cref{f:async_gpu_cpu}).

	The reason why code branching is bad for GPU parallelisation is down to the fact that they work like software customisable vector machines. Where collections of threads all carry out the same operation on different pieces of data at the same time. This means that regardless of whether a condition is true or false, the code will execute. It is only data storage that depends on the condition. When working with CUDA, one must avoid code branching as much as possible, particularly rare but computationally expensive branches.

	Dislocation Dynamics (DD)---in particular 3D Discrete Dislocation Dynamics (3D DDD)---can greatly benefit from parallelisation, especially when coupling to Finite Element Methods (FEM). It is worth noting that there are potential issues arising from the very computationally expensive functions and special cases that often arise from analytical solutions in 3D DDD. There are also potential issues with data redundancy---which are non-limiting in the short term---that may eventually require a more data-efficient approach as the computational capabilities and data capabilities of GPUs converge. \Cref{s:para_ddd} expands on these issues in the context of DD.

	\section{Parallelisation on Graphics Processing Units}
	Efficient parallelisation requires coalesced memory access, which means we have to be extremely careful when mapping CPU memory to device memory. The fact that threads work ``simultaneously''\footnote{Not quite but essentially simultaneously.} means that in order to obtain good performance, data which is to be ``simultaneously'' loaded into each thread must be contiguous. This maximises cache memory use and therefore reduces slow memory fetch operations.
	%
	\subsection{Data Mapping}
		%
		\subsubsection{Elements: Host $ \mapsto $ Device}
			%
			\begin{algorithm}
				\caption{Elements in host $ \mapsto $ device.}
				\label{a:ehd}
				\begin{algorithmic}[1]
					\Function{element\_host\_device\_map}{\hvar{\vec{X}[N][3\times E]}}
						\State{$ i,\, j,\, k \gets 0 $}
						\State{$ \dvar{\vec{X}} \gets $ malloc($ 3\times E\times N $)}
						\For{$(n = 0;\, n < N;\, n++)$}
							\State{$ k \gets j $}
							\For{$ (c = 0;\, c < 3;\, c++) $}
								\State{$ i \gets c $}
								\For{$ (e = 0;\, e < E;\, e++) $}
									\State{$ \dvar{\vec{X}[k + e]} \gets \hvar{\vec{X}[n][i]} $}
									\State{$ i \gets i + 3 $}
								\EndFor
								\State{$ k \gets k + E \times N $}
							\EndFor
							\State{$ j \gets j + E $}
						\EndFor
						\State{\Return{\dvar{\vec{X}}}}
					\EndFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Elements: Device $ \mapsto $ Thread}
			\begin{algorithm}
				\caption{Elements in device $ \mapsto $ thread.}
				\label{a:edt}
				\begin{algorithmic}[1]
						\GPUFunction[element\_device\_thread\_map]{\dvar{\vec{X}[3\times E\times N]}, \tvar{\vec{X}[N][3]}}
						\State{$ \rvar{idx},\, i \gets \rvar{threadIdx}.x + \rvar{blockIdx}.x\times \rvar{blockDim}.x $}
						\For{$ (c = 0;\, c < 3;\, c++) $}
							\For{$ (n = 0;\, n < N;\, n++) $}
								\State{$ \tvar{\vec{X}[n][c]} \gets \dvar{\vec{X}[i + n\times E]}$}
							\EndFor
							\State{$ i \gets i + E\times N $}
						\EndFor
						\State{\Return{\tvar{\vec{X}[n][c]}}}
					\EndGPUFunction
				\end{algorithmic}    	
			\end{algorithm}
		\subsubsection{Force: Thread $ \xmapsto{+} $ Device}
			\begin{algorithm}
				\caption{Force in thread $ \xmapsto{+} $ device.}
				\begin{algorithmic}[1]
						\GPUFunction[add\_force\_thread\_device]{\tvar{\vec{F_{n}}[N][3]}, \tvar{\vec{F_{e}}[3]}, \dvar{\vec{F_{n}}[3\times E\times N]},\newline{}\dvar{\vec{F_{e}}[3\times E]}, \rvar{idx}}
						\State{\Comment{Nodal force.}}
						\State{\Comment{Set output index to whatever parallelisation index is given to the function. In this case the same index we use for the main parallelisation.}}
						\State{$ i \gets \rvar{idx} $}
						\For{$ (n = 0;\, n < N;\, n++) $} \Comment{Loop over nodes.}
							\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
								\State{\Comment{Ensure nodal forces are correctly added and mapped from local thread memory to global device memory.}}
								\State{atomicAdd(\dvar{\vec{F_{n}}[i + c\times E\times N]}, \tvar{\vec{F_{n}}[n][c]})}
							\EndFor
							\State{\Comment{Displace output index to point at the first coordinate of the $ (n+1)\textsuperscript{th} $ node of the \rvar{idx}\textsuperscript{th} SE.}}
							\State{$ i \gets i + E $}
						\EndFor
						\State{\Comment{Total force.}}	
						\State{$ i \gets \rvar{idx} $} \Comment{Reset output index.}
						\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
							\State{atomicAdd(\dvar{\vec{F_{e}}[i]}, \tvar{\vec{F_{e}}[c]})}
							\State{\Comment{Advance the output index to point at the $ (i+1)\textsuperscript{th} $ coordinate of the $ \rvar{idx}\textsuperscript{th} $ SE.}}
							\State{$ i \gets i + E $}
						\EndFor
						\State{\Return{\dvar{\vec{F_{n}}}, \dvar{\vec{F_{e}}}}}
					\EndGPUFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Force (Parallelise over Dislocations): Thread $ \xmapsto{+} $ Device}
			\begin{algorithm}
				\caption{Force (parallelise over dislocations) in thread $ \xmapsto{+} $ device.}
				\begin{algorithmic}[1]
					\GPUFunction[dln\_add\_force\_thread\_device]{\tvar{\vec{F_{n}}[N][3]}, \tvar{\vec{F_{e}}[3]},\newline{}\dvar{\vec{F_{n}}[3\times E\times N]}, \dvar{\vec{F_{e}}[3\times E]}, $ k $}
						\State{\Comment{Nodal force.}}
						\State{\Comment{Set output index to correspond to whatever SE we're on. By parallelising over dislocation lines, we must loop through SEs in the main code, this is the value of $ k $ we provide. Multiply by 3 and $ N $ because each SE has 3 coordinates and $ N $ nodes.}}
						\State{$ i \gets 3\times N\times k $}
						\State{$ j \gets 0 $} \Comment{Auxiliary index.}
						\For{$ (n = 0;\, n < N;\, n++) $} \Comment{Loop over nodes.}
							\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
								\State{\Comment{Ensure nodal forces are correctly added and mapped from local thread memory to global device memory.}}
								\State{atomicAdd(\dvar{\vec{F_{n}}[i + j + c]}, \tvar{\vec{F_{n}}[n][c]})}
							\EndFor
							\State{\Comment{Displace auxiliary index to point at the first coordinate of the $ (n+1)\textsuperscript{th} $ node of the $ k \textsuperscript{th}$ SE.}}
							\State{$ j \gets j + 3 $}
						\EndFor
						\State{\Comment{Total force.}}
						\State{\Comment{Set auxiliary index to point at the first coordinate of the $ k\textsuperscript{th} $ SE.}}
						\State{$ j \gets 3\times k $}
						\For{$ (c = 0;\, c < 3;\, c++) $} \Comment{Loop over coordinates.}
							\State{atomicAdd(\dvar{\vec{F_{e}}[j+c]}, \tvar{\vec{F_{e}}[c]})}
						\EndFor
						\State{\Return{\dvar{\vec{F_{n}}}, \dvar{\vec{F_{e}}}}}
					\EndGPUFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Nodal Force: Device $ \mapsto $ Host}
			\begin{algorithm}
				\caption{Nodal force in device $ \mapsto $ host.}
				\begin{algorithmic}[1]
					\Function{fx\_device\_host\_map}{\dvar{\vec{F_{n}}[3\times E\times N]}, \hvar{\vec{F_{n}}[N][3\times E]}}
						\State{$ i,~j \gets 0 $} \Comment{Set input and output indices to zero.}
						\For{$ n = 0;\, n < N;\, n++ $} \Comment{Loop over nodes.}
							\State{$ j \gets 0 $} \Comment{Reset output index to point at the first element.}
							\For{$ e = 0;\, e < E;\, e++ $} \Comment{Loop over elements.}
								\For{$ c = 0;\, c < 3;\, c++ $} \Comment{Loop over coordinates.}
									\State{$ \hvar{\vec{F_{n}}[n][j + c]} = \dvar{\vec{F_{n}}[i + e + c\times E\times N]} $}
								\EndFor
								\State{\Comment{Advance output index to point at the first coordinate of the $ (e+1)\textsuperscript{th} $ element.}}
								\State{$ j \gets j + 3 $}
							\EndFor
							\State{\Comment{Advance input index to point at the first coordinate of the $ (n+1)\textsuperscript{th} $ node of the first element.}}
							\State{$ i \gets i + E $}
						\EndFor
						\State{\Return{\hvar{\vec{F_{n}}}}}
					\EndFunction
				\end{algorithmic}
			\end{algorithm}
		\subsubsection{Total Force: Device $ \mapsto $ Host}
			\begin{algorithm}
				\caption{Total force in device $ \mapsto $ host.}
				\begin{algorithmic}[1]
					\Function{ftot\_device\_host\_map}{\dvar{\vec{F_{e}}[3\times E]}, \hvar{\vec{F_{e}}[3\times E]}}
						\State{$ i \gets 0 $} \Comment{Set output index to zero.}
						\For{$ e = 0;\, e < E;\, e++ $} \Comment{Loop over elements.}
							\For{$ c = 0;\, c < 3;\, c++ $} \Comment{Loop over coordinates.}
								\State{$ \hvar{\vec{F_{e}}[i + c]} = \dvar{\vec{F_{e}}[e + c\times E]} $}
							\EndFor
							\State{\Comment{Advance the output index to point at the first coordinate of the $ (e+1)\textsuperscript{th} $ surface element.}}
							\State{$ i \gets i + 3 $}
						\EndFor
						\State{\Return{\hvar{\vec{F_{e}}}}}
					\EndFunction
				\end{algorithmic}
			\end{algorithm}
	\begin{subequations}\label{e:fcne}
		\begin{align}
			\vec{X}_{en}			&\coloneqq	\left[x_{en},\, y_{en},\, z_{en}\right]\\
			\vec{X}_{(1\to E)n}		&\mapsto 	\vec{X}_{n} \nn
			\vec{X}_{n}				&\coloneqq	\left[x_{1n},\, y_{1n},\, z_{1n},\ldots,x_{En},\, y_{En},\, z_{En}\right]\label{se:xn_arr}\\
			\vec{X}_{1\to N}		&\mapsto	\vec{X}^{\textrm{SE}}\nn
			\vec{X}^{\textrm{SE}}	&\coloneqq 
			\begin{aligned}
				&\left[x_{11},\, \ldots,\, x_{E1},\, x_{12},\, \ldots,\, x_{E2},\, \ldots,\, x_{1N},\, \ldots,\, x_{EN}, \right.\\
				&\left.\,y_{11},\, \ldots,\, y_{E1},\, y_{12},\, \ldots,\, y_{E2},\, \ldots,\, y_{1N},\, \ldots,\, y_{EN}, \right.\\
				&\left.\,z_{11},\, \ldots,\, z_{E1},\, z_{12},\, \ldots,\, z_{E2},\, \ldots,\, z_{1N},\, \ldots,\, z_{EN}  \right]
			\end{aligned}
		\end{align}
	\end{subequations}
	where $ e $ is the SE label, $ n $ the node label, $ E $ the number of SEs in the scope. $ N $ the number of nodes in a SE.

	Data-mapping according to \cref{a:fcne} and relabelling the nodes so they go from $ 0 \to N-1 $, the data from \cref{f:lrse_map} would be arranged in device memory like \cref{e:fcne_eg},
	\begin{align}\label{e:fcne_eg}
		\vec{X}^{\textrm{SE}} &= \begin{aligned}
			\left[\underbrace{h_{x},\, i_{x},\, f_{x},\, g_{x}}_{\mathbf{x_{0}}},\, 
			\underbrace{a_{x},\, b_{x},\, i_{x},\, h_{x}}_{\mathbf{x_{1}}},\, 
			\right.&\underbrace{i_{x},\, d_{x},\, e_{x},\, f_{x}}_{\mathbf{x_{2}}},\, 
			\underbrace{b_{x},\, c_{x},\, d_{x},\, i_{x}}_{\mathbf{x_{3}}},\\
			\ldots~y&\textrm{-coord}~\ldots,\\
			\ldots~z&\textrm{-coord}~\ldots]
		\end{aligned}
	\end{align}
	%

	In the GPU, each thread will cater to one SE at a time. This means that each thread will have to extract the relevant data from the 1D array with length $ 3\times E\times N $ into four 1D arrays of length $ 3 $. The purpose of CNE mapping is to provide the warp with coalesced memory access. This is achieved via \cref{a:bcne}.

	Since \cref{a:bcne} is performed in a CUDA GPU, threads in a single block execute sequentially from,
	\begin{align}
		\rvar{threadIdx}.x &= 0 \to \rvar{threadIdx}.x = \rvar{blockDim}.x - 1\,,
	\end{align}
	while threads in different blocks execute in parallel. coalesced memory access is ensured by having each block load a cache line whose entries are contiguously accessed by the threads in the block. Using the same notation as \cref{a:fcne}, full cache line utilisation (optimal cache use) is achieved if cache lines can accomodate $ l $ entries given by \cref{e:opt_cache_len_bcne},
	\begin{align}
		\label{e:opt_cache_len_bcne}
		l =
		\begin{cases}
			a \times N \times E &,\, a > 0 \in \mathbb{N}\\
			&\textrm{or}\\
			\dfrac{1}{2^{a}} \times N \times E &,\, a \geq 0 \in \mathbb{N},\, N \times E \equiv 0\; (\bmod\; 2^{a})\,.
		\end{cases}
	\end{align}
	\subsubsection{Node Coordinate Element Map}
	%
	The node-coordinate-element (NCE) data mapping in \cref{e:fnce} is carried out by \cref{a:fnce}, each thread looks after a given SE.
	\begin{algorithm}
		\caption{NCE data mapping.}
		\label{a:fnce}
		\begin{algorithmic}
			\ForAll{n nodes $ \in $ surface element}
			\ForAll{c coordinates $ \in [x,\, y,\, z] $}
			\ForAll{e surface elements $ \in $ surface mesh section}
			\State list.append(data of the $ n\textsuperscript{th}$ node with $ c\textsuperscript{th} $ coordinate of the $ e\textsuperscript{th} $ SE)
			\EndFor
			\EndFor
			\EndFor
		\end{algorithmic}
	\end{algorithm}
	\begin{subequations}\label{e:fnce}
		\begin{align}
			\vec{X}_{en}			&\coloneqq \left[x_{en},\, y_{en},\, z_{en}\right]\\
			\vec{X}_{(1\to E)n}		&\mapsto \vec{X}_{n} \nn
			\vec{X}_{n}				&\coloneqq \left[x_{1n},\ldots,\, x_{En},\, y_{1n},\ldots,\, y_{En},\, z_{1n},\ldots,\, z_{En}\right]\\
			\vec{X}_{1\to N}		&\mapsto \vec{X}^{\textrm{SE}}\nn
			\vec{X}^{\textrm{SE}}	&\coloneqq 
			\begin{aligned}
				\left[x_{11},\ldots,\, x_{E1},\, y_{11},\right.&\ldots,\, y_{E1},\, z_{11},\ldots,\, z_{E1}\\
				,&\ldots,\\
				x_{1M},\ldots,\, x_{EN},\, y_{1N},&\left.\ldots,\, y_{EN},\, z_{1N},\ldots,\, z_{EN}\right]
			\end{aligned}
		\end{align}
	\end{subequations}
	where $ e $ is the surface \textbf{e}lement, $ n $ the \textbf{n}ode, $ E $ the total number of SEs in scope, $ N $ the total number of nodes in each SE.

	Data-mapping according to \cref{a:fnce} and relabelling the nodes so they go from $ 0 \to N-1 $, the data from \cref{f:lrse_map} would be arranged in device memory like \cref{e:fnce_eg},
	\begin{align}\label{e:fnce_eg}
		\vec{X}^{\textrm{SE}} &= \begin{aligned}
			&\left[\underbrace{h_{x},\, i_{x},\, f_{x},\, g_{x},\, 
				h_{y},\, i_{y},\, f_{y},\, g_{y},\, 
				h_{z},\, i_{z},\, f_{z},\, g_{z}}_{\mathbf{x_{0}}}\right.,\\
			&~\ldots~\mathbf{x_{1}},\, xyz\textrm{-coords}~\ldots,\\
			&~\ldots~\mathbf{x_{2}},\, xyz\textrm{-coords}~\ldots,\\
			&~\ldots~\mathbf{x_{3}},\, xyz\textrm{-coords}~\ldots]
		\end{aligned}
	\end{align}
	%
	\subsubsection{Resolving Data Write Conflicts}
	Data write conflicts can be a problem in parallel applications where global data is changed by multiple threads within the same clock tick. This can be avoided with atomic operations.
	%
	\subsection[Parallel Dislocation Line Segments to Surface Elements]{Resolving Parallel Dislocation Line Segments to Surface Elements}
	%
	Dealing with the special case when the dislocation line segment $ \vec{t} $ is parallel to the SE is relatively trivial when in a serial program. By the mean value theorem, we can slightly perturb $ \vec{t} $ by rotating it by a small angle around the midpoint of $ \vec{t} $ with respect to the axis of rotation defined by $ \vec{t} \times \vec{n} $. In contrast to serial code, program branches can have a serious effect on parallel performance due to warp divergence. Due to the complexity of the force calculation and relative rarity of the edge case, there is no branching behaviour in the parallel code until \emph{after} the calculation is performed. Where \cref{a:plse_p} is performed.
	\begin{algorithm}
		\caption{Resolving cases when $ \vec{t} \parallel \vec{n} $ on GPUs.}
		\label{a:plse_p}
		\begin{algorithmic}
			\ForAll{surface elements \emph{and} line segments}
			\State $ \ldots $
			\If{$ \vec{t}_{\textrm{thread}} \parallel \vec{n}_{\textrm{thread}} $}
			\State $ \vec{x}_{\textrm{buffer}} \gets \vec{x}_{\textrm{thread}} $
			\State $ \vec{t}_{\textrm{buffer}} \gets \vec{t}_{\textrm{thread}} $
			\Else
			\State $ \vec{F}_{\textrm{total}} += \vec{F}_{\textrm{thread}} $
			\EndIf
			\EndFor
			\State return to serial code
			\If{$ \vec{x}_{\textrm{buffer}} \neq $ empty}
			\ForAll{surface elements \emph{and} line segments}
			\State perform calculation for $ \vec{t} \parallel \vec{n} $
			\EndFor
			\EndIf
		\end{algorithmic}
	\end{algorithm}

\section{Theory}\label{s:theory}

\section{Methodology}\label{s:method}

\section{Results}

\section{Acknowledgements}

We would like to thank Prof. Sylvain Queyreau and Lawrence Livermore National Laboratory for their invaluable input. This work was supported by the Consejo Nacional de Ciencia y Tecnologia, Fondo Sectorial CONACYT-Secretaria de Energia-Sustentabilidad Energetica Cuarto Periodo [291129]. This work was supported by the Engineering and Physical Sciences Research Council Centre for Doctoral Training in the Science and Technology of Fusion Energy EP/L01663X/1 and Fellowship grant EP/N007239/1.
  %% References
  %%
  %% Following citation commands can be used in the body text:
  %% Usage of \cite is as follows:
  %%   \cite{key}          ==>>  [#]
  %%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
  %%   \citet{key}         ==>>  Author [#]

  %% References with bibTeX database:
  \newcommand{\newblock}{}
  \bibliographystyle{unsrtnat}
  \bibliography{references.bib}

  %% Authors are advised to submit their bibtex database files. They are
  %% requested to list a bibtex style file in the manuscript if they do
  %% not want to use model1-num-names.bst.

  %% References without bibTeX database:

  % \begin{thebibliography}{00}

  %% \bibitem must have the following form:
  %%   \bibitem{key}...
  %%

  % \bibitem{}

  % \end{thebibliography}
\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2020-09-25 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m
Format

@@ -29,52 +29,52 @@ cntr = 0;
 
 for j = 20
     mx = j;
-    
+
     gridSize = mx;
     x = linspace(0, dx, gridSize);
     y = linspace(0.5 * dy, 0.5 * dy, gridSize);
     z = linspace(0, dz, gridSize);
     [X, Z] = meshgrid(x, z);
     Y = meshgrid(y);
-    
+
     clear x y z;
-    
+
     loading = 1;
     vertices = [0, 0, 0; ...
-        dx, 0, 0; ...
-        0, dy, 0; ...
-        dx, dy, 0; ...
-        0, 0, dz; ...
-        dx, 0, dz; ...
-        0, dy, dz; ...
-        dx, dy, dz];
-    
+                dx, 0, 0; ...
+                0, dy, 0; ...
+                dx, dy, 0; ...
+                0, 0, dz; ...
+                dx, 0, dz; ...
+                0, dy, dz; ...
+                dx, dy, dz];
+
     plim = 12 / amag; %12microns
     [xnodes, mno, nc, n, D, kg, K, L, U, Sleft, Sright, Stop, Sbot, ...
-        Sfront, Sback, Smixed, gammat, gammau, gammaMixed, fixedDofs, freeDofs, ...
-        w, h, d, my, mz, mel] = STATIC_finiteElement3D(dx, dy, dz, mx, MU, NU, loading);
-    
+            Sfront, Sback, Smixed, gammat, gammau, gammaMixed, fixedDofs, freeDofs, ...
+            w, h, d, my, mz, mel] = STATIC_finiteElement3D(dx, dy, dz, mx, MU, NU, loading);
+
     gamma_dln = [gammat(:, 1)];
-    
+
     % Set surface node labels for surface node extraction.
     n_nodes = 4;
     surf_node_util = zeros(n_nodes + 2, 6);
     xy = mx * my;
     xz = mx * mz;
     yz = my * mz;
-    
+
     f_hat = zeros(3 * mno, 1);
     [x3x6_lbl, x3x6, n_se] = extract_surface_nodes(xnodes, nc, [mx; my; mz], ...
[…]

### 2020-09-25 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m
Fixed sign.

@@ -188,7 +188,7 @@ for k = 1:2
 end
 
 %% Screw
-b = [0 1 0];
+b = -[0 1 0];
 
 for i = 1:len - 1
     links(i, :) = [i, i + 1, b, n];
@@ -440,7 +440,7 @@ function [tyz] = imageStressAnalyticScrew(mu, b, nu, x, y, a, c)
     xpa = x + a;
     ymc = y - c;
 
-    tyz = xpa ./ (xpa.^2 + ymc.^2);
+    tyz = -xpa ./ (xpa.^2 + ymc.^2);
     tyz = D .* tyz;
 end
 

### 2020-09-30 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/STATIC_finiteElement3D.m
Fixes #36

@@ -309,6 +309,7 @@ for p = 1:mel%all elements
     end
 
 end
+
 clear B;
 % ensure ke is symmetric eg remove any very small entries due to numerical
 % error.
@@ -509,6 +510,83 @@ if loading == 1 || loading == 0% cantilever bending
 
     end
 
+%     m = 1;
+%     Sbot = zeros((mx + 1) * (my + 1), 5);
+%     for j = 1:my + 1
+%         for i = 1:mx + 1
+%             % bottom surface of beam (t=0)
+%             gn = i + (mx + 1) * (mz + 1) * (j - 1);
+%             Sbot(m, 1) = gn;
+% 
+%             L1 = w;
+% 
+%             if j == 1 || j == my + 1
+%                 L2 = 0.5 * h;
+%             else
+%                 L2 = h;
+%             end
+% 
+%             Sbot(m, 2) = L1 * L2;
+%             Sbot(m, 3:5) = [0, 0, -1];
+%             m = m + 1;
+%         end
+% 
+%     end
+%     
+%     m = 1;
+%     Sleft = zeros((my -1) * (mz), 5); % second priority
+%     for j = 2:my
+%         for k = 2:mz + 1
+%             % left surface of beam (u=0)
+%             gn = 1 + (k - 1) * (mx + 1) + (mx + 1) * (mz + 1) * (j - 1);
+%             Sleft(m, 1) = gn;
+% 
+%             if k == 1 || k == mz + 1
+%                 L3 = 0.5 * d;
+%             else
+%                 L3 = d;
+%             end
+% 
+%             if j == 1 || j == my + 1
+%                 L2 = 0.5 * h;
+%             else
+%                 L2 = h;
+%             end
+% 
+%             Sleft(m, 2) = L2 * L3;
+%             Sleft(m, 3:5) = [-1, 0, 0];
+%             m = m + 1;
+%         end
+% 
+%     end
+%     
+%     m = 1;
+%     Sright = zeros((my + 1) * (mz-1), 3);
+%     for j = 1:my + 1
+%         for k = 2:mz
+%             % right surface of beam (t=0)
+%             gn = k * (mx + 1) + (mx + 1) * (mz + 1) * (j - 1);
+%             Sright(m, 1) = gn;
+% 
+%             if k == 1
+%                 L3 = 0.5 * d;
+%             else
+%                 L3 = d;
+%             end
+% 
+%             if j == 1 || j == my + 1
[…]

### 2020-09-30 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/STATIC_finiteElement3D.m
Cleanup

@@ -510,83 +510,6 @@ if loading == 1 || loading == 0% cantilever bending
 
     end
 
-%     m = 1;
-%     Sbot = zeros((mx + 1) * (my + 1), 5);
-%     for j = 1:my + 1
-%         for i = 1:mx + 1
-%             % bottom surface of beam (t=0)
-%             gn = i + (mx + 1) * (mz + 1) * (j - 1);
-%             Sbot(m, 1) = gn;
-% 
-%             L1 = w;
-% 
-%             if j == 1 || j == my + 1
-%                 L2 = 0.5 * h;
-%             else
-%                 L2 = h;
-%             end
-% 
-%             Sbot(m, 2) = L1 * L2;
-%             Sbot(m, 3:5) = [0, 0, -1];
-%             m = m + 1;
-%         end
-% 
-%     end
-%     
-%     m = 1;
-%     Sleft = zeros((my -1) * (mz), 5); % second priority
-%     for j = 2:my
-%         for k = 2:mz + 1
-%             % left surface of beam (u=0)
-%             gn = 1 + (k - 1) * (mx + 1) + (mx + 1) * (mz + 1) * (j - 1);
-%             Sleft(m, 1) = gn;
-% 
-%             if k == 1 || k == mz + 1
-%                 L3 = 0.5 * d;
-%             else
-%                 L3 = d;
-%             end
-% 
-%             if j == 1 || j == my + 1
-%                 L2 = 0.5 * h;
-%             else
-%                 L2 = h;
-%             end
-% 
-%             Sleft(m, 2) = L2 * L3;
-%             Sleft(m, 3:5) = [-1, 0, 0];
-%             m = m + 1;
-%         end
-% 
-%     end
-%     
-%     m = 1;
-%     Sright = zeros((my + 1) * (mz-1), 3);
-%     for j = 1:my + 1
-%         for k = 2:mz
-%             % right surface of beam (t=0)
-%             gn = k * (mx + 1) + (mx + 1) * (mz + 1) * (j - 1);
-%             Sright(m, 1) = gn;
-% 
-%             if k == 1
-%                 L3 = 0.5 * d;
-%             else
-%                 L3 = d;
-%             end
-% 
-%             if j == 1 || j == my + 1
-%                 L2 = 0.5 * h;
-%             else
-%                 L2 = h;
-%             end
-% 
-%             Sright(m, 2) = L2 * L3;
[…]

### 2020-09-30 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Fixes #29
Fixed sign.
Added stuff to explain dislocation equations.

--- 2020-09-23 src/wip/DanielCelisGarza/Accurate evaluation of dislocation tractions/paper/main.tex
@@
     \vec{F}^{a} = \int_{S^{e}} \left[\tilde{\bm{\sigma}}(\vec{x}) \cdot \vec{n}\right] N^{a}(\vec{x})\; \mathrm{d}S\,,
-    \label{e:ddd_fem_force}
+    \label{eq:ddd_fem_force}
 \end{align}
@@
 where $\mathrm{d}S^{e}$ is the surface of element $e$ with surface area $S^{e}$ and $N^{a}$ is the finite element shape function for node $a$ which is bi-linear in this paper.
-In the parent element (shown in figure  \ref{f:2d_gaussian_quad}) the shape functions are,
+In the parent element (shown in \cref{f:2d_gaussian_quad}) the shape functions are,
 
 \begin{align}
-    \label{e:shape_function}
+    \label{eq:shape_function}
     N^{1} & = \dfrac{1}{4}(1-s_1)(1-s_2)             \\
@@
 
-Usually Gauss quadrature is used to evaluate the surface integral in equation (\ref{e:ddd_fem_force}) numerically. The 1D Gauss quadrature is,
+Usually Gauss quadrature is used to evaluate the surface integral in \cref{eq:ddd_fem_force} numerically. The 1D Gauss quadrature is,
 %
 \begin{align}
-    \label{e:gauss_leg}
+    \label{eq:gauss_leg}
     \int\limits_{-1}^{1} f(s)\;\mathrm{d}s \approx \sum\limits_{i=1}^{n} w_{i} f(s_{i}) \quad \textrm{where}\quad
@@
 
-For rectangular surface elements we must transform from the parent element in $(s_1,\,s_2)$ in equation (\ref{e:gauss_leg}) to the real element coordinate system $(x,y,z)$ shown in \cref{f:force_lin_rect}.
-Evaluating equation (\ref{e:ddd_fem_force}) in the parent element and mapping to the real element gives the force on node $a$,
+For rectangular surface elements we must transform from the parent element in $(s_1,\,s_2)$ in \cref{eq:gauss_leg} to the real element coordinate system $(x,y,z)$ shown in \cref{f:force_lin_rect}.
+Evaluating \cref{eq:ddd_fem_force} in the parent element and mapping to the real element gives the force on node $a$,
 %
 \begin{align}
-    \label{e:gauss_leg_ddd_fem_force}
+    \label{eq:gauss_leg_ddd_fem_force}
     \vec{F}^{a} \approx \sum\limits_{i=1}^{Q} w_{i} \sum\limits_{j=1}^{Q} w_{j} [\tns{\sigma}(r_{i}, s_{j})\cdot \vec{n}] N^{a}(r_{i}, s_{j}) \det(\mtx{J})\,.
@@
 
-Equation \ref{e:ddd_fem_force} is actually a triple vector integral.
+\Cref{eq:ddd_fem_force} is actually a triple vector integral.
 It involves integrating over the surface element and along the dislocation line segment, as shown in \cref{f:force_lin_rect}.
@@
 \begin{align}
-    \label{e:stress}
+    \label{eq:stress}
     \tns{\sigma}(\vec{x}) = &
@@
 %
-The vectors $\vec{p}$ and $\vec{q}$ are aligned with the edges of the rectangular finite element, $\vec{n} = \vec{p} \times \vec{q}$ is the element surface normal (pointing away from the dislocation), and $\vec{l}$ is parallel to the dislocation line segment as shown in figure \ref{f:force_lin_rect}.
+The vectors $\vec{p}$ and $\vec{q}$ are aligned with the edges of the rectangular finite element, $\vec{n} = \vec{p} \times \vec{q}$ is the element surface normal (pointing away from the dislocation), and $\vec{l}$ is parallel to the dislocation line segment as shown in \cref{f:force_lin_rect}.
 Then (provided $\vec{l}$ is not parallel to $\vec{p}$ or $\vec{q}$) $\vec{R}$ can be expressed in terms of $(\vec{l},~\vec{p},~\vec{q})$ with coefficients
@@
 \begin{align}
-    y = \dfrac{\vec{R}\cdot \vec{n}}{\vec{l}\cdot \vec{n}} \label{se:problem},\quad
+    y = \dfrac{\vec{R}\cdot \vec{n}}{\vec{l}\cdot \vec{n}} \label{eq:problem},\quad
     %
@@
 %
-Substituting (\ref{e:stress}) and (\ref{e:shape_function}) into (\ref{e:ddd_fem_force}) yields four long and messy equations (one for each FE node) that were elegantly solved by \citet{Queyreau} by utilising the fact that the triple integrals all had the form,
+Substituting \cref{eq:stress} and \cref{eq:shape_function} into \cref{eq:ddd_fem_force} yields four long and messy equations (one for each FE node) that were elegantly solved by \citet{Queyreau} by utilising the fact that the triple integrals all had the form,
 %
 \begin{align}
-    H_{ijkl}        & = \int\limits_{r_{1}}^{r_{2}}\int\limits_{s_{1}}^{s_{2}}\int\limits_{y_{1}}^{y_{2}} \dfrac{r^i s^j y^k}{R_{a}^{m}}\label{e:triple_int} \\
+    H_{ijkl}        & = \int\limits_{r_{1}}^{r_{2}}\int\limits_{s_{1}}^{s_{2}}\int\limits_{y_{1}}^{y_{2}} \dfrac{r^i s^j y^k}{R_{a}^{m}}\label{eq:triple_int} \\
     \textrm{when }m & = 5 \textrm{ then } i,\, j \in [0,\,3],~k \in [0,\,2]\nonumber                                                                          \\
@@
 %
-Using partial differentiation and integration by parts, they found a series of recurrence relations that lead to double and single integrals with a similar form to equation (\ref{e:triple_int}).
+Using partial differentiation and integration by parts, they found a series of recurrence relations that lead to double and single integrals with a similar form to equation (\cref{eq:triple_int}).
 Together they are used to construct a full solution.
@@
 In order to validate and compare the differences in tractions have on dislocation plasticity simulations we compare the analytic expressions for infinite dislocations in inhomogenous media by \citet{head1953edge}.
-The original paper has a few typos that have been replicated in other sources so we write the correct expressions for an edge dislocation parallel to a surface described by the line $x = 0$, where the dislocation coordinates are $(a,~c)$ and we are looking at the $xy$-plane where $\vec{b}$ is perpendicular to the surface in \cref{e:imageStressAnalyticEdge1},
+The original paper has a few typos that have been replicated in other sources so we write the correct expressions for an edge dislocation parallel to a surface described by the line $x = 0$, where the dislocation coordinates are $(a,~c)$ and we are looking down the $xy$-plane where $\vec{b}$ is perpendicular to the surface in \cref{eq:imageStressAnalyticEdge1},
+% TODO #37
 \begin{subequations}
-    \begin{align}\label{e:imageStressAnalyticEdge1}
+    \begin{align}\label{eq:imageStressAnalyticEdge1}
         \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} + \dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2}\right.
@@
 \end{subequations}
-The case where the Burgers vector lies parallel to the surface is found in \cref{e:imageStressAnalyticEdge2}.
+The case where the Burgers vector lies parallel to the surface is found in \cref{eq:imageStressAnalyticEdge2}.
 \begin{subequations}
-    \begin{align}\label{e:imageStressAnalyticEdge2}
+    \begin{align}\label{eq:imageStressAnalyticEdge2}
         \sigma_{xx} = D         & \left\{ (x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} -(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} \right.     \\\nonumber
@@
 \end{subequations}
-
-% TODO #27
+Screw dislocations are markedly simpler, as only the shear components are non-zero. Their equations are the following.
+\begin{subequations}
+    \begin{align}\label{eq:imageStressAnalyticScrew}
+        \sigma_{xz} & = -D \left(\dfrac{y - c}{(x - a)^2 + (y - c)^2} - \dfrac{y - c}{(x + a)^2 + (y - c)^2}\right) \\
+        \sigma_{yz} & = D \left(\dfrac{x - a}{(x - a)^2 + (y - c)^2} - \dfrac{x + a}{(x + a)^2 + (y - c)^2}\right)
+    \end{align}
+\end{subequations}
+Note the first terms of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} all correspond to the stress field generated by the dislocation.
+The following terms are the corrective terms required to make the boundary conditions on the surface equal to zero.
 
@@
 The implementation of the analytic solution is also much more involved.
-One issue is the calculation of the $y$-coordinate in the local coordinate frame as shown in \cref{f:force_lin_rect} and equation (\ref{se:problem}), if $\vec{l} \perp \vec{n}$, we get a singularity.
+One issue is the calculation of the $y$-coordinate in the local coordinate frame as shown in \cref{f:force_lin_rect} and \cref{eq:problem}, if $\vec{l} \perp \vec{n}$, we get a singularity.
 As mentioned in \cite{Queyreau}, an easy fix is to rotate the line segment about its midpoint around the $\vec{l} \times \vec{n}$ axis and use the mean values either side as the true result.
@@
             \vec{x_{9}}
-        \end{bmatrix}\,.\label{e:force_imp}
+        \end{bmatrix}\,.\label{eq:force_imp}
     \end{align}
@@
 $\vec{x_n}$ is a $3\times1$ column vector corresponding to the total $x,~y,~z$ dislocation induced forces on node $n$.
-These are used to shorten the definition of equation (\ref{e:force_imp}) and are not explicitly defined in the implementation, rather they give the force matrices $\mtx{F_{e}}$ and $\vec{\tilde{F}}$ a specific row order.
+These are used to shorten the definition of \cref{eq:force_imp} and are not explicitly defined in the implementation, rather they give the force matrices $\mtx{F_{e}}$ and $\vec{\tilde{F}}$ a specific row order.
 $\mtx{N_{L}}$ is crucial for the correct implementation of this analytical solution in traditional FE codes.
@@
 
-The following algorithm illustrates how the total force on each node is obtained. The resulting force vector is later used in eq. (\ref{eq:thatbc}) as $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
+The following algorithm illustrates how the total force on each node is obtained. The resulting force vector is later used in \cref{eq:thatbc} as $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
 \begin{algorithm}
@@
 
-For a segment parallel to a surface, Gauss quadrature performs far worse than for a perpendicular segment, as shown in figure \ref{f:rel_err_par_edge}.
+For a segment parallel to a surface, Gauss quadrature performs far worse than for a perpendicular segment, as shown in \cref{f:rel_err_par_edge}.
 This is because numerical quadrature is only accurate for integrating functions that can be approximated by polynomials.
 Whereas the dislocation stress field \cite{Cai2006} decays as $1/R_{a}$.
-This makes numerical quadrature unsuitable as (\ref{e:gauss_leg_ddd_fem_force}) fails to accurately capture the stress, which varies rapidly across the element surface for small $R_a$.
+This makes numerical quadrature unsuitable as \cref{eq:gauss_leg_ddd_fem_force} fails to accurately capture the stress, which varies rapidly across the element surface for small $R_a$.
 The relevant components of the stress tensor for a perpendicular edge segment which is not penetrating the surface are shown in \cref{f:sigma_perp_edge}.

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Fixes Define D, it's in the code. #37

@@
 
-The force exerted by a dislocation ensemble on a node $a$ belong to element $e$ is given by,
+The force exerted by a dislocation ensemble on a node $a$ belonging to element $e$ is given by,
 %
 \begin{align}
-    \vec{F}^{a} = \int_{S^{e}} \left[\tilde{\bm{\sigma}}(\vec{x}) \cdot \vec{n}\right] N^{a}(\vec{x})\; \mathrm{d}S\,,
+    \vec{F}_{a} = \int_{S_{e}} \left[\tilde{\bm{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,,
     \label{eq:ddd_fem_force}
@@
 %
-where $\mathrm{d}S^{e}$ is the surface of element $e$ with surface area $S^{e}$ and $N^{a}$ is the finite element shape function for node $a$ which is bi-linear in this paper.
+where $\mathrm{d}S_{e}$ is the surface of element $e$ with surface area $S_{e}$ and $N_{a}$ is the finite element shape function for node $a$ which is bi-linear in this paper.
 In the parent element (shown in \cref{f:2d_gaussian_quad}) the shape functions are,
@@
     \label{eq:shape_function}
-    N^{1} & = \dfrac{1}{4}(1-s_1)(1-s_2)             \\
-    N^{2} & = \dfrac{1}{4}(1+s_1)(1-s_2)\nonumber    \\
-    N^{3} & = \dfrac{1}{4}(1+s_1)(1+s_2)\nonumber    \\
-    N^{4} & = \dfrac{1}{4}(1-s_1)(1+s_2)\nonumber\,.
+    N_{1} & = \dfrac{1}{4}(1-s_1)(1-s_2)             \\
+    N_{2} & = \dfrac{1}{4}(1+s_1)(1-s_2)\nonumber    \\
+    N_{3} & = \dfrac{1}{4}(1+s_1)(1+s_2)\nonumber    \\
+    N_{4} & = \dfrac{1}{4}(1-s_1)(1+s_2)\nonumber\,.
 \end{align}
@@
     \label{eq:gauss_leg_ddd_fem_force}
-    \vec{F}^{a} \approx \sum\limits_{i=1}^{Q} w_{i} \sum\limits_{j=1}^{Q} w_{j} [\tns{\sigma}(r_{i}, s_{j})\cdot \vec{n}] N^{a}(r_{i}, s_{j}) \det(\mtx{J})\,.
+    \vec{F}_{a} \approx \sum\limits_{i=1}^{Q} w_{i} \sum\limits_{j=1}^{Q} w_{j} [\tns{\sigma}(r_{i}, s_{j})\cdot \vec{n}] N_{a}(r_{i}, s_{j}) \det(\mtx{J})\,.
 \end{align}
 %
-Where the sum is over the $Q$ quadrature points and $J_{ij}=dx_{i}/ds_{j}$ is the element Jacobian defining the transformation from $(s_1,\,s_2) \mapsto (x,\,y)$; as the real element is rectangular with surface area $S^e$, $\det(\mtx{J})=S^e/4$.
+Where the sum is over the $Q$ quadrature points and $J_{ij}=dx_{i}/ds_{j}$ is the element Jacobian defining the transformation from $(s_1,\,s_2) \mapsto (x,\,y)$; as the real element is rectangular with surface area $S_e$, $\det(\mtx{J})=S_e/4$.
 \Cref{f:2d_gaussian_quad} contains examples of how the Gauss points are distributed on the surface.
@@
 The point size represents the weight $w$ of the integration point.
-The parent elements are centred at the origin and $s_1,\, s_2 \in [-1,\,1]$ with node anticlockwise node numbering.}
+The parent elements are centred at the origin and $s_1,\, s_2 \in [-1,\,1]$.
+We use an anticlockwise node numbering scheme.}
     \label{f:2d_gaussian_quad}
@@
 
-In simulations, the tractions are manifested in the reaction forces calculated by the FE solver at FE nodes.
-In order to validate and compare the differences in tractions have on dislocation plasticity simulations we compare the analytic expressions for infinite dislocations in inhomogenous media by \citet{head1953edge}.
-The original paper has a few typos that have been replicated in other sources so we write the correct expressions for an edge dislocation parallel to a surface described by the line $x = 0$, where the dislocation coordinates are $(a,~c)$ and we are looking down the $xy$-plane where $\vec{b}$ is perpendicular to the surface in \cref{eq:imageStressAnalyticEdge1},
+In simulations, the tractions are manifested in the image stresses calculated by the FE solver at FE nodes.
+In order to validate and compare the practical differences between analytic and gauss quadrature methods, we use them both to calculate the reaction stresses produced by the tractions with the same FE solver and compare the results with the analytic expressions for infinite dislocations in inhomogenous media in \cite{head1953edge} for edge dislocations as well as those for screw dislocations found in \cite[p.~59,~64]{hirth1983theory}, where the traction surface is the line $x=0$, looking at the $xy$-plane in the positive $z$-direction, where the dislocation coordinates are represented by $(a,~c)$ and points in the plane described by their $(x,~y)$ coordinates.
+
+The original paper by \citet{head1953edge} has a few typos that have been replicated in other sources, so we include the complete and correct expressions.
+\citet{head1953edge} gives two basic cases.
+The first case in \cref{eq:imageStressAnalyticEdge1} corresponds to the case where $\vec{b}$ is perpendicular to the surface and positive $b$ points in the positive $x$ direction,
 % TODO #37
@@
 \end{subequations}
-Screw dislocations are markedly simpler, as only the shear components are non-zero. Their equations are the following.
+Screw dislocations are markedly simpler, as only the shear components are non-zero \cref{eq:imageStressAnalyticScrew},
 \begin{subequations}
@@
         \sigma_{xz} & = -D \left(\dfrac{y - c}{(x - a)^2 + (y - c)^2} - \dfrac{y - c}{(x + a)^2 + (y - c)^2}\right)   \\
-        \sigma_{yz} & = D \left(\dfrac{x - a}{(x - a)^2 + (y - c)^2} - \dfrac{x + a}{(x + a)^2 + (y - c)^2}\right)
+        \sigma_{yz} & = D \left(\dfrac{x - a}{(x - a)^2 + (y - c)^2} - \dfrac{x + a}{(x + a)^2 + (y - c)^2}\right)\,.
     \end{align}
 \end{subequations}
+In every case, the constant $D$ is defined by \cref{eq:Dconstant}
+\begin{align}\label{eq:Dconstant}
+    D = \dfrac{\mu}{2\pi} \cdot \dfrac{1+\nu}{1-\nu^2} \bm{b}\,.
+\end{align}
 Note the first terms of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} all correspond to the stress field generated by the dislocation.
 The following terms are the corrective terms required to make the boundary conditions on the surface equal to zero.
+Therefore, we can split these equations and only look at the real or corrective terms, which we do in order to visualise the effect of the different traction calculations.
+Furthermore \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} are all singular at the dislocation coordinates, our simulation code uses non singular expressions found by \citet{Cai2006}, which smooth out drastic increases in stresses and avoid numerical blow up as we near the dislocation core.
 
@@
     \label{f:err_basic_cantilever}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{head_vs_fe_tractions_setup_diagram.pdf}
+    \caption{Dislocation parallel to a surface described by the line $x = 0$ (the $yz$-plane in 3D), where the dislocation coordinates are $(a,~c)$, looking down the $xy$-plane where the $x$-axis is horizontal and the $y$-axis vertical.
+(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000~ \vec{b}$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
+(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\bm{b}_\textrm{e1}$ perpendicular to the surface and pointing in the positive $x$ direction, $\bm{b}_\textrm{e2}$ parallel to the surface and pointing in the positive $y$ direction; and the screw Burgers vector parallel to the surface and pointing in the line direction as posited in \cite{hirth1983theory}.}
+    \label{f:headvstractionfem}
 \end{figure}
@@
 This is because numerical quadrature is only accurate for integrating functions that can be approximated by polynomials.
-Whereas the dislocation stress field \cite{Cai2006} decays as $1/R_{a}$.
-This makes numerical quadrature unsuitable as \cref{eq:gauss_leg_ddd_fem_force} fails to accurately capture the stress, which varies rapidly across the element surface for small $R_a$.
+Whereas the dislocation stress field \cite{Cai2006} decays as $\mathcal{O}(1/R)$.
+This makes Gauss quadrature unsuitable as \cref{eq:gauss_leg_ddd_fem_force} fails to accurately capture the stress, which varies rapidly across the element surface for small $R$.
 The relevant components of the stress tensor for a perpendicular edge segment which is not penetrating the surface are shown in \cref{f:sigma_perp_edge}.

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
More writing.

@@
 \citet{head1953edge} gives two basic cases.
-The first case in \cref{eq:imageStressAnalyticEdge1} corresponds to the case where $\vec{b}$ is perpendicular to the surface and positive $b$ points in the positive $x$ direction,
-% TODO #37
+The first case in \cref{eq:imageStressAnalyticEdge1} corresponds to the case where $\vec{b}$ is perpendicular to the surface and positive $b$ means it points in the positive $x$ direction,
 \begin{subequations}
@@
 \end{subequations}
-The case where the Burgers vector lies parallel to the surface is found in \cref{eq:imageStressAnalyticEdge2}.
+The case where the $\bm{b}$ lies parallel to the surface and positive $b$ means it points in the positive $y$ direction, is found in \cref{eq:imageStressAnalyticEdge2},
 \begin{subequations}
@@
 \end{subequations}
-Screw dislocations are markedly simpler, as only the shear components are non-zero \cref{eq:imageStressAnalyticScrew},
+Screw dislocations are markedly simpler, as only the shear components are non-zero.
+Here $\bm{b} = \bm{l}$ and therefore positive $b$ means it points in the positive $z$ direction (away from the observer) \cref{eq:imageStressAnalyticScrew},
 \begin{subequations}
@@
 \begin{align}\label{eq:Dconstant}
-    D = \dfrac{\mu}{2\pi} \cdot \dfrac{1+\nu}{1-\nu^2} \bm{b}\,.
+    D = \dfrac{\mu}{2\pi} \cdot \dfrac{1+\nu}{1-\nu^2} \cdot b\,.
 \end{align}
@@
 The following terms are the corrective terms required to make the boundary conditions on the surface equal to zero.
-Therefore, we can split these equations and only look at the real or corrective terms, which we do in order to visualise the effect of the different traction calculations.
+Therefore, we can split these equations and only look at the real or corrective terms, which we do in order to only visualise the effect of the different traction calculations.
 Furthermore \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} are all singular at the dislocation coordinates, our simulation code uses non singular expressions found by \citet{Cai2006}, which smooth out drastic increases in stresses and avoid numerical blow up as we near the dislocation core.
@@
 \section{Methodology}\label{s:method}
-Numerical integration of tractions can produces unexpected behaviour such as force hot spots (see \cref{f:err_basic_cantilever}) and sign inversions as a dislocation approaches a surface.
+Numerical integration of tractions can produces unexpected behaviour such as force hot spots and sign inversions as a dislocation approaches a surface.
 During a large simulation, these effects are hard to spot.
-\citet{Queyreau} identified that for a given number of quadrature points, the error is dependent on the dislocation character but always increases rapidly as the distance between the segment and element surface decrease (see \cref{f:rel_err_perp_edge,f:rel_err_par_edge}).
-%
-\begin{figure}[htb]
+\Cref{f:err_basic_cantilever} has a quick example of the relative errors for an idealised system not disimilar to what can be found with in a simple cantilever bending simulation with a single dislocation loop.
+As expected, the errors decrease as the mesh gets finer.
+\begin{figure}
     \centering
@@
 The dislocation is of pure edge character with $\vec{b} = [1\,0\,\overline{1}]$, and line direction, $\vec{l} = \left[\overline{1}\,2\,\overline{1}\right]/\sqrt{6}$ which pierces both $xz$-faces.
-The dislocation has its centre at the centroid of the cantilever.
-%The absolute difference cutoff was set to $10^{-9}$ to avoid post-processing artefacts arising from truncation and roundoff errors in floating point arithmetic.
-    }
+The dislocation has its centre at the centroid of the cantilever.}
     \label{f:err_basic_cantilever}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{head_vs_fe_tractions_setup_diagram.pdf}
-    \caption{Dislocation parallel to a surface described by the line $x = 0$ (the $yz$-plane in 3D), where the dislocation coordinates are $(a,~c)$, looking down the $xy$-plane where the $x$-axis is horizontal and the $y$-axis vertical.
-(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000~ \vec{b}$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
-(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\bm{b}_\textrm{e1}$ perpendicular to the surface and pointing in the positive $x$ direction, $\bm{b}_\textrm{e2}$ parallel to the surface and pointing in the positive $y$ direction; and the screw Burgers vector parallel to the surface and pointing in the line direction as posited in \cite{hirth1983theory}.}
-    \label{f:headvstractionfem}
-\end{figure}
-%
+\citet{Queyreau} identified that for a given number of quadrature points, the error is dependent on the dislocation character but always increases rapidly as the distance between the segment and element surface decrease (see \cref{f:rel_err_perp_edge,f:rel_err_par_edge}).
+
 Expanding the test cases reveals just how problematic numerical integration of the tractions can be when a dislocation approaches a surface.
@@
 An example of what this looks like in terms of forces can be seen in \cref{f:rotate} (we removed the singularity to keep the graph smooth).
-%
 \begin{figure}[htb]
@@
 \end{figure}
-
-The specific shape of the curves will vary depending on the element/segment configuration, but is smooth and well-behaved about singularity.
+The specific shape of the curves will vary depending on the element-segment configuration, but is smooth and well-behaved about singularity.
 For our purposes, we used 4 perturbations each of $1\,\deg$, in the clockwise and anti-clockwise directions (8 rotations in total) w.r.t.
@@
 \end{algorithm}
-Our implementation does not strictly follow \cref{a:tot_force} because we also memoise a generalised version of $\vec{L}$ upon simulation initialisation instead of finding one at every iteration, reducing computational time but requiring us to account for nodes without traction boundary conditions.
-Our indexing also starts at 1, so the algorithm further adjusted for this.
+Our implementation does not strictly follow \cref{a:tot_force} because we memoise a generalised version of $\vec{L}$ upon simulation initialisation instead of finding one at every iteration, reducing computational time but requiring us to account for nodes without traction boundary conditions.
+Our indexing also starts at 1, but zero indexing makes the algorithm easier to follow.
+
+After the tractions have been calculated, they are used by the FE solver to generate the corresponding image stresses.
+\Cref{f:headvstractionfem} shows the system we used to compare the image stresses calculated by our FE solver using numeric tractions v.s.
+analytic tractions v.s.
+infinite-domain, singular image stresses found in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{head_vs_fe_tractions_setup_diagram.pdf}
+    \caption{Dislocation parallel to a surface described by the line $x = 0$ (the $yz$-plane in 3D), where the dislocation coordinates are $(a,~c)$, looking down the $xy$-plane where the $x$-axis is horizontal and the $y$-axis vertical.
+(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000~ \vec{b}$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
+(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\bm{b}_\textrm{e1}$ perpendicular to the surface and pointing in the positive $x$ direction, $\bm{b}_\textrm{e2}$ parallel to the surface and pointing in the positive $y$ direction; and the screw Burgers vector parallel to the surface and pointing in the line direction as posited in \cite{hirth1983theory}.}
+    \label{f:headvstractionfem}
+\end{figure}
+
+Finally, we ran a simple simulation where the differences between methods can be readily observed.
 
@@
 
+All our subsequent simulations have used analytic tractions as they run faster and yield more reasonable dislocation structures, particularly for more complex simulations.
+
 \section{Acknowledgements}

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Nicer graphs, added to paper.

@@
 \section{Introduction}\label{s:intro}
+
 Coupling discrete dislocation dynamics (DDD) to the finite element method (FEM) allows micromechanical tests to be simulated \cite{Groh2009}.
@@
 
+% TODO #48
 Finally, we ran a simple simulation where the differences between methods can be readily observed.
 
-\section{Results}
+\section{Results}\label{s:results}
 
-\begin{figure}[t]
+Isolated test cases were useful in order to gain insight into the differences between the numerical and analytical approaches.
+When the stress field on the surface element is highly symmetric, numerical integration works well; showing good convergence with increasing number of quadrature points.
+
+\Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5b$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 Gauss quadrature points $Q$, for all segment lengths tested.
+It also shows a very peculiar issue Gauss quadrature has when computing integrals of rational functions when the Gauss points are close poles/maximal values.
+This undesirable behaviour is observed in the case where $Q = 11$.
+Where the highest weighted Gauss node is closest to the point where $1/R_{a}$ is maximal, resulting in lower accuracy when compared to $Q = 2, 10$ in \cref{f:rel_err_perp_edge} (a) and (b).
+\begin{figure}
     \centering
@@
 
-Isolated test cases were useful in order to gain insight into the differences between the numerical and analytical approaches.
-When the stress field on the surface element is highly symmetric numerical integration works well; showing good convergence with increasing number of quadrature points.
-\Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5b$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 quadrature points, for all segment lengths tested.
-However, as stated in \cref{s:theory}, the limitations of Gauss quadrature are also evident.
-\Cref{f:rel_err_perp_edge,f:rel_err_par_edge} showcase the problem with numerical integration to compute integrals of rational functions close to a pole.
-The comparatively large relative errors with $Q = 11$, compared to fewer quadrature points, as the dislocation nears the element face makes it hard to globally minimise the error by picking a specific number of quadrature points while maintaining a feasible computational cost.
-
-Gauss quadrature fails to capture the $1/R_a$ nature of the stress tensor, especially when a segment is close to a heavily weighted quadrature point.
-When the dislocation node $\mathbf{x_{1}}$ is close to the surface element (see \cref{f:gauss_quad_test}), 11 Gauss points ($Q=11$) performs worse than with $Q=2$, as shown in \cref{f:rel_err_perp_edge} (a) and (b).
-This is because When $Q$ is odd a Gauss point is at the element center, as shown in \Cref{f:2d_gaussian_quad}, directly in front of the dislocation segment.
-
-The limitations of Gauss quadrature become evident when the dislocation line segment is parallel to a surface element.
+The limitations of Gauss quadrature become even more evident when the dislocation line segment is parallel to a surface element.
 \Cref{f:rel_err_par_edge} shows the relative errors for a parallel edge dislocation.
-In this configuration the forces due to a screw dislocations vanish as the stress field is antisymmetric.
-%
-\begin{figure}[t]
+\begin{figure}
     \centering
@@
 \end{figure}
-%
 In \cref{f:rel_err_par_edge}, we observe the relative errors decrease and then converge to $\sim 1$ as the distance grows larger.
-The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, which results in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim 1$ when done with limited precision.
-Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$.
-The absolute error \textit{always} decreases as the distance from the surface element increases, but absolute errors are not as useful tools of comparison.
+The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, resulting in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim 1$ when done with limited precision.
+Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$\footnote[1]{The absolute error \textit{always} decreases as the distance from the surface element increases, but absolute errors are not as useful tools of comparison as long as we are conscious of small artifacting from limited precision.}.
 However, when the segment is close to the surface, the relative errors are large ($\gg1$) unless using a large number of quadrature points, for example \cref{f:gauss_quad_test}(a) shows that $Q\geq100$ are required when the distance $x^1_z = 15b$.
+This figure backs up the earlier point regarding Gauss nodes close to maximal rational values, as $Q = 2$ performs significantly better than $Q = 10, 11, 100, 100$ at smaller distances from the surface.
+Generally, there is no best value of $Q$ other than very large.
 
-For a segment parallel to a surface, Gauss quadrature performs far worse than for a perpendicular segment, as shown in \cref{f:rel_err_par_edge}.
-This is because numerical quadrature is only accurate for integrating functions that can be approximated by polynomials.
-Whereas the dislocation stress field \cite{Cai2006} decays as $\mathcal{O}(1/R)$.
-This makes Gauss quadrature unsuitable as \cref{eq:gauss_leg_ddd_fem_force} fails to accurately capture the stress, which varies rapidly across the element surface for small $R$.
-The relevant components of the stress tensor for a perpendicular edge segment which is not penetrating the surface are shown in \cref{f:sigma_perp_edge}.
-The $\sigma_{xz}$ and $\sigma_{zz}$ components are antisymmetric and the resultant forces vanish which is captured when numerically integrating with small $Q$, while $\sigma_{yz}$ does not but can be accurately integrated with sufficiently large $Q$.
+From \cref{f:rel_err_perp_edge,f:rel_err_par_edge} one might be tempted to say that for a segment parallel to a surface, Gauss quadrature performs far worse than for a perpendicular one.
+However there is a further wrinkle in this problem: symmetry.
+To exemplify this we plot the relevant components of the stress tensor for the arrangement in \cref{f:gauss_quad_test}(a) we find \cref{f:sigma_perp_edge}.
+The $\sigma_{xz}$ and $\sigma_{zz}$ components are antisymmetric about the centre of the element.
+If we use Gauss quadrature on them, we sample equivalent but oppositely valued points that equally weighted, thus the sum vanishes.
+$\sigma_{yz}$ does not, but it can be accurately integrated with sufficiently large $Q$.
+If we were to move the dislocation off-centre such that the rotational anti-symmetry about the origin is broken, the errors would increase.
 
-\begin{figure}[t]
+\begin{figure}
     \centering
@@
 
-It is evident that symmetry plays a role in the accuracy of numerical integration.
-If a stress field has the appropriate symmetry, as in \cref{f:sigma_perp_edge}, Gauss quadrature will be accurate given enough quadrature points.
-However, when the segment is translated off-centre, this breaks the symmetry and the symmetric weighting of the Gauss quadrature scheme fails to accurately integrate the stress fields when the segment is close to the surface.
-The latter case is of course much more common in a simulation than the former, so in reality the errors between analytical and numerical solutions are larger than what is led on by these contrived cases.
-The error convergence with higher numbers of quadrature points is consistent with the findings of \cite{Queyreau}.
+Despite these being somewhat contrived examples that illustrate the failings of Gauss quadrature, problematic scenarios are commonly to show up in simulations.
+They are worse with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces and more permissive mobility functions.
+They are fairly localised given the $\mathcal{O}(1/R)$ decay but under unfortunate cirumstances, these spikes in the image forces result in unwarranted topological changes to the dislocation structure by causing segments to move in erroneous or erratic ways.
+Such changes to the dislocation structure tend to have large and cascading effects as simulations advance.
+Which is particularly deleterious when doing simulations with higher dislocation densities and/or where a large number of dislocations are close to the surface, such as nanoindentation simulations.
 
-The isolated tractions are only part of the story however, as they are used to calculate the image forces as a result of the boundary.
-We therefore also compare image forces calculated from numeric ($Q = 1$) tractions and analytic traction calculations affect the image forces to see the extent to which higher accuracy tractions affect the FE part of the simulation.
-To do so we compare the traction + FEM calculation to analytic solutions by \citet{head1953edge}.
+As stated in \cref{s:method}, tractions are used to calculate the image stresses resulting from the boundary conditions.
+We therefore also compare the differences in image stresses resulting from numeric ($Q = 1$) and analytic traction calculations and how they compare to the infinite-domain, singular expressions in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}\footnote{The first term in each equation corresponds to the real stresses, we can omit these to view the image stresses.}.
+
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxxEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxAeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxxAEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxNeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxxNEperp.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syyEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyAeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syyAEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyNeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syyNEperp.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxyEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyAeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxyAEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyNeperp}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxyNEperp.pdf}}
+    }
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, with $a = 10~b$ with coordinates $(26.3158,~ 500)~b$, i.e.
+the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
+Here $b = \lVert \bm{b} \rVert$.}
+    \label{f:head_vs_ana_vs_num_eperp}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxxEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxAepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxxAEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxNepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxxNEpar.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syyEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyAepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syyAEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyNepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syyNEpar.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxyEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyAepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxyAEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyNepar}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxyNEpar.pdf}}
+    }
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
+    \label{f:head_vs_ana_vs_num_epar}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxzscrew}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxzscrew.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxzAscrew}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxzAscrew.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxzNscrew}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/sxzNscrew.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:szyscrew}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syzscrew.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syzAscrew}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syzAscrew.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syzNscrew}]
+    {
+    {\includegraphics[width=0.3\linewidth]{images/syzNscrew.pdf}}
+    }
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
+    \label{f:head_vs_ana_vs_num_screw}
+\end{figure}
 
@@
 
-In a DDP simulation it is rare to find a dislocation segment so close to a quadrature point that the errors spike so dramatically.
+% In a DDP simulation it is rare to find a dislocation segment so close to a quadrature point that the errors spike so dramatically.
 However, numerical integration with small $Q$ produces noticeable errors over a wide range of distances and segment lengths.
@@
 
-It is worth noting that rotational perturbation required for the analytic solution to be non-singular when a dislocation segment is parallel to a surface element can introduce small erroneous force components if the rotation is too large.
+% It is worth noting that rotational perturbation required for the analytic solution to be non-singular when a dislocation segment is parallel to a surface element can introduce small erroneous force components if the rotation is too large.
 If the rotational perturbations were small enough and floating point arithmetic exact, these erroneous forces would cancel when averaged over two opposite rotations.
@@
 
-% TODO #23
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.7\linewidth]{images/load_disp.pdf}
-    \caption{Load-displacement curve.
+% % TODO #23
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=0.7\linewidth]{images/load_disp.pdf}
+%     \caption{Load-displacement curve.
 When the tractions are evaluated analytically the curve is less noisy compared to numerical integration.
 As expected the yield point remains the same in both cases.}
-    \label{f:load_disp_curve}
-\end{figure}
+%     \label{f:load_disp_curve}
+% \end{figure}
 
-The purpose of the cantilever simulation showed herein is not to be have an exactly physical when it comes to dislocation structure.
+% The purpose of the cantilever simulation showed herein is not to be have an exactly physical when it comes to dislocation structure.
 Our initial source sizes and structure are somewhat unphysical, i.e.
@@
 % TODO #22 
-A full discrete dislocation plasticity simulation of a microcantilever bend test demonstrates the benefits of using the analytic solution over numerical integration.
+% A full discrete dislocation plasticity simulation of a microcantilever bend test demonstrates the benefits of using the analytic solution over numerical integration.
 The FE nodal forces were evaluated using Gauss quadrature with a single integration point for one simulation, and analytical tractions for the other.
@@
 
-The inset in \cref{f:load_disp_curve} shows the yield point remains the same, but the reaction forces diverge from each other as the simulation progresses.
+% The inset in \cref{f:load_disp_curve} shows the yield point remains the same, but the reaction forces diverge from each other as the simulation progresses.
 It should be noted that the dislocation structure was unchanged and so the change in the mechanical response is due entirely to the accuracy of the force calculation.
@@
 
-The dislocation structure did not change much in either case.
+% The dislocation structure did not change much in either case.
 In fact, when looking at it from the zoom level of \cref{f:dln_struc}, they both appear identical.
@@
 
-% TODO #24
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.7\linewidth]{images/analytic_struct.pdf}
-    \caption{Final dislocation structure using analytic tractions.}
-    \label{f:dln_struc}
-\end{figure}
+% % TODO #24
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=0.7\linewidth]{images/analytic_struct.pdf}
+%     \caption{Final dislocation structure using analytic tractions.}
+%     \label{f:dln_struc}
+% \end{figure}
 
-There are a few things that determine whether the numerical solutions are good enough for a given problem.
+% There are a few things that determine whether the numerical solutions are good enough for a given problem.
 When primarily investigating larger scale features of a dislocation structure---such as larger scale investigation of dislocation forresting around inclusions---Gauss quadrature is quite suitable.

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m

@@ -201,91 +201,91 @@ for k = 1:2
     % Image stresses
     symbol = '\hat{\sigma}';
     % Head
-    [~, meanvalxx, stddevxx] = plotCountourfSigmaHat(X, Y, txx, x1, y1, orientationB, symbol, 'xx', '', 'x,~b', 'y,~b', '$\mu$', 15, doSave);
-    [~, meanvalyy, stddevyy] = plotCountourfSigmaHat(X, Y, tyy, x1, y1, orientationB, symbol, 'yy', '', 'x,~b', 'y,~b', '$\mu$', 15, doSave);
-    [~, meanvalxy, stddevxy] = plotCountourfSigmaHat(X, Y, txy, x1, y1, orientationB, symbol, 'xy', '', 'x,~b', 'y,~b', '$\mu$', 15, doSave);
+    [~, meanvalxx, stddevxx] = plotCountourfSigmaHat(X, Y, txx, x1, y1, orientationB, symbol, 'xx', '', 'x,~b', 'y,~b', '$\mu$', 22, doSave);
+    [~, meanvalyy, stddevyy] = plotCountourfSigmaHat(X, Y, tyy, x1, y1, orientationB, symbol, 'yy', '', 'x,~b', 'y,~b', '$\mu$', 22, doSave);
+    [~, meanvalxy, stddevxy] = plotCountourfSigmaHat(X, Y, txy, x1, y1, orientationB, symbol, 'xy', '', 'x,~b', 'y,~b', '$\mu$', 22, doSave);
     % FEM + Analytic tractions
-    plotCountourfSigmaHat(X, Y, sxxA, x1, y1, orientationB, symbol, 'xx', 'A', 'x,~b', 'y,~b', '$\mu$', 15, doSave, meanvalxx, stddevxx)
-    plotCountourfSigmaHat(X, Y, syyA, x1, y1, orientationB, symbol, 'yy', 'A', 'x,~b', 'y,~b', '$\mu$', 15, doSave, meanvalyy, stddevyy)
-    plotCountourfSigmaHat(X, Y, sxyA, x1, y1, orientationB, symbol, 'xy', 'A', 'x,~b', 'y,~b', '$\mu$', 15, doSave, meanvalxy, stddevxy)
[…]

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Added line plots, improved plots.

@@
     \begin{array}{l}
-        \nabla\cdot{\bm{\tilde{\sigma}}} = 0                  \\
-        \bm{\tilde{\sigma}} = \bm{C}:\tilde{\bm{\varepsilon}} \\
-        \tilde{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla\tilde{\bm{u}}+(\nabla\tilde{\bm{u}})^T\right)
+        \nabla\cdot{\vec{\tilde{\sigma}}} = 0                    \\
+        \vec{\tilde{\sigma}} = \vec{C}:\tilde{\vec{\varepsilon}} \\
+        \tilde{\vec{\varepsilon}}=\frac{1}{2}\left(\nabla\tilde{\vec{u}}+(\nabla\tilde{\vec{u}})^T\right)
     \end{array}
@@
     %
-     & \tilde{\bm{\sigma}}\cdot\bm{n} = \tilde{\bm{T}} \textrm{ on } S_T \\
+     & \tilde{\vec{\sigma}}\cdot\vec{n} = \tilde{\vec{T}} \textrm{ on } S_T \\
     %
@@
     \begin{array}{l}
-        \tilde{\bm{u}} = \tilde{\bm{U}} \quad t>0 \\
-        \tilde{\bm{u}} = \bm{0} \quad t=0
+        \tilde{\vec{u}} = \tilde{\vec{U}} \quad t>0 \\
+        \tilde{\vec{u}} = \vec{0} \quad t=0
         \label{eq:utildebc}
@@
 %
-As the dislocation fields do not vanish on $S$ the dislocations load the volume by generating tractions, $\tilde{\bm{T}}$, on $S_T$ and displacements, $\tilde{\bm{U}}$, on $S_U$ this additional loading deforms $V$ generating an additional ``image'' stress which the dislocations then feel.
+As the dislocation fields do not vanish on $S$ the dislocations load the volume by generating tractions, $\tilde{\vec{T}}$, on $S_T$ and displacements, $\tilde{\vec{U}}$, on $S_U$ this additional loading deforms $V$ generating an additional ``image'' stress which the dislocations then feel.
 Therefore corrective ($\hat{~}$) fields must be superimposed to satisfy the desired boundary conditions.
@@
     \begin{array}{l}
-        \nabla\cdot{\bm{\hat{\sigma}}} = 0                \\
-        \bm{\hat{\sigma}} = \bm{C}:\hat{\bm{\varepsilon}} \\
-        \hat{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla\hat{\bm{u}}+(\nabla\hat{\bm{u}})^{T}\right)
+        \nabla\cdot{\vec{\hat{\sigma}}} = 0                  \\
+        \vec{\hat{\sigma}} = \vec{C}:\hat{\vec{\varepsilon}} \\
+        \hat{\vec{\varepsilon}}=\frac{1}{2}\left(\nabla\hat{\vec{u}}+(\nabla\hat{\vec{u}})^{T}\right)
     \end{array}
@@
     %
-     & \hat{\bm{\sigma}}\cdot\bm{n} = \bm{T} - \tilde{\bm{T}} \textrm{ on } S_T\label{eq:thatbc} \\
+     & \hat{\vec{\sigma}}\cdot\vec{n} = \vec{T} - \tilde{\vec{T}} \textrm{ on } S_T\label{eq:thatbc} \\
     %
-     & \hat{\bm{u}} = \bm{U} - \tilde{\bm{U}} \textrm{ on } S_U \label{eq:uhatbc}
+     & \hat{\vec{u}} = \vec{U} - \tilde{\vec{U}} \textrm{ on } S_U \label{eq:uhatbc}
 \end{align}
@@
     \begin{array}{l}
-        \nabla\cdot\bm{\sigma}=\nabla\cdot\left(\bm{\hat{\sigma}} +\bm{\tilde{\sigma}}\right) = 0                                                         \\
-        \bm{\sigma} =\bm{\hat{\sigma}}+\bm{\tilde{\sigma}}= \bm{C}:\left(\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}\right)=\bm{C}:{\bm{\varepsilon}} \\
-        \bm{\varepsilon}=\hat{\bm{\varepsilon}}+\tilde{\bm{\varepsilon}}=\frac{1}{2}\left(\nabla(\hat{\bm{u}}+\tilde{\bm{u}})+\left(\nabla(\hat{\bm{u}}+\tilde{\bm{u}})\right)^T\right) =\frac{1}{2}\left(\nabla\bm{u}+(\nabla\bm{u})^{T}\right)
+        \nabla\cdot\vec{\sigma}=\nabla\cdot\left(\vec{\hat{\sigma}} +\vec{\tilde{\sigma}}\right) = 0                                                              \\
+        \vec{\sigma} =\vec{\hat{\sigma}}+\vec{\tilde{\sigma}}= \vec{C}:\left(\hat{\vec{\varepsilon}}+\tilde{\vec{\varepsilon}}\right)=\vec{C}:{\vec{\varepsilon}} \\
+        \vec{\varepsilon}=\hat{\vec{\varepsilon}}+\tilde{\vec{\varepsilon}}=\frac{1}{2}\left(\nabla(\hat{\vec{u}}+\tilde{\vec{u}})+\left(\nabla(\hat{\vec{u}}+\tilde{\vec{u}})\right)^T\right) =\frac{1}{2}\left(\nabla\vec{u}+(\nabla\vec{u})^{T}\right)
     \end{array}
@@
     %
-     & \bm{\sigma}\cdot\bm{n} = \bm{T}  \textrm{ on } S_T \\
+     & \vec{\sigma}\cdot\vec{n} = \vec{T}  \textrm{ on } S_T \\
     %
@@
     \begin{array}{l}
-        \bm{u} = \bm{U} \quad t>0 \\
-        \bm{u} = \bm{0} \quad t=0
+        \vec{u} = \vec{U} \quad t>0 \\
+        \vec{u} = \vec{0} \quad t=0
     \end{array}
@@
 This in turn will increase the computational cost.
-In order to simulate polycrystalline or composite materials using superposition requires methods to accurately evaluate both $\tilde{\bm{U}}$ and $\tilde{\bm{T}}$.
+In order to simulate polycrystalline or composite materials using superposition requires methods to accurately evaluate both $\tilde{\vec{U}}$ and $\tilde{\vec{T}}$.
 The displacements can be evaluated analytically \cite{ddd_disp} and this paper investigates the evaluation of the dislocation tractions analytically.
@@
 \begin{align}
-    \vec{F}_{a} = \int_{S_{e}} \left[\tilde{\bm{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,,
+    \vec{F}_{a} = \int_{S_{e}} \left[\tilde{\vec{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,,
     \label{eq:ddd_fem_force}
@@
 \end{subequations}
-The case where the $\bm{b}$ lies parallel to the surface and positive $b$ means it points in the positive $y$ direction, is found in \cref{eq:imageStressAnalyticEdge2},
+The case where the $\vec{b}$ lies parallel to the surface and positive $b$ means it points in the positive $y$ direction, is found in \cref{eq:imageStressAnalyticEdge2},
 \begin{subequations}
@@
 Screw dislocations are markedly simpler, as only the shear components are non-zero.
-Here $\bm{b} = \bm{l}$ and therefore positive $b$ means it points in the positive $z$ direction (away from the observer) \cref{eq:imageStressAnalyticScrew},
+Here $\vec{b} = \vec{l}$ and therefore positive $b$ means it points in the positive $z$ direction (away from the observer) \cref{eq:imageStressAnalyticScrew},
 \begin{subequations}
@@
     \caption{Dislocation parallel to a surface described by the line $x = 0$ (the $yz$-plane in 3D), where the dislocation coordinates are $(a,~c)$, looking down the $xy$-plane where the $x$-axis is horizontal and the $y$-axis vertical.
-(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000~ \vec{b}$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
-(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\bm{b}_\textrm{e1}$ perpendicular to the surface and pointing in the positive $x$ direction, $\bm{b}_\textrm{e2}$ parallel to the surface and pointing in the positive $y$ direction; and the screw Burgers vector parallel to the surface and pointing in the line direction as posited in \cite{hirth1983theory}.}
+(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000~ \lVert \vec{b} \rVert$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
+(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ and the screw Burgers vector $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ as posited in \cite{hirth1983theory}.}
     \label{f:headvstractionfem}
@@
     \caption{Log-log plot of the relative error as a function of distance from the surface element for a parallel edge dislocation (\cref{f:gauss_quad_test}b).
-Burgers vector, $\bm{b} = [0 1 0]$, line direction, $\bm{l} = [1 0 0]$, dislocation core and surface element parameters are the same as \cref{f:rel_err_perp_edge}.
+Burgers vector, $\vec{b} = [0 1 0]$, line direction, $\vec{l} = [1 0 0]$, dislocation core and surface element parameters are the same as \cref{f:rel_err_perp_edge}.
 The dislocation length is fixed to $10^{6}\, b,\, x\in\left[-0.5\times10^{6},\, 0.5\times10^{6} \right]$ and bisects the surface element along the $[1 0 0]$ direction.
@@
     \centering
-    \subfloat[$\hat{\sigma}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxeperp}]
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxAeperp}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxNeperp}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNeperp}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyeperp}]
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:syyeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyAeperp}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:syyAeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyNeperp}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:syyNeperp}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyeperp}]
+    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:sxyeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyAeperp}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$.\label{sf:sxyAeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyNeperp}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$.\label{sf:sxyNeperp}]
     {
@@
 the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
-Here $b = \lVert \bm{b} \rVert$.}
+Here $b = \lVert \vec{b} \rVert \equiv 1$.}
     \label{f:head_vs_ana_vs_num_eperp}
@@
 
+Note the sign inversion just to the right of the dislocation in \cref{sf:sxxNepar} compared to \cref{sf:sxxepar,sf:sxxAepar}.
+Stresses like those can lead to dislocations being repelled by surfaces and make the dislocation topology more complex than it should, potentially leading to slowdown or gridlock later in the simulation.
 \begin{figure}
     \centering
-    \subfloat[$\hat{\sigma}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxepar}]
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxAepar}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxxNepar}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNepar}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyepar}]
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:syyepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyAepar}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:syyAepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syyNepar}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:syyNepar}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyepar}]
+    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:sxyepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyAepar}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$.\label{sf:sxyAepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxyNepar}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$.\label{sf:sxyNepar}]
     {
@@
     \centering
-    \subfloat[$\hat{\sigma}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxzscrew}]
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxzscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxzAscrew}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxzAscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$, $\bm{b}_{\textrm{e1}}$.\label{sf:sxzNscrew}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxzNscrew}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:szyscrew}]
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:szyscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syzAscrew}]
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:syzAscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$, $\bm{b}_{\textrm{e1}}$.\label{sf:syzNscrew}]
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:syzNscrew}]
     {
@@
     }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
     \label{f:head_vs_ana_vs_num_screw}
@@
 
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxperp}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:line_syyeperp}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_syyEperp.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:line_sxyeperp}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxyEperp.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_sxxepar}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:line_syyepar}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_syyEpar.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:line_sxyepar}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxyEpar.pdf}}
+    }
+
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_sxzscrew}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxzscrew.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:line_syzscrew}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_syzscrew.pdf}}
+    }
+    \caption{Line plots of the image stresses at $x = 52.6316\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
+The line corresponds to the first set of nodes away from the boundary at $x = 0$.
+(a) to (c) correspond to $\vec{b}_{\textrm{e1}}$, (d) to (f) $\vec{b}_{\textrm{e2}}$ and (g) to (h) to $\vec{b}_{\textrm{s}}$.}
+    \label{f:head_vs_ana_vs_num_eperp}
+\end{figure}
 % TODO #28

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m

@@ -201,69 +201,69 @@ for k = 1:2
     % Image stresses
     symbol = '\hat{\sigma}';
     % Head
-    [~, meanvalxx, stddevxx] = plotCountourfSigmaHat(X, Y, txx, x1, y1, orientationB, symbol, 'xx', '', 'x,~b', 'y,~b', '$\mu$', 22, doSave);
-    [~, meanvalyy, stddevyy] = plotCountourfSigmaHat(X, Y, tyy, x1, y1, orientationB, symbol, 'yy', '', 'x,~b', 'y,~b', '$\mu$', 22, doSave);
-    [~, meanvalxy, stddevxy] = plotCountourfSigmaHat(X, Y, txy, x1, y1, orientationB, symbol, 'xy', '', 'x,~b', 'y,~b', '$\mu$', 22, doSave);
+    [~, meanvalxx, stddevxx] = plotCountourfSigmaHat(X, Y, txx, x1, y1, orientationB, symbol, 'xx', '', 'x,~b', 'y,~b', '$\mu$', 30, doSave);
+    [~, meanvalyy, stddevyy] = plotCountourfSigmaHat(X, Y, tyy, x1, y1, orientationB, symbol, 'yy', '', 'x,~b', 'y,~b', '$\mu$', 30, doSave);
+    [~, meanvalxy, stddevxy] = plotCountourfSigmaHat(X, Y, txy, x1, y1, orientationB, symbol, 'xy', '', 'x,~b', 'y,~b', '$\mu$', 30, doSave);
     % FEM + Analytic tractions
-    plotCountourfSigmaHat(X, Y, sxxA, x1, y1, orientationB, symbol, 'xx', 'A', 'x,~b', 'y,~b', '$\mu$', 22, doSave, meanvalxx, stddevxx)
-    plotCountourfSigmaHat(X, Y, syyA, x1, y1, orientationB, symbol, 'yy', 'A', 'x,~b', 'y,~b', '$\mu$', 22, doSave, meanvalyy, stddevyy)
-    plotCountourfSigmaHat(X, Y, sxyA, x1, y1, orientationB, symbol, 'xy', 'A', 'x,~b', 'y,~b', '$\mu$', 22, doSave, meanvalxy, stddevxy)
[…]

### 2020-11-12 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Gave burgers vector definitions in text.

@@
 infinite-domain, singular image stresses found in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}.
+We use three test cases, two edge dislocations and one screw, all of which have line direction $\vec{l} = [0\, 0\, 1]$ with Burgers vectors $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ \cite{head1953edge}, and $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ \cite{hirth1983theory}.
 \begin{figure}

### 2020-11-13 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Double label.
Fleshing out more of the first draft.

@@
 Evaluating \cref{eq:ddd_fem_force} in the parent element and mapping to the real element gives the force on node $a$,
-%
 \begin{align}
@@
 \end{align}
-%
 Where the sum is over the $Q$ quadrature points and $J_{ij}=dx_{i}/ds_{j}$ is the element Jacobian defining the transformation from $(s_1,\,s_2) \mapsto (x,\,y)$; as the real element is rectangular with surface area $S_e$, $\det(\mtx{J})=S_e/4$.
 \Cref{f:2d_gaussian_quad} contains examples of how the Gauss points are distributed on the surface.
-%
-\begin{figure}[htb]
+\begin{figure}
     \centering
@@
 \end{figure}
-%        
-\begin{figure}[htb]
+\begin{figure}
     \centering
@@
 \end{figure}
-%
-
 \Cref{eq:ddd_fem_force} is actually a triple vector integral.
@@
 Using the isotropic Burgers vector distribution proposed in \cite{Cai2006}, the dyadic form of the stress tensor produced by a straight finite dislocation segment bounded by nodes at $\mathbf{x_1}$ and $\mathbf{x_2}$ is \cite{Queyreau},
-%
 \begin{align}
@@
 \end{align}
-where
+where,
 \begin{align}
@@
 \end{align}
-%
 The vectors $\vec{p}$ and $\vec{q}$ are aligned with the edges of the rectangular finite element, $\vec{n} = \vec{p} \times \vec{q}$ is the element surface normal (pointing away from the dislocation), and $\vec{l}$ is parallel to the dislocation line segment as shown in \cref{f:force_lin_rect}.
-Then (provided $\vec{l}$ is not parallel to $\vec{p}$ or $\vec{q}$) $\vec{R}$ can be expressed in terms of $(\vec{l},~\vec{p},~\vec{q})$ with coefficients
-%
+Then (provided $\vec{l}$ is not parallel to $\vec{p}$ or $\vec{q}$) $\vec{R}$ can be expressed in terms of $(\vec{l},~\vec{p},~\vec{q})$ with coefficients,
 \begin{align}
@@
 \end{align}
-%
+
 Substituting \cref{eq:stress} and \cref{eq:shape_function} into \cref{eq:ddd_fem_force} yields four long and messy equations (one for each FE node) that were elegantly solved by \citet{Queyreau} by utilising the fact that the triple integrals all had the form,
-%
 \begin{align}
@@
 \end{align}
-%
+
 Using partial differentiation and integration by parts, they found a series of recurrence relations that lead to double and single integrals with a similar form to equation (\cref{eq:triple_int}).
@@
 \end{subequations}
+
 The case where the $\vec{b}$ lies parallel to the surface and positive $b$ means it points in the positive $y$ direction, is found in \cref{eq:imageStressAnalyticEdge2},
@@
 \end{subequations}
+
 Screw dislocations are markedly simpler, as only the shear components are non-zero.
@@
 \end{subequations}
+
 In every case, the constant $D$ is defined by \cref{eq:Dconstant}
@@
 An example of what this looks like in terms of forces can be seen in \cref{f:rotate} (we removed the singularity to keep the graph smooth).
-\begin{figure}[htb]
+\begin{figure}
     \centering
@@
 %
-\begin{figure}[htb]
+\begin{figure}
     \centering
@@
 
-The following algorithm illustrates how the total force on each node is obtained. The resulting force vector is later used in \cref{eq:thatbc} as $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
+The following algorithm illustrates how the total force on each node is obtained.
 \begin{algorithm}
@@
 
-After the tractions have been calculated, they are used by the FE solver to generate the corresponding image stresses.
-\Cref{f:headvstractionfem} shows the system we used to compare the image stresses calculated by our FE solver using numeric tractions v.s.
+The resulting force vector is later used in \cref{eq:thatbc} as $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
+\Cref{f:headvstractionfem} shows the simple system we used to compare the image stresses calculated by our FE solver using numeric tractions v.s.
 analytic tractions v.s.
@@
     \caption{Dislocation parallel to a surface described by the line $x = 0$ (the $yz$-plane in 3D), where the dislocation coordinates are $(a,~c)$, looking down the $xy$-plane where the $x$-axis is horizontal and the $y$-axis vertical.
-(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000~ \lVert \vec{b} \rVert$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
+(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000\, \lVert \vec{b} \rVert$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
 (b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ and the screw Burgers vector $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ as posited in \cite{hirth1983theory}.}
@@
 \end{figure}
+The slices we took for our contour plots in \cref{s:results} taken from the midpoint of the $z$-axis to ensure minimal interferance from the $xy$-plane boundaries at $z=0,\, 1000\,b$.
 
@@
 
-\Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5b$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 Gauss quadrature points $Q$, for all segment lengths tested.
+\Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5\, b$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 Gauss quadrature points $Q$, for all segment lengths tested.
 It also shows a very peculiar issue Gauss quadrature has when computing integrals of rational functions when the Gauss points are close poles/maximal values.
@@
 If we were to move the dislocation off-centre such that the rotational anti-symmetry about the origin is broken, the errors would increase.
-
 \begin{figure}
@@
 
-Despite these being somewhat contrived examples that illustrate the failings of Gauss quadrature, problematic scenarios are commonly to show up in simulations.
-They are worse with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces and more permissive mobility functions.
-They are fairly localised given the $\mathcal{O}(1/R)$ decay but under unfortunate cirumstances, these spikes in the image forces result in unwarranted topological changes to the dislocation structure by causing segments to move in erroneous or erratic ways.
+Despite these being artificially ideal examples that illustrate the failings of Gauss quadrature, other problematic scenarios commonly to show up in simulations.
+The problems tend to worsen with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces and more permissive mobility functions.
+Despite the highly localised nature of these large errors, the $\mathcal{O}(1/R)$ decay rate and chaotic nature of dislocation dynamics, means they often result in unwarranted topological changes.
 Such changes to the dislocation structure tend to have large and cascading effects as simulations advance.
@@
 As stated in \cref{s:method}, tractions are used to calculate the image stresses resulting from the boundary conditions.
-We therefore also compare the differences in image stresses resulting from numeric ($Q = 1$) and analytic traction calculations and how they compare to the infinite-domain, singular expressions in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}\footnote{The first term in each equation corresponds to the real stresses, we can omit these to view the image stresses.}.
+We therefore compare the differences in image stresses resulting from numeric ($Q = 1$) and analytic traction calculations of both our implementations and how they compare to the infinite-domain, singular expressions in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}\footnote{Since the first term in each equation corresponds to the real stresses, we omit them to view the image stresses.}.
+The stress field comparisons for all three cases are found in \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw}, where the dislocation is denoted by a white dot.
 
+\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, a $\textrm{A}$ superscript are the stresses derived from analytic tractions and $\textrm{N}$ for those coming from numeric ones.
+The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}}$.
+It is clear edge effects play a role in the generated stresses.
+All three components have notable differences from the infinite-domain solutions resulting from the finite constraints.
+Regardless, the overall shape of the isolines is similar in all three solutions for corresponding stress components, particularly $\hat{\sigma}_{yy}$.
+The lobes of $\hat{\sigma}_{xx}$ for analytic and numeric tractions are deformed by the displacement boundary conditions on all surfaces other than $x = 0\, b$, where tractions are calculated.
+The effect is most dramatic when looking near the top and bottom of the domain, where the final isolines flare towards the traction surface.
+The shear stresses $\hat{\sigma}_{xy}$ are also somewhat different, with similar flaring.
+However, as they radiate in the $x$-direction, the deviations away from the infinite-domain solutions flare away from the $x = 1000\, b$ surface.
+That said, all stress fields calculated from analytic and numeric tractions look fairly similar for $\vec{b} = \vec{b}_{\textrm{e1}}$.
 \begin{figure}
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxxEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEperp.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxxAEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEperp.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxxNEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEperp.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syyEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyEperp.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syyAEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyAEperp.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syyNEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyNEperp.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxyEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyEperp.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxyAEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyAEperp.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxyNEperp.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyNEperp.pdf}}
     }
@@
 
-Note the sign inversion just to the right of the dislocation in \cref{sf:sxxNepar} compared to \cref{sf:sxxepar,sf:sxxAepar}.
-Stresses like those can lead to dislocations being repelled by surfaces and make the dislocation topology more complex than it should, potentially leading to slowdown or gridlock later in the simulation.
+Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}}$ in \cref{f:head_vs_ana_vs_num_epar}.
+Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions.
+If we look at the neighbourhood of the dislocation, we will find a sign inversion as well as a drastically different isosurface shape, where the isolines are not merely deformed, they are fundamentally different when calculated with numeric tractions.
+Stresses like those can lead to dislocations problems, particularly if it just so happens that the sign inversion also comes with an increased force magnitude, something that is possible judging from \cref{f:rel_err_par_edge,f:rel_err_par_edge}.
+Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive.
+It is as absurd as a ship inverts the Archimidean principle.
+The other two stress fields $\hat{\sigma}_{yy}$, $\hat{\sigma}_{xy}$ follow similar trends to what we have already observed, where the isolines get squashed and flair towards the traction free surface.
 \begin{figure}
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxxEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxxAEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxxNEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syyEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syyAEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyAEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syyNEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyNEpar.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxyEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxyAEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyAEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxyNEpar.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyNEpar.pdf}}
     }
@@
 
+Perhaps the most evident deformation resulting from the displacement boundaries can be seen when $\vec{b} = \vec{b}_{\textrm{s}}$ in \cref{f:head_vs_ana_vs_num_screw}, where the lobes of the isolines are highly deformed when compared to the infinite-domain solutions.
+The familiar lobes look very different, but both analytic and numeric tractions yield fairly similar fields.
 \begin{figure}
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxzscrew.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzscrew.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxzAscrew.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzAscrew.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxzNscrew.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzNscrew.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syzscrew.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzscrew.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syzAscrew.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzAscrew.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syzNscrew.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzNscrew.pdf}}
     }
@@
 
+From \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw} it seems
+like both analytic and numeric tractions are both appropriate in most cases.
+At least at these scales, there is only one instance where numeric tractions yield very incorrect results.
+Although these can have significant consequences later in a simulation's runtime, and particularly in simulations where dislocations regularly come into close contact with surfaces.
+
+It is also worth looking at the stress fields with a finer lens.
+\Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e.
+through the line $x = 52.6316\, b$.
+\Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$.
+Here the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in the stresses.
+In general, the non-singular formulation smoothes out the stress line plots.
+However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions.
+Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in every case.
 \begin{figure}
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:line_syyeperp}]
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:line_sxyeperp}]
+    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyeperp}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_sxxepar}]
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:line_syyepar}]
+    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:line_sxyepar}]
+    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyepar}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_sxzscrew}]
+    \subfloat[$\hat{\sigma}_{xz}$.\label{sf:line_sxzscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:line_syzscrew}]
+    \subfloat[$\hat{\sigma}_{yz}$.\label{sf:line_syzscrew}]
     {
@@
     \caption{Line plots of the image stresses at $x = 52.6316\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
-The line corresponds to the first set of nodes away from the boundary at $x = 0$.
-(a) to (c) correspond to $\vec{b}_{\textrm{e1}}$, (d) to (f) $\vec{b}_{\textrm{e2}}$ and (g) to (h) to $\vec{b}_{\textrm{s}}$.}
-    \label{f:head_vs_ana_vs_num_eperp}
+The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$.
+(a) to (c) correspond to $\vec{b} = \vec{b}_{\textrm{e1}}$, (d) to (f) $\vec{b} = \vec{b}_{\textrm{e2}}$ and (g) to (h) to $\vec{b} = \vec{b}_{\textrm{s}}$.}
+    \label{f:line_head_vs_ana_vs_num}
 \end{figure}
+
+For completeness, we also show a few examples of line plots and stress fields as dislocations move further away from the traction surface.
+As it can be observed, both analytic and numeric tractions converge to similar shapes to each other, which is to be expected.
+
+This does not mean numeric tractions are useless, in fact, they mostly work quite well.
+However, the impact their inherent numerical instability can be quite large.
+For us, analytic tractions despite being approximately an order of magnitude slower than numerically calculated tractions with $Q = 1$ \cite{Queyreau} (our tests agree with their findings), yield more stable and ultimately faster simulations.
+Even simple simulations are typically faster when using analytic tractions over numeric ones.
+The margin grows the more complex the simulation and the further each simulation gets.
+It's all down to better behaved segments at or near surfaces.
+As such, we cannot recommend using numeric tractions when analytic ones are available.
+The losses in computational speed that result from moving from one to the other are more than made up for by the fewer topological operations, fewer generated segments, and more accurate velocities.
+All of which result in fewer calculations of segment-segment interactions, fewer collisions, larger timesteps and ultimately cleaner simulations that run into fewer snags along the way.
+
+% Add line plot for a dislocation further away from the edge.
 % TODO #28

### 2020-11-13 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m

@@ -196,7 +196,7 @@ for k = 1:2
         tyyPar = tyy;
         txyPar = txy;
     end
-
+    
     % Edge
     % Image stresses
     symbol = '\hat{\sigma}';
@@ -286,7 +286,10 @@ for k = 1:2
 %     plotCountourfSigmaHat(X, Y, (sxxN + sxxFP) - (txxT), x1, y1, orientationB, symbol, 'xx', '$\Delta$N', 'x,~b', 'y,~b', '$\mu$', 30, doSave)
 %     plotCountourfSigmaHat(X, Y, (syyN + syyFP) - (tyyT), x1, y1, orientationB, symbol, 'yy', '$\Delta$N', 'x,~b', 'y,~b', '$\mu$', 30, doSave)
 %     plotCountourfSigmaHat(X, Y, (sxyN + sxyFP) - (txyT), x1, y1, orientationB, symbol, 'xy', '$\Delta$N', 'x,~b', 'y,~b', '$\mu$', 30, doSave)
+
 end
+
+%%
 
 % Screw
 close all
@@ -445,7 +448,7 @@ plot(linspace(x(2), x(2), j), y, 'LineWidth', 2, 'LineStyle', '--')
 hold off
 set(gcf(), 'Units', 'Inches');
 pos = get(gcf(), 'Position');
-set(gcf(), 'PaperPositionMode', 'Auto', 'PaperUnits', 'Inches', 'PaperSize', [pos(3), pos(4)])
+set(gcf(), 'PaperPositionMode', 'Auto', 'PaperUnits', 'Inches', 'PaperSize', [pos(3)+pos(3)*0.1, pos(4)])
 print(gcf(), sprintf('./paper/images/contourLine.pdf'), '-dpdf', '-r0')
 % plotCountourfSigmaHat(X, Y, tyz, x1, y1, orientationB, symbol, 'yz', '', 'x,~b', 'y,~b', '$\mu$', 30, doSave)
 % hold on
@@ -478,7 +481,7 @@ function fig = linePlot(analytic, numeric, head, orientationB, stress, component
         name = erase(sprintf('line_s%s%s', component, orientationB), ["\", "$"]);
         set(fig, 'Units', 'Inches');
         pos = get(fig, 'Position');
-        set(fig, 'PaperPositionMode', 'Auto', 'PaperUnits', 'Inches', 'PaperSize', [pos(3), pos(4)])
[…]

### 2020-11-18 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Added images for dislocation further away from surface Fixes #24 #28 #38

@@
 
-For completeness, we also show a few examples of line plots and stress fields as dislocations move further away from the traction surface.
-As it can be observed, both analytic and numeric tractions converge to similar shapes to each other, which is to be expected.
+We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $26.3158\, b$ (centre of the first element) to $500\, b$ (centre of the 10th element).
+The line plots are taken from the closest set of nodes in the positive $x$-direction i.e.
+at $x = 52.6316\, 526.3158\, b$.
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar2}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar2.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar2}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar2.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:sxxNepar2}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar2.pdf}}
+    }
 
-This does not mean numeric tractions are useless, in fact, they mostly work quite well.
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar11}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar11.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar11}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar11.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNepar11}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar11.pdf}}
+    }
+
+    \subfloat[$\sigma_{xx}$.\label{sf:sxxepartot2}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot2.pdf}}
+    }~
+    \subfloat[$\sigma^\textrm{A}_{x}$.\label{sf:sxxAepartot2}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot2.pdf}}
+    }~
+    \subfloat[$\sigma^\textrm{N}_{xx}$.\label{sf:sxxNepartot2}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot2.pdf}}
+    }
+
+    \subfloat[$\sigma_{xx}$.\label{sf:sxxepartot11}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot11.pdf}}
+    }~
+    \subfloat[$\sigma^\textrm{A}_{xx}$.\label{sf:sxxAepartot11}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot11.pdf}}
+    }~
+    \subfloat[$\sigma^\textrm{N}_{xx}$.\label{sf:sxxNepartot11}]
+    {
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot11.pdf}}
+    }
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$.
+(a) to (c) and (g) to (i) at $(26.3158\,, 500)\, b$; (d) to (f) and (j) to (l) at $(500\,, 500)\, b$.
+(a) to (g) image stresses; (g) to (l) total stresses.}
+    \label{f:head_vs_ana_vs_num_epar2to11}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar2}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar2.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_syyepar11}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar11.pdf}}
+    }
+
+    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot2}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot2.pdf}}
+    }~
+    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot11}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot11.pdf}}
+    }
+
+    \caption{Line plots corresponding to \cref{f:head_vs_ana_vs_num_epar2to11}.
+(a) and (c) are of image stresses; (b) and (d) are of total stresses.
+(a) and (b) are of a dislocation at $(26.3158,\, 500)\, b$, taken along the line $x = 52.6316\, b$.
+(b) and (d) are of a dislocation at $(500,\, 500)\, b$ taken along the line $x = 526.3158\, b$.}
+    \label{f:line_head_vs_ana_vs_num_epar2to11}
+\end{figure}
+From the line plots, it can be observed that both analytic and numeric tractions converge to similar shapes to each other, which is to be expected.
+However it also becomes clear that the infinite-domain solution is not totally accurate for image stresses in finite domains due to edge effects.
+However, the glaring issue is that total stresses for each solution are significantly different as dislocations near the surface.
+The instability of Gauss quadrature when integrating rational functions tends to produce values that are outside the range of the infinite-domain solution, as well as being less smooth than the two other solutions.
+
+As expected, all solutions converge as the distance from the dislocation to surface increases because the magnitude of the real stresses increases in relation to that of the image stresses\footnote{The image stress components of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2} are reflections about the line $x=0$ plus a corrective term that decays faster than the reflection term.
+In \cref{eq:imageStressAnalyticScrew}, the image term is a reflection about the line $x=0$.
+Therefore in both cases, as the dislocation moves away from the surface, the real stresses get relatively larger.}.
+
+In order to show the effects numerical tractions have on simulations, we ran a very simple cantilever bending simulation where the only difference was the traction calculation method.
+A very simple yet illustrative qualitative example is to produce a scatter plot of the numerically calculated tractions vs analytically calculated tractions at any time during the simulation.
+To obviate the problem even more, it helps making the axes proportional.
+What is observed in practically every case, is a positive correlation (though as we have seen in \cref{sf:sxxepar,sf:sxxAepar,sf:sxxNepar}, numerical tractions can produce sign inversions under specific conditions), but the axis that represents the numerically calculated tractions will be visually larger, as numeric tractions produce more extreme values.
+Statistically speaking, the closer the $R$-value is to 1 and the closer a linear fit is to $y=x$, the more accurate numerical tractions are for any given moment in a simulation.
+We have yet to find a single example where this happens.
+Furthermore, the chaotic nature of dislocation dynamics means that slight deviations will yield noticeably different results for the same starting conditions.
+
+This does not mean numeric tractions are useless, in fact, thethiny mostly work quite well.
 However, the impact their inherent numerical instability can be quite large.

### 2020-11-18 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m

@@ -525,7 +525,7 @@ for node = [2, 5, 11, 18]
     
     [txx, tyy, txy] = imageStressAnalyticEdgePar(MU, b, NU, X, Y, x1, y1);
     [txxFP, tyyFP, txyFP] = FPStressAnalyticEdgePar(MU, b, NU, X, Y, x1, y1);
-    orientationB = 'EparQuarter';
+    orientationB = sprintf('Epar%d', node);
     
     sxxApar = sxxA;
     syyApar = syyA;
@@ -555,7 +555,6 @@ for node = [2, 5, 11, 18]
     plotCountourfSigmaHat(X, Y, syyN, x1, y1, orientationB, symbol, 'yy', 'N', 'x,~b', 'y,~b', '$\mu$', 30, doSave, meanvalyy, stddevyy)
     plotCountourfSigmaHat(X, Y, sxyN, x1, y1, orientationB, symbol, 'xy', 'N', 'x,~b', 'y,~b', '$\mu$', 30, doSave, meanvalxy, stddevxy)
     
-    orientationB = sprintf('Epar%d', node);
     linePlot(sxxApar(:, node), sxxNpar(:, node), txxPar(:, node), orientationB, symbol, 'xx', 'Grid Point', '$\mu$', 30, doSave)
     linePlot(syyApar(:, node), syyNpar(:, node), tyyPar(:, node), orientationB, symbol, 'yy', 'Grid Point', '$\mu$', 30, doSave)
     linePlot(sxyApar(:, node), sxyNpar(:, node), txyPar(:, node), orientationB, symbol, 'xy', 'Grid Point', '$\mu$', 30, doSave)
@@ -565,6 +564,7 @@ for node = [2, 5, 11, 18]
     % Total stresses
     symbol = '\sigma';
     % Head
+    orientationB = sprintf('EparTot%d', node);
     [~, meanvalxx, stddevxx] = plotCountourfSigmaHat(X, Y, txx+sxxFP, x1, y1, orientationB, symbol, 'xx', '', 'x,~b', 'y,~b', '$\mu$', 30, doSave);
     [~, meanvalyy, stddevyy] = plotCountourfSigmaHat(X, Y, tyy+syyFP, x1, y1, orientationB, symbol, 'yy', '', 'x,~b', 'y,~b', '$\mu$', 30, doSave);
[…]

### 2020-11-18 input/hcp/Zr600KFRvac2c.m
Updated architecture to enable increased generalisations
Semi-generalised FEM structure, organised several files, and enabled modular inputs for cuboid geometry and time-dependent boundary conditions.

This code has not been tested and is still a work in progress.

@@ -1,0 +1,752 @@
+%% Input file created by Daniel Hortelano Roig (17/07/2020) %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Sections are the following:
+% 0) SIMULATION META-INFORMATION
+% 1) MATERIAL CONSTANTS
+% 2) SOURCE GENERATION PARAMETERS
+% 3) FEM PARAMETERS
+% 4) DDLab PARAMETERS
+%       - Meshing
+%       - Integrator
+%       - Simulation time
+%       - Plotting
+%       - Mobility module
+%       - Dislocation nodes (rn) and segments (links)
+% 5) PRINT INFORMATION
+% 6) REFERENCES
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+clear all
+dbstop if error % Applies debugging breakpoint instead of error
+
+
+
+
+
+%% SIMULATION META-INFORMATION %%
+
+
+%%% Input name
+
+INPUTNAME = mfilename;
+
+%%% MATLAB version year
+
+% Release version of MATLAB client currently running:
+MATLABrelease = ver('MATLAB').Release;
+
+%%% Add EasyDD subfolders to MATLAB path
+
+% Main 'EasyDD' folder:
+mainpath = '../../';
+addpath(mainpath);
+
+% Subprocesses folders:
+addpath([mainpath 'Mobility']); % Mobility laws
+addpath([mainpath 'Integrator']); % Time integrators
+
+% Functions designed for use in the input file:
+addpath([mainpath 'Inputs/HCP/InputFunctions']);
+
+% Input figures:
+%addpath([mainpath 'Inputs/HCP/Figures']);
+
+% Output figures:
+frameext = '.jpg'; % File extension of saved frames
+movieext = '.mp4'; % File extension of saved movies
+outputspath = append('Outputs/',INPUTNAME,'/'); % Path to saved figures
+if ~exist([mainpath outputspath], 'dir')
+       mkdir([mainpath outputspath]);
+end
[…]

### 2020-11-18 input/hcp/Zr600KFRvac2d.m

@@ -1,0 +1,752 @@
+%% Input file created by Daniel Hortelano Roig (17/07/2020) %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Sections are the following:
+% 0) SIMULATION META-INFORMATION
+% 1) MATERIAL CONSTANTS
+% 2) SOURCE GENERATION PARAMETERS
+% 3) FEM PARAMETERS
+% 4) DDLab PARAMETERS
+%       - Meshing
+%       - Integrator
+%       - Simulation time
+%       - Plotting
+%       - Mobility module
+%       - Dislocation nodes (rn) and segments (links)
+% 5) PRINT INFORMATION
+% 6) REFERENCES
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+clear all
+dbstop if error % Applies debugging breakpoint instead of error
+
+
+
+
+
+%% SIMULATION META-INFORMATION %%
+
+
+%%% Input name
+
+INPUTNAME = mfilename;
+
+%%% MATLAB version year
+
+% Release version of MATLAB client currently running:
+MATLABrelease = ver('MATLAB').Release; % Do this to reduce overhead later
+
+%%% Add EasyDD subfolders to MATLAB path
+
+% Main 'EasyDD' folder:
+mainpath = '../../';
+addpath(mainpath);
+
+% Subprocesses folders:
+addpath([mainpath 'Mobility']); % Mobility laws
+addpath([mainpath 'Integrator']); % Time integrators
+
+% Functions designed for use in the input file:
+addpath([mainpath 'Inputs/HCP/InputFunctions']);
+
+% Input figures:
+%addpath([mainpath 'Inputs/HCP/Figures']);
+
+% Output figures:
+frameext = '.jpg'; % File extension of saved frames
+movieext = '.mp4'; % File extension of saved movies
+outputspath = append('Outputs/',INPUTNAME,'/'); % Path to saved figures
+if ~exist([mainpath outputspath], 'dir')
[…]

### 2020-11-18 input/hcp/input_Zr600KFRvac1e5strain.m

@@ -1,0 +1,746 @@
+%% Input file created by Daniel Hortelano Roig (17/07/2020) %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Sections are the following:
+% 0) SIMULATION META-INFORMATION
+% 1) MATERIAL CONSTANTS
+% 2) SOURCE GENERATION PARAMETERS
+% 3) FEM PARAMETERS
+% 4) DDLab PARAMETERS
+%       - Meshing
+%       - Integrator
+%       - Simulation time
+%       - Plotting
+%       - Mobility module
+%       - Dislocation nodes (rn) and segments (links)
+% 5) PRINT INFORMATION
+% 6) REFERENCES
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+clear all
+dbstop if error % Applies debugging breakpoint instead of error
+
+
+
+
+
+%% SIMULATION META-INFORMATION %%
+
+
+%%% Input name
+
+INPUTFILENAME = mfilename;
+INPUTNAME = INPUTFILENAME(7:end);
+
+%%% MATLAB version year
+
+% Release version of MATLAB client currently running:
+MATLABrelease = ver('MATLAB').Release;
+
+%%% Add EasyDD subfolders to MATLAB path
+
+% Main 'EasyDD' folder:
+mainpath = '../../';
+addpath(mainpath);
+
+% Subprocesses folders:
+addpath([mainpath 'Mobility']); % Mobility laws
+addpath([mainpath 'Integrator']); % Time integrators
+
+% Functions designed for use in the input file:
+addpath([mainpath 'Inputs/HCP/InputFunctions']);
+
+% Input figures:
+%addpath([mainpath 'Inputs/HCP/Figures']);
+
+% Output figures:
+frameext = '.jpg'; % File extension of saved frames
+movieext = '.mp4'; % File extension of saved movies
+outputspath = append('Outputs/',INPUTNAME,'/'); % Path to saved figures
+if ~exist([mainpath outputspath], 'dir')
[…]

### 2020-11-18 input/hcp/inputfunctions/IndicesMBToCartesianNormal.m

@@ -1,0 +1,50 @@
+function [unitNormalVec] = IndicesMBToCartesianNormal(indices,a1,a2,a3)
+	% INPUT:
+	%		indices: four MB indices (hkil) describing the plane -- size (1,4)
+	%                NOTE: Miller indices (hkl) with size (1,3) will also work
+	%       a1,a2,a3: three linearly independent HCP lattice basis vectors -- each size (1,3)
+    %       eps_VolLat: tolerance for linear independence of the three input HCP lattice vectors -- size (1)
+	% OUTPUT:
+	%		unitNormalVec: corresponding plane unit normal vector in cartesian coordinates -- size (1,3)
+    
+    % Tolerance for linear independence of three input HCP vectors:
+    eps_VolLat = 1e-12;
+    
+	% HCP lattice basis vectors in a matrix form:
+	basis = [a1;a2;a3]; % size (3,3)
+	
+	% Volume of cell generated by (a1,a2,a3):
+	vol = det(basis); % size (1)
+	
+	% Checking linear independence of (a1,a2,a3):
+	if abs(vol) < eps_VolLat
+        warning('The volume generated by the three chosen HCP lattice vectors is %0.2s, which is less than the tolerance %0.2s.\n',abs(vol),eps_VolLat)
+	end
+	
+	% Reciprocal lattice basis vectors:
+	g1 = cross(a2,a3) ./ vol;
+	g2 = cross(a3,a1) ./ vol;
+	g3 = cross(a1,a2) ./ vol;
+	
+	if size(indices,2) == 4 % indices contains Miller-Bravais indices
+		if indices(3) ~= -(indices(1) + indices(2))
+            warning('i = %d != -(h + k) = %d for these Miller-Bravais indices.\n',indices(3),-(indices(1) + indices(2)))
+		end
+		indices(3) = []; % Removes linearly dependent index
+	elseif size(indices,2) == 3 % indices contains Miller indices
+		% Do nothing! Miller indices are apparently already given
+    else
+        error('The number of indices describing this plane is unexpectedly %d, and should be either 3 or 4.\n',size(indices,2))
+	end
+	
+	% Miller indices in standard notation:
+	h = indices(1);
+	k = indices(2);
+	l = indices(3);
+	
+	% Normal vector to (hkl) plane:
+	normalVec = h*g1 + k*g2 + l*g3;
+	
+	% Unit normal vector:
+	unitNormalVec = normalVec/norm(normalVec);
+end

### 2020-11-18 input/hcp/inputfunctions/PrintInformation.m

@@ -1,0 +1,32 @@
+%===============================================================%
+% Daniel Hortelano Roig (11/11/2020)
+% daniel.hortelanoroig@materials.ox.ac.uk 
+
+% Prints identifying information from input file.
+%===============================================================%
+%%
+% Material
+fprintf('================ %s ================\n\n', mfilename);
+fprintf('Material: %s\n\n',             materialname);
+fprintf('Temperature: %0.2e K\n',       temperature);
+fprintf('Shear modulus: %0.2e GPa\n',   pressureSI/1e9);
+fprintf('Poisson ratio: %0.2e\n',       NU);
+fprintf('c/a ratio: %0.2e\n',           HCPc);
+
+% Selected subprocesses
+fprintf('\n--------------   Subprocesses   --------------\n\n');
+fprintf('Boundary condition: %s\n',     simType);
+fprintf('Loading condition: %s\n',      loading);
+fprintf('Integrator function: %s\n',    integrator);
+fprintf('Mobility function: %s\n',      mobility);
+
+% Simulation units in SI
+fprintf('\n-------------- Simulation Units --------------\n\n');
+fprintf('Distance: %0.2e m\n',          lengthSI);
+fprintf('Time: %0.2e s\n',              timeSI);
+fprintf('Velocity: %0.2e m/s\n',        velocitySI);
+fprintf('Pressure: %0.2e Pa\n',         pressureSI);
+fprintf('Force: %0.2e Pa m^2\n',        forceSI);
+fprintf('Nodal force: %0.2e Pa m\n',    nodalforceSI);
+fprintf('Drag: %0.2e Pa s\n',           dragSI);
+fprintf('Temperature: %0.2e K\n',       temperatureSI);

### 2020-11-18 input/hcp/inputtemplate.m

@@ -1,0 +1,690 @@
+%% Input file created by Daniel Hortelano Roig (11/11/2020) %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Sections are the following:
+% 1) SIMULATION META-INFORMATION
+% 2) MATERIAL PARAMETERS
+% 3) SOURCE GENERATION PARAMETERS
+% 4) FEM PARAMETERS
+% 5) EasyDD PARAMETERS
+%       - Parallelisation
+%       - Meshing
+%       - Time integrator
+%       - Simulation time
+%       - Plotting
+%       - Mobility law
+%       - Dislocation nodes (rn) and segments (links)
+% 6) INFO & CHECKS
+% 7) REFERENCES
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+clear % Removes all items from workspace
+dbstop if error % Applies debugging breakpoint instead of error
+
+
+
+
+
+%% SIMULATION META-INFORMATION %%
+
+
+%%% Simulation name
+
+INPUTNAME = mfilename; % Input file name excluding '.m' extension
+simName = append(INPUTNAME,'_',date,'_',char(timeofday(datetime)));
+
+%%% MATLAB version
+
+% Release version of MATLAB client currently running:
+MATLABrelease = ver('MATLAB').Release;
+
+%%% Input paths & folders
+
+% Functions designed for use in the input file:
+if ~exist('inputfunctions/', 'dir')
+       mkdir('inputfunctions/');
+end
+addpath('inputfunctions/');
+
+% Initial nodal network figures:
+if ~exist('figures/', 'dir')
+       mkdir('figures/');
+end
+
+
+
+
+
+%% MATERIAL PARAMETERS %%
+
+
+materialname = "alpha-Zr"; % alpha-Zirconium (temperature below ~900K)
+CRYSTAL_STRUCTURE = 'hcp';
+
+%%% Simulation units (SI)
+
+simscale = struct; % Store scaling units in a structure
+
[…]

### 2020-11-18 src/EasyDD.m

@@ -1,60 +1,15 @@
 %=========================================================================%
-% EasyDD.m v2.0
-%
-% 3D Discrete Dislocation Plasticity. Is currently capable of simulating
-% nanoindentation, micropillar compression and cantilever bending.
-% Mixed-language model C, CUDA and Matlab so requires at least a C/C++
-% compatible compiler, CUDA computation is optional. Explicitly calculates
-% dislocation-dislocation interactions O(N^2).
-%
-%-------------------------------------------------------------------------%
-%
-% Data structure:
-% rn: (:,4) array of nodal positions (x, y, z, label)
-% vn: (:,3) array of nodal velocities (vx, vy, vz)
-% fn: (:,3) array of nodal forces (fx, fy, fz)
-% links: (:,8) array of links (idx1, idx2, bx, by, bz, nx, ny, nz)
-%
-%-------------------------------------------------------------------------%
-%
-% Compatibility:
-% As long as Matlab and a compatible C/C++ and/or CUDA compiler are
-% supported, the code will be compatible.
-%
-%-------------------------------------------------------------------------%
-%
-% Known issues and Improvement wish list:
-% * Memory model is highly inefficient. There is a lot of naive dynamic
-%   resizing of arrays.
-% * Some matrices variables change in their number of columns are are hard
-%   to track/debug (rn, connectivity).
-% * Some variables hang around unused.
-% * Collision, Separation and Remeshing can be antagonistic at higher
-%   dislocation densities and may end up repeating processes until the
-%   simulation progresses enough.
-% * FEM boundary conditions need reworking so they can be passed in as
-%   inputs rather than soft-coded into the FEM mesh builder.
-% * There is no sanity check on input parameters.
-% * Some performance-critical functions have no Matlab equivalent so a
-%   C/C++ compiler is strictly required.
-% * There are potential opportunities for further parallelisation in
[…]

### 2020-11-18 src/FEM_DDD_Superposition.m

@@ -1,25 +1,28 @@
-function [f_bar, f_hat, f_tilda, u_bar, u_hat, u_tilda, r_hat] = FEM_DDD_Superposition(...
-        rn, links, a, MU, NU, xnodes, kg, L, U, gamma_disp, gamma_mixed, fixedDofs, ...
-        freeDofs, dx, dy, dz, simTime, mx, my, mz, sign_u_dot, u_dot, sign_f_dot, ...
-        f_dot, u_tilda_0, u, u_hat, u_tilda, loading, a_trac, gamma_dln, x3x6, n_nodes, ...
+function [f, f_hat, f_tilda, u, u_hat, u_tilda, r_hat, BCstore] = FEM_DDD_Superposition(...
+        rn, links, a, MU, NU, xnodes, kg, L, U, bcwt, gamma_disp, gamma, S, ...
+        fixedDofs, freeDofs, dx, dy, dz, simTime, mx, my, mz, diffBC, ...
+        u_tilda_0, u, u_hat, u_tilda, loading, BCstore, a_trac, gamma_dln, x3x6, n_nodes, ...
         n_nodes_t, n_se, idxi, f, f_tilda_node, f_tilda_se, f_tilda, f_hat, use_gpu, ...
         n_threads, para_scheme, para_tol)
+    %=====================================================================%
+    % Oxford Materials (as of 11/11/2020)
 
-    u(:, 1) = 0;
-    u_hat(:, 1) = 0;
-    u_tilda(:, 1) = 0;
-    f(:, 1) = 0;
-    f_hat(:, 1) = 0;
-    f_tilda(:, 1) = 0;
-
-    [u, u_bar, f, f_bar, calculateR_hat] = feval(loading, u, u_dot, sign_u_dot, f, f_dot, sign_f_dot, simTime, gamma_mixed);
-
+    % Couples FEM and DDD using the superposition principle method (SPM).
+    %=====================================================================%
+    
+    %% Reset fields
+    
+    % Reset displacements and forces.
+    u_hat(:) = 0; u_tilda(:) = 0;
+    f_hat(:) = 0; f_tilda(:) = 0;
+    
+    %% Compute dislocation fields
+    
     % Calculate adjusted U_tilda.
     u_tilda = calculateUtilda(rn, links, gamma_disp, NU, xnodes, dx, ...
         dy, dz, mx, my, mz, u_tilda) - u_tilda_0;
-
-    u_hat(fixedDofs) = u(fixedDofs) - u_tilda(fixedDofs);
-
+    
[…]

### 2020-11-18 src/addPaths.m

@@ -1,0 +1,20 @@
+%===============================================================%
+% Daniel Hortelano Roig (11/11/2020)
+% daniel.hortelanoroig@materials.ox.ac.uk 
+
+% Adds all relative paths required to run the simulation.
+%===============================================================%
+
+%% Source folder paths
+
+mainpath = '../';
+addpath(mainpath); % Main
+addpath(genpath([mainpath 'src/modules/'])); % Selected subprocesses
+addpath(genpath([mainpath 'src/init/'])); % Preamble functions
+
+%% Output folder paths
+
+outputpath = append('output/',INPUTNAME,'/');
+if ~exist([mainpath outputpath], 'dir')
+       mkdir([mainpath outputpath]);
+end

### 2020-11-18 src/displacementControl.m

@@ -1,6 +1,0 @@
-function [u, u_bar, f, f_bar, calculateR_hat] = displacementControl(u, u_dot, sign_u_dot, f, f_dot, sign_f_dot, simTime, gamma_mixed)
-    f_bar = 0;
-    u_bar = u_dot * simTime;
-    u(3 * gamma_mixed(:, 1)) = sign_u_dot * u_bar;
-    calculateR_hat = true;
-end

### 2020-11-18 src/drndt.m

@@ -13,14 +13,17 @@ function [vnvec, fn, fseg] = drndt(rnvec, flag, MU, NU, a, Ec, links, connectivi
     %rn(:,1:3)
 
     %nodal driving force
-    fseg = segforcevec(MU, NU, a, Ec, rn, links, 0, vertices, ...
+    linkid = 0;
+    fseg = segforcevec(MU, NU, a, Ec, rn, links, linkid, vertices, ...
         uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag);
 
     %mobility function
-    [vn, fn] = feval(mobility, fseg, rn, links, connectivity, [], [], Bcoeff);
-    % fixed nodes (flag==7) are not allowed to move.
-    % flag == 6, are only allowed to move on the surface they live at.
-    % flag == 67, are virtual nodes that are not allowed to move.
+    nodelist = []; conlist = []; % Default node and connectivity lists
+    [vn, fn] = feval(mobility, fseg, rn, links, connectivity, ...
+        nodelist, conlist, ...
+        Bcoeff);
+    
+    % Perform integration
     for p = 1:size(vn, 1)
 
         % Virtual and fixed nodes have zero velocity

### 2020-11-18 src/init/AuxFEMCoupler.m

@@ -1,7 +1,7 @@
 function [f, f_hat, para_tol, x3x6, n_se, gamma_dln, f_tilda_node, f_tilda_se,...
         f_tilda, idxi, n_nodes_t, n_threads, para_scheme, gamma_disp, u_tilda_0,...
          u, u_hat, u_tilda] = AuxFEMCoupler(mno, dx, dy, dz, mx, my, mz, xnodes,...
-          nc, gammat, gammau, gammaMixed, a_trac, CUDA_flag, n_threads, para_scheme)
+          nc, gamma, a_trac, CUDA_flag, n_threads, para_scheme)
     %=========================================================================%
     % Sets up auxiliary data structures for analytic traction calculations.
     %
@@ -14,7 +14,7 @@ function [f, f_hat, para_tol, x3x6, n_se, gamma_dln, f_tilda_node, f_tilda_se,..
     % mx, my, mz := number of nodes in x, y, z dimension.
     % xnodes := coordinates and labels of FE nodes
     % nc := FE node connectivity matrix
-    % gammat, gammau, gammaMixed := traction, displacement, mixed boundary
+    % gamma := traction, displacement, mixed boundary
     %   conditions.
     % a_trac := flag for analytic tractions.
     % CUDA_flag := flag in case CUDA codes required. If true compile, else do
@@ -40,7 +40,14 @@ function [f, f_hat, para_tol, x3x6, n_se, gamma_dln, f_tilda_node, f_tilda_se,..
     %   2 parallelises over surface elements
     % gamma_disp := nodes with displacement boundary conditions
     %=========================================================================%
-
+    
+    %% Extract BCs
+    gammat = gamma.t;
+    gammau = gamma.u;
+    gammaMixed = gamma.Mixed;
+    
+    %% Initialise parameters
+    
     f = zeros(3 * mno, 1);
     f_hat = zeros(3 * mno, 1);
     gamma_disp = [gammau(:, 1); gammaMixed(:, 1)];
@@ -49,7 +56,9 @@ function [f, f_hat, para_tol, x3x6, n_se, gamma_dln, f_tilda_node, f_tilda_se,..
     u_tilda_0 = zeros(3 * mno, 1);
     u_tilda = zeros(3 * mno, 1);
     gamma_dln = [gammat; gammaMixed];
-
+    
+    %%
+    
     if (~exist('CUDA_flag', 'var'))
         CUDA_flag = false;
     end

### 2020-11-18 src/init/MeshSurfaceTriangulation.m

@@ -1,9 +1,9 @@
-function [P, fn, tri, Xb] = MeshSurfaceTriangulation(xnodes, Stop, Sbot, Sfront, Sback, Sleft, Sright, Smixed)
-
+function [P, fn, tri, Xb] = MeshSurfaceTriangulation(xnodes, Scat)
+        
     % Beginning of surface remeshing for surface node. %%%%%%%%%%%%%%%%%%%%
 
     %create triangulation (uses all surface nodes from FEM code)
-    pts = xnodes([Stop(:, 1); Sbot(:, 1); Sfront(:, 1); Sback(:, 1); Sleft(:, 1); Sright(:, 1); Smixed(:, 1)], :);
+    pts = xnodes(Scat(:, 1), :);
     dt = delaunayTriangulation(pts);
     %dt = delaunayTriangulation(vertices); %coarse triangulation
 

### 2020-11-18 src/init/compileCode.m

@@ -2,7 +2,7 @@ function CUDA_flag = compileCode(CUDA_flag)
     %=========================================================================%
     % Compile MEX and MEXCUDA files.
     %
-    % Compiles files if they have not been compiled of if they were compiled
+    % Compiles files if they have not been compiled or if they were compiled
     % over 30 days ago.
     %
     % Daniel Celis Garza, Aug 2020

### 2020-11-18 src/init/finiteElement3D.m

@@ -1,4 +1,5 @@
-function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel] = finiteElement3D(dx, dy, dz, mx, mu, nu)
+function [B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel, globnidx] = ...
+    finiteElement3D(dx, dy, dz, mx, mu, nu)
     %=========================================================================%
     % E Tarleton edmund.tarleton@materials.ox.ac.uk
     % 3D FEM code using linear 8 node element with 8 integration pts (2x2x2)
@@ -26,20 +27,19 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel] = finite
     % |------>x-----------------------------------------
     %=========================================================================%
 
-    fprintf('Constructing stiffness matrix K and precomputing L,U decompositions. Please wait.\n');
+    fprintf('Constructing stiffness matrix K...\n');
 
     % Simulation domain vertices. Required for surface remeshing.
-    vertices = [0, 0, 0; ...
-                dx, 0, 0; ...
-                0, dy, 0; ...
-                dx, dy, 0; ...
-                0, 0, dz; ...
-                dx, 0, dz; ...
-                0, dy, dz; ...
-                dx, dy, dz];
+%     vertices = [0, 0, 0; ...
+%                 dx, 0, 0; ...
+%                 0, dy, 0; ...
+%                 dx, dy, 0; ...
+%                 0, 0, dz; ...
+%                 dx, 0, dz; ...
+%                 0, dy, dz; ...
+%                 dx, dy, dz];
     % not that this code uses a constant element size in base and beam: (w,h,d)
     % also gammau is the left surface (eg baseLength=0)
-    % loading = 1;
 
     w = dx / mx; % elements width
 
@@ -114,16 +114,24 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel] = finite
     %    .            .                .
     %    1+(mx+1)  2+(mx+1)  ...   2*(mx+1)
     %    1         2         ...     mx+1
+    
+    
+    % Store global node index based on (x,y,z) indices:
+    globnidx = zeros(mx + 1, my + 1, mz + 1);
+    
[…]

### 2020-11-18 src/init/inputCompletion.m

@@ -52,28 +52,6 @@ if ~exist('loading', 'var')
     fprintf('Providing default value for loading = %s.', loading)
 end
 
-if ~exist('vertices', 'var')
-    vertices = [0, 0, 0; ...
-                dx, 0, 0; ...
-                0, dy, 0; ...
-                dx, dy, 0; ...
-                0, 0, dz; ...
-                dx, 0, dz; ...
-                0, dy, dz; ...
-                dx, dy, dz];
-    fprintf('Providing default value for vertices.\n')
-end
-
-if ~exist('faces', 'var')
-    faces = [1, 3, 4, 2; % Faces of cuboid as defined by vertices
-        5, 6, 8, 7;
-        2, 4, 8, 6;
-        1, 5, 7, 3;
-        1, 2, 6, 5;
-        3, 7, 8, 4];
-    fprintf('Providing default value for faces.\n')
-end
-
 if ~exist('MU', 'var')
     MU = 1;
     fprintf('Providing default value for MU = %f.\n', MU)
@@ -89,12 +67,12 @@ if ~exist('mobility', 'var')
     fprintf('Providing default value for mobility = %s.\n', mobility)
 end
 
-if ~exist('Bcoeff', 'var')
-    Bcoeff = struct('screw', 10, 'edge', 1, 'climb', 1e10, 'line', 1e-4);
-    fprintf('Providing default value for Bcoeff.screw = %f.\n', Bcoeff.screw)
-    fprintf('Providing default value for Bcoeff.edge = %f.\n', Bcoeff.edge)
-    fprintf('Providing default value for Bcoeff.climb = %f.\n', Bcoeff.climb)
-    fprintf('Providing default value for Bcoeff.line = %f.\n', Bcoeff.line)
+if ~exist('mobstruct', 'var')
+    mobstruct = struct('screw', 10, 'edge', 1, 'climb', 1e10, 'line', 1e-4);
+    fprintf('Providing default value for mobstruct.screw = %f.\n', mobstruct.screw)
+    fprintf('Providing default value for mobstruct.edge = %f.\n', mobstruct.edge)
+    fprintf('Providing default value for mobstruct.climb = %f.\n', mobstruct.climb)
+    fprintf('Providing default value for mobstruct.line = %f.\n', mobstruct.line)
 end
 
 if ~exist('maxconnections', 'var')
@@ -209,7 +187,7 @@ end
 
 if ~exist('simName', 'var')
[…]

### 2020-11-18 src/init/plotFEMDomain.m

@@ -1,0 +1,14 @@
+function fig = plotFEMDomain(S, xnodes)
+    
+    fig = figure(1); clf; hold on; view(3)
+    xlabel('x'); ylabel('y'); zlabel('z')
+    plot3(xnodes(S.top(:, 1), 1), xnodes(S.top(:, 1), 2), xnodes(S.top(:, 1), 3), 'r*')
+    plot3(xnodes(S.bot(:, 1), 1), xnodes(S.bot(:, 1), 2), xnodes(S.bot(:, 1), 3), 'r*')
+    plot3(xnodes(S.right(:, 1), 1), xnodes(S.right(:, 1), 2), xnodes(S.right(:, 1), 3), 'b.')
+    plot3(xnodes(S.left(:, 1), 1), xnodes(S.left(:, 1), 2), xnodes(S.left(:, 1), 3), 'b.')
+    plot3(xnodes(S.front(:, 1), 1), xnodes(S.front(:, 1), 2), xnodes(S.front(:, 1), 3), 'k*')
+    plot3(xnodes(S.back(:, 1), 1), xnodes(S.back(:, 1), 2), xnodes(S.back(:, 1), 3), 'k*')
+    plot3(xnodes(S.topright(:, 1), 1), xnodes(S.topright(:, 1), 2), xnodes(S.topright(:, 1), 3), 'g*')
+    axis('equal')
+    hold off
+end

### 2020-11-18 src/modules/fembc/deformationControl.m

@@ -1,0 +1,30 @@
+function [u, f] = deformationControl(...
+    u, f, diffBC, simTime, gamma, S, fixedDofs, freeDofs)
+    %===============================================================%
+    % Daniel Hortelano Roig (11/11/2020)
+    % daniel.hortelanoroig@materials.ox.ac.uk 
+    
+    % Specifies (possibly time-dependent) applied boundary conditions
+    % given the fixed and free degrees of freedom and their
+    % corresponding surface sets.
+    %===============================================================%
+    
+    %% Initialise BCs
+    
+    u(:) = 0; f(:) = 0;
+    
+    %% Force conditions
+    
+    f(freeDofs) = 0; % All freeDofs have zero applied force BCs
+    
+    %% Displacement conditions
+    
+    % FixedDofs corresponding to zero displacement:
+    fixedDofs_0 = [3*gamma.u(:,1)-2; 3*gamma.u(:,1)-1; 3*gamma.u(:,1)];
+    u(fixedDofs_0) = 0;
+    
+    % FixedDofs corresponding to affinely increasing displacement:
+    fixedDofs_U = 3*gamma.Mixed(:, 1);
+    u(fixedDofs_U) = diffBC.u_dot * simTime;
+    
+end

### 2020-11-18 src/modules/fembc/displacementControl.m

@@ -1,0 +1,11 @@
+function [u, u_bar, f, f_bar, calculateR_hat] = displacementControl(...
+    u, u_dot, sign_u_dot, f, f_dot, sign_f_dot, simTime, ...
+    gamma)
+    
+    % Deformation conditions:
+    f_bar = 0;
+    u_bar = u_dot * simTime;
+    u(3 * gamma_mixed(:, 1)) = sign_u_dot * u_bar;
+    
+    calculateR_hat = true;
+end

### 2020-11-18 src/modules/femgeo/cantilever/cantilever.m

@@ -1,0 +1,285 @@
+function [S, Scat] = cantilever(...
+    w, h, d, mx, my, mz, globnidx)
+    %===============================================================%
+    % Daniel Hortelano Roig (11/11/2020)
+    % daniel.hortelanoroig@materials.ox.ac.uk 
+    
+    % Defines the geometry of the simulation domain surfaces.
+    % This function specifically defines a cantilever (cuboid) with
+    % orthorhombic axes.
+    %===============================================================%
+    
+    %% Define surface sets
+    
+    S = struct; % Struct contains surface sets
+    % S.s = [global node idx, nodal area, outward normal]
+    % Each surface set corresponds to a subset of the FE nodes
+    % Nodes are never shared between surface sets
+    
+    %%% Faces
+    
+    % Constant x:
+    S.left = zeros((my-1)*(mz-1), 5);
+    S.right = zeros((my-1)*(mz-1), 5);
+    
+    % Constant y:
+    S.front = zeros((mx-1)*(mz-1), 5);
+    S.back = zeros((mx-1)*(mz-1), 5);
+    
+    % Constant z:
+    S.top = zeros((mx-1)*(my-1), 5);
+    S.bot = zeros((mx-1)*(my-1), 5);
+    
+    
+    
+    %%% Edges
+    
+    % Top edges:
+    S.topleft = zeros(my-1, 5); % Top left edge
+    S.topright = zeros(my-1, 5); % Top right edge
+    S.topfront = zeros(mx-1, 5); % Top front edge (& front top edge)
+    S.topback = zeros(mx-1, 5); % Top back edge (& back top edge)
+    
+    % Bottom edges:
+    S.botleft = zeros(my-1, 5);
+    S.botright = zeros(my-1, 5);
+    S.botfront = zeros(mx-1, 5); % Bot front edge (& front bot edge)
+    S.botback = zeros(mx-1, 5); % Bot front edge (& front bot edge)
+    
+    % Front edges:
+    S.frontleft = zeros(mz-1, 5);
+    S.frontright = zeros(mz-1, 5);
+    % Back edges:
+    S.backleft = zeros(mz-1, 5);
+    S.backright = zeros(mz-1, 5);
+    
+    %%% Corners
+    
[…]

### 2020-11-18 src/modules/femgeo/cantilever/cantileverBC.m

@@ -1,0 +1,53 @@
+function [gamma, fixedDofs, freeDofs, t, Usim, Fsim] = ...
+    cantileverBC(S, maxstepsBC)
+    %===============================================================%
+    % Daniel Hortelano Roig (11/11/2020)
+    % daniel.hortelanoroig@materials.ox.ac.uk 
+    
+    % Specifies the fixed and free degrees of freedom of the surface
+    % nodes of a deforming cantilever (cuboid).
+    %===============================================================%
+    
+    %% Specify BCs
+    
+    %%% Store surfaces
+    
+    gamma = struct; % Stores surfaces with displacement/traction BCs
+    
+    % Traction BCs:
+    gamma.t = [S.top; S.bot; S.right; S.front; S.back; ... % Faces
+        S.botright; S.frontright; S.backright; ...
+        S.topfront; S.topback; S.botfront; S.botback; ... % Edges
+        reshape(S.corners(2,1,1,:),1,5); reshape(S.corners(2,2,1,:),1,5)]; % Corners
+    % Displacement BCs:
+    gamma.u = [S.left; ... % Faces
+        S.topleft; S.botleft; S.frontleft; S.backleft; ... % Edges
+        reshape(S.corners(1,1,1,:),1,5); reshape(S.corners(1,2,1,:),1,5); ...
+        reshape(S.corners(1,1,2,:),1,5); reshape(S.corners(1,2,2,:),1,5)]; % Corners
+    % Mixed traction and displacement BCs:
+    gamma.Mixed = [S.topright; ... % Edges
+        reshape(S.corners(2,1,2,:),1,5); reshape(S.corners(2,2,2,:),1,5)]; % Corners
+    
+    %%% Specify fixed Dofs
+
+    dofUx = 3*gamma.u(:, 1)-2;
+    dofUy = 3*gamma.u(:, 1)-1;
+    dofUz = [3*gamma.u(:, 1); 3*gamma.Mixed(:, 1)];
+    
+    fixedDofs = [dofUx; dofUy; dofUz];
+    
+    %%% Specify free Dofs
+    
+    dofTx = [3*gamma.t(:, 1)-2; 3*gamma.Mixed(:, 1)-2];
+    dofTy = [3*gamma.t(:, 1)-1; 3*gamma.Mixed(:, 1)-1];
+    dofTz = 3*gamma.t(:, 1);
+    
[…]

### 2020-11-18 src/modules/femgeo/cantilever/cantileverForceDisp.m

@@ -1,0 +1,27 @@
+function [Fsim, Usim, t] = cantileverForceDisp(BCstore, ...
+        f, f_hat, f_tilda, u, u_hat, u_tilda, r_hat, ...
+        gamma, fixedDofs, freeDofs, curstep, simTime)
+    %===============================================================%
+    % Daniel Hortelano Roig (11/11/2020)
+    % daniel.hortelanoroig@materials.ox.ac.uk
+    
+    % Prints and stores applied forces and displacements into the Fsim and
+    % Usim objects. These are later plotted.
+    %===============================================================%
+    
+    %%
+    
+    % Sum concentrated forces:
+    f_out = sum(r_hat(3*gamma.Mixed(:, 1)) + f_tilda(3*gamma.Mixed(:, 1)));
+    
+    % FixedDofs corresponding to affinely increasing displacement:
+    fixedDofs_U = 3*gamma.Mixed(:, 1);
+    u_out = abs(u(fixedDofs_U(1)));
+
+    BCstore.Fsim(curstep + 1) = f_out;
+    BCstore.Usim(curstep + 1) = u_out;
+    BCstore.t(curstep + 1) = simTime;
+
+    fprintf('f_out = %d, u_out = %d, simTime = %d\n', f_out, u_out, simTime);
+
+end

### 2020-11-18 src/modules/femgeo/cantilever/cantileverK.m

@@ -1,0 +1,45 @@
+function [K, L, U, bcwt] = cantileverK(kg, fixedDofs, freeDofs)
+    %===============================================================%
+    % Daniel Hortelano Roig (11/11/2020)
+    % daniel.hortelanoroig@materials.ox.ac.uk 
+    
+    % Reformats stiffness matrix based on the prescribed
+    % boundary conditions on the degrees of freedom.
+    %===============================================================%
+    
+    %%
+    
+    fprintf('Cantilever boundary conditions: reformatting K.\n');
+    
+    % {freeDofs,fixedDofs} should contain every degree of freedom on
+    % boundary + any internal Dofs with a force or displacement specified.
+    if length([fixedDofs; freeDofs]) > length(unique([fixedDofs; freeDofs]))
+        fprintf('error\n')
+        pause
+    end
+    
+    K = kg; % Reallocate stiffness matrix
+    
+    % Weighing factor to retain conditioning of K:
+    bcwt = mean(diag(kg)); % = trace(K)/length(K)
+    bcwt = full(bcwt); % Convert sparse matrix --> full matrix
+    
+    for m = 1:length(fixedDofs)
+        i = fixedDofs(m);
+        K(:, i) = 0;
+        K(i, :) = 0;
+        K(i, i) = bcwt;
+    end
+    % K should still be symmetric!
+    
+    fprintf('Cholesky factorisation of K...\n');
+    tic;
+    U = chol(K);
+    L = U';
+    toc;
+    fprintf('Finished Cholesky factorisation of K.\n');
+    
+    processForceDisp = 'cantileverBendingForceDisp';
+    plotForceDisp = 'cantileverBendingPlot';
+
+end

### 2020-11-18 src/modules/femgeo/cantilever/cantileverPlot.m

@@ -1,0 +1,37 @@
+function cantileverPlot(BCstore, curstep, simscale)
+    %===============================================================%
+    % Daniel Hortelano Roig (11/11/2020)
+    % daniel.hortelanoroig@materials.ox.ac.uk 
+    
+    % Plots relationship between displacement and force BCs as
+    % the time-steps progress. The scale structure stores the BCs
+    % and their scaling for the plot.
+    %===============================================================%
+    
+    %% Extraction
+    
+    Usim = BCstore.Usim; Fsim = BCstore.Fsim;
+    
+    %% Plotting
+    
+    % Setup figure:
+    cantileverPlot_figname = "Bending cantilever BCs";
+    figure('Name',cantileverPlot_figname);
+    grid on, hold on
+    
+    % Plotting:
+    plot(Usim(1:curstep), -Fsim(1:curstep), ... % Main plot
+        '-','LineWidth',3,'Color','magenta')
+    plot([min(Usim) max(Usim)], zeros(2),'--','LineWidth',1,'Color','black') % x-axis
+    plot(zeros(2), [min(Fsim) max(Fsim)],'--','LineWidth',1,'Color','black') % y-axis
+    
+    % Axes and labels:
+    ax = gca; % Define axes object
+    ax.XLim = [min(Usim) max(Usim)]; % Define limits on axes
+    ax.YLim = [min(Fsim) max(Fsim)];
+    xlabel('Force','FontSize',14); % Label axes
+    ylabel('Displacement','FontSize',14);
+    title(cantileverPlot_figname,'FontSize',20); % Title plot
+    legend('x-axis','y-axis','8b'); % Legend
+    
+end

### 2020-11-18 src/modules/femgeo/cantileverBending/cantileverBending.m

@@ -3,13 +3,16 @@ function [K, L, U, Sleft, Sright, Stop, Sbot, Sfront, Sback, Smixed, gammat, gam
     kg, w, h, d, mx, my, mz)
 
     fprintf('Cantilever bending boundary conditions: reformatting K\n');
-
+    
     K = kg;
-    bcwt = mean(diag(kg)); %=trace(K)/length(K)
-    bcwt = full(bcwt);
-
+    
+    % Weighing factor to retain conditioning of kg:
+    bcwt = mean(diag(kg)); % = trace(K)/length(K)
+    bcwt = full(bcwt); % Sparse matrix --> full matrix
+    
     % define empty sets (not used but allows same code as for bending)
     % priority for inclusion of shared nodes is in order below
+    
     %S = [node #, nodal Area, outward normal]
     Smixed = zeros(my + 1, 5); % top right edge (u3=U) first priority
 

### 2020-11-18 src/modules/femgeo/cantileverBending/cantileverBendingForceDisp.m

@@ -8,6 +8,6 @@ function [Fsim, Usim, t] = cantileverBendingForceDisp(Fsim, f_bar, f_hat, f_tild
     Usim(curstep + 1) = u_out;
     t(curstep + 1) = simTime;
 
-    fprintf('fend = %d, Ubar = %d, simTime = %d\n', f_out, u_out, simTime);
+    fprintf('f_out = %d, u_out = %d, simTime = %d\n', f_out, u_out, simTime);
 
 end

### 2020-11-18 src/modules/mobility/hcp/mobhcp0.m

@@ -1,0 +1,763 @@
+%===============================================================%
+% Daniel Hortelano Roig (15/11/2020)
+% daniel.hortelanoroig@materials.ox.ac.uk
+
+% For an overview of the HCP mobility law and notation used in this script,
+% see Aubry et al: http://dx.doi.org/10.1016/j.jmps.2016.04.019
+%===============================================================%
+
+function [vn,fn] = mobhcp0(fseg,rn,links,connectivity,nodelist,conlist, ...
+mobstruct)
+% OUTPUT:
+%		fn: matrix of nodal forces -- size (N,3) for N input nodes
+%       vn: matrix of corresponding nodal response velocities -- size (N,3)
+
+%% Mobility structure extraction %%
+
+%%% Glissile cartesian slip systems:
+slipsystems = mobstruct.slipsystemsref; % Cartesian
+[numburgs,numplanetypes,~] = size(slipsystems);
+maxedgedatadirs = mobstruct.maxedgedatadirs;
+
+%%% Reference Burgers vectors:
+burgscart = mobstruct.burgscart; % Cartesian
+
+%%% Drag coefficients:
+dragline = mobstruct.dragline; % Line
+dragclimb = mobstruct.dragclimb; % Climb
+glidecoefficients = mobstruct.glidecoefficients; % Glide
+dragsessile = mobstruct.dragsessile; % Sessile ("junction")
+
+%%% Critical resolved shear stress (CRSS):
+crsscoefficients = mobstruct.crsscoefficients;
+crsssessile = mobstruct.crsssessile;
+
+%%% MATLAB release:
+MATLABrelease = mobstruct.MATLABrelease;
+
+%%% Dimension checks:
+assert(all(size(burgscart) == [numburgs,3]), ...
+    'Assertion failed: all(size(burgscart) == [numburgs,3])')
+assert(all(size(glidecoefficients) == [numburgs,numplanetypes,2]), ...
+    'Assertion failed: all(size(glidecoefficients) == [numburgs,numplanetypes,2])')
+assert(all(size(crsscoefficients) == [numburgs,numplanetypes + 1]), ...
+    'Assertion failed: all(size(crsscoefficients) == [numburgs,numplanetypes + 1])')
+
+
+%% Mobility law parameters %%
+
+%%% Numerical tolerances:
+eps_seglen = 1e7; % Max segment length before linprog could have problems
+eps_reflist = 1e-2; % Min difference between actual and reference vectors
[…]

### 2020-11-18 src/plotFEMDomain.m

@@ -1,13 +1,0 @@
-function fig = plotFEMDomain(Stop, Sbot, Sright, Sleft, Sfront, Sback, Smixed, xnodes)
-    fig = figure(1); clf; hold on; view(3)
-    xlabel('x'); ylabel('y'); zlabel('z')
-    plot3(xnodes(Stop(:, 1), 1), xnodes(Stop(:, 1), 2), xnodes(Stop(:, 1), 3), 'r*')
-    plot3(xnodes(Sbot(:, 1), 1), xnodes(Sbot(:, 1), 2), xnodes(Sbot(:, 1), 3), 'r*')
-    plot3(xnodes(Sright(:, 1), 1), xnodes(Sright(:, 1), 2), xnodes(Sright(:, 1), 3), 'b.')
-    plot3(xnodes(Sleft(:, 1), 1), xnodes(Sleft(:, 1), 2), xnodes(Sleft(:, 1), 3), 'b.')
-    plot3(xnodes(Sfront(:, 1), 1), xnodes(Sfront(:, 1), 2), xnodes(Sfront(:, 1), 3), 'k*')
-    plot3(xnodes(Sback(:, 1), 1), xnodes(Sback(:, 1), 2), xnodes(Sback(:, 1), 3), 'k*')
-    plot3(xnodes(Smixed(:, 1), 1), xnodes(Smixed(:, 1), 2), xnodes(Smixed(:, 1), 3), 'g*')
-    axis('equal')
-    hold off
-end

### 2020-11-18 src/plotSimulation.m

@@ -1,12 +1,12 @@
-function plotSimulation(Usim, Fsim, rn, links, plim, vertices, plotFreq, viewangle, plotForceDisp, amag, mumag, curstep)
-
+function plotSimulation(rn, links, plim, vertices, plotFreq, viewangle, plotForceDisp, BCstore, simscale, curstep)
+    
     if (mod(curstep, plotFreq) == 0)
         figure(1)
         plotnodes(rn, links, plim, vertices);
         view(viewangle);
         drawnow
-
-        feval(plotForceDisp, Usim, Fsim, amag, mumag, curstep);
+        
+        feval(plotForceDisp, BCstore, simscale, curstep);
         pause(0.01);
     end
 

### 2020-11-18 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Editing

@@
 From \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw} it seems
-like both analytic and numeric tractions are both appropriate in most cases.
+like both analytic and numeric tractions are appropriate in most cases.
 At least at these scales, there is only one instance where numeric tractions yield very incorrect results.
@@
 
-In order to show the effects numerical tractions have on simulations, we ran a very simple cantilever bending simulation where the only difference was the traction calculation method.
-A very simple yet illustrative qualitative example is to produce a scatter plot of the numerically calculated tractions vs analytically calculated tractions at any time during the simulation.
+In order to show the effects numerical tractions have on simulations, we ran a very simple simulation where the only difference was the traction calculation method.
+A very simple yet illustrative qualitative example is to produce a scatter plot of the numerically calculated tractions vs analytically calculated ones at any time during any simulation.
 To obviate the problem even more, it helps making the axes proportional.

### 2020-11-19 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
More generalising of finite element routine.

@@
     }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
+    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
     \label{f:head_vs_ana_vs_num_screw}
@@
     \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$.
-(a) to (c) and (g) to (i) at $(26.3158\,, 500)\, b$; (d) to (f) and (j) to (l) at $(500\,, 500)\, b$.
+(a) to (c) and (g) to (i) at $(26.3158,\, 500)\, b$; (d) to (f) and (j) to (l) at $(500,\, 500)\, b$.
 (a) to (g) image stresses; (g) to (l) total stresses.}
@@
 In \cref{eq:imageStressAnalyticScrew}, the image term is a reflection about the line $x=0$.
-Therefore in both cases, as the dislocation moves away from the surface, the real stresses get relatively larger.}.
+Therefore in both cases, as the dislocation moves away from the surface, the real stresses get relatively larger when compared to the image ones.}.
 

### 2020-11-19 input/inputsquareloopcollision.m

@@ -172,3 +172,8 @@ links = [1 2 b1 n1;
 % Bscrew = 10;
 % mobility = 'mobbcc_bb1b';
 % a_trac = 1;
+
+my = round(mx * dy / dx); % # elements in y direction
+my = max(my, 1);
+mz = round(mx * dz / dx); % elements in z direction
+mz = max(mz, 1);

### 2020-11-19 src/EasyDD.m

@@ -70,8 +70,8 @@ CUDA_flag = compileCode(CUDA_flag);
 consistencycheck(rn, links, connectivity, linksinconnect);
 
 % Construct stiffeness matrix K and pre-compute L,U decompositions.
-[vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel] = ...
-    finiteElement3D(dx, dy, dz, mx, MU, NU);
+[vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = ...
+    finiteElement3D(dx, dy, dz, mx, my, mz, MU, NU);
 
 [K, L, U, Sleft, Sright, Stop, Sbot, Sfront, Sback, Smixed, gammat, ...
         gammau, gammaMixed, fixedDofs, freeDofs, processForceDisp, plotForceDisp] = ...

### 2020-11-19 src/finiteElement3D.m

@@ -1,4 +1,4 @@
-function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel] = finiteElement3D(dx, dy, dz, mx, mu, nu)
+function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = finiteElement3D(dx, dy, dz, mx, my, mz, mu, nu)
     %=========================================================================%
     % E Tarleton edmund.tarleton@materials.ox.ac.uk
     % 3D FEM code using linear 8 node element with 8 integration pts (2x2x2)
@@ -42,13 +42,7 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, my, mz, mel] = finite
     % loading = 1;
 
     w = dx / mx; % elements width
-
-    my = round(mx * dy / dx); % # elements in y direction
-    my = max(my, 1);
     h = dy / my; % element height
-
-    mz = round(mx * dz / dx); % elements in z direction
-    mz = max(mz, 1);
     d = dz / mz; % element depth
 
     mel = mx * my * mz;

### 2020-11-19 src/inputCompletion.m

@@ -44,6 +44,10 @@ end
 
 if ~exist('mx', 'var')
     mx = 20;
+    my = round(mx * dy / dx); % # elements in y direction
+    my = max(my, 1);
+    mz = round(mx * dz / dx); % elements in z direction
+    mz = max(mz, 1);
     fprintf('Providing default value for mx = %f.\n', mx)
 end
 

### 2020-11-25 src/drndt.m
Non-constant loading.

@@ -1,5 +1,5 @@
 function [vnvec, fn, fseg] = drndt(rnvec, flag, MU, NU, a, Ec, links, connectivity, ...
-        mobility, vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag)
+        mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag)
 
     % This needs to be an input/obtained from the surface nodes. This is a temporary fix for cuboid.
     normals = [1 0 0;
@@ -17,7 +17,7 @@ function [vnvec, fn, fseg] = drndt(rnvec, flag, MU, NU, a, Ec, links, connectivi
         uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag);
 
     %mobility function
-    [vn, fn] = feval(mobility, fseg, rn, links, connectivity, [], [], Bcoeff);
+    [vn, fn] = feval(mobility, fseg, rn, links, connectivity, [], [], Bcoeff, rotMatrix);
     % fixed nodes (flag==7) are not allowed to move.
     % flag == 6, are only allowed to move on the surface they live at.
     % flag == 67, are virtual nodes that are not allowed to move.
@@ -27,7 +27,7 @@ function [vnvec, fn, fseg] = drndt(rnvec, flag, MU, NU, a, Ec, links, connectivi
         if rn(p, 4) == 7 || rn(p, 4) == 67
             vn(p, :) = [0 0 0];
             % Surface nodes are confined to moving in the movement plane and surface plane.
-        % TODO #41
+            % TODO #41
         elseif rn(p, 4) == 6
             % Skip stationary surface nodes
             if norm(vn(p, :)) < eps

### 2020-11-25 src/int_trapezoid.m

@@ -1,5 +1,5 @@
 function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, links, connectivity, ...
-        rmax, rntol, mobility, vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag)
+        rmax, rntol, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag)
 
     %Implicit numerical integrator using the Euler-trapezoid method adapted
     %from [Cai & Bulatov, Algorithm 10.2, pg. 216]. The tiemstep size is
@@ -12,7 +12,7 @@ function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, link
 
     %Calculate the current nodal velocities
     [vnvec0, fn, fseg] = drndt(rnvec0, flag, MU, NU, a, Ec, links, connectivity, ...
-        mobility, vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag);
+        mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag);
 
     maxiter = 10; %Maximum number of times the timestep can be increased
     counter = 1; %Counter variable for the while loop
@@ -32,7 +32,7 @@ function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, link
         %Calculate the nodal velocities for the next timestep accordin to
         %Euler forward method
         [vnvec1, fn, fseg] = drndt(rnvec1, flag, MU, NU, a, Ec, links, connectivity, ...
-            mobility, vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag);
+            mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag);
         distvec = rnvec1 - rnvec0;
         distmag = max(abs(distvec)); %Largest distance any node moves
         err = distvec - (vnvec1 + vnvec0) / 2 * dt; %Euler-trapezoid method

### 2020-11-25 src/remesh.m

@@ -1,18 +1,23 @@
-function [rn, links, connectivity, linksinconnect, fseg] = remesh(rn, links, connectivity, linksinconnect, fseg, lmin, lmax, areamin, areamax, MU, NU, a, Ec, mobility, vertices, ...
-        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff)
+function [rn, links, connectivity, linksinconnect, fseg] = remesh(rn, links, ...
+        connectivity, linksinconnect, fseg, lmin, lmax, areamin, areamax, MU, ...
+        NU, a, Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, ...
+        w, h, d, CUDA_flag, Bcoeff)
     % first coarsen the parts of the mesh than can be coarsened
     % then refine the parts of the mesh that need it
     % meshcoarsen is done first because it relies on positions of nodes that were introduced at the end of the previous time step
     % do not change the order of these two subroutines
-    [rn, links, connectivity, linksinconnect, fseg] = meshcoarsen(rn, links, connectivity, linksinconnect, fseg, lmin, lmax, areamin, MU, NU, a, Ec, mobility, vertices, ...
+    [rn, links, connectivity, linksinconnect, fseg] = meshcoarsen(rn, links, connectivity, ...
+        linksinconnect, fseg, lmin, lmax, areamin, MU, NU, a, Ec, mobility, vertices, rotMatrix, ...
         uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff);
 
-    [rn, links, connectivity, linksinconnect, fseg] = meshrefine(rn, links, connectivity, linksinconnect, fseg, lmin, lmax, areamax, MU, NU, a, Ec, mobility, vertices, ...
+    [rn, links, connectivity, linksinconnect, fseg] = meshrefine(rn, links, connectivity, ...
+        linksinconnect, fseg, lmin, lmax, areamax, MU, NU, a, Ec, mobility, vertices, rotMatrix, ...
         uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff);
 end
 
-function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = meshcoarsen(rn, links, connectivity, linksinconnect, fseg, lmin, lmax, areamin, MU, NU, a, Ec, mobility, vertices, ...
[…]

### 2020-11-25 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/STATIC_finiteElement3D.m

@@ -234,6 +234,7 @@ if any(dNds ~= ns)
     pause
 end
 
+% TODO #50 mel are all identical, could be 1.
 J = zeros(3, 3, mel, 8); % 3Dx3D, mel elements, 8 quad pts/element
 invJ = zeros(3, 3); % inv(J)
 detJ = zeros(mel, 8); % det(J) at mel elements, 9 quad points/element

### 2020-11-25 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/STATIC_finiteElement3D.m
`mel` are all identical, could be 1. Fixes #50

@@ -234,13 +234,13 @@ if any(dNds ~= ns)
     pause
 end
 
-J = zeros(3, 3, mel, 8); % 3Dx3D, mel elements, 8 quad pts/element
+J = zeros(3, 3, 1, 8); % 3Dx3D, mel elements, 8 quad pts/element
 invJ = zeros(3, 3); % inv(J)
-detJ = zeros(mel, 8); % det(J) at mel elements, 9 quad points/element
-nx = zeros(mel, 8, 8, 3); % derivative of shape functions w.r.t global x,y
-B = zeros(6, 24, mel, 8); % (# strain components, # dof/element, # elements, int pts/element)
+detJ = zeros(1, 8); % det(J) at mel elements, 9 quad points/element
+nx = zeros(1, 8, 8, 3); % derivative of shape functions w.r.t global x,y
+B = zeros(6, 24, 1, 8); % (# strain components, # dof/element, # elements, int pts/element)
 
-for p = 1:mel% all elements
+for p = 1:1% all elements
 
     for q = 1:8% integration points per element
 
@@ -300,9 +300,9 @@ for p = 1:mel% all elements
 end
 
 disp('local K...');
-ke = zeros(24, 24, mel); %local stiffness matrix
+ke = zeros(24, 24, 1); %local stiffness matrix
 
-for p = 1:mel%all elements
+for p = 1:1%all elements
 
     for q = 1:8% int points per element
         ke(:, :, p) = ke(:, :, p) + B(:, :, p, q)' * D * B(:, :, p, q) * detJ(p, q);
@@ -310,7 +310,7 @@ for p = 1:mel%all elements
 
 end
 
-clear B;
+% clear B;
 % ensure ke is symmetric eg remove any very small entries due to numerical
 % error.
 disp('global K...');
@@ -370,7 +370,7 @@ for p = 1:mel
             ntriplets = ntriplets + 1;
             I(ntriplets) = dof(i);
             J(ntriplets) = dof(j);
-            X(ntriplets) = ke(dofLocal(i), dofLocal(j), p);
+            X(ntriplets) = ke(dofLocal(i), dofLocal(j), 1);
         end
 
     end
@@ -591,6 +591,7 @@ else
     pause
 end
 
+% TODO #54 delete rows that correspond to the free degrees of fredom. Using problem sheet.
 for m = 1:length(fixedDofs)
     i = fixedDofs(m);
     K(:, i) = 0;

### 2020-12-09 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
sync before new images + simulation

@@
 \begin{align}
-    \vec{F}_{a} = \int_{S_{e}} \left[\tilde{\vec{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,,
+    \vec{F}_{a} = \int_{S_{e}} \left[\tns{\tilde{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,,
     \label{eq:ddd_fem_force}
@@
     \label{eq:gauss_leg_ddd_fem_force}
-    \vec{F}_{a} \approx \sum\limits_{i=1}^{Q} w_{i} \sum\limits_{j=1}^{Q} w_{j} [\tns{\sigma}(r_{i}, s_{j})\cdot \vec{n}] N_{a}(r_{i}, s_{j}) \det(\mtx{J})\,.
+    \vec{F}_{a} \approx \sum\limits_{i=1}^{Q} w_{i} \sum\limits_{j=1}^{Q} w_{j} [\tns{\tilde{\sigma}}(r_{i}, s_{j})\cdot \vec{n}] N_{a}(r_{i}, s_{j}) \det(\mtx{J})\,.
 \end{align}
@@
     \label{eq:stress}
-    \tns{\sigma}(\vec{x}) = &
+    \tns{\tilde{\sigma}}(\vec{x}) = &
     - \dfrac{\mu}{8\pi} \int\limits_{\mathbf{x_1}}^{\mathbf{x_2}} \left( \dfrac{2}{R_{a}^{3}} + \dfrac{3a^2}{R_{a}^{5}} \right) \left[ \left(\vec{R} \times \vec{b}\right) \otimes \mathrm{d}\vec{x'} + \mathrm{d}\vec{x'} \otimes \left(\vec{R} \times \vec{b}\right) \right]          \\
@@
 An example of what this looks like in terms of forces can be seen in \cref{f:rotate} (we removed the singularity to keep the graph smooth).
+% TODO #53 zoom in at 0 +/-10 degrees 
 \begin{figure}
@@
 We use three test cases, two edge dislocations and one screw, all of which have line direction $\vec{l} = [0\, 0\, 1]$ with Burgers vectors $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ \cite{head1953edge}, and $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ \cite{hirth1983theory}.
+% TODO #52 make coordinate system right handed, z out of the page
 \begin{figure}
@@
 However there is a further wrinkle in this problem: symmetry.
-To exemplify this we plot the relevant components of the stress tensor for the arrangement in \cref{f:gauss_quad_test}(a) we find \cref{f:sigma_perp_edge}.
+To exemplify this we plot the relevant components of the stress tensor for the arrangement found in \cref{f:gauss_quad_test}(a) we find \cref{sf:xzeperp,sf:yzeperp,sf:zzeperp}.
 The $\sigma_{xz}$ and $\sigma_{zz}$ components are antisymmetric about the centre of the element.
@@
 If we were to move the dislocation off-centre such that the rotational anti-symmetry about the origin is broken, the errors would increase.
-\begin{figure}
-    \centering
-    \subfloat[$\sigma_{xz}$.\label{sf:xzeperp}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/xz_eperp_5_000000.pdf}}
+
+We also plot the relevant stresses for the arrangement described by \cref{f:gauss_quad_test}(b) in \cref{sf:xzepar,sf:yzepar,sf:zzepar}.
+It is immediately apparent why gauss quadrature fails so spectacularly in \cref{f:rel_err_par_edge}.
+At low numbers of quadrature points, it fails to appropriately sample the rapidly changing value of $\tilde{\sigma}_{xz}$ at both ends of the dislocation as seen in \cref{sf:xzepar}, as well as the neighbourhood of the dislocation where $\tilde{\sigma}_{yz}$ changes most raplidly as shown in \cref{sf:yzepar}.
+Moreover, the further away the quadrature points are from the midpoint of the domain, the lower their relative weighting.
+So even with a relatively large number of them, there can still be large errors.
+Which is a particularly egregious problem in \cref{sf:yzepar}, and explains why such a large number of quadrature points is required to accurately compute the integral.
+\begin{figure}
+    \centering
+    \subfloat[\label{sf:xzeperp}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/sxzperpEdgeFiveb.pdf}}
     }
     ~
-    \subfloat[$\sigma_{yz}$.\label{sf:yzeperp}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/yz_eperp_5_000000.pdf}}
+    \subfloat[\label{sf:yzeperp}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/syzperpEdgeFiveb.pdf}}
     }
     ~
-    \subfloat[$\sigma_{zz}$.\label{sf:zzeperp}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/zz_eperp_5_000000.pdf}}
-    }
-    \caption{Relevant stress components to \cref{f:rel_err_perp_edge}.
-The antisymmetry of $\sigma_{xz}$ and $\sigma_{zz}$ makes them vanish when integrating.
-$\sigma_{yz}$ does not vanish, but its symmetry means Gauss quadrature works if sufficient quadrature points are used.}
-    \label{f:sigma_perp_edge}
+    \subfloat[\label{sf:zzeperp}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/szzperpEdgeFiveb.pdf}}
+    }
+
+    \subfloat[\label{sf:xzepar}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/sxzparEdgeFiveb.pdf}}
+    }
+    ~
+    \subfloat[\label{sf:yzepar}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/syzparEdgeFiveb.pdf}}
+    }
+    ~
+    \subfloat[\label{sf:zzepar}]
+    {
+        {\includegraphics[width=0.3\linewidth]{images/szzparEdgeFiveb.pdf}}
+    }
+    \caption{(a) to (c) show the relevant stress fields from a dislocation in the same configuration that yields the plots found in \cref{f:rel_err_perp_edge} as shown in \cref{f:gauss_quad_test}(a), where the closest node is a dislocation core radius away from the surface, $a = 5b$.
+(e) to (f) does the same for the configuration that yields \cref{f:rel_err_par_edge} as shown in \cref{f:gauss_quad_test}(b), where the whole dislocation is a core radius away from the surface, $a = 5b$.
+The white line or dot is the dislocation.}
+    \label{f:sigma_edge_test_config}
 \end{figure}
@@
 Despite these being artificially ideal examples that illustrate the failings of Gauss quadrature, other problematic scenarios commonly to show up in simulations.
-The problems tend to worsen with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces and more permissive mobility functions.
-Despite the highly localised nature of these large errors, the $\mathcal{O}(1/R)$ decay rate and chaotic nature of dislocation dynamics, means they often result in unwarranted topological changes.
-Such changes to the dislocation structure tend to have large and cascading effects as simulations advance.
-Which is particularly deleterious when doing simulations with higher dislocation densities and/or where a large number of dislocations are close to the surface, such as nanoindentation simulations.
+The problems tend to worsen with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces, more permissive mobility functions, and coarser FE meshes.
+The $\mathcal{O}(1/R)$ decay rate and chaotic nature of dislocation dynamics, means these errors may result in unwarranted topological changes that cascade a the simulation advances.
+This is particularly deleterious when doing simulations with higher dislocation densities and/or where a large number of dislocations are close to the surface, such as nanoindentation simulations.
 
@@
 
-\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, a $\textrm{A}$ superscript are the stresses derived from analytic tractions and $\textrm{N}$ for those coming from numeric ones.
-The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}}$.
+\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, the $\textrm{A}$ superscript are the stresses calculated from analytic tractions and the $\textrm{N}$ superscript are those coming from numeric tractions where $Q = 1$ (we use the same nomenclature in \cref{f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw}).
+The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}} = [1 0 0]$.
 It is clear edge effects play a role in the generated stresses.
 All three components have notable differences from the infinite-domain solutions resulting from the finite constraints.
-Regardless, the overall shape of the isolines is similar in all three solutions for corresponding stress components, particularly $\hat{\sigma}_{yy}$.
-The lobes of $\hat{\sigma}_{xx}$ for analytic and numeric tractions are deformed by the displacement boundary conditions on all surfaces other than $x = 0\, b$, where tractions are calculated.
-The effect is most dramatic when looking near the top and bottom of the domain, where the final isolines flare towards the traction surface.
-The shear stresses $\hat{\sigma}_{xy}$ are also somewhat different, with similar flaring.
-However, as they radiate in the $x$-direction, the deviations away from the infinite-domain solutions flare away from the $x = 1000\, b$ surface.
-That said, all stress fields calculated from analytic and numeric tractions look fairly similar for $\vec{b} = \vec{b}_{\textrm{e1}}$.
-\begin{figure}
-    \centering
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxeperp}]
+There is also some artifacting (\cref{sf:syyAeperp,sf:sxyAeperp}) arising from the perturbation needed to avoid the singularity in the analytic traction calculation and error propagation from floating point arithmetic, as mentioned in \cref{s:method}.
+Of note is the large degree of asymmetry between both lobes of \cref{sf:sxxNeperp}, this is not a simple artifact due to numerical precision but a result of the numerical instability of gauss quadrature.
+Regardless, the overall shape of the isolines is similar in all three solutions for corresponding stress components.
+% TODO #51 make sure captions are correct and set the axes properly in figs 13-15 and 17
+\begin{figure}
+    \centering
+    \subfloat[%$\hat{\sigma}_{xx}$.
+        \label{sf:sxxeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAeperp}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
+        \label{sf:sxxAeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNeperp}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
+        \label{sf:sxxNeperp}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:syyeperp}]
+    \subfloat[%$\hat{\sigma}_{yy}$.
+        \label{sf:syyeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:syyAeperp}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
+        \label{sf:syyAeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:syyNeperp}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
+        \label{sf:syyNeperp}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:sxyeperp}]
+    \subfloat[%$\hat{\sigma}_{xy}$.
+        \label{sf:sxyeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$.\label{sf:sxyAeperp}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
+        \label{sf:sxyAeperp}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$.\label{sf:sxyNeperp}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
+        \label{sf:sxyNeperp}]
     {
@@
     }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, with $a = 10~b$ with coordinates $(26.3158,~ 500)~b$, i.e.
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, where $a = 10~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
 the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
-Here $b = \lVert \vec{b} \rVert \equiv 1$.}
+From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript).
+The subfigure rows from top to bottom represent $\hat{\sigma}_{xx}$, $\hat{\sigma}_{yy}$ and $\hat{\sigma}_{xy}$.}
     \label{f:head_vs_ana_vs_num_eperp}
@@
 Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions.
-If we look at the neighbourhood of the dislocation, we will find a sign inversion as well as a drastically different isosurface shape, where the isolines are not merely deformed, they are fundamentally different when calculated with numeric tractions.
-Stresses like those can lead to dislocations problems, particularly if it just so happens that the sign inversion also comes with an increased force magnitude, something that is possible judging from \cref{f:rel_err_par_edge,f:rel_err_par_edge}.
+If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion (yellow and green contours as opposed to purple and blue) as well as a drastically different isosurface shape Here the isolines are not merely deformed nor pinched in the way that is indicative of numerical artifacting.
+They are fundamentally different when calculated with numeric tractions.
+Image stresses like those can lead dislocations to behave differently than they should, particularly if the sign inversion also comes with an increased force magnitude, which judging from \cref{f:rel_err_par_edge} is quite possible.
 Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive.
@@
     \centering
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar}]
+    \subfloat[%$\hat{\sigma}_{xx}$.
+        \label{sf:sxxepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
+        \label{sf:sxxAepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNepar}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
+        \label{sf:sxxNepar}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:syyepar}]
+    \subfloat[%$\hat{\sigma}_{yy}$.
+        \label{sf:syyepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:syyAepar}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
+        \label{sf:syyAepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:syyNepar}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
+        \label{sf:syyNepar}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:sxyepar}]
+    \subfloat[%$\hat{\sigma}_{xy}$.
+        \label{sf:sxyepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xy}$.\label{sf:sxyAepar}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
+        \label{sf:sxyAepar}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xy}$.\label{sf:sxyNepar}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
+        \label{sf:sxyNepar}]
     {
@@
     }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$, where $a = 10~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
+the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
+From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript).
+The subfigure rows from top to bottom represent $\hat{\sigma}_{xx}$, $\hat{\sigma}_{yy}$ and $\hat{\sigma}_{xy}$.}
     \label{f:head_vs_ana_vs_num_epar}
@@
     \centering
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxzscrew}]
+    \subfloat[%$\hat{\sigma}_{xz}$.
+        \label{sf:sxzscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxzAscrew}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xz}$.
+        \label{sf:sxzAscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxzNscrew}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xz}$.
+        \label{sf:sxzNscrew}]
     {
@@
 
-    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:szyscrew}]
+    \subfloat[%$\hat{\sigma}_{yz}$.
+        \label{sf:szyscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{yy}$.\label{sf:syzAscrew}]
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{yz}$.
+        \label{sf:syzAscrew}]
     {
@@
     }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:syzNscrew}]
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{yz}$.
+        \label{sf:syzNscrew}]
     {
@@
     }
-    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$. The rest is the same as \cref{f:head_vs_ana_vs_num_eperp}.}
+    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$, where $a = 10~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
+the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
+From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript).
+The subfigure rows from top to bottom represent $\hat{\sigma}_{xz}$ and $\hat{\sigma}_{yz}$.}
     \label{f:head_vs_ana_vs_num_screw}
@@
 \Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e.
-through the line $x = 52.6316\, b$.
+through the line $x = 50\, b$.
 \Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$.
@@
 However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions.
-Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in every case.
+Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
 \begin{figure}
@@
     }
-    \caption{Line plots of the image stresses at $x = 52.6316\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
+    \caption{Line plots of the image stresses at $x = 50\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
 The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$.
@@
 
-We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $26.3158\, b$ (centre of the first element) to $500\, b$ (centre of the 10th element).
+We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $25.6410\, b$ (centre of the first element) to $1000\, b$ (centre of the 10th element).
 The line plots are taken from the closest set of nodes in the positive $x$-direction i.e.
-at $x = 52.6316\, 526.3158\, b$.
+at $x = 50\, 526.3158\, b$.
 \begin{figure}
@@
     {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar2.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar2.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar.pdf}}
     }~
@@
     {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar2.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar.pdf}}
     }
@@
     \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$.
-(a) to (c) and (g) to (i) at $(26.3158,\, 500)\, b$; (d) to (f) and (j) to (l) at $(500,\, 500)\, b$.
+(a) to (c) and (g) to (i) at $(25.6410,\, 1000)\, b$; (d) to (f) and (j) to (l) at $(1000,\, 1000)\, b$.
 (a) to (g) image stresses; (g) to (l) total stresses.}
@@
 (a) and (c) are of image stresses; (b) and (d) are of total stresses.
-(a) and (b) are of a dislocation at $(26.3158,\, 500)\, b$, taken along the line $x = 52.6316\, b$.
-(b) and (d) are of a dislocation at $(500,\, 500)\, b$ taken along the line $x = 526.3158\, b$.}
+(a) and (b) are of a dislocation at $(25.6410,\, 1000)\, b$, taken along the line $x = 50\, b$.
+(b) and (d) are of a dislocation at $(1000,\, 1000)\, b$ taken along the line $x = 1525\, b$.}
     \label{f:line_head_vs_ana_vs_num_epar2to11}

### 2020-12-09 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m

@@ -101,7 +101,7 @@ for j = 40%61%80%81
     y1 = y(1);
     t = [0 0 1];
     n = [1 0 0];
-    rn = zeros(len, 3);
+    rn = zeros(len, 4);
     rn(:, 1) = x;
     rn(:, 2) = y;
     rn(:, 3) = z;
@@ -155,7 +155,7 @@ for k = 1:2
     syyN = squeeze(sigmaN(2, 2, :, :));
     sxyN = squeeze(sigmaN(1, 2, :, :));
 
-    segments = constructsegmentlist(rn, links, doSave);
+    segments = constructsegmentlist(rn, links, true);
     p1 = [segments(:, 6) segments(:, 7) segments(:, 8)];
     p2 = [segments(:, 9) segments(:, 10) segments(:, 11)];
 
@@ -312,7 +312,7 @@ end
 [uhat2, fend2, Ubar2, fnum] = STATIC_FEMcoupler(rn, links, 0, a, MU, NU, xnodes, mno, kg, K, L, U, P_l, P_u, ...
     gammau, gammat, gammaMixed, fixedDofs, freeDofs, dx, simTime);
 
-segments = constructsegmentlist(rn, links, doSave);
+segments = constructsegmentlist(rn, links, true);
 p1 = [segments(:, 6) segments(:, 7) segments(:, 8)];
 p2 = [segments(:, 9) segments(:, 10) segments(:, 11)];
 
@@ -404,12 +404,12 @@ plotCountourfSigmaHat(X, Y, syzN, x1, y1, orientationB, symbol, 'yz', 'N', 'x,~b
 % Line plots
 % Edge perp
 close all
-i = 2;
+i = 3;
 symbol = '\hat{\sigma}';
 orientationB = 'Eperp';
-linePlot(sxxAperp(:, i), sxxNperp(:, i), txxPerp(:, i), orientationB, symbol, 'xx', 'Grid Point', '$\mu$', 30, doSave)
-linePlot(syyAperp(:, i), syyNperp(:, i), tyyPerp(:, i), orientationB, symbol, 'yy', 'Grid Point', '$\mu$', 30, doSave)
-linePlot(sxyAperp(:, i), sxyNperp(:, i), txyPerp(:, i), orientationB, symbol, 'xy', 'Grid Point', '$\mu$', 30, doSave)
[…]

### 2020-12-09 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Update coordinates.

@@
     }
-    \caption{Line plots of the image stresses at $x = 50\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
+    \caption{Line plots of the image stresses at $x = 102.5641\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
 The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$.
@@
 We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $25.6410\, b$ (centre of the first element) to $1000\, b$ (centre of the 10th element).
-The line plots are taken from the closest set of nodes in the positive $x$-direction i.e.
-at $x = 50\, 526.3158\, b$.
+The line plots are taken from the second closest set of nodes in the positive $x$-direction i.e.
+at $x = 102.5641\, \sim 1076.9231\, b$.
 \begin{figure}
@@
 (a) and (c) are of image stresses; (b) and (d) are of total stresses.
-(a) and (b) are of a dislocation at $(25.6410,\, 1000)\, b$, taken along the line $x = 50\, b$.
-(b) and (d) are of a dislocation at $(1000,\, 1000)\, b$ taken along the line $x = 1525\, b$.}
+(a) and (b) are of a dislocation at $(25.6410,\, 1000)\, b$, taken along the line $x = 102.5641\, b$.
+(b) and (d) are of a dislocation at $(1000,\, 1000)\, b$ taken along the line $x \approx 1076.9231\, b$.}
     \label{f:line_head_vs_ana_vs_num_epar2to11}
@@
 
-As expected, all solutions converge as the distance from the dislocation to surface increases because the magnitude of the real stresses increases in relation to that of the image stresses\footnote{The image stress components of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2} are reflections about the line $x=0$ plus a corrective term that decays faster than the reflection term.
+As expected, all solutions converge as the distance from the dislocation to surface increases because the magnitude of the real stresses increases in relation to that of the image stresses\textsuperscript{\footnote{The image stress components of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2} are reflections about the line $x=0$ plus a corrective term that decays faster than the reflection term.
 In \cref{eq:imageStressAnalyticScrew}, the image term is a reflection about the line $x=0$.
-Therefore in both cases, as the dislocation moves away from the surface, the real stresses get relatively larger when compared to the image ones.}.
+Therefore in both cases, as the dislocation moves away from the surface, the real stresses get relatively larger when compared to the image ones.}}.
 

### 2020-12-11 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/HeadVsFEM_ReactionForce.m
New figures.

@@ -17,7 +17,7 @@ MU = 1;
 NU = 0.28;
 
 % Lattice constants
-a = 10;
+a = 5;
 bVec = [[1 0 0]; [0 1 0]];
 nVec = [[0 1 0]; [1 0 0]];
 

### 2020-12-11 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex

@@
 The whole dislocation was segmented into $10^4$ pieces of length $100\, b$ to prevent the dislocation from intersecting the surface element when they were rotated to avoid the singularity.
-The relative error at large distances ($>10^6 b$) converges to one due to artifacting when dividing two very small double precision numbers.
+The relative error at large distances ($>10^6 b$) converges to one due to loss of significance when dividing two very small, limited precision numbers.
 The absolute error always goes towards zero with increasing distance from the surface.}
@@
     }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, where $a = 10~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
 the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
@@
     }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$, where $a = 10~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
 the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
@@
     }
-    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$, where $a = 10~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
+    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
 the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
@@
     {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot2.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot3.pdf}}
     }~
@@
     {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot2.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot3.pdf}}
     }~
@@
     {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot2.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot3.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar2.pdf}}
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar3.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot2.pdf}}
+        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot3.pdf}}
     }~

### 2021-01-06 src/EasyDD.m
Made changes to save and simulation ending. Fixes #62

@@ -100,13 +100,21 @@ plotFEMDomain(Stop, Sbot, Sright, Sleft, Sfront, Sback, Smixed, xnodes)
 u_tilda_0 = calculateUtilda(rn, links, gamma_disp, NU, xnodes, dx, ...
     dy, dz, mx, my, mz, u_tilda_0);
 close all
-% TODO #62
-save(sprintf('../output/initial_%s_%d', simName, curstep));
+save(sprintf('../output/initial_%s_%d', simName, curstep), 'K','kg','L','U','P_l','P_u');
 
 fprintf('Initialisation complete.\n');
 %%
 while simTime < totalSimTime
-
+    if ~any(rn(:, 4) == 0)
+        fprintf('No more real segments, ending simulation.\n')
+        return;
+    end
+    
+    if mod(curstep, saveFreq) == 0
+        close all
+        save(sprintf('../output/%s_%d', simName, curstep), '-regexp', '^(?!(K|kg|L|U|P_l|P_u)$).');
+    end
+    
     % Loading function.
     [sign_u_dot, u_dot, sign_f_dot, f_dot, u_tilda_0, u, u_hat, u_tilda] = calculateLoading(...
         sign_u_dot, u_dot, sign_f_dot, f_dot, u_tilda_0, u, f_bar, f_hat, f_tilda, u_bar, ...
@@ -161,21 +169,8 @@ while simTime < totalSimTime
         linksnew, connectivitynew, linksinconnectnew, fsegnew);
 
     [curstep, simTime] = updateTime(curstep, simTime, dt);
-
-    if mod(curstep, saveFreq) == 0
-        close all;
-        save(sprintf('../output/%s_%d', simName, curstep), '-regexp', '^(?!(K|kg|L|U|P_l|P_u)$).');
-    end
-
-    if ~any(rn(:, 4) == 0)
-        fprintf('No more real segments, ending simulation.\n')
-        close all;
-        save(sprintf('../output/%s_%d', simName, curstep), '-regexp', '^(?!(K|kg|L|U|P_l|P_u)$).');
-        return;
-    end
-
 end
 
 fprintf('Simulation completed.\n')
-close all;
+close all
 save(sprintf('../output/%s_%d', simName, curstep), '-regexp', '^(?!(K|kg|L|U|P_l|P_u)$).');

### 2021-01-06 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Added zoom to rotation graph. Fixes zoom in at 0 +/-10 degrees #53.

@@
 An example of what this looks like in terms of forces can be seen in \cref{f:rotate} (we removed the singularity to keep the graph smooth).
-% TODO #53 zoom in at 0 +/-10 degrees 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect.pdf}
+\begin{figure}
+    \centering
+    \subfloat[Full rotation of a segment.]{{\includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect.pdf}}}
+
+    \subfloat[Zoom of the rotation of a segment $\pm 10~\text{deg}$.]{{\includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect_zoom.pdf}}}
     \caption{Example of the components of the total force on a surface element (the force summed over all four FE nodes) as a dislocation segment parallel to the surface element ($\theta = 0$) is rotated about its midpoint around the axis defined by $\vec{l}\times\vec{n}$.

### 2021-01-06 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/images/tilted_segment.py

@@ -1,0 +1,54 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jun  6 15:55:48 2017
+
+@author: daniel
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+# Close all figures.
+plt.close("all")
+# Matplotlib parameters to use TeX font and customise text size.
+plt.rc("text", usetex=True)
+plt.rc("font", family="serif", size=18)
+plt.rcParams["lines.linewidth"] = 4
+plt.rcParams["text.latex.preamble"] = r"\usepackage{bm}"
+plt.rcParams.update({'figure.autolayout': True})
+
+data = np.loadtxt("test.txt")
+theta = data[0:, 0]
+fx = data[0:, 1]
+fy = data[0:, 2]
+fz = data[0:, 3]
+
+
+fig = plt.figure(1, figsize=(10, 10/1.618))
+ax = fig.add_subplot(111)
+ax.plot(theta, fx, "-", label=r"$F_{x}(\theta)$")
+ax.plot(theta, fy, "-", label=r"$F_{y}(\theta)$")
+ax.plot(theta, fz, "-", label=r"$F_{z}(\theta)$")
+ax.legend(bbox_to_anchor=(0.3, 0.4))
+ax.set_ylabel(r"Force, A.U.")
+ax.set_xlabel(r"$\theta$, deg")
+ax.set_xlim([-180, 180])
+ax.set_yticks(np.arange(-0.05, 0.06, 0.01))
+ax.set_xticks(np.arange(-180, 210, 30))
+ax.grid(True, which='both')
+plt.savefig('ftot_rotation.pdf', format='pdf')
+
+
+fig = plt.figure(2, figsize=(10, 10/1.618))
+ax = fig.add_subplot(111)
+ax.plot(theta, fx, "-", label=r"$F_{x}(\theta)$")
+ax.plot(theta, fy, "-", label=r"$F_{y}(\theta)$")
+ax.plot(theta, fz, "-", label=r"$F_{z}(\theta)$")
+ax.legend(bbox_to_anchor=(0.3, 0.4))
+ax.set_ylabel(r"Force, A.U.")
+ax.set_xlabel(r"$\theta$, deg")
+ax.set_xlim([-10, 10])
+ax.set_yticks(np.arange(-0.05, 0.06, 0.01))
+ax.set_xticks(np.arange(-10, 11, 2))
+ax.grid(True, which='both')
[…]

### 2021-01-06 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Fixed some footnotes.

@@
 The whole dislocation was segmented into $10^4$ pieces of length $100\, b$ to prevent the dislocation from intersecting the surface element when they were rotated to avoid the singularity.
-The relative error at large distances ($>10^6 b$) converges to one due to loss of significance when dividing two very small, limited precision numbers.
-The absolute error always goes towards zero with increasing distance from the surface.}
+The relative error at large distances ($>10^6 b$) converges to one due to loss of significance.}
     \label{f:rel_err_par_edge}
@@
 In \cref{f:rel_err_par_edge}, we observe the relative errors decrease and then converge to $\sim 1$ as the distance grows larger.
-The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, resulting in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim 1$ when done with limited precision.
-Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$\footnote[1]{The absolute error \textit{always} decreases as the distance from the surface element increases, but absolute errors are not as useful tools of comparison as long as we are conscious of small artifacting from limited precision.}.
+The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, resulting in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim 1$.
+This is a well-known problem when dealing with finite precision arithmetic known as loss of significance.
+Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$.
 However, when the segment is close to the surface, the relative errors are large ($\gg1$) unless using a large number of quadrature points, for example \cref{f:gauss_quad_test}(a) shows that $Q\geq100$ are required when the distance $x^1_z = 15b$.

### 2021-01-08 src/mobbcc_bb1b.m
Added new flag for fixed surface nodes. Found a case where numeric tractions go wrong.

@@ -213,6 +213,7 @@ function [vn, fn] = mobbcc_bb1b(fseg, rn, links, connectivity, nodelist, conlist
         end
 
     end
+    
     if rotateCoords
         vn = vn * rotMatrix';
         fn = fn * rotMatrix';

### 2021-01-08 src/remesh_surf.m

@@ -134,7 +134,7 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = ...
 
     while i < size(rnnew, 1)
 
-        if rnnew(i, end) ~= 6
+        if rnnew(i, end) ~= 6 || rnnew(i, end) ~= 61
             i = i + 1;
             continue
         end
@@ -145,7 +145,7 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = ...
         for j = 1:numcon
             connode = linksnew(connectivitynew(i, 2 * j), 3 - connectivitynew(i, 2 * j + 1));
 
-            if rnnew(connode, end) == 6
+            if rnnew(connode, end) == 6 || rnnew(connode, end) == 61
                 [rnnew, connectivitynew, linksnew, linksinconnectnew, fsegnew, ~] = mergenodes(rnnew, connectivitynew, linksnew, linksinconnectnew, fsegnew, connode, i, 1, 1, 1, 1);
                 %             if nodeid~=0
                 %                 [rnnew] = movetosurf(rnnew,linksnew,nodeid,vertices);
@@ -170,7 +170,7 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = ...
 
     for i = 1:L1%length(rnnew)  ET updated- check!
 
-        if rnnew(i, end) ~= 6
+        if rnnew(i, end) ~= 6 || rnnew(i, end) ~= 61
             continue;
         end
 
@@ -205,7 +205,7 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = ...
 
     while i < size(rnnew, 1)
 
-        if rnnew(i, end) ~= 6
+        if rnnew(i, end) ~= 6 || rnnew(i, end) ~= 61
             i = i + 1;
             continue
         end

### 2021-01-08 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/Input_HeadVsFEM_ReactionForce.m

@@ -19,12 +19,12 @@ a = 5;
 % nVec = [-1 1 0];
 
 % With rotation matrix.
-n1 = [1 0 0]; e1 = [1;-1;0]; e1 = e1/norm(e1);
-n2 = [0 1 0]; e2 = [1;1;1]; e2 = e2/norm(e2);
+n1 = [1 0 0]; e1 = [1;1;1]; e1 = e1/norm(e1);
+n2 = [0 1 0]; e2 = [1;-1;0]; e2 = e2/norm(e2);
 n3 = cross(n1,n2); e3 = cross(e1,e2); e3 = e3/norm(e3);
 rotMatrix = [e1 e2 e3]';
-bVec = [0 1 0];
-nVec = [-1 0 0];
+bVec = [1 0 0]*sqrt(3)/2;
+nVec = [0 1 0];
 
 bVec * rotMatrix
 nVec * rotMatrix
@@ -37,9 +37,9 @@ mx = 20;
 my = 20;
 mz = 20;
 
-mobility = @mobbcc1;
-% mobility = @mobbcc_bb1b;
-% simName = strcat(simName, '_bb');
+% mobility = @mobbcc1;
+mobility = @mobbcc_bb1b;
+simName = strcat(simName, '_bb');
 simType = @NumTracVsAnaTrac;
 
 Fsim = [];
@@ -69,10 +69,14 @@ len = 100;
 xcoord = linspace(0, dx, gridSize);
 ycoord = linspace(0, dy, gridSize);
 %  xcoord = xcoord(2) / 4 % there were substantial differences
-xcoord = xcoord(2)/2; % middle of first element.
-% xcoord = dx / 16; % eigth of the domain.
+% xcoord = xcoord(2)/2; % middle of first element.
+xcoord = dx / 32; % eigth of the domain.
+% xcoord = 3*dx / 32; % eigth of the domain.
 % xcoord = dy / 16; % middle of third element.
-
+%% This makes the numeric tractions exit but not the analytic. Haven't found another case.
+% ycoord = dy / 2 + 20; % middle of the domain
+% xcoord = dx / 16; % eigth of the domain.
+%%
 ycoord = dy / 2; % middle of the domain
 % ycoord = ycoord(2)/2; % middle of first element
 simName = strcat(simName, 'corner');
@@ -88,14 +92,91 @@ rn(:, 1) = x;
 rn(:, 2) = y;
 rn(:, 3) = z;
 links = zeros(len - 1, 8);
[…]

### 2021-01-08 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex

@@
     }
-    \caption{Line plots of the image stresses at $x = 102.5641\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
+    \caption{Line plots of the image stresses at $x = 102.5641\, b$ (start of the third element) for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
 The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$.

### 2021-02-14 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Fixed separation-collision loop, added infrastructure and input files for tensile tests, improved integrator, fixed out of bound indexing in pkforce, fixed fcc mobility, added stuff for traction paper, backported node sets.

--- 2021-01-06 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
@@
 \usepackage{lmodern}
+% \usepackage{snapshot}
 \graphicspath{{./images/}}
@@
 We compare the behaviour of the errors which arise when using numerical integration, provide insight into how and why they occur and give recommendations on avoiding numerical issues when implementing the analytic solution.
-Evaluating the tractions analytically in a large scale discrete dislocation plasticity simulations of a microcantilever showed a clear difference in the simulated load-displacement curve while the dislocation structure was unchanged.
+Comparisons to infinite-domain solutions and a very simple unloaded simulation shows the drastic differences between the two methods.
 \end{abstract}
@@
 
-Coupling discrete dislocation dynamics (DDD) to the finite element method (FEM) allows micromechanical tests to be simulated \cite{Groh2009}.
+Coupling discrete dislocation dynamics (DDD) to the finite element method (FEM) allows micromechanical tests to be simulated with explicit dislocation interactions \cite{Groh2009}.
 Virtual experiments are essential for interpreting experimental data and relating the measured mechanical response to dislocation mechanisms \cite{0965-0393-6-6-007,doi:10.1080/14786430500341250,tarleton2015discrete,YU2018}.
-One of the most popular methods for coupling DDD and FEM is the superposition method \cite{superposition_scheme0,superposition_scheme1,superposition_scheme2}.
+One of the most popular and simplest methods for coupling DDD and FEM is the superposition method \cite{superposition_scheme0,superposition_scheme1,superposition_scheme2}, which works by decomposing the problem into separate DDD and FE problems as illustrated in \cref{f:superposition_scheme}.
 %
@@
 The volume $V$ is bounded by a surface $S = S_{T} \cup S_{U}$ and contains a dislocation ensemble and is subjected to tractions $\vec{T}$ on $S_{T}$ and $\vec{u}$ on $S_{u}$.
-First, the traction, $\vec{\tilde{T}}$, and displacement, $\vec{\tilde{U}}$, fields due to the dislocations in the infinite domain (DDD) are evaluated on the boundaries $S_{T}$ and $S_{U}$ respectively.
+First, the traction, $\vec{\tilde{T}}$, and displacement, $\vec{\tilde{u}}$, fields due to the dislocations in the infinite domain (DDD) are evaluated on the boundaries $S_{T}$ and $S_{U}$ respectively.
 Then an elastic boundary value problem can be solved with FEM to calculate the corrective elastic fields required to satisfy the boundary conditions $\vec{\hat{T}} = \vec{T} - \vec{\tilde{T}}$ and $\vec{\hat{u}} = \vec{U} - \vec{\tilde{U}}$.}
@@
 \end{figure}
-%        
-The superposition scheme works by decomposing the problem into separate DDD and FE problems as in \cref{f:superposition_scheme}.
-A linear-elastic solid $V$ bounded by a surface $S$ is subjected to traction boundary conditions, $\vec{T}$, on $S_{T}$ and displacement boundary conditions, $\vec{U}$, on $S_{U}$.
-The ($\tilde{~}$) fields are those generates by the dislocations in an infinite solid and are obtained by evaluating analytic solutions in a DDD simulation \cite{Cai2006}.
-Formally the dislocation field satisfies
-%
+
+Specifically, a linear-elastic solid $V$ bounded by a surface $S$ is subjected to traction boundary conditions, $\vec{T}$, on $S_{T}$ and displacement boundary conditions, $\vec{U}$, on $S_{U}$.
+The ($\tilde{~}$) fields are those generated by the dislocations in an infinite solid and in our case are obtained by evaluating analytic solutions in a DDD simulation \cite{Cai2006}.
+Formally, the dislocation field satisfies,
 \begin{align}
@@
     \begin{array}{l}
-        \nabla\cdot{\vec{\tilde{\sigma}}} = 0                    \\
-        \vec{\tilde{\sigma}} = \vec{C}:\tilde{\vec{\varepsilon}} \\
-        \tilde{\vec{\varepsilon}}=\frac{1}{2}\left(\nabla\tilde{\vec{u}}+(\nabla\tilde{\vec{u}})^T\right)
+        \nabla \cdot \tns{\tilde{\sigma}} = \vec{0}                \\
+        \tns{\tilde{\sigma}} = \tns{C} : \tns{\tilde{\varepsilon}} \\
+        \tns{\tilde{\varepsilon}} = \frac{1}{2} \left( \nabla \vec{\tilde{u}} + (\nabla \vec{\tilde{u}})^T \right)
     \end{array}
-    \right\}\textrm{in V}                                                   \\
-    %
-     & \tilde{\vec{\sigma}}\cdot\vec{n} = \tilde{\vec{T}} \textrm{ on } S_T \\
+    \right\} \quad \textrm{in V}                                                   \\
+    %
+     & \tilde{\tns{\sigma}} \cdot \vec{n} = \tilde{\vec{T}} \quad \textrm{on } S_T \\
     %
@@
     \begin{array}{l}
-        \tilde{\vec{u}} = \tilde{\vec{U}} \quad t>0 \\
-        \tilde{\vec{u}} = \vec{0} \quad t=0
+        \vec{\tilde{u}} = U, \quad t>0 \\
+        \vec{\tilde{u}} = \vec{0}, \quad t=0
         \label{eq:utildebc}
     \end{array}
-    \right\} \textrm{ on } S_U.
-\end{align}
-%
-As the dislocation fields do not vanish on $S$ the dislocations load the volume by generating tractions, $\tilde{\vec{T}}$, on $S_T$ and displacements, $\tilde{\vec{U}}$, on $S_U$ this additional loading deforms $V$ generating an additional ``image'' stress which the dislocations then feel.
+    \right\} \quad \textrm{on } S_U \,.
+\end{align}
+%
+As the dislocation fields do not vanish on $S$, the dislocations load the volume by generating tractions, $\tilde{\vec{T}}$, on $S_T$ and displacements, $\vec{\tilde{u}}$, on $S_U$.
+This additional loading deforms $V$, generating an additional ``image'' stress which the dislocations then feel.
 Therefore corrective ($\hat{~}$) fields must be superimposed to satisfy the desired boundary conditions.
-The corrective field which accounts for both the applied and image stress is obtained numerically by solving the elastic boundary value problem
+The corrective field which accounts for both the applied and image stress is obtained numerically by solving the elastic boundary value problem,
 %
@@
     \begin{array}{l}
-        \nabla\cdot{\vec{\hat{\sigma}}} = 0                  \\
-        \vec{\hat{\sigma}} = \vec{C}:\hat{\vec{\varepsilon}} \\
-        \hat{\vec{\varepsilon}}=\frac{1}{2}\left(\nabla\hat{\vec{u}}+(\nabla\hat{\vec{u}})^{T}\right)
-    \end{array}
-    \right\}\textrm{in V}                                                                            \\
-    %
-     & \hat{\vec{\sigma}}\cdot\vec{n} = \vec{T} - \tilde{\vec{T}} \textrm{ on } S_T\label{eq:thatbc} \\
-    %
-     & \hat{\vec{u}} = \vec{U} - \tilde{\vec{U}} \textrm{ on } S_U \label{eq:uhatbc}
-\end{align}
-%
-once the solution to both problems are known, then their superposition solves the desired mixed boundary value problem:
+        \nabla \cdot \tns{\hat{\sigma}} = \vec{0}              \\
+        \tns{\hat{\sigma}} = \tns{C} : \tns{\hat{\varepsilon}} \\
+        \tns{\hat{\varepsilon}} = \frac{1}{2} \left( \nabla \vec{\hat{u}} + (\nabla \vec{\hat{u}})^{T} \right)
+    \end{array}\right\} \quad \textrm{in V}                                                  \\
+    %
+     & \hat{\tns{\sigma}}\cdot\vec{n} = \vec{T} - \tilde{\vec{T}} \quad \textrm{on } S_T \label{eq:thatbc} \\
+    %
+     & \vec{\hat{u}} = \vec{U} - \vec{\tilde{u}} \quad \textrm{on } S_U \,. \label{eq:uhatbc}
+\end{align}
+%
+Once the solutions to both problems are known, their superposition solves the desired mixed boundary value problem,
 %
@@
     \begin{array}{l}
-        \nabla\cdot\vec{\sigma}=\nabla\cdot\left(\vec{\hat{\sigma}} +\vec{\tilde{\sigma}}\right) = 0                                                              \\
-        \vec{\sigma} =\vec{\hat{\sigma}}+\vec{\tilde{\sigma}}= \vec{C}:\left(\hat{\vec{\varepsilon}}+\tilde{\vec{\varepsilon}}\right)=\vec{C}:{\vec{\varepsilon}} \\
-        \vec{\varepsilon}=\hat{\vec{\varepsilon}}+\tilde{\vec{\varepsilon}}=\frac{1}{2}\left(\nabla(\hat{\vec{u}}+\tilde{\vec{u}})+\left(\nabla(\hat{\vec{u}}+\tilde{\vec{u}})\right)^T\right) =\frac{1}{2}\left(\nabla\vec{u}+(\nabla\vec{u})^{T}\right)
+        \nabla \cdot \tns{\sigma} = \nabla \cdot \left( \tns{\hat{\sigma}} + \tns{\tilde{\sigma}} \right) = \vec{0}                                                             \\
+        \tns{\sigma} = \tns{\hat{\sigma}} + \tns{\tilde{\sigma}} = \tns{C} : \left( \tns{\hat{\varepsilon}} + \tns{\tilde{\varepsilon}} \right) = \tns{C} : {\tns{\varepsilon}} \\
+        \tns{\varepsilon} = \tns{\hat{\varepsilon}} + \tns{\tilde{\varepsilon}} = \frac{1}{2} \left( \nabla ( \vec{\hat{u}} + \vec{\tilde{u}} ) + \left[ \nabla ( \vec{\hat{u}} + \vec{\tilde{u}} ) \right]^T \right) = \frac{1}{2} \left( \nabla \vec{u} + ( \nabla \vec{u} )^{T} \right)
     \end{array}
-    \right\}\textrm{in V}                                    \\
-    %
-     & \vec{\sigma}\cdot\vec{n} = \vec{T}  \textrm{ on } S_T \\
+    \right\}\quad \textrm{in V}                                    \\
+    %
+     & \tns{\sigma} \cdot \vec{n} = \vec{T} \quad \textrm{on } S_T \\
     %
@@
     \begin{array}{l}
-        \vec{u} = \vec{U} \quad t>0 \\
-        \vec{u} = \vec{0} \quad t=0
+        \vec{u} = \vec{U}, \quad t>0 \\
+        \vec{u} = \vec{0}, \quad t=0
     \end{array}
-    \right\} \textrm{ on } S_U
+    \right\} \quad \textrm{on } S_U
     \label{eq:ubc}
@@
 
-The method is not without problems however.
-As a dislocation segment moves closer to the surface, its ($\tilde{~}$) field diverges and starts causing numerical problems \cite{boundary_problems_in_dd}.
-This can be partially solved by using a non-singular formulation such as that proposed by \citet{Cai2006} however the gradients in the dislocation field are difficult to accurately capture when a dislocation approaches $S$.
-Another problem with this method is the computational cost when simulating a heterogeneous solid as it requires calculating polarisation stresses due to the difference in the elastic constants in a secondary phase \cite{superposition_scheme0,boundary_problems_in_dd,ddd_precipitate}.
-A modified superposition scheme \cite{ODay2004} can overcome this by dividing the problem into separate DDD/FEM problems coupled through 1 elastic FE problem.
-This requires accurate evaluation of $\tilde{T}$ on the domain boundaries which can only be captured with a fine FE mesh.
-This in turn will increase the computational cost.
-In order to simulate polycrystalline or composite materials using superposition requires methods to accurately evaluate both $\tilde{\vec{U}}$ and $\tilde{\vec{T}}$.
-The displacements can be evaluated analytically \cite{ddd_disp} and this paper investigates the evaluation of the dislocation tractions analytically.
-
-The relative simplicity of the superposition method has made it a popular choice for coupling DDD and FEM since all it requires is the evaluation of FE nodal forces and displacements on the boundary.
-Furthermore, analytic expressions for the stress field produced by a finite straight dislocation line segment, has allowed \citet{Queyreau} to use a non-singular formulation to obtain a closed-form solution for the tractions generated by a segment on the surface of a finite element.
-They used integration by parts giving rise to a number of recursion relations that can be used to construct the full solution from a small set of seed functions.
+For all its simplicity and elegance, the method is not without issue.
+As the distance between dislocation and surface decreases, $\tns{\tilde{\sigma}}$ diverges \cite{boundary_problems_in_dd}.
+This can be partially solved by using a non-singular formulation for $\tns{\tilde{\sigma}}$, such as that proposed by \citet{Cai2006}.
+Regardless, the steep gradients in the dislocation field are difficult to accurately capture as the dislocation approaches $S$.
+Another problem with this method is the large computational cost when simulating a heterogeneous solid, as this requires calculating polarisation stresses due to the difference in the elastic constants between phases \cite{superposition_scheme0,boundary_problems_in_dd,ddd_precipitate}.
+
+A modified superposition scheme \cite{ODay2004} can overcome this by dividing the problem into separate DDD-FEM problems coupled through a elastic FE problem.
+This requires accurate evaluation of $\vec{\tilde{T}}$ on the domain boundaries---which can only be captured with a fine FE mesh---increasing the computational cost.
+Therefore, simulating polycrystalline or composite materials using superposition necesitates methods to accurately evaluate both $\vec{\tilde{u}}$ and $\vec{\tilde{T}}$.
+The displacements can be evaluated analytically as shown by \cite{bromage2018calculating} and this paper investigates the evaluation of the dislocation tractions analytically.
+
+As previously mentioned, the relative simplicity of the superposition method has made it a popular choice for coupling DDD and FEM as all it needs is the evaluation of FE nodal forces and displacements on the boundary.
+Furthermore, the analytic expression for the stress field produced by a finite, straight dislocation line segment has allowed \citet{Queyreau} to use the non-singular formulation \cite{Cai2006} to obtain closed-form solutions for the tractions generated by the segment on the surface of a finite element.
 
@@
 
-The force exerted by a dislocation ensemble on a node $a$ belonging to element $e$ is given by,
-%
-\begin{align}
-    \vec{F}_{a} = \int_{S_{e}} \left[\tns{\tilde{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,,
+The force exerted by a dislocation ensemble on a node, $a$, belonging to element, $e$, is given by,
+%
+\begin{align}
+    \vec{F}_{a} = \int_{S_{e}} \left[\tns{\tilde{\sigma}}(\vec{x}) \cdot \vec{n}\right] N_{a}(\vec{x})\; \mathrm{d}S_{e}\,.
     \label{eq:ddd_fem_force}
@@
 %
-where $\mathrm{d}S_{e}$ is the surface of element $e$ with surface area $S_{e}$ and $N_{a}$ is the finite element shape function for node $a$ which is bi-linear in this paper.
-In the parent element (shown in \cref{f:2d_gaussian_quad}) the shape functions are,
-
+Where $\mathrm{d}S_{e}$ is the surface of element $e$ with surface area $S_{e}$, and $N_{a}$ is the finite element shape function for node $a$.
+The solutions are for linear rectangular surface elements and as such the shape functions are,
 \begin{align}
@@
 \end{align}
-
-Usually Gauss quadrature is used to evaluate the surface integral in \cref{eq:ddd_fem_force} numerically. The 1D Gauss quadrature is,
+Where $s_1$ and $s_2$ are the orthogonal coordinates local to the element.
+
+Gauss quadrature is usually used to numerically evaluate the surface integral in \cref{eq:ddd_fem_force}. In 1D this is,
 %
@@
     %
-    w_{i} = \dfrac{2}{\left(1-s_{i}^{2}\right) \left[P_{n}^{'}\left(s_{i}\right)\right]^{2}},
-\end{align}
-%
-is the weighting of the Gauss point $s_{i}$ which is the $i\textsuperscript{th}$ root of $P_{n}$; the $n\textsuperscript{th}$ Legendre polynomial normalised so $P_{n}(1) = 1$.
+    w_{i} = \dfrac{2}{\left(1-s_{i}^{2}\right) \left[P_{n}^{'}\left(s_{i}\right)\right]^{2}}\,,
+\end{align}
+%
+is the weighting of the Gauss point, $s_{i}$, which is the $i\textsuperscript{th}$ root of the $n\textsuperscript{th}$ normalised Legendre polynomial, $P_{n}(1) = 1$.
 $P_{n}^{'}$ is the first order derivative of $P_{n}$.
-
-The method is very accurate for functions that can be approximated by polynomials, but unsuitable for functions with singularities and near singularities \cite{gauss_leg, gauss_leg_sing}.
-We use a non-singular formulation for the forces \cite{Cai2006}, but the singularity is avoided by adding a small cut off radius to account for the dislocation core.
-However if the integration point falls close to or within the dislocation core, numerical integration can still generate large errors.
-
-For rectangular surface elements we must transform from the parent element in $(s_1,\,s_2)$ in \cref{eq:gauss_leg} to the real element coordinate system $(x,y,z)$ shown in \cref{f:force_lin_rect}.
+This method is very accurate for functions that can be accurately approximated by polynomials.
+In fact, for a polynomial of degree $n$, one needs $n-1$ points to obtain an exact numerical solution.
+However, this quadrature is well-known for being unsuitable for integrating functions with poles or near-poles \cite{gauss_leg, gauss_leg_sing}.
+
+We avoid the strict pole in $\tns{\tilde{\sigma}}$ by using the non-singular formulation described in \cite{Cai2006}, where the true singularity is avoided by adding a small cut-off radius to account for the dislocation core.
+However, if an integration point falls close to, or within the dislocation core, Gauss quadrature can still produce large errors.
+
+For rectangular surface elements, we must transform from the parent element in $(s_1,\,s_2)$ in \cref{eq:gauss_leg} to the real element coordinate system $(x\,,y\,,z)$.
 Evaluating \cref{eq:ddd_fem_force} in the parent element and mapping to the real element gives the force on node $a$,
@@
 \end{align}
-Where the sum is over the $Q$ quadrature points and $J_{ij}=dx_{i}/ds_{j}$ is the element Jacobian defining the transformation from $(s_1,\,s_2) \mapsto (x,\,y)$; as the real element is rectangular with surface area $S_e$, $\det(\mtx{J})=S_e/4$.
+Where the sum is over the $Q$ quadrature points and $J_{ij} = dx_{i}/ds_{j}$, is the element Jacobian defining the transformation from $(s_1,\,s_2) \mapsto (x,\,y)$.
+Since the real element is rectangular with surface area $S_e$, then $\det(\mtx{J}) = S_e/4$.
 \Cref{f:2d_gaussian_quad} contains examples of how the Gauss points are distributed on the surface.
@@
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{images/force_calc_linear_rectangle.pdf}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{force_calc_linear_rectangle.pdf}
     \caption{Diagram of the parametric line integrals solved by \citet{Queyreau} to find the forces on linear rectangular surface elements.}
@@
 \end{figure}
-\Cref{eq:ddd_fem_force} is actually a triple vector integral.
-It involves integrating over the surface element and along the dislocation line segment, as shown in \cref{f:force_lin_rect}.
-Using the isotropic Burgers vector distribution proposed in \cite{Cai2006}, the dyadic form of the stress tensor produced by a straight finite dislocation segment bounded by nodes at $\mathbf{x_1}$ and $\mathbf{x_2}$ is \cite{Queyreau},
+Explicitly, \cref{eq:ddd_fem_force} is actually a triple vector integral as shown in \cref{f:force_lin_rect}.
+This is because given the isotropic Burgers vector distribution proposed in \cite{Cai2006}, the dyadic form of the stress tensor produced by a straight, finite dislocation segment bounded by nodes at $\mathbf{x_1}$ and $\mathbf{x_2}$ \cite{Queyreau} is,
 \begin{align}
@@
     %
-    \mathrm{d}\vec{x'} & = -\mathrm{d} y \vec{l}
+    \mathrm{d}\vec{x'} & = -\mathrm{d} y \vec{l}\,.
 \end{align}
@@
     \textrm{when }m & = 3 \textrm{ then } i,\, j \in [0,\,2],~k \in [0,\,1]\nonumber                                                                          \\
-    \textrm{when }m & = 1 \textrm{ then } i = j = k = 0\nonumber.
-\end{align}
-
-Using partial differentiation and integration by parts, they found a series of recurrence relations that lead to double and single integrals with a similar form to equation (\cref{eq:triple_int}).
-Together they are used to construct a full solution.
+    \textrm{when }m & = 1 \textrm{ then } i = j = k = 0\,.
+\end{align}
+Using partial differentiation and integration by parts, they found a series of recurrence relations that lead to double and single integrals of similar form to \cref{eq:triple_int}.
+All of which are used to construct a full, exact solution.
 The recurrence relations stop working when $i = j = k = 0 \textrm{ and } m = 1,\, 3$.
-At which point, direct integration of the resulting single and double integrals (the last triple integrals all cancel out in the global calculation) yields six seed functions that are used as the starting point for the recurrence relations.
+At which point, direct integration of the remaining single and double integrals (the last triple integrals all cancel out in the global calculation) yields six seed functions that are used as the starting point for the recurrence relations.
 Three of them are logarithms and three either arctangents or---if a discriminant is negative---hyperbolic arctangents.
@@
 
-Although exact, the use of arctangents/hyperbolic arctangents and logarithmic functions, compounded by the large number of recurrence relations is prime territory for error propagation and numerical problems (see \cref{s:method}).
-This is particularly egregious when using general purpose compilers instead of high-performance or scientific computing compilers where mathematical functions are implemented more precisely.
-These issues must be taken into account when using analytic tractions in the form of numeric tolerances.
-
-In simulations, the tractions are manifested in the image stresses calculated by the FE solver at FE nodes.
-In order to validate and compare the practical differences between analytic and gauss quadrature methods, we use them both to calculate the reaction stresses produced by the tractions with the same FE solver and compare the results with the analytic expressions for infinite dislocations in inhomogenous media in \cite{head1953edge} for edge dislocations as well as those for screw dislocations found in \cite[p.~59,~64]{hirth1983theory}, where the traction surface is the line $x=0$, looking at the $xy$-plane in the positive $z$-direction, where the dislocation coordinates are represented by $(a,~c)$ and points in the plane described by their $(x,~y)$ coordinates.
-
-The original paper by \citet{head1953edge} has a few typos that have been replicated in other sources, so we include the complete and correct expressions.
+Although exact, the use of arctangents, hyperbolic arctangents and logarithmic functions, compounded by the large number of recurrence relations is prime territory for error propagation and numerical problems (see \cref{s:method}).
+The problem is particularly egregious when using general purpose compilers instead of high-performance or scientific computing compilers where mathematical functions are implemented more precisely.
+Such issues must be taken into account when using analytic tractions, which can be done by using numerical tolerances as described in \cref{s:method}.
+
+In simulations, tractions are manifested as image stresses calculated by the FE solver at FE nodes.
+In order to validate and compare the practical differences between analytic and numeric methods, we compare the resulting image stresses from both methods to the analytic expressions for infinite dislocations in inhomogenous media for edge dislocations \cite{head1953edge}, as well as those for screw dislocations \cite[p.~59,~64]{hirth1983theory}.
+We keep the same nomenclature and coordinate system as both infinite-domain solutions.
+Where the traction surface is the line $x=0$, the dislocation line direction is the positive $z$-direction (pointing out of the page), the dislocation coordinates are represented by $(a,~c)$, and points in the $xy$-plane described by their $(x,\,y)$ coordinates.
+
+The original paper by \citet{head1953edge} has a few typos that have been replicated in other sources.
+We therefore include the complete and correct expressions in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}.
 \citet{head1953edge} gives two basic cases.
-The first case in \cref{eq:imageStressAnalyticEdge1} corresponds to the case where $\vec{b}$ is perpendicular to the surface and positive $b$ means it points in the positive $x$ direction,
-\begin{subequations}
-    \begin{align}\label{eq:imageStressAnalyticEdge1}
+\Cref{eq:imageStressAnalyticEdge1} corresponds to the case where $\vec{b}$ is perpendicular to the surface and positive $b$ means it points in the positive $x$-direction,
+\begin{subequations}\label{eq:imageStressAnalyticEdge1}
+    \begin{align}
         \sigma_{xx} = D (y - c) & \left\{-\dfrac{3 (x - a)^2 + (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} + \dfrac{3 (x + a)^2 + (y - c)^2}{[(x + a)^2 + (y - c)^2]^2}\right.
@@
 \end{subequations}
-
-The case where the $\vec{b}$ lies parallel to the surface and positive $b$ means it points in the positive $y$ direction, is found in \cref{eq:imageStressAnalyticEdge2},
-\begin{subequations}
-    \begin{align}\label{eq:imageStressAnalyticEdge2}
+\Cref{eq:imageStressAnalyticEdge2} corresponds to the case where the $\vec{b}$ lies parallel to the surface and positive $b$ means it points in the positive $y$-direction,
+\begin{subequations}\label{eq:imageStressAnalyticEdge2}
+    \begin{align}
         \sigma_{xx} = D         & \left\{ (x - a) \dfrac{(x - a)^2 - (y - c)^2}{[(x - a)^2 + (y - c)^2]^2} -(x + a) \dfrac{(x + a)^2 - (y - c)^2}{[(x + a)^2 + (y - c)^2]^2} \right.     \\\nonumber
@@
 \end{subequations}
-
-Screw dislocations are markedly simpler, as only the shear components are non-zero.
-Here $\vec{b} = \vec{l}$ and therefore positive $b$ means it points in the positive $z$ direction (away from the observer) \cref{eq:imageStressAnalyticScrew},
-\begin{subequations}
-    \begin{align}\label{eq:imageStressAnalyticScrew}
+\Cref{eq:imageStressAnalyticScrew} corresponds to screw dislocations, which are markedly simpler as only the shear components are non-zero.
+Here $\vec{b} = \vec{l}$ so positive $b$ means it points in the positive $z$-direction,
+\begin{subequations}\label{eq:imageStressAnalyticScrew}
+    \begin{align}
         \sigma_{xz} & = -D \left(\dfrac{y - c}{(x - a)^2 + (y - c)^2} - \dfrac{y - c}{(x + a)^2 + (y - c)^2}\right)   \\
@@
 \end{subequations}
-
-In every case, the constant $D$ is defined by \cref{eq:Dconstant}
+In every case, the constant $D$ is defined by \cref{eq:Dconstant},
 \begin{align}\label{eq:Dconstant}
@@
 \end{align}
-Note the first terms of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} all correspond to the stress field generated by the dislocation.
+Note the first terms of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} all correspond to the stress field generated by the dislocation itself.
 The following terms are the corrective terms required to make the boundary conditions on the surface equal to zero.
-Therefore, we can split these equations and only look at the real or corrective terms, which we do in order to only visualise the effect of the different traction calculations.
-Furthermore \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} are all singular at the dislocation coordinates, our simulation code uses non singular expressions found by \citet{Cai2006}, which smooth out drastic increases in stresses and avoid numerical blow up as we near the dislocation core.
+Therefore, we can split these equations and only look at the real or corrective terms independently, which we do in order to only visualise the effect of the different traction calculations.
+Furthermore, \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew} are all singular at the dislocation coordinates.
+Our simulation code uses the non singular expressions found by \citet{Cai2006}, which smooth out drastic increases in stresses and avoid numerical blow up as we near the dislocation core.
 
 \section{Methodology}\label{s:method}
+
 Numerical integration of tractions can produces unexpected behaviour such as force hot spots and sign inversions as a dislocation approaches a surface.
@@
 The two basic test cases, an orthogonal and parallel edge segment, are shown in \cref{f:gauss_quad_test}.
-
-The symmetry of the simple test cases can also influence how solution is as the stress fields exhibit symmetries about the dislocation line.
-If the dislocation is centered at the center of the element and orthogonal to it then the numerical solution becomes more accurate.
-However isolated test cases are far from typical simulation scenarios.
-A single quadrature point is often used to evaluate tractions due to the low computational cost and works well for segments which are not close to the surface.
-This is therefore the benchmark against which we measure the cost-benefit of implementing and utilising the analytic solutions.
-It should also be noted that by using a single Gauss point, one can use the same FE mesh as for the Gauss points, simplifying the implementation.
-%		
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{images/test_gauss_quad.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{test_gauss_quad.pdf}
     \caption{Simple test cases for an edge segment and surface element perpendicular (a) and parallel (b).
 The perpendicular dislocation is centered at the midpoint of the surface element, node $\mathbf{x_1}$ is separated by a perpendicular distance $\mathbf{x_1}^z$ to prevent the dislocation from intersecting the surface.
-On the right, the parallel dislocation runs along the$x$-axis at half the height of the surface element.
+On the right, the parallel dislocation runs along the $x$-axis at half the height of the surface element.
 The nodes of each dislocation line segment are kept at a perpendicular distance of at least one core radius away from the surface element.}
@@
 
-\citet{Queyreau} found the analytic solution is approximately 10 times more computationally expensive than its numerical counterpart for 1 quadrature point.
-The implementation of the analytic solution is also much more involved.
-One issue is the calculation of the $y$-coordinate in the local coordinate frame as shown in \cref{f:force_lin_rect} and \cref{eq:problem}, if $\vec{l} \perp \vec{n}$, we get a singularity.
-As mentioned in \cite{Queyreau}, an easy fix is to rotate the line segment about its midpoint around the $\vec{l} \times \vec{n}$ axis and use the mean values either side as the true result.
-An example of what this looks like in terms of forces can be seen in \cref{f:rotate} (we removed the singularity to keep the graph smooth).
-\begin{figure}
-    \centering
-    \subfloat[Full rotation of a segment.]{{\includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect.pdf}}}
-
-    \subfloat[Zoom of the rotation of a segment $\pm 10~\text{deg}$.]{{\includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect_zoom.pdf}}}
-    \caption{Example of the components of the total force on a surface element (the force summed over all four FE nodes) as a dislocation segment parallel to the surface element ($\theta = 0$) is rotated about its midpoint around the axis defined by $\vec{l}\times\vec{n}$.
-The force is smooth but not necessarily antisymmetric about the neighbourhood of $\theta=0$.}
+The symmetry of these simple test cases benefits the accuracy of the numerical solutions because the stress fields exhibit symmetries about the dislocation line.
+If under ideal conditions for error cancellation, it can be proven that the numerical method is inferior to the analytic one, it can be more effectively argued that the analytic one should always be used instead.
+
+\citet{Queyreau} found the analytic solution is approximately 10 times more computationally expensive than its numerical counterpart for 1 quadrature point, our findings agree with this result but the implications for a whole simulation are favourable (see \cref{s:results}).
+
+One serious disadvantage of the analytic tractions is that the implementation of the analytic solution is also much more involved and full of snags.
+One issue is the calculation of the $y$-coordinate in the local coordinate frame as shown in \cref{f:force_lin_rect} and \cref{eq:problem}.
+If $\vec{l} \perp \vec{n}$, we get a singularity.
+As mentioned in \cite{Queyreau}, an easy fix is to rotate the line segment.
+We do this about its midpoint and around the $\vec{l} \times \vec{n}$ axis in both clockwise and anticlockwise directions.
+We use the mean of the values as the answer for $\theta = 0$.
+An example of what this rotation looks like in terms of the forces on a surface element can be seen in \cref{f:rotate} (avoiding the singularity at $\theta = 0$).
+\begin{figure}
+    \centering
+    \subfloat[]{\includegraphics[width=0.45\linewidth]{ftot_rotation_lin_rect.pdf}}
+    ~
+    \subfloat[]{\includegraphics[width=0.45\linewidth]{ftot_rotation_lin_rect_zoom.pdf}}
+    % \includegraphics[width=0.8\linewidth]{ftot_rotation_lin_rect_inlaid.pdf}
+    \caption{(a) Example of the components of the total force on a surface element (the force summed over all four FE nodes) as a dislocation segment parallel to the surface element ($\theta = 0$) is rotated about its midpoint around the axis defined by $\vec{l}\times\vec{n}$.
+(b) is zomms into $\pm 10 \deg$, the force is smooth but not necessarily antisymmetric about the neighbourhood of $\theta=0$.}
     \label{f:rotate}
@@
 The specific shape of the curves will vary depending on the element-segment configuration, but is smooth and well-behaved about singularity.
-For our purposes, we used 4 perturbations each of $1\,\deg$, in the clockwise and anti-clockwise directions (8 rotations in total) w.r.t.
-the parallel position.
-
-However, the check for orthogonality is dependent on the length scales involved in the simulation, we found that machine precision plays an important part in deciding how strict the tolerance should be.
-If,
-%
-\begin{align}
-    \lvert\vec{l}\cdot\vec{n}\rvert \lesssim \dfrac{\max\left(\lvert\vec{R}\cdot\vec{n}\rvert\right)}{10^8}\,,
-\end{align}
-%
-it is advisable to treat the segment as parallel to the surface element.
-In our case the numerator on the RHS is simply the cantilever's largest dimension.
-$10^8$ is used instead of actual machine precision $\sim10^{15}$ because the seed functions and large number of recurrence relations of the solution propagate errors.
-Smaller tolerances lead to these errors growing so much that the simulation can be impacted; this is a problem when such dislocations move slightly during a simulation and become nearly parallel with the surface, which are detected if the tolerance is too small, yet the limited numerical precision leads to round off and truncation errors during the calculation.
-Ironically tolerances which are too large can cause the perturbations to rotate the dislocation segment closer to the singularity also producing erroneous results.
+For our purposes, we use a total of 8 perturbations of $1\deg$ each (4 clockwise and 4 anti-clockwise).
+We found this worked well, but can be changed if desired.
+
+However, under finite-precision arithmetic, the check for orthogonality is dependent on the length scales involved in the simulation.
+This is particularly important considering the aforementioned use of arctangents, hyperbolic arctangents, logarithms and the large number of recurrence relations.
+Causing unexpected and rampant error propagation and numerical blow up is not difficult to achieve.
+When it happens, finding the root cause can lead one on a wild goose chase that is best avoided and often leads to a single segment in a single step of a long simulation that is slightly too small compared to its distance to a surface element to which it is slightly too parallel.
+To avoid these rare but high impact scenarios, we created a heuristic that dictates how strict the tolerance should be in order for the code to consider a segment to be parallel,
+%
+\begin{align}
+    \lvert\vec{l}\cdot\vec{n}\rvert \lesssim \dfrac{\max\left(\lvert\vec{R}\cdot\vec{n}\rvert\right)}{10^8}\,.
+\end{align}
+%
+In our case the numerator on the RHS is simply the FEM domain's largest dimension.
+$10^8$ is used instead of actual machine precision $\sim10^{15}$ because the seed functions and large number of recurrence relations of the solution propagate errors if the value of $\vec{l} \cdot \vec{n}$ is too close to zero.
+Ironically, tolerances which are too large can cause the perturbations to rotate the dislocation segment closer to the singularity, producing erroneous results.
 Larger than necessary tolerances can also slow down the calculation by detecting dislocations that are far enough from the special case that they can be treated like non-parallel segments.
-
-In general one does not want a dislocation segment to intersect the surface when it is being rotated. Naively one would calculate the maximum rotational angle, $\theta_{\textrm{max}}$, to be,
-%
-\begin{align}
-    \theta_{\textrm{max}} & = \arctan\left(\dfrac{2 d}{\left\lvert\mathbf{x_2} - \mathbf{x_1}\right\rvert}\right)\,,
-\end{align}
-%
-where $d$ is the minimum orthogonal distance from the dislocation to the surface element (collision distance), and $\mathbf{x_1},\,\mathbf{x_2}$ are the dislocation segment node coordinates.
-However, $\theta_\textrm{max}$ might be too small (due to numerical precision) in cases when the segment length is too small compared to the distance to a surface element or when the segment length is much greater than $d$.
-Fine tuning the angle is a task that involves knowing the minimum collision distance, minimum segment length, dislocation core radius, and the compiler's implementation of mathematical functions.
-Given the rarity of such cases and their comparatively low impact, we chose our perturbation such that we safely avoid this problem.
+This heuristic is a good general purpose rule that keeps the tolerance in a goldilocks zone.
+
+Another issue with the rotation is that one does not want a dislocation segment to intersect the surface when it is being rotated.
+Naively one would calculate the maximum rotational angle, $\theta_{\textrm{max}}$, to be,
+%
+\begin{align}
+    \theta_{\textrm{max}} & = \arctan\left(\dfrac{2 d}{\left\lvert\mathbf{x_2} - \mathbf{x_1}\right\rvert}\right)\,.
+\end{align}
+%
+Where $d$ is the minimum orthogonal distance from the dislocation to the surface element i.e.
+the collision distance---which in our case is a function of the dislocation core radius---and $\mathbf{x_1},\,\mathbf{x_2}$ are the dislocation segment node coordinates---whose maximum and minimum lengths are also functions of the dislocation core radius.
+However, $\theta_\textrm{max}$ might be too small in cases where the segment length is too small compared to the distance to a surface element, or when the segment length is much greater than $d$.
+Fine-tuning the angle is a task that involves knowing the minimum collision distance, minimum segment length, dislocation core radius, and the compiler's implementation of mathematical functions.
+Given the rarity of such cases and their comparatively low impact, we chose our $1\deg$ perturbation such that we safely avoid this problem while keeping within the bounds of the non-singular model.
 
 Furthermore, the chirality and self-consistency of the FE nodes must be accounted for such that they are in the proper order regardless of the element face they belong to.
-Here we use 8  node linear hexahedral (brick) elements with the node numbering shown in \cref{f:fe_numbering}.
-The node ordering for the various surfaces are obtained by placing an observer inside the element and noting the nodes for the faces of the element, these are shown in \cref{f:surface_nodes}.
-%
-\begin{figure}
-    \centering
-    \subfloat[Node numbering for our FE voxels.\label{f:fe_numbering}]
-    {
-        { \includegraphics[width=0.375\linewidth]{images/fe_numbering.pdf} }
-    }
-    \hfill
-    \subfloat[Surface nodes selected for each face.\label{f:surface_nodes}]
-    {
-        { \includegraphics[width=0.525\linewidth]{images/surf_node_plane.pdf} }
-    }
-    \caption{Surface element nodes must be self-consistent so the forces have the correct sign.}
-\end{figure}
-%
+Here we use 8-node linear hexahedral (brick) elements.
+The node ordering for the various surfaces is that for which the calculated normals point out from the the domain, this is dependant on the specific FE mesh implementation.
+
 The total force on a given node must include the force contributions from every element in which said node appears, see \cref{f:shared_node}.
-%
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{images/lrse_thread_map.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{lrse_thread_map.pdf}
     \caption{FE nodes are shared by either 4 element faces or 3 if it is a corner node. The total force on a given node is the summation of the force contributions from each element it belongs to.}
@@
 \end{figure}
-%
 The specifics of the mapping depend on the global FE node numbering.
@@
 \end{subequations}
-Where $\vec{x_{e,n}}$ is a $3\times1$ column vector corresponding to the $x,~y,~z$ dislocation induced forces on node $n$ on the surface element $e$.
+Where $\vec{x_{e,n}}$ is a $3\times1$ column vector corresponding to the $(x\,,y\,,z)$ dislocation induced forces on node, $n$, on the surface element, $e$.
 There are four of these per rectangular surface element, where a given node, $n$, can appear in multiple surface elements (e.g.
 node 5 in \cref{f:shared_node} is shared by all 4 surface elements), all of which independently contribute to the total force on said node.
-$\vec{x_n}$ is a $3\times1$ column vector corresponding to the total $x,~y,~z$ dislocation induced forces on node $n$.
+$\vec{x_n}$ is a $3\times1$ column vector corresponding to the total $(x\,,y\,,z)$ dislocation induced forces on node $n$.
 These are used to shorten the definition of \cref{eq:force_imp} and are not explicitly defined in the implementation, rather they give the force matrices $\mtx{F_{e}}$ and $\vec{\tilde{F}}$ a specific row order.
@@
 
-The following algorithm illustrates how the total force on each node is obtained.
+\Cref{a:tot_force} illustrates how the total force on each node is obtained.
+However, our implementation does not strictly follow it because we memoise a generalised version of $\vec{L}$ upon simulation initialisation instead of finding one at every iteration, reducing computational time but requiring us to account for nodes without traction boundary conditions.
+Our indexing also starts at 1, but zero indexing makes the algorithm easier to follow.
 \begin{algorithm}
@@
 \end{algorithm}
-Our implementation does not strictly follow \cref{a:tot_force} because we memoise a generalised version of $\vec{L}$ upon simulation initialisation instead of finding one at every iteration, reducing computational time but requiring us to account for nodes without traction boundary conditions.
-Our indexing also starts at 1, but zero indexing makes the algorithm easier to follow.
-
-The resulting force vector is later used in \cref{eq:thatbc} as $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
+
+The resulting force vector is then used in \cref{eq:thatbc} to calculate $\tns{\hat{\sigma}}$, since $\tilde{\vec{T}} \equiv \tilde{\vec{F}}$.
 \Cref{f:headvstractionfem} shows the simple system we used to compare the image stresses calculated by our FE solver using numeric tractions v.s.
 analytic tractions v.s.
-infinite-domain, singular image stresses found in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}.
-We use three test cases, two edge dislocations and one screw, all of which have line direction $\vec{l} = [0\, 0\, 1]$ with Burgers vectors $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ \cite{head1953edge}, and $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ \cite{hirth1983theory}.
-% TODO #52 make coordinate system right handed, z out of the page
+infinite-domain, singular image stresses in \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2,eq:imageStressAnalyticScrew}.
+The three test cases are: two edge dislocations and one screw, all of which have line direction $\vec{l} = [0\, 0\, 1]$.
+The Burgers vectors for the different scenarios are $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$, as defined in \cite{head1953edge}; and $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $, as defined in \cite[p.~59,~64]{hirth1983theory}.
+
+The units in all our examples are normalised to lattice parameter, $a$ is the dislocation core radius for the non-singular formulation discussed in \cite{Cai2006}, and $b \equiv \lVert \vec{b} \rVert$.
 \begin{figure}
@@
     \includegraphics[width=0.8\linewidth]{head_vs_fe_tractions_setup_diagram.pdf}
-    \caption{Dislocation parallel to a surface described by the line $x = 0$ (the $yz$-plane in 3D), where the dislocation coordinates are $(a,~c)$, looking down the $xy$-plane where the $x$-axis is horizontal and the $y$-axis vertical.
-(a) describes the box we used for our comparison, a  $20 \times 20 \times 20$ element cubic box with side lengths equal to $1000\, \lVert \vec{b} \rVert$ with $\vec{T} = \vec{0}$ traction boundary conditions only on the nodes occupying the $yz$-plane and $\vec{U} = \vec{0}$ displacement conditions everywhere else, and a dislocation with line direction in the positive $z$ direction.
-(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors as described by \cite{head1953edge}, $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ and the screw Burgers vector $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ as posited in \cite{hirth1983theory}.}
+    \caption{Dislocation parallel to a surface described by the line $x = 0$, where the $(x,\,y)$ dislocation coordinates are $(a,\,c)$ and the dislocation line going in the positive $z$-direction.
+(a) describes the box we used for our comparison, a  $40 \times 40 \times 40$ element cubic box with side lengths equal to $2000$ with $\vec{T} = \vec{0}$, traction boundary conditions only on the nodes along $x = 0$, and $\vec{U} = \vec{0}$, displacement conditions everywhere else.
+(b) is the 2D view with the dislocation coordinates $(a,~c)$, as well as the two edge Burgers vectors in \cite{head1953edge}, $\vec{b}_\textrm{e1} \equiv \vec{b} = [1\, 0\, 0]$, $\vec{b}_\textrm{e2} \equiv \vec{b} = [0\, 1\, 0]$ and the screw Burgers vector $\vec{b}_\textrm{s} \equiv \vec{b} = \vec{l} = [0\, 0\, 1] $ in \cite[p.~59,~64]{hirth1983theory}.}
     \label{f:headvstractionfem}
 \end{figure}
-The slices we took for our contour plots in \cref{s:results} taken from the midpoint of the $z$-axis to ensure minimal interferance from the $xy$-plane boundaries at $z=0,\, 1000\,b$.
-
-% TODO #48
-Finally, we ran a simple simulation where the differences between methods can be readily observed.
-
-\section{Results}\label{s:results}
-
-Isolated test cases were useful in order to gain insight into the differences between the numerical and analytical approaches.
-When the stress field on the surface element is highly symmetric, numerical integration works well; showing good convergence with increasing number of quadrature points.
-
-\Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5\, b$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 Gauss quadrature points $Q$, for all segment lengths tested.
-It also shows a very peculiar issue Gauss quadrature has when computing integrals of rational functions when the Gauss points are close poles/maximal values.
+The slices we took for our contour plots in \cref{s:results} are on the middle plane of the domain at $z = 1000$.
+
+We also ran a very simple simulation comparing the results between using analytic tractions as opposed to numeric ones.
+Finding a simple yet clear case of tractions producing catastrophically wrong behaviours can be difficult.
+Large differences in image forces are relatively rare and other factors often dominate.
+Such factors include the core radius---which affects the dislocation line tension and therefore works against the deformation of a dislocation line---mobility law and mobility parameters used, external loading, etc.
+
+However, we found a simple and realistic configuration that is close to the setup in the infinite domain examples.
+The differences between those comparisons and the simulation are described in \cref{t:simulation_params}.
+We use a mobility law developed in-house by B.
+Bromage \cite{bromage2018calculating}, that corrects common issues found in other laws.
+We also rotate the domain such that the $[1\, 1\, 1]$ and $[1\, \overline{1}\, 0]$ crystallographic directions respectively correspond to the simulation's $x$ and $y$-directions, for this we use the same rotation technique as \cite{YU2018}.
+The dislocation was allowed to move under no external loads or displacements, with $\vec{T} = \vec{0}$ boundary conditions only on the $yz$-plane and $\vec{U} = \vec{0}$ everywhere else.
+\begin{table}
+    \centering
+    \caption{Parameters for our simulation.
+Where $\mtx{R}$ is a rotation matrix such that the $\vec{x},\, \vec{y},\, \vec{z}$ basis vectors of our simulation correspond to the $\vec{b},\, \vec{n},\, \vec{l}$ crystallographic directions, i.e.
+$\mtx{R} \vec{x} = \vec{b}$.
+Everything else was kept just as the previous comparisons.
+All values are in units of lattice parameters.}
+    \label{t:simulation_params}
+    \begin{tabular}{ll}
+        \toprule
+        Parameter          & Value                                           \\
+        \midrule
+        Crystal Structure  & BCC                                             \\
+        $\vec{b}$          & $[1\, 1\, 1]$                                   \\
+        $\vec{n}$          & $[1\, \overline{1}\, 0]$                        \\
+        $\vec{l}$          & $[1\, 1\, \overline{2}]$                        \\
+        $b$                & $\sqrt{3}/2$                                    \\
+        $a$                & $5\, $                                          \\
+        Grid Size          & $(20,\, 20,\, 20)$                              \\
+        Domain Size        & $(2000,\, 2000,\, 2000)\, $                     \\
+        Lattice size       & $3.18\times 10^{-4}~\mu\text{m}$                \\
+        $(x_{0},\, y_{0})$ & $(62.5,\, 1000)\, $                             \\
+        Min segment length & $50\, $                                         \\
+        Max segment length & $125\, $                                        \\
+        $\mtx{R}$          & $[\hat{\vec{b}}~ \hat{\vec{n}}~ \hat{\vec{l}}]$ \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\section{Results and Discussion}\label{s:results}
+
+\Cref{f:rel_err_perp_edge} shows that even for dislocations only one dislocation core radius ($5$) away from the surface element, the force can be obtained, up to numerical precision, with 1000 Gauss quadrature points $Q$ for all segment lengths tested.
+It also shows a very peculiar issue Gauss quadrature has when computing integrals of rational functions when the Gauss nodes are close poles/maximal values.
 This undesirable behaviour is observed in the case where $Q = 11$.
@@
     {
-        {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=15.pdf}}
+        {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=15_leg.pdf}}
     }
@@
     {
-        {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=1005.pdf}}
+        {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.475\linewidth]{perp_e_xz=1005_leg.pdf}}
     }
@@
     {
-        {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.47\linewidth]{perp_e_xz=100005.pdf}}
+        {\includegraphics[trim={0.5cm 0.55cm 0.65cm 0.1cm},clip,width=0.47\linewidth]{perp_e_xz=100005_leg.pdf}}
     }
@@
 $x^{1}_{z}$ is the $z$-coordinate of node $\mathbf{x_1}$.
-$\vec{b} = [1 0 0]$, line direction, $\vec{l} = [0 0 1]$, and dislocation core radius, $a = 5b$, the surface element's normal and size are, $\vec{n} = [0 0 1]$, $L = 1000b$, respectively.
+$\vec{b} = [1\, 0\, 0]$, line direction, $\vec{l} = [0\, 0\, 1]$, and dislocation core radius, $a = 5$, the surface element's normal and size are, $\vec{n} = [0\, 0\, 1]$, $L = 1000$, respectively.
 $Q$ is the number of quadrature points per dimension.}
@@
 \end{figure}
-
-The limitations of Gauss quadrature become even more evident when the dislocation line segment is parallel to a surface element.
-\Cref{f:rel_err_par_edge} shows the relative errors for a parallel edge dislocation.
+It is worth noting however that the relative errors for small numbers of quadrature points don't really start decreasing until relatively large distances.
+And when close to a surface, these can be quite large even under highly symmetric circumstances.
+
+The limitations become even more evident when the dislocation line segment is parallel to a surface element.
+In \cref{f:rel_err_par_edge}, we observe the relative errors are quite large when close to the surface.
+At distances larger than $10^4\, $, loss of significance causes the relative errors to converge at $\sim 1$ which is expected as two finite precision floating point numbers get closer to zero.
+Of particular note is how large the relative errors are even at $100$ lattice units away from the surface, even for large numbers of quadrature points.
+This figure backs up the earlier point regarding Gauss nodes close to maximal values of rational functions.
+It can be shocking to see that as $Q = 2$ performs significantly better than $Q = 10, 11, 100, 100$ at distances from the surface as having nodes near the maximal values is a large source of error.
+Consequently, different configurations have different optimal numbers of points.
+The numerical instability of this method, which when coupled to the chaotic nature of dislocation dynamics and stiffness of the equations of motion, can lead to large deviations between simulations.
 \begin{figure}
@@
     \caption{Log-log plot of the relative error as a function of distance from the surface element for a parallel edge dislocation (\cref{f:gauss_quad_test}b).
-Burgers vector, $\vec{b} = [0 1 0]$, line direction, $\vec{l} = [1 0 0]$, dislocation core and surface element parameters are the same as \cref{f:rel_err_perp_edge}.
-The dislocation length is fixed to $10^{6}\, b,\, x\in\left[-0.5\times10^{6},\, 0.5\times10^{6} \right]$ and bisects the surface element along the $[1 0 0]$ direction.
-The whole dislocation was segmented into $10^4$ pieces of length $100\, b$ to prevent the dislocation from intersecting the surface element when they were rotated to avoid the singularity.
-The relative error at large distances ($>10^6 b$) converges to one due to loss of significance.}
+Burgers vector, $\vec{b} = [0\, 1\, 0]$, line direction, $\vec{l} = [1\, 0\, 0]$, dislocation core and surface element parameters are the same as \cref{f:rel_err_perp_edge}.
+The dislocation length is fixed to $10^{6},\, x\in\left[-0.5\times10^{6},\, 0.5\times10^{6} \right]$ and bisects the surface element along the $[1\, 0\, 0]$ direction.
+The whole dislocation was segmented into $10^4$ pieces of length $100$ to prevent the dislocation from intersecting the surface element when they were rotated to avoid the singularity.
+The relative error at large distances ($>10^6\, $) converges to one due to loss of significance.}
     \label{f:rel_err_par_edge}
 \end{figure}
-In \cref{f:rel_err_par_edge}, we observe the relative errors decrease and then converge to $\sim 1$ as the distance grows larger.
-The convergence to $\sim 1$ is an artifact arising from the fact that the forces on the surface element get asymptotically closer to zero with increasing distance from the surface element, resulting in the division of two increasingly similar, small, non-zero numbers, resulting in $\sim 1$.
-This is a well-known problem when dealing with finite precision arithmetic known as loss of significance.
-Given infinite precision, it is not unreasonable to assume the relative error would converge to $\sim10^{-3},~ \sim10^{-4}$.
-However, when the segment is close to the surface, the relative errors are large ($\gg1$) unless using a large number of quadrature points, for example \cref{f:gauss_quad_test}(a) shows that $Q\geq100$ are required when the distance $x^1_z = 15b$.
-This figure backs up the earlier point regarding Gauss nodes close to maximal rational values, as $Q = 2$ performs significantly better than $Q = 10, 11, 100, 100$ at smaller distances from the surface.
-Generally, there is no best value of $Q$ other than very large.
 
@@
 However there is a further wrinkle in this problem: symmetry.
-To exemplify this we plot the relevant components of the stress tensor for the arrangement found in \cref{f:gauss_quad_test}(a) we find \cref{sf:xzeperp,sf:yzeperp,sf:zzeperp}.
+To exemplify this we plot the relevant components of the stress tensor for the arrangement found in \cref{f:gauss_quad_test}(a) in \cref{sf:xzeperp,sf:yzeperp,sf:zzeperp}.
 The $\sigma_{xz}$ and $\sigma_{zz}$ components are antisymmetric about the centre of the element.
-If we use Gauss quadrature on them, we sample equivalent but oppositely valued points that equally weighted, thus the sum vanishes.
-$\sigma_{yz}$ does not, but it can be accurately integrated with sufficiently large $Q$.
-If we were to move the dislocation off-centre such that the rotational anti-symmetry about the origin is broken, the errors would increase.
+If we use Gauss quadrature on them, we sample equivalent but oppositely valued points that are equally weighted, thus the sum vanishes and therefore do not contribute to \cref{f:rel_err_perp_edge}.
+However, $\sigma_{yz}$ does not vanish, but can be accurately integrated with sufficiently large $Q$.
+If we were to move the dislocation off-centre such that these symmetries are broken, the errors would increase.
 
 We also plot the relevant stresses for the arrangement described by \cref{f:gauss_quad_test}(b) in \cref{sf:xzepar,sf:yzepar,sf:zzepar}.
-It is immediately apparent why gauss quadrature fails so spectacularly in \cref{f:rel_err_par_edge}.
-At low numbers of quadrature points, it fails to appropriately sample the rapidly changing value of $\tilde{\sigma}_{xz}$ at both ends of the dislocation as seen in \cref{sf:xzepar}, as well as the neighbourhood of the dislocation where $\tilde{\sigma}_{yz}$ changes most raplidly as shown in \cref{sf:yzepar}.
+From \cref{sf:xzepar} and \cref{sf:yzepar}, it is immediately apparent why gauss quadrature fails so spectacularly in \cref{f:rel_err_par_edge}.
+At low numbers of quadrature points, it fails to appropriately sample the rapidly changing value of $\tilde{\sigma}_{xz}$ at both ends of the dislocation, as well those in the neighbourhood of the dislocation in $\tilde{\sigma}_{yz}$.
 Moreover, the further away the quadrature points are from the midpoint of the domain, the lower their relative weighting.
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxzperpEdgeFiveb.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{sxzperpEdgeFiveb.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syzperpEdgeFiveb.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{syzperpEdgeFiveb.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/szzperpEdgeFiveb.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{szzperpEdgeFiveb.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/sxzparEdgeFiveb.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{sxzparEdgeFiveb.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/syzparEdgeFiveb.pdf}}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{syzparEdgeFiveb.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/szzparEdgeFiveb.pdf}}
-    }
-    \caption{(a) to (c) show the relevant stress fields from a dislocation in the same configuration that yields the plots found in \cref{f:rel_err_perp_edge} as shown in \cref{f:gauss_quad_test}(a), where the closest node is a dislocation core radius away from the surface, $a = 5b$.
-(e) to (f) does the same for the configuration that yields \cref{f:rel_err_par_edge} as shown in \cref{f:gauss_quad_test}(b), where the whole dislocation is a core radius away from the surface, $a = 5b$.
-The white line or dot is the dislocation.}
+        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{szzparEdgeFiveb.pdf}}
+    }
+    \caption{(a) to (c) show the real stress fields from a dislocation in the same configuration that yields the plots found in \cref{f:rel_err_perp_edge} as shown in \cref{f:gauss_quad_test}(a), where the closest node is a dislocation core radius away from the surface, $a = 5$.
+(e) to (f) does the same for the configuration that yields \cref{f:rel_err_par_edge} as shown in \cref{f:gauss_quad_test}(b), where the whole dislocation is a core radius away from the surface, $a = 5$.
+The white line or dot is the dislocation.
+Units are in terms of lattice parameters.}
     \label{f:sigma_edge_test_config}
@@
 
-Despite these being artificially ideal examples that illustrate the failings of Gauss quadrature, other problematic scenarios commonly to show up in simulations.
-The problems tend to worsen with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces, more permissive mobility functions, and coarser FE meshes.
-The $\mathcal{O}(1/R)$ decay rate and chaotic nature of dislocation dynamics, means these errors may result in unwarranted topological changes that cascade a the simulation advances.
+Despite these being artificially idealised examples that illustrate the failings of Gauss quadrature, other problematic scenarios commonly show up in simulations.
+These tend to worsen with smaller core radii $a$, fewer Gauss nodes, higher dislocation densities near surfaces, more permissive mobility functions, and coarser FE meshes.
+The $\mathcal{O}(1/R)$ decay rate of $\tns{\tilde{\sigma}}$ and chaotic nature of dislocation dynamics, means these errors may result in unwarranted topological changes that cascade as the simulation advances.
 This is particularly deleterious when doing simulations with higher dislocation densities and/or where a large number of dislocations are close to the surface, such as nanoindentation simulations.
 
+\begin{figure}
+    \centering
+    \subfloat[%$\hat{\sigma}_{xx}$.
+        \hspace{-0.8cm}\label{sf:sxxeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxEperp_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
+        \hspace{-0.8cm}\label{sf:sxxAeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxAEperp_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
+        \hspace{-0.8cm}\label{sf:sxxNeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxNEperp_leg.pdf}}
+    }~
+    \subfloat{\includegraphics[height = 0.22\linewidth]{sxxNAEperp_leg.pdf}}
+
+    \subfloat[%$\hat{\sigma}_{yy}$.
+        \hspace{-0.8cm}\label{sf:syyeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syyEperp_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
+        \hspace{-0.8cm}\label{sf:syyAeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syyAEperp_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
+        \hspace{-0.8cm}\label{sf:syyNeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syyNEperp_leg.pdf}}
+    }~
+    \subfloat{\includegraphics[height = 0.22\linewidth]{syyNAEperp_leg.pdf}}
+
+    \hspace*{0.2cm}\subfloat[%$\hat{\sigma}_{xy}$.
+        \hspace{-0.8cm}\label{sf:sxyeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxyEperp_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
+        \hspace{-0.8cm}\label{sf:sxyAeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxyAEperp_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
+        \hspace{-0.8cm}\label{sf:sxyNeperp}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxyNEperp_leg.pdf}}
+    }~
+    \hspace*{-0.2cm}\subfloat{
+        \includegraphics[height = 0.22\linewidth]{sxyNAEperp_leg.pdf}
+    }
+
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, where $a = 5$, with coordinates $(26,\, 1000)$, i.e.
+the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box along the $y$-direction.
+(a), (e) and (i) are the stress fields for the infinite-domain solution, $\tns{\hat{\sigma}}$; (b), (f) and (j) are those obtaine from analytic tractions + FEM, $\tns{\hat{\sigma}}^{\textrm{A}}$; (c), (g) and (k) are those obtained using numeric tractions ($Q = 1$) + FEM, $\tns{\hat{\sigma}}^{\textrm{N}}$.
+(a) to (c) represent the $xx$; (e) to (g) the $yy$; and (i) to (k) the $xy$ components of the stress tensor.}
+    \label{f:head_vs_ana_vs_num_eperp}
+\end{figure}
 As stated in \cref{s:method}, tractions are used to calculate the image stresses resulting from the boundary conditions.
@@
 
-\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, the $\textrm{A}$ superscript are the stresses calculated from analytic tractions and the $\textrm{N}$ superscript are those coming from numeric tractions where $Q = 1$ (we use the same nomenclature in \cref{f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw}).
-The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}} = [1 0 0]$.
+\begin{figure}[t]
+    \centering
+    \subfloat[%$\hat{\sigma}_{xx}$.
+        \hspace{-0.8cm}\label{sf:sxxepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxEpar_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
+        \hspace{-0.8cm}\label{sf:sxxAepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxAEpar_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
+        \hspace{-0.8cm}\label{sf:sxxNepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxNEpar_leg.pdf}}
+    }~
+    \subfloat{
+        \includegraphics[height = 0.227\linewidth]{sxxNAEpar_leg.pdf}
+    }
+
+    \hspace*{0.3cm}\subfloat[%$\hat{\sigma}_{yy}$.
+        \hspace{-0.8cm}\label{sf:syyepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syyEpar_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
+        \hspace{-0.8cm}\label{sf:syyAepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syyAEpar_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
+        \hspace{-0.8cm}\label{sf:syyNepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syyNEpar_leg.pdf}}
+    }~
+    \subfloat{
+        \includegraphics[height = 0.227\linewidth]{syyNAEpar_leg.pdf}
+    }
+
+    \hspace*{0.3cm}\subfloat[%$\hat{\sigma}_{xy}$.
+        \hspace{-0.8cm}\label{sf:sxyepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxyEpar_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
+        \hspace{-0.8cm}\label{sf:sxyAepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxyAEpar_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
+        \hspace{-0.8cm}\label{sf:sxyNepar}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxyNEpar_leg.pdf}}
+    }~
+    \subfloat{
+        \includegraphics[height = 0.227\linewidth]{sxyNAEpar_leg.pdf}
+    }
+
+    \caption{Image stresses for an edge dislocation with $\vec{l} = [0\, 0\, 1]$, $\vec{b} = [0\, 1\, 0]$, where $a = 5$, with coordinates $(26,\, 1000)\, $, i.e.
+the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
+(a), (e) and (i) are the stress fields for the infinite-domain solution, $\tns{\hat{\sigma}}$; (b), (f) and (j) are those obtaine from analytic tractions + FEM, $\tns{\hat{\sigma}}^{\textrm{A}}$; (c), (g) and (k) are those obtained using numeric tractions ($Q = 1$) + FEM, $\tns{\hat{\sigma}}^{\textrm{N}}$.
+(a) to (c) represent the $xx$; (e) to (g) the $yy$; and (i) to (k) the $xy$ components of the stress tensor.}
+    \label{f:head_vs_ana_vs_num_epar}
+\end{figure}
+\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, the $\textrm{A}$ superscript are the stresses calculated from analytic tractions and the $\textrm{N}$ superscript are those coming from numeric tractions where $Q = 1$ (same nomenclature in \cref{f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw}).
+The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}} = [1\, 0\, 0]$ and the dislocation is found at $(26, 1000)$.
+
 It is clear edge effects play a role in the generated stresses.
-All three components have notable differences from the infinite-domain solutions resulting from the finite constraints.
-There is also some artifacting (\cref{sf:syyAeperp,sf:sxyAeperp}) arising from the perturbation needed to avoid the singularity in the analytic traction calculation and error propagation from floating point arithmetic, as mentioned in \cref{s:method}.
-Of note is the large degree of asymmetry between both lobes of \cref{sf:sxxNeperp}, this is not a simple artifact due to numerical precision but a result of the numerical instability of gauss quadrature.
-Regardless, the overall shape of the isolines is similar in all three solutions for corresponding stress components.
-% TODO #51 make sure captions are correct and set the axes properly in figs 13-15 and 17
-\begin{figure}
-    \centering
-    \subfloat[%$\hat{\sigma}_{xx}$.
-        \label{sf:sxxeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEperp.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
-        \label{sf:sxxAeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEperp.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
-        \label{sf:sxxNeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEperp.pdf}}
-    }
-
-    \subfloat[%$\hat{\sigma}_{yy}$.
-        \label{sf:syyeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyEperp.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
-        \label{sf:syyAeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyAEperp.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
-        \label{sf:syyNeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyNEperp.pdf}}
-    }
-
-    \subfloat[%$\hat{\sigma}_{xy}$.
-        \label{sf:sxyeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyEperp.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
-        \label{sf:sxyAeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyAEperp.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
-        \label{sf:sxyNeperp}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyNEperp.pdf}}
-    }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [1 0 0]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
+All three components have notable differences from the infinite-domain solutions resulting from the finite constraints, but the overall agreement between them all is quite good.
+
+\begin{figure}
+    \centering
+    \subfloat[%$\hat{\sigma}_{xz}$.
+        \hspace{-0.8cm}\label{sf:sxzscrew}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxzscrew_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{xz}$.
+        \hspace{-0.8cm}\label{sf:sxzAscrew}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxzAscrew_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{xz}$.
+        \hspace{-0.8cm}\label{sf:sxzNscrew}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxzNscrew_leg.pdf}}
+    }~
+    \subfloat{
+        \includegraphics[height = 0.227\linewidth]{sxzNAscrew_leg.pdf}
+    }
+
+    \subfloat[%$\hat{\sigma}_{yz}$.
+        \hspace{-0.8cm}\label{sf:szyscrew}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syzscrew_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{A}_{yz}$.
+        \hspace{-0.8cm}\label{sf:syzAscrew}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syzAscrew_leg.pdf}}
+    }~
+    \subfloat[%$\hat{\sigma}^\textrm{N}_{yz}$.
+        \hspace{-0.8cm}\label{sf:syzNscrew}]
+    {
+        {\includegraphics[width=0.25\linewidth]{syzNscrew_leg}}
+    }~
+    \subfloat{
+        \includegraphics[height = 0.227\linewidth]{syzNAscrew_leg.pdf}
+    }
+    \caption{Image stresses for a screw dislocation with $\vec{l} = [0\, 0\, 1]$, $\vec{b} = [0\, 0\, 1]$, where $a = 5$, with coordinates $(26,\, 1000)\, $, i.e.
 the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
-From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript).
-The subfigure rows from top to bottom represent $\hat{\sigma}_{xx}$, $\hat{\sigma}_{yy}$ and $\hat{\sigma}_{xy}$.}
-    \label{f:head_vs_ana_vs_num_eperp}
-\end{figure}
-
-Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}}$ in \cref{f:head_vs_ana_vs_num_epar}.
+(a) and (e) are the stress fields for the infinite-domain solution, $\tns{\hat{\sigma}}$; (b) and (f) are those obtaine from analytic tractions + FEM, $\tns{\hat{\sigma}}^{\textrm{A}}$; (c) and (g) are those obtained using numeric tractions ($Q = 1$) + FEM, $\tns{\hat{\sigma}}^{\textrm{N}}$.
+(a) to (c) represent the $xz$; (e) to (g) the $yz$.}
+    \label{f:head_vs_ana_vs_num_screw}
+\end{figure}
+Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}} = [0\, 1\, 0]$ in \cref{f:head_vs_ana_vs_num_epar} for a dislocation in the same place, $(26, 1000)$.
 Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions.
-If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion (yellow and green contours as opposed to purple and blue) as well as a drastically different isosurface shape Here the isolines are not merely deformed nor pinched in the way that is indicative of numerical artifacting.
-They are fundamentally different when calculated with numeric tractions.
-Image stresses like those can lead dislocations to behave differently than they should, particularly if the sign inversion also comes with an increased force magnitude, which judging from \cref{f:rel_err_par_edge} is quite possible.
+If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion i.e.
+yellow and green contours as opposed to purple and blue.
+As well as a drastically different isosurface shape.
+Image stresses like those can lead dislocations to behave quite differently than they should, particularly if the sign inversion also has a significantly different magnitude than the correct solution.
 Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive.
-It is as absurd as a ship inverts the Archimidean principle.
-The other two stress fields $\hat{\sigma}_{yy}$, $\hat{\sigma}_{xy}$ follow similar trends to what we have already observed, where the isolines get squashed and flair towards the traction free surface.
-\begin{figure}
-    \centering
-    \subfloat[%$\hat{\sigma}_{xx}$.
-        \label{sf:sxxepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
-        \label{sf:sxxAepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
-        \label{sf:sxxNepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar.pdf}}
-    }
-
-    \subfloat[%$\hat{\sigma}_{yy}$.
-        \label{sf:syyepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyEpar.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
-        \label{sf:syyAepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyAEpar.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
-        \label{sf:syyNepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyNEpar.pdf}}
-    }
-
-    \subfloat[%$\hat{\sigma}_{xy}$.
-        \label{sf:sxyepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyEpar.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
-        \label{sf:sxyAepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyAEpar.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
-        \label{sf:sxyNepar}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyNEpar.pdf}}
-    }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
-the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
-From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript).
-The subfigure rows from top to bottom represent $\hat{\sigma}_{xx}$, $\hat{\sigma}_{yy}$ and $\hat{\sigma}_{xy}$.}
-    \label{f:head_vs_ana_vs_num_epar}
-\end{figure}
+It is as absurd as a ship that floats by lowering the water level.
 
 Perhaps the most evident deformation resulting from the displacement boundaries can be seen when $\vec{b} = \vec{b}_{\textrm{s}}$ in \cref{f:head_vs_ana_vs_num_screw}, where the lobes of the isolines are highly deformed when compared to the infinite-domain solutions.
-The familiar lobes look very different, but both analytic and numeric tractions yield fairly similar fields.
-\begin{figure}
-    \centering
-    \subfloat[%$\hat{\sigma}_{xz}$.
-        \label{sf:sxzscrew}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzscrew.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{xz}$.
-        \label{sf:sxzAscrew}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzAscrew.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{xz}$.
-        \label{sf:sxzNscrew}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzNscrew.pdf}}
-    }
-
-    \subfloat[%$\hat{\sigma}_{yz}$.
-        \label{sf:szyscrew}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzscrew.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{A}_{yz}$.
-        \label{sf:syzAscrew}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzAscrew.pdf}}
-    }~
-    \subfloat[%$\hat{\sigma}^\textrm{N}_{yz}$.
-        \label{sf:syzNscrew}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzNscrew.pdf}}
-    }
-    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e.
-the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom.
-From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript).
-The subfigure rows from top to bottom represent $\hat{\sigma}_{xz}$ and $\hat{\sigma}_{yz}$.}
-    \label{f:head_vs_ana_vs_num_screw}
-\end{figure}
-
-From \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw} it seems
-like both analytic and numeric tractions are appropriate in most cases.
-At least at these scales, there is only one instance where numeric tractions yield very incorrect results.
-Although these can have significant consequences later in a simulation's runtime, and particularly in simulations where dislocations regularly come into close contact with surfaces.
-
-It is also worth looking at the stress fields with a finer lens.
-\Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e.
-through the line $x = 50\, b$.
-\Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$.
-Here the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in the stresses.
-In general, the non-singular formulation smoothes out the stress line plots.
-However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions.
-Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
+Though deformed, their familiar shape is still recognisable and both analytic and numeric tractions yield fairly similar fields.
+
 \begin{figure}
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEperp.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_sxxEperp_leg.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_syyEperp.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_syyEperp_leg.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxyEperp.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_sxyEperp_leg.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_sxxEpar_leg.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_syyEpar.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_syyEpar_leg.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxyEpar.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_sxyEpar_leg.pdf}}
     }
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxzscrew.pdf}}
+        {\includegraphics[width=0.3\linewidth]{line_sxzscrew_leg.pdf}}
     }~
@@
     {
-        {\includegraphics[width=0.3\linewidth]{images/line_syzscrew.pdf}}
-    }
-    \caption{Line plots of the image stresses at $x = 102.5641\, b$ for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
-The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$.
+        {\includegraphics[width=0.3\linewidth]{line_syzscrew_leg.pdf}}
+    }
+    \caption{Line plots of the image stresses of a dislocation at $(26, 1000)$ for a line going through $x = 103$ (start of the third element) for the analytic image stresses, as well as those calculated with numeric and analytic tractions.
 (a) to (c) correspond to $\vec{b} = \vec{b}_{\textrm{e1}}$, (d) to (f) $\vec{b} = \vec{b}_{\textrm{e2}}$ and (g) to (h) to $\vec{b} = \vec{b}_{\textrm{s}}$.}
@@
 \end{figure}
-
-We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $25.6410\, b$ (centre of the first element) to $1000\, b$ (centre of the 10th element).
+From \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw} it seems like both analytic and numeric tractions are appropriate in most cases.
+At least at these scales, there is only one instance where numeric tractions yield very incorrect results.
+That said, these can have a significant impact on simulations, particularly those where multiple dislocations interact with surfaces in close proximity with one another.
+
+\begin{figure}
+    \centering
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxepar2}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxEpar3_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepar2}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxAEpar3_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepar2}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxNEpar3_leg.pdf}}
+    }
+    ~
+    \subfloat
+    {
+        {\includegraphics[height=0.227\linewidth]{sxxNAEpar3_leg.pdf}}
+    }
+
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxepar11}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxEpar11_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepar11}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxAEpar11_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepar11}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxNEpar11_leg.pdf}}
+    }~
+    {
+    {\includegraphics[height=0.227\linewidth]{sxxNAEpar11_leg.pdf}}
+    }
+
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxepartot2}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxEparTot3_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepartot2}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxAEparTot3_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepartot2}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxNEparTot3_leg.pdf}}
+    }~
+    {
+    {\includegraphics[height=0.227\linewidth]{sxxNAEparTot3_leg.pdf}}
+    }
+
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxepartot11}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxEparTot11_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepartot11}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxAEparTot11_leg.pdf}}
+    }~
+    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepartot11}]
+    {
+        {\includegraphics[width=0.25\linewidth]{sxxNEparTot11_leg.pdf}}
+    }
+    ~
+    {
+    {\includegraphics[height=0.227\linewidth]{sxxNAEparTot11_leg.pdf}}
+    }
+    \caption{Stresses for an edge dislocation with $\vec{l} = [0\, 0\, 1]$, $\vec{b} = [0\, 1\, 0]$.
+Subfigures (a) to (g) show image stresses; (h) to (m) show total stresses.
+In subfigures (a) to (c) and (h) to (j) the dislocation is found at $(77,\, 1000)$; in (e) to (g) and (k) to (m) the dislocation is at $(487,\, 1000)$.}
+    \label{f:head_vs_ana_vs_num_epar2to11}
+\end{figure}
+We also produced line plots to better show how the stress fields deviate from one another.
+\Cref{f:line_head_vs_ana_vs_num} shows line plots through the line $x = 103$ for a dislocation at $(26, 1000)$.
+\Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} to $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$.
+Here, the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in its stresses.
+In general, the non-singular formulation smoothes out the stress line plots.
+However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions such as in \cref{sf:line_sxxepar}.
+Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
+
+\begin{figure}
+    \centering
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar2}]
+    {
+        {\includegraphics[width=0.3\linewidth]{line_sxxEpar3.pdf}}
+    }~
+    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_syyepar11}]
+    {
+        {\includegraphics[width=0.3\linewidth]{line_sxxEpar11_leg.pdf}}
+    }
+
+    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot2}]
+    {
+        {\includegraphics[width=0.3\linewidth]{line_sxxEparTot3_leg.pdf}}
+    }~
+    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot11}]
+    {
+        {\includegraphics[width=0.3\linewidth]{line_sxxEparTot11_leg.pdf}}
+    }
+
+    \caption{Line plots corresponding to \cref{f:head_vs_ana_vs_num_epar2to11}.
+(a) and (c) are of the image stresses; (b) and (d) are of total stresses.
+(a) and (b) are of a dislocation at $(77,\, 1000)$, taken along the line $x = 103$.
+(b) and (d) are of a dislocation at $(487,\, 1000)$, taken along the line $x = 513$.}
+    \label{f:line_head_vs_ana_vs_num_epar2to11}
+\end{figure}
+To show the convergence in methods we also show stress fields in \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $(77,\, 1000)$ to  $(487,\, 1000)$.
 The line plots are taken from the second closest set of nodes in the positive $x$-direction i.e.
-at $x = 102.5641\, \sim 1076.9231\, b$.
-\begin{figure}
-    \centering
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar2}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar.pdf}}
-    }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar2}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar.pdf}}
-    }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:sxxNepar2}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar.pdf}}
-    }
-
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar11}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar11.pdf}}
-    }~
-    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar11}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar11.pdf}}
-    }~
-    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNepar11}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar11.pdf}}
-    }
-
-    \subfloat[$\sigma_{xx}$.\label{sf:sxxepartot2}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot3.pdf}}
-    }~
-    \subfloat[$\sigma^\textrm{A}_{x}$.\label{sf:sxxAepartot2}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot3.pdf}}
-    }~
-    \subfloat[$\sigma^\textrm{N}_{xx}$.\label{sf:sxxNepartot2}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot3.pdf}}
-    }
-
-    \subfloat[$\sigma_{xx}$.\label{sf:sxxepartot11}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot11.pdf}}
-    }~
-    \subfloat[$\sigma^\textrm{A}_{xx}$.\label{sf:sxxAepartot11}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot11.pdf}}
-    }~
-    \subfloat[$\sigma^\textrm{N}_{xx}$.\label{sf:sxxNepartot11}]
-    {
-        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot11.pdf}}
-    }
-    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$.
-(a) to (c) and (g) to (i) at $(25.6410,\, 1000)\, b$; (d) to (f) and (j) to (l) at $(1000,\, 1000)\, b$.
-(a) to (g) image stresses; (g) to (l) total stresses.}
-    \label{f:head_vs_ana_vs_num_epar2to11}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar2}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar3.pdf}}
-    }~
-    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_syyepar11}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar11.pdf}}
-    }
-
-    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot2}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot3.pdf}}
-    }~
-    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot11}]
-    {
-        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot11.pdf}}
-    }
-
-    \caption{Line plots corresponding to \cref{f:head_vs_ana_vs_num_epar2to11}.
-(a) and (c) are of image stresses; (b) and (d) are of total stresses.
-(a) and (b) are of a dislocation at $(25.6410,\, 1000)\, b$, taken along the line $x = 102.5641\, b$.
-(b) and (d) are of a dislocation at $(1000,\, 1000)\, b$ taken along the line $x \approx 1076.9231\, b$.}
-    \label{f:line_head_vs_ana_vs_num_epar2to11}
-\end{figure}
-From the line plots, it can be observed that both analytic and numeric tractions converge to similar shapes to each other, which is to be expected.
+at $x = 103,\, 513$.
+
+Notice that the image stresses in \cref{sf:sxxepar2,sf:sxxAepar2,sf:sxxNepar2} are all very close to \cref{sf:sxxNepar}, which is the stress field calculated via numerical tractions for a dislocation that is slightly closer to the surface.
+Essentially, the numerical tractions over or underestimated a set of forces something that become the dominant contributors as the dislocation moves away from the surface.
+
+From \cref{f:head_vs_ana_vs_num_epar2to11,f:line_head_vs_ana_vs_num_epar2to11} it can be observed that both analytic and numeric tractions converge to similar shapes to each other as expected.
 However it also becomes clear that the infinite-domain solution is not totally accurate for image stresses in finite domains due to edge effects.
-However, the glaring issue is that total stresses for each solution are significantly different as dislocations near the surface.
-The instability of Gauss quadrature when integrating rational functions tends to produce values that are outside the range of the infinite-domain solution, as well as being less smooth than the two other solutions.
-
-As expected, all solutions converge as the distance from the dislocation to surface increases because the magnitude of the real stresses increases in relation to that of the image stresses\textsuperscript{\footnote{The image stress components of \cref{eq:imageStressAnalyticEdge1,eq:imageStressAnalyticEdge2} are reflections about the line $x=0$ plus a corrective term that decays faster than the reflection term.
-In \cref{eq:imageStressAnalyticScrew}, the image term is a reflection about the line $x=0$.
-Therefore in both cases, as the dislocation moves away from the surface, the real stresses get relatively larger when compared to the image ones.}}.
-
-In order to show the effects numerical tractions have on simulations, we ran a very simple simulation where the only difference was the traction calculation method.
-A very simple yet illustrative qualitative example is to produce a scatter plot of the numerically calculated tractions vs analytically calculated ones at any time during any simulation.
-To obviate the problem even more, it helps making the axes proportional.
-What is observed in practically every case, is a positive correlation (though as we have seen in \cref{sf:sxxepar,sf:sxxAepar,sf:sxxNepar}, numerical tractions can produce sign inversions under specific conditions), but the axis that represents the numerically calculated tractions will be visually larger, as numeric tractions produce more extreme values.
-Statistically speaking, the closer the $R$-value is to 1 and the closer a linear fit is to $y=x$, the more accurate numerical tractions are for any given moment in a simulation.
-We have yet to find a single example where this happens.
-Furthermore, the chaotic nature of dislocation dynamics means that slight deviations will yield noticeably different results for the same starting conditions.
-
-This does not mean numeric tractions are useless, in fact, thethiny mostly work quite well.
-However, the impact their inherent numerical instability can be quite large.
-For us, analytic tractions despite being approximately an order of magnitude slower than numerically calculated tractions with $Q = 1$ \cite{Queyreau} (our tests agree with their findings), yield more stable and ultimately faster simulations.
+
+Lastly, to show how much numeric tractions can affect a result, \cref{f:simulation} shows a few snapshots of the simulation described in \cref{s:method}.
+The figures shown are not at equivalent times because the simulations using numeric tractions ran indefenitely.
+The line tension equilibrated with the image forces on the traction-free surface, preventing the dislocation from exiting and keeping it oscillating in a local energy minimum.
+The simulation using analytic tractions ended when the dislocation completely exited the surface as expected.
+It is feasable that at some point, the simulation using numeric tractions could jump out of the local minimum due to some spike in the tractions, but the last image was taken for a simulation time approximately 20 times greater than it took the one using analytic tractions to end when the dislocation fully exited the box.
+\begin{figure}
+    \subfloat[Analytic tractions $t = 0$.]
+    {
+        {\includegraphics[width=0.3\linewidth]{analytic_0.pdf}}
+    }~
+    \subfloat[Analytic tractions mid simulation.]
+    {
+        {\includegraphics[width=0.3\linewidth]{analytic_50.pdf}}
+    }~
+    \subfloat[Analytic tractions end.]
+    {
+        {\includegraphics[width=0.3\linewidth]{analytic_66.pdf}}
+    }
+
+    \subfloat[Numeric tractions $t = 0$.]
+    {
+        {\includegraphics[width=0.3\linewidth]{numeric_0.pdf}}
+    }~
+    \subfloat[Numeric tractions mid simulation.]
+    {
+        {\includegraphics[width=0.3\linewidth]{numeric_78.pdf}}
+    }~
+    \subfloat[Numeric tractions $t \to \infty$.]
+    {
+        {\includegraphics[width=0.3\linewidth]{numeric_156.pdf}}
+    }
+    \caption{Progression of simulations using both traction calculation methods.}
+    \label{f:simulation}
+\end{figure}
+
+\section{Conclusion}
+
+Often the effects of tractions on a simulation can be quite subtle if things do not go catastrophically wrong, but a quick and easy way of seeing how the numeric tractions have a tendancy to spike and invert sign (as in \cref{sf:line_sxxepar}) is to pause a simulation while its running and scatter plot the numeric tractions vs analytic ones.
+The plot will show a positive correlation---as the sign inversions in numeric tractions are relatively rare events---but whichever axis corresponds to the numeric tractions will have the largest range.
+Using proportional axes makes the differences quite evident even at a quick glance as the aspect ratio will be far from 1:1.
+
+In other parts of our work, we have noted that despite the analytic tractions taking approximately 10 times longer to compute than numerically calculated tractions with $Q = 1$ (which agrees with the findings in \cite{Queyreau}), yield more stable and ultimately faster simulations.
 Even simple simulations are typically faster when using analytic tractions over numeric ones.
-The margin grows the more complex the simulation and the further each simulation gets.
-It's all down to better behaved segments at or near surfaces.
-As such, we cannot recommend using numeric tractions when analytic ones are available.
+This was not the case with the simulation we show here, but the numeric tractions led to a hung simulation, which we have found is quite common.
+The margin by which using analytic tractions leads to faster overall simulations grows as simulation complexity increases.
+Only the simplest simulations initially benefit from numeric tractions but this often decreases and reverses as the simulation advances.
+Another fortunate side effect of more accurate tractions is the fact that fewer dislocation segments are generated during simulations, which \citet{bromage2018calculating} found when correctly accounting for the displacements generated by dislocations.
+
+Given our findings, we cannot recommend using numeric tractions when analytic ones are available.
 The losses in computational speed that result from moving from one to the other are more than made up for by the fewer topological operations, fewer generated segments, and more accurate velocities.
@@
 
-% Add line plot for a dislocation further away from the edge.
-% TODO #28
-
-% In a DDP simulation it is rare to find a dislocation segment so close to a quadrature point that the errors spike so dramatically.
-However, numerical integration with small $Q$ produces noticeable errors over a wide range of distances and segment lengths.
-Simulations usually contain a large number of dislocations which are parallel or near-parallel and close to surface elements.
-\Cref{f:rel_err_par_edge} shows it is not possible to accurately compute the tractions and nodal forces using Gauss quadrature even with a large number of quadrature points.
-
-% It is worth noting that rotational perturbation required for the analytic solution to be non-singular when a dislocation segment is parallel to a surface element can introduce small erroneous force components if the rotation is too large.
-If the rotational perturbations were small enough and floating point arithmetic exact, these erroneous forces would cancel when averaged over two opposite rotations.
-We found that a maximum rotation angle of $\pm0.5^\circ$ makes these erroneous force components negligible.
-
-% % TODO #23
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=0.7\linewidth]{images/load_disp.pdf}
-%     \caption{Load-displacement curve.
-When the tractions are evaluated analytically the curve is less noisy compared to numerical integration.
-As expected the yield point remains the same in both cases.}
-%     \label{f:load_disp_curve}
-% \end{figure}
-
-% The purpose of the cantilever simulation showed herein is not to be have an exactly physical when it comes to dislocation structure.
-Our initial source sizes and structure are somewhat unphysical, i.e.
-square sources with segment lengths on the order of the FE mesh courseness.
-There are also known issues with junction formation when multiple active slip systems are used in a single simulation.
-However, we are investigating not only the results but also the robustness and numerical stability of a fully integrated implementation of analytical solutions to dislocation tractions.
-By throwing the worst case scenario at both numerical and analytic traction calculations, we ensure both numerical and analytic solutions work even when the multiscale nature of the problem causes serious floating point arithmetic errors.
-
-% TODO #22 
-% A full discrete dislocation plasticity simulation of a microcantilever bend test demonstrates the benefits of using the analytic solution over numerical integration.
-The FE nodal forces were evaluated using Gauss quadrature with a single integration point for one simulation, and analytical tractions for the other.
-The simulations were otherwise identical with a finite element size of $0.25\mu\textrm{m}$ and sixty initial sources equally distributed on the 12 $\{1\bar{1}0\}\langle111\rangle$ bcc slip systems randomly distributed inside the region occuping the central $70\%$ of the cantilever ensuring the simulation proceeded at an acceptable rate and avoiding dislocations from exiting the fixed end, which can lead to problems due to the necessary FEM boundary conditions.
-The beam was fixed at $x=0$ and displaced by $U_{z}=-0.15~\mu\textrm{m}$ at $x=L=15~\mu\textrm{m}$.
-The material parameters were those of bcc tungsten, $\mu = 145\,\textrm{GPa}$ and $\nu = 0.28$.
-The analytic solution significantly reduced the noise in the load displacement curve as shown in \cref{f:load_disp_curve}.
-
-% The inset in \cref{f:load_disp_curve} shows the yield point remains the same, but the reaction forces diverge from each other as the simulation progresses.
-It should be noted that the dislocation structure was unchanged and so the change in the mechanical response is due entirely to the accuracy of the force calculation.
-The fluctuations are due to dislocations approaching a free surface and generating a large traction which is suddenly removed when the segment exits.
-These events are difficult to capture accurately when using numerical integration.
-
-% The dislocation structure did not change much in either case.
-In fact, when looking at it from the zoom level of \cref{f:dln_struc}, they both appear identical.
-There are however, many small differences in node position.
-Surprisingly, depending on the specific simulation, we have found between $10--20\%$ less dislocation segments when the analytic solution is used.
-Meaning the numerical solution systematically underestimates the average contribution of every single dislocation segment, with occasional massive spikes in force when a dislocation nears a gauss point.
-We expect these differences to get larger as simulation runtime increases.
-This is a fundamental and practically unavoidable problem of the numerical solution.
-
-% % TODO #24
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=0.7\linewidth]{images/analytic_struct.pdf}
-%     \caption{Final dislocation structure using analytic tractions.}
-%     \label{f:dln_struc}
-% \end{figure}
-
-% There are a few things that determine whether the numerical solutions are good enough for a given problem.
-When primarily investigating larger scale features of a dislocation structure---such as larger scale investigation of dislocation forresting around inclusions---Gauss quadrature is quite suitable.
-However, if one is interested in investigating the finer details of a dislocation structure---such as the nuanced interactions with closly packed inclusions---the analytic method is best.
-Furthermore, when investigating load-displacement curves, the analytical solutions provide a much better description for a relatively small increase in computational cost \cite{Queyreau}.
-That being said, the cost is nowhere near rate limiting, segment-segment forces and topological changes quickly become much more expensive as they both have worse asymptotic scaling, and topological changes also quickly become memory bound.
-An accurate description of load-displacement curves should also implement the exact displacement boundary conditions obtained by \citet{ddd_disp}.
-
-All our subsequent simulations have used analytic tractions as they run faster and yield more reasonable dislocation structures, particularly for more complex simulations.
+There is a case however, for combining both approaches in larger scale simulations.
+Since both numeric and analytic tractions converge to the same value as the dislocation-surface distance increases, a hybrid approach may possibly be undertaken without many negatives.
+Furthermore, \cite{Queyreau} also derived a Taylor series expansion of the solutions which can be used in cases where the dislocation-surface distance is large.
+These may be worth exploring in larger scale simulatios.
+However, in the types of systems we model, other parts of our model tend to be much more rate-limiting than tractions.
+As such, we have all but ceased to use numeric tractions in our work.
 
@@
 Sylvain Queyreau and Lawrence Livermore National Laboratory for their invaluable input.
-This work was supported by the Consejo Nacional de Ciencia y Tecnologia, Fondo Sectorial CONACYT-Secretaria de Energia-Sustentabilidad Energetica Cuarto Periodo [291129].
 This work was supported by the Engineering and Physical Sciences Research Council Centre for Doctoral Training in the Science and Technology of Fusion Energy EP/L01663X/1 and Fellowship grant EP/N007239/1.

### 2021-02-14 input/Tensile_Ni_100_size_effect.m

@@ -1,0 +1,151 @@
+clear all;
+close all;
+CRYSTAL_STRUCTURE = 'fcc';
+
+slipPlanes = [
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0
+        ];
+
+bVec = [
+    1.0 -1.0 0.0;
+    1.0 0.0 -1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    1.0 0.0 1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    0.0 1.0 1.0;
+    1.0 0.0 -1.0;
+    1.0 0.0 1.0;
+    0.0 1.0 1.0;
+    1.0 -1.0 0.0
+    ];
+
+% Values from https://www.azom.com/properties.aspx?ArticleID=2193
+% Nickel lattice parameter: 3.499 Angstroms
+amag = 3.499 * 1e-4; % microns * burgers vector
+
+% Nickel shear modulus: 72 - 86 GPa
+mumag = 79e3; % MPa
+MU = 1.0;
+
+% Nickel poisson's ratio 0.305 - 0.315.
+NU = 0.31;
+
+% x = <100>, y = <010>, z = <001>
+% FE domain dimensions: x/amag := x microns.
+% The size effect is given by the size disparity between dislocations and
+% volume. We can either change the size of the volume or the size of the
+% dislocations. 10x10x10 micron domain.
+dx = 10 / amag;
+dy = dx;
+dz = dx;
+mx = 20;
+my = 20;
+mz = 20;
+
+% Dislocation segment lengths and integration tolerances.
+% Try segLen = dx / 100, dx / 50, dx / 25, dx / 10, dx / 5, dx / 2
+segLen = dx / 10; % Source segment length.
+lmin = segLen / 10; % Minimum allowed segment length.
+lmax = segLen / 5; % Maximum allowed segment length.
+a = lmin / 20; % Dislocation core radius (for non-singular stresses).
+rann = lmin / 2; % Collision distance between two dislocations.
[…]

### 2021-02-14 input/Thesis_Ni_100_tensile.m

@@ -1,0 +1,221 @@
+% Results in strain-stress
+% Stress := load/area = Fsim/area of cantilever face
+% Strain := displacement/length = Usim/cantilever length
+clear all;
+close all;
+CRYSTAL_STRUCTURE = 'fcc';
+
+slipPlanes = [
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0
+        ];
+bVec = [
+    1.0 -1.0 0.0;
+    1.0 0.0 -1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    1.0 0.0 1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    0.0 1.0 1.0;
+    1.0 0.0 -1.0;
+    1.0 0.0 1.0;
+    0.0 1.0 1.0;
+    1.0 -1.0 0.0
+    ];
+
+% Values from https://www.azom.com/properties.aspx?ArticleID=2193
+% Nickel lattice parameter: 3.499 Angstroms
+amag = 3.499 * 1e-4; % microns * burgers vector
+% Nickel shear modulus: 72 - 86 GPa
+mumag = 79e3; % MPa
+MU = 1.0;
+% Nickel poisson's ratio 0.305 - 0.315.
+NU = 0.31;
+
+% x = <100>, y = <010>, z = <001>
+dz = 8.711 / amag; % 8.711 microns
+dx = 3 * dz;
+dy = 2 * dz;
+
+vertices = [0, 0, 0; ...
+            dx, 0, 0; ...
+            0, dy, 0; ...
+            dx, dy, 0; ...
+            0, 0, dz; ...
+            dx, 0, dz; ...
+            0, dy, dz; ...
+            dx, dy, dz];
+% u_dot = [m]/MPa, u_dot_real = [m]/[s]
+% mumag*1e6 converts the meters to micrometers in the units.
+% The experimental displacement rate is 5 nm = 5e-3 micrometers.
+% The cantilever is dx micrometers long.
[…]

### 2021-02-14 input/Thesis_Ni_110_tensile.m

@@ -1,0 +1,208 @@
+% Results in strain-stress
+% Stress := load/area = Fsim/area of cantilever face
+% Strain := displacement/length = Usim/cantilever length
+clear all;
+close all;
+CRYSTAL_STRUCTURE = 'fcc';
+
+slipPlanes = [
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0
+        ];
+bVec = [
+    1.0 -1.0 0.0;
+    1.0 0.0 -1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    1.0 0.0 1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    0.0 1.0 1.0;
+    1.0 0.0 -1.0;
+    1.0 0.0 1.0;
+    0.0 1.0 1.0;
+    1.0 -1.0 0.0
+    ];
+
+% Values from https://www.azom.com/properties.aspx?ArticleID=2193
+% Nickel lattice parameter: 3.499 Angstroms
+amag = 3.499 * 1e-4; % microns * burgers vector
+% Nickel shear modulus: 72 - 86 GPa
+mumag = 79e3; % MPa
+MU = 1.0;
+% Nickel poisson's ratio 0.305 - 0.315.
+NU = 0.31;
+
+% x = <110>, y = <1-10>, z = <001>
+dz = 8.711 / amag; % 8.711 microns
+dx = 3 * dz;
+dy = 2 * dz;
+
+vertices = [0, 0, 0; ...
+            dx, 0, 0; ...
+            0, dy, 0; ...
+            dx, dy, 0; ...
+            0, 0, dz; ...
+            dx, 0, dz; ...
+            0, dy, dz; ...
+            dx, dy, dz];
+% u_dot = [m]/MPa, u_dot_real = [m]/[s]
+% mumag*1e6 converts the meters to micrometers in the units.
+% The experimental displacement rate is 5 nm = 5e-3 micrometers.
+% The cantilever is dx micrometers long.
[…]

### 2021-02-14 input/Thesis_Zinc_100_tensile.m

@@ -1,0 +1,226 @@
+% Results in strain-stress
+% Stress := load/area = Fsim/area of cantilever face
+% Strain := displacement/length = Usim/cantilever length
+clear all;
+close all;
+CRYSTAL_STRUCTURE = 'fcc';
+
+slipPlanes = [
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        -1.0 1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 -1.0 1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0;
+        1.0 1.0 -1.0
+        ];
+bVec = [
+    1.0 -1.0 0.0;
+    1.0 0.0 -1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    1.0 0.0 1.0;
+    0.0 1.0 -1.0;
+    1.0 1.0 0.0;
+    0.0 1.0 1.0;
+    1.0 0.0 -1.0;
+    1.0 0.0 1.0;
+    0.0 1.0 1.0;
+    1.0 -1.0 0.0
+    ];
+
+% Values from https://www.azom.com/properties.aspx?ArticleID=2193
+% Nickel lattice parameter: 3.499 Angstroms
+amag = 3.499 * 1e-4; % microns * burgers vector
+% Nickel shear modulus: 72 - 86 GPa
+mumag = 79e3; % MPa
+MU = 1.0;
+% Nickel poisson's ratio 0.305 - 0.315.
+NU = 0.31;
+
+% x = <100>, y = <010>, z = <001>
+% 10 x 10 cross sectional area.
+% yield strength point
+% 13 dln/m^2, 10/ micron^2
+dz = 8.711 / amag; % 8.711 microns
+dx = 3 * dz;
+dy = 2 * dz;
+
+vertices = [0, 0, 0; ...
+            dx, 0, 0; ...
+            0, dy, 0; ...
+            dx, dy, 0; ...
+            0, 0, dz; ...
+            dx, 0, dz; ...
+            0, dy, dz; ...
+            dx, dy, dz];
+% u_dot = [m]/MPa, u_dot_real = [m]/[s]
+% mumag*1e6 converts the meters to micrometers in the units.
[…]

### 2021-02-14 input/fccLoops.m

@@ -1,0 +1,104 @@
+prismLinks = zeros(96, 2);
+prismbVec = zeros(96, 3);
+prismSlipPlane = zeros(96, 3);
+prismCoord = zeros(96, 3);
+shearLinks = zeros(96, 2);
+shearbVec = zeros(96, 3);
+shearSlipPlane = zeros(96, 3);
+shearCoord = zeros(96, 3);
+prismLinks(1:8,:) = [1 2; 2 3; 3 4; 4 5; 5 6; 6 7; 7 8; 8 1];
+prismbVec(1:8,:) = [0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0; 0.7071067811865475 -0.7071067811865475 0.0];
+prismSlipPlane(1:8,:) = [0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258; 0.5773502691896258 0.5773502691896258 0.5773502691896258];
+prismCoord(1:8,:) = [-0.577350269189626 -0.577350269189626 -0.5773502691896261; -0.16910197872576294 -0.16910197872576294 -1.393846850117352; 0.4082482904638629 0.4082482904638629 -0.8164965809277263; 0.9855985596534886 0.9855985596534886 -0.23914631173810041; 0.5773502691896257 0.5773502691896257 0.5773502691896258; 0.16910197872576282 0.16910197872576282 1.393846850117352; -0.40824829046386313 -0.40824829046386313 0.8164965809277264; -0.9855985596534891 -0.9855985596534891 0.23914631173810064];
+shearLinks(1:8,:) = [1 2; 2 3; 3 4; 4 5; 5 6; 6 7; 7 8; 8 1];
[…]

### 2021-02-14 src/AuxFEMCoupler.m

@@ -43,6 +43,8 @@ function [f, f_hat, para_tol, x3x6, n_se, gamma_dln, f_tilda_node, f_tilda_se,..
 
     f = zeros(3 * mno, 1);
     f_hat = zeros(3 * mno, 1);
+%     f = sparse(3*mno, 1);
+%     f_hat = sparse(3 * mno, 1);
     if isempty(gammaMixed)
         gamma_disp = gammau(:, 1);
         gamma_dln = gammat;
@@ -52,8 +54,13 @@ function [f, f_hat, para_tol, x3x6, n_se, gamma_dln, f_tilda_node, f_tilda_se,..
     end
     u = zeros(3 * mno, 1);
     u_hat = zeros(3 * mno, 1);
+%     u = sparse(3 * mno, 1);
+%     u_hat = sparse(3 * mno, 1);
+    
     u_tilda_0 = zeros(3 * mno, 1);
     u_tilda = zeros(3 * mno, 1);
+%     u_tilda_0 = sparse(3 * mno, 1);
+%     u_tilda = sparse(3 * mno, 1);
     
 
     if (~exist('CUDA_flag', 'var'))

### 2021-02-14 src/CollisionCheckerMex.c

@@ -39,7 +39,7 @@ void mexFunction(int nlhs, mxArray *plhs[],
     double vx0[3], vx1[3], vy0[3], vy1[3];
     double dist2[1] = {0}, ddist2dt[1] = {0}, L1[1] = {0}, L2[1] = {0};
     int logic, flag1, flag2, remesh_flag;
-    int i, j, k;
+    int i, j, k, s;
     int link_col, link_row, nodenoti, linkid, tmp;
     const double eps = 1E-12;
     int connectivity_M, connectivity_N;
@@ -53,6 +53,10 @@ void mexFunction(int nlhs, mxArray *plhs[],
     double bi[3], ni[3], bj[3], nj[3];
     double xmid[3], ymid[3];
     double Lcr_temp2 = 0.0;
+    double *s1Skip;
+    double *s2Skip;
+    int numLinksSkipped;
+    bool skipSegs = false;
     /********* MEX memory management *********/
     rn_x = (double *)mxGetPr(prhs[0]);
     rn_y = (double *)mxGetPr(prhs[1]);
@@ -71,6 +75,9 @@ void mexFunction(int nlhs, mxArray *plhs[],
     plane_x = (double *)mxGetPr(prhs[14]);
     plane_y = (double *)mxGetPr(prhs[15]);
     plane_z = (double *)mxGetPr(prhs[16]);
+    s1Skip = (double *)mxGetPr(prhs[17]);
+    s2Skip = (double *)mxGetPr(prhs[18]);
+    numLinksSkipped = mxGetNumberOfElements(prhs[17]);
     rn_length = mxGetNumberOfElements(prhs[0]);
     links_length = mxGetNumberOfElements(prhs[7]);
 
@@ -153,6 +160,23 @@ void mexFunction(int nlhs, mxArray *plhs[],
             while (k <= (int)round(connectivity[0][i]) - 1 /*correct for matlab indexing*/)
             {
                 linkid = (int)round(connectivity[2 * k + 1][i]) - 1; /*correct for matlab indexing*/
+                
+                // Skip segments that collided and got separated immediately after.
+                for (s = 0; s < numLinksSkipped; s++){
+                    if (linkid + 1 == (int)round(s1Skip[s]) && link_row + 1 == (int)round(s2Skip[s]) || linkid + 1 == (int)round(s2Skip[s]) && link_row + 1 == (int)round(s1Skip[s])){
+                        skipSegs = true;
+                        break;
+                    }
+                    else {
+                        skipSegs = false;
+                    }
+                }
+                
[…]

### 2021-02-14 src/EasyDD.m

@@ -58,7 +58,7 @@
 run inputCompletion.m
 
 % Compile mex files.
-CUDA_flag = compileCode(CUDA_flag);
+% CUDA_flag = compileCode(CUDA_flag);
 
 % Cleanup input structures.
 [rn, links] = cleanupnodes(rn, links);
@@ -70,12 +70,12 @@ CUDA_flag = compileCode(CUDA_flag);
 consistencycheck(rn, links, connectivity, linksinconnect);
 
 % Construct stiffeness matrix K and pre-compute L,U decompositions.
-[vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = ...
+[S, vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = ...
     finiteElement3D(dx, dy, dz, mx, my, mz, MU, NU);
 
 [K, L, U, P_l, P_u, Sleft, Sright, Stop, Sbot, Sfront, Sback, Smixed, gammat, ...
         gammau, gammaMixed, fixedDofs, freeDofs, processForceDisp, plotForceDisp] = ...
-    simType(kg, w, h, d, mno, mx, my, mz);
+    simType(kg, w, h, d, mno, mx, my, mz, S);
 
 plotFEMDomain(Stop, Sbot, Sright, Sleft, Sfront, Sback, Smixed, xnodes)
 
@@ -114,7 +114,7 @@ while simTime < totalSimTime
         close all
         save(sprintf('../output/%s_%d', simName, curstep), '-regexp', '^(?!(K|kg|L|U|P_l|P_u)$).');
     end
-    
+
     % Loading function.
     [sign_u_dot, u_dot, sign_f_dot, f_dot, u_tilda_0, u, u_hat, u_tilda] = calculateLoading(...
         sign_u_dot, u_dot, sign_f_dot, f_dot, u_tilda_0, u, f_bar, f_hat, f_tilda, u_bar, ...
@@ -132,13 +132,13 @@ while simTime < totalSimTime
         r_hat, gammaMixed, fixedDofs, freeDofs, curstep, t, simTime);
 
     %integrating equation of motion
-    [rnnew, vn, dt, fn, fseg] = integrator(rn, dt, dt0, MU, NU, a, Ec, links, connectivity, ...
-        rmax, rntol, mobility, vertices, rotMatrix, u_hat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag);
[…]

### 2021-02-14 src/FEM_DDD_Superposition.m

@@ -35,7 +35,7 @@ function [f_bar, f_hat, f_tilda, u_bar, u_hat, u_tilda, r_hat] = FEM_DDD_Superpo
     f(fixedDofs) = bcwt * u_hat(fixedDofs);
 
     if isempty(U)
-        u_hat = K(freeDofs) \ f(freeDofs);
+        u_hat(freeDofs) = K \ f(freeDofs);
     else
         u_hat(freeDofs) = P_l \ (U \ (L \ (P_u \ f(freeDofs)))); % using LU decomposition for sparse matrices
     end

### 2021-02-14 src/Utilda_bb_vec.m

@@ -187,8 +187,8 @@ function [Ux, Uy, Uz] = Utilda_bb_vec(rn, links, gnl, NU, xnodes, dx, ...
                 disp_dislo_tri_ABC_plas(Bprime', Aprime', Ctemp', nodepoints', b');
         end
 
-        if any(isnan(Utilda))
-            fprintf('Error in line 130 of Utilda_bb3_vec: Some output values are NaN')
+        if any(any(isnan(Utilda))) || any(any(isinf(Utilda)))
+            fprintf('Error in line 130 of Utilda_bb3_vec: Some output values are NaN or Inf')
             pause
         end
 

### 2021-02-14 src/cantileverBending.m

@@ -1,6 +1,6 @@
 function [K, L, U, P_l, P_u, Sleft, Sright, Stop, Sbot, Sfront, Sback, Smixed, gammat, gammau,...
     gammaMixed, fixedDofs, freeDofs, processForceDisp, plotForceDisp] = cantileverBending(...
-    kg, w, h, d, mno, mx, my, mz)
+    kg, w, h, d, mno, mx, my, mz,~)
 
     fprintf('Cantilever bending boundary conditions: reformatting K\n');
 

### 2021-02-14 src/cantileverBendingPlot.m

@@ -1,4 +1,4 @@
-function cantileverBendingPlot(Usim, Fsim, amag, mumag, curstep)
+function cantileverBendingPlot(Usim, Fsim, amag, mumag, curstep, args)
     figure(2)
     plot(Usim(1:curstep) * amag, -Fsim(1:curstep) * amag^2 * mumag);
     drawnow

### 2021-02-14 src/collideAndSeparateNodesAndSegments.m

@@ -1,15 +1,17 @@
 function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = collideAndSeparateNodesAndSegments(docollision, doseparation, ...
         rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew, rann, MU, NU, a, Ec, mobility, vertices, rotMatrix, ...
-        u_hat, nc, xnodes, D, mx, mz, w, h, d, lmin, CUDA_flag, Bcoeff, curstep)
+        u_hat, nc, xnodes, D, mx, my, mz, w, h, d, lmin, CUDA_segseg_flag, Bcoeff, curstep)
 
     if (docollision)
 
         % Collision detection and handling
         colliding_segments = 1;
-
+        
+        s1Skip = [];
+        s2Skip = [];
         while colliding_segments == 1
             [colliding_segments, n1s1, n2s1, n1s2, n2s2, floop, s1, s2, segpair] = CollisionCheckerMex(rnnew(:, 1), rnnew(:, 2), rnnew(:, 3), rnnew(:, end), ...
-                rnnew(:, 4), rnnew(:, 5), rnnew(:, 6), linksnew(:, 1), linksnew(:, 2), connectivitynew, rann,linksnew(:,3),linksnew(:,4),linksnew(:,5),linksnew(:,6),linksnew(:,7),linksnew(:,8));
+                rnnew(:, 4), rnnew(:, 5), rnnew(:, 6), linksnew(:, 1), linksnew(:, 2), connectivitynew, rann,linksnew(:,3),linksnew(:,4),linksnew(:,5),linksnew(:,6),linksnew(:,7),linksnew(:,8), s1Skip, s2Skip);
 
             if colliding_segments == 1%scan and update dislocation structure.
 
@@ -18,18 +20,47 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = collid
                 elseif floop == 2
                     fprintf("Step %d. Links %d and %d colliding by hinge condition.\n", curstep, s1, s2)
                 end
+                
+                numNode = size(rnnew, 1);
+                numSeg = size(linksnew, 1);
 
                 if colliding_segments == 1
-                    [rnnew, linksnew, ~, ~, fsegnew, colliding_segments] = collision(rnnew, linksnew, connectivitynew, ...
+                    [rnnewTmp, linksnewTmp, ~, ~, fsegnewTmp, colliding_segments] = collision(rnnew, linksnew, connectivitynew, ...
[…]

### 2021-02-14 src/collision.m

@@ -1,6 +1,6 @@
 function [rn, links, connectivity, linksinconnect, fseg, colliding_segments] = collision(...
         rn, links, connectivity, linksinconnect, fseg, mindist, MU, NU, a, Ec, mobility, vertices, rotMatrix, ...
-        uhat, nc, xnodes, D, mx, mz, w, h, d, floop, n1s1, n2s1, n1s2, n2s2, s1, s2, ~, lmin, CUDA_flag, Bcoeff)
+        uhat, nc, xnodes, D, mx, my, mz, w, h, d, floop, n1s1, n2s1, n1s2, n2s2, s1, s2, ~, lmin, CUDA_flag, Bcoeff)
     %floop to know wich loop has to be run
 
     colliding_segments = 1;
@@ -111,7 +111,7 @@ function [rn, links, connectivity, linksinconnect, fseg, colliding_segments] = c
 
                     for k = 1:connectivity(mergednodeid, 1)
                         linkid = connectivity(mergednodeid, 2 * k);
-                        fseg(linkid, :) = segforcevec(MU, NU, a, Ec, rn(:, [1 2 3 lrn2]), links, linkid, vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag);
+                        fseg(linkid, :) = segforcevec(MU, NU, a, Ec, rn(:, [1 2 3 lrn2]), links, linkid, vertices, uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag);
                         othernode = links(linkid, 3 - connectivity(mergednodeid, 2 * k + 1)); % 3-connectivity(mergednodeid,2*k+1) = 1 or 2, it corresponds to the position of the other node of the link ( the one which is not mergenode ) M
                         clist = [connectivity(othernode, 1) linspace(1, connectivity(othernode, 1), connectivity(othernode, 1))];
                         [rn(othernode, 4:6), ~] = mobility(fseg, rn, links, connectivity, othernode, clist, Bcoeff, rotMatrix);
@@ -222,7 +222,7 @@ function [rn, links, connectivity, linksinconnect, fseg, colliding_segments] = c
 
                 for k = 1:connectivity(mergednodeid, 1)
                     linkid = connectivity(mergednodeid, 2 * k);
[…]

### 2021-02-14 src/cuda_vector_map_utils.h

@@ -62,7 +62,7 @@ double *element_host_device_map(double *i_node_arr[], int i_n_elem_scope, int i_
         // Advance the input index to point at the j'th coordinate of the (k+1)'th element of the i'th node.
         idxi += 3;
       }
-      // Advance the output index to point at the i'th node of the j'th coordinate of the first element.
+      // Advance the output index to point at the i'th node of the (j+1)'th coordinate of the first element.
       idxf += n_elem_n_nodes;
     }
     // Advance the temporary index to point at the (i+1)'th node of the first coordinate of the first element.

### 2021-02-14 src/displacementControlMicropillarTensile.m

@@ -1,0 +1,10 @@
+function [u, u_bar, f, f_bar, calculateR_hat] = displacementControlMicropillarTensile(u, u_dot, sign_u_dot, u_bar_0, f, f_dot, sign_f_dot, f_bar_0, simTime, holdingTime, gamma_mixed)
+    f_bar = 0;
+    if simTime < holdingTime
+        u_bar = u_bar_0;
+    else
+        u_bar = u_dot * (simTime - holdingTime) + u_bar_0;
+    end
+    u(3 * gamma_mixed(:, 1) - 2) = sign_u_dot * u_bar;
+    calculateR_hat = true;
+end

### 2021-02-14 src/drndt.m

@@ -1,5 +1,5 @@
 function [vnvec, fn, fseg] = drndt(rnvec, flag, MU, NU, a, Ec, links, connectivity, ...
-        mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag)
+        mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, my, mz, w, h, d, Bcoeff, CUDA_flag)
 
     % This needs to be an input/obtained from the surface nodes. This is a temporary fix for cuboid.
     normals = [1 0 0;
@@ -14,7 +14,7 @@ function [vnvec, fn, fseg] = drndt(rnvec, flag, MU, NU, a, Ec, links, connectivi
 
     %nodal driving force
     fseg = segforcevec(MU, NU, a, Ec, rn, links, 0, vertices, ...
-        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag);
+        uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag);
 
     %mobility function
     [vn, fn] = mobility(fseg, rn, links, connectivity, [], [], Bcoeff, rotMatrix);

### 2021-02-14 src/finiteElement3D.m

@@ -1,4 +1,4 @@
-function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = finiteElement3D(dx, dy, dz, mx, my, mz, mu, nu)
+function [S, vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = finiteElement3D(dx, dy, dz, mx, my, mz, mu, nu)
     %=========================================================================%
     % E Tarleton edmund.tarleton@materials.ox.ac.uk
     % 3D FEM code using linear 8 node element with 8 integration pts (2x2x2)
@@ -108,7 +108,9 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = fi
     %    .            .                .
     %    1+(mx+1)  2+(mx+1)  ...   2*(mx+1)
     %    1         2         ...     mx+1
-
+    
+    % @dhortela made this, i'm backporting.
+    globnidx = zeros(mx + 1, my + 1, mz + 1);
     for k = 1:mz + 1
 
         for j = 1:my + 1% nodes in x direction
@@ -118,6 +120,7 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = fi
                 xnodes(gn, 1) = (i - 1) * w;
                 xnodes(gn, 2) = (j - 1) * h;
                 xnodes(gn, 3) = (k - 1) * d;
+                globnidx(i,j,k) = gn;
             end
 
         end
@@ -154,6 +157,9 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = fi
         end
 
     end
+    
+    % Backporting @dhortela's node set.
+    S = surfaceCuboid(w, h, d, mx, my, mz, globnidx, [1;0;0], [0;1;0], [0;0;1]);
 
     % figure(1);clf;hold on;view(3)
     % xlabel('x');ylabel('y');zlabel('z')
@@ -190,12 +196,15 @@ function [vertices, B, xnodes, mno, nc, n, D, kg, w, h, d, mx, my, mz, mel] = fi
         ns(q, 1, 1) = -1/8 * (1 - z(q, 2)) * (1 - z(q, 3));
[…]

### 2021-02-14 src/inputCompletion.m

@@ -7,6 +7,10 @@ if ~exist('amag', 'var')
     fprintf('Providing default value for amag = %f.\n', amag)
 end
 
+if ~exist('plotArgs', 'var')
+    plotArgs = [];
+end
+
 if ~exist('mumag', 'var')
     mumag = 1.6e5; % MPa only for plotting.
     fprintf('Providing default value for mumag = %f.\n', mumag)
@@ -125,12 +129,12 @@ if ~exist('lmin', 'var')
 end
 
 if ~exist('areamin', 'var')
-    areamin = lmin * lmin * sin(60/180 * pi) * 0.5;
+    areamin = lmin * lmin * 0.5;
     fprintf('Providing default value for areamin = %f.\n', areamin)
 end
 
 if ~exist('areamax', 'var')
-    areamax = 20 * areamin;
+    areamax = max(4*sind(45)*lmax^2/2, 1.2*areamin);%lmax * lmax * 0.5;%20 * areamin;
     fprintf('Providing default value for areamax = %f.\n', areamax)
 end
 
@@ -196,7 +200,7 @@ if ~exist('Ec', 'var')
 end
 
 if ~exist('rann', 'var')
-    rann = 0.9 * lmin;
+    rann = lmin/2;%0.9 * lmin;
     fprintf('Providing default value for rann = %f.\n', rann)
 end
 
@@ -266,6 +270,12 @@ if ~exist('para_scheme', 'var')
     para_scheme = 1;
     fprintf('Providing default value for para_scheme = %d, parallelise over dislocation segments.\n', para_scheme)
 end
+
+if ~exist('CUDA_segseg_flag', 'var')
+    CUDA_segseg_flag = false;
+    fprintf('Providing default value for para_scheme = %d, parallelise segseg forces.\n', CUDA_segseg_flag)
+end
+
 
 if ~exist('sign_u_dot', 'var')
     sign_u_dot = -1;
@@ -361,6 +371,11 @@ end
 if ~exist('dt', 'var')
     dt = dt0;
     fprintf('Providing default value for dt = %f.\n', dt)
+end
+
+if ~exist('dtMin', 'var')
+    dtMin = dt0*1e-6;
+    fprintf('Providing default value for dtMin = %f.\n', dtMin)
 end
 
 if ~exist('rotMatrix', 'var')

### 2021-02-14 src/int_trapezoid.m

@@ -1,5 +1,5 @@
-function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, links, connectivity, ...
-        rmax, rntol, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag)
+function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, dtMin, MU, NU, a, Ec, links, connectivity, ...
+        rmax, rntol, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, my, mz, w, h, d, Bcoeff, CUDA_flag)
 
     %Implicit numerical integrator using the Euler-trapezoid method adapted
     %from [Cai & Bulatov, Algorithm 10.2, pg. 216]. The tiemstep size is
@@ -12,7 +12,7 @@ function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, link
 
     %Calculate the current nodal velocities
     [vnvec0, fn, fseg] = drndt(rnvec0, flag, MU, NU, a, Ec, links, connectivity, ...
-        mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, Bcoeff, CUDA_flag);
+        mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, my, mz, w, h, d, Bcoeff, CUDA_flag);
 
     maxiter = 10; %Maximum number of times the timestep can be increased
     counter = 1; %Counter variable for the while loop
@@ -21,7 +21,6 @@ function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, link
     exponent = 20; %Variable that controls the degree that the calculated error affects the cange in timestep
     dt_old_good = 0; %Logical which flags whether an acceptable timestep has been calculated
     convergent = 0; %Logical for the operation of the while loop
-
     while (~convergent)
         rnvec1 = rnvec0 + vnvec0 * dt; %Euler forward method [Cai & Bulatov, eq. 10.43]
 
@@ -32,12 +31,13 @@ function [rn, vn, dt, fn, fseg] = int_trapezoid(rn, dt, dt0, MU, NU, a, Ec, link
         %Calculate the nodal velocities for the next timestep accordin to
[…]

### 2021-02-14 src/micropillarTensile.m

@@ -1,0 +1,105 @@
+function [K, L, U, P_l, P_u, Sleft, Sright, Stop, Sbot, Sfront, Sback, Smixed, gammat, gammau,...
+    gammaMixed, fixedDofs, freeDofs, processForceDisp, plotForceDisp] = micropillarTensile(kg, ~, ~, ~, mno, ~, ~, ~, S)
+
+
+Sleft = [S.left; S.topleft; S.botleft; S.frontleft; S.backleft; S.corners([1,3,5,7],:)];
+for i = 1:size(Sleft,1)
+    Sleft(i, 3:5) = [-1 0 0];
+end
+
+Sright = [S.right; S.topright; S.botright; S.frontright; S.backright];
+for i = 1:size(Sright,1)
+    Sright(i, 3:5) = [1 0 0];
+end
+
+for i = [2,4,6,8]
+    S.corners(i,3:5) = [1 0 0];
+end
+
+Stop = [S.top; S.topfront; S.topback];
+for i = 1:size(Stop,1)
+    Stop(i, 3:5) = [0 0 1];
+end
+
+Sbot = [S.bot; S.botfront; S.botback];
+for i = 1:size(Sbot,1)
+    Sbot(i, 3:5) = [0 0 -1];
+end
+
+Sfront = [S.front];
+Sback = [S.back];
+
+srfSet = cat(1, Sleft, Sright, S.corners([2,4,6,8],:), Stop, Sbot, Sfront, Sback);
+
+gammau = Sleft;
+gammaMixed = S.corners([2,4,6,8], :);
+[~, gammatIdx] = setdiff(srfSet(:,1),[gammau(:,1); gammaMixed(:,1)]);
+gammat = srfSet(gammatIdx, :);
+
+Smixed = gammaMixed;
+
+% Sleft = [S.left(:,1);
+% S.botleft(:,1);
+% S.topleft(:,1);
+% S.frontleft(:,1);
+% S.backleft(:,1);
+% S.corners([1,3,5,7], 1)];
+% 
+% Sback = [S.backleft(:,1);
+%     S.corners([3,7], 1)];
+% 
+% Sfront = [S.botleft(:,1);
+%     S.corners([1,3], 1)];
+% 
+% Sright = [S.corners([2,4,6,8], 1)];
+
+fixedDofs = [
+    3*S.left(:,1) - 2;
+    3*S.botleft(:,1) - 2;
+    3*S.topleft(:,1) - 2;
+    3*S.frontleft(:,1) - 2;
[…]

### 2021-02-14 src/micropillarTensileForceDisp.m

@@ -1,0 +1,15 @@
+function [Fsim, Usim, t] = micropillarTensileForceDisp(Fsim, f_bar, f_hat, f_tilda, Usim, u_bar, u_hat, u_tilda, r_hat, ...
+        gammaMixed, fixedDofs, freeDofs, curstep, t, simTime)
+
+    f_out = sum(r_hat(3 * gammaMixed(:, 1) - 2) + f_tilda(3 * gammaMixed(:, 1) - 2));
+    u_out = u_bar;
+
+    Fsim(curstep + 1) = f_out;
+    Usim(curstep + 1) = u_out;
+    t(curstep + 1) = simTime;
+
+    fprintf('fend = %d, Ubar = %d, simTime = %d\n', f_out, u_out, simTime);
+
+end
+
+

### 2021-02-14 src/micropillarTensilePlot.m

@@ -1,0 +1,7 @@
+function micropillarTensilePlot(Usim, Fsim, amag, mumag, curstep, args)
+    factDisp = args.factDisp;
+    factForce = args.factForce;
+    figure(2)
+    plot(Usim(1:curstep-1)*factDisp,Fsim(1:curstep-1)*factForce)
+    drawnow
+end

### 2021-02-14 src/mobfcc0.m

@@ -1,124 +1,150 @@
-function [vn, fn] = mobfcc0(fseg, rn, links, connectivity, nodelist, conlist)
-    %mobility law function (model: FCC0)
+function [vn, fn] = mobfcc0(fseg, rn, links, connectivity, nodelist, conlist, Bcoeff, rotMatrix) %#codegen
+%mobility law function (model: FCC0)
 
-    %Drag (Mobility) parameters (should be specified by Input file)
-    global Beclimb Bedge Bscrew Bline;
-    Bclimb = Beclimb;
+%Drag (Mobility) parameters (should be specified by Input file)
+Bscrew = Bcoeff.screw(1);
+Bedge = Bcoeff.edge(1);
+Bclimb = Bcoeff.climb(1);
+Bline = Bcoeff.line(1);
+%     global Beclimb Bedge Bscrew Bline;
+%     Bclimb = Beclimb;
 
-    %numerical tolerance
-    eps = 1e-10;
+rotateCoords = false;
 
-    % length of the nodelist for which the velocity will be calculated
-    L1 = size(nodelist, 1);
-    % if no nodelist is given then the nodelist becomes the whole node population
-    % this portion of the code sets up that nodelist along with the connlist
-    % that contains all of the nodal connections
-    if L1 == 0
-        L1 = size(rn, 1);
-        nodelist = linspace(1, L1, L1)';
-        [L2, L3] = size(connectivity);
-        conlist = zeros(L2, (L3 - 1) / 2 + 1);
-        conlist(:, 1) = connectivity(:, 1);
+if ~isempty(rotMatrix)
+    rotateCoords = true;
+    rn(:, 1:3) = rn(:, 1:3) * rotMatrix;
+    fseg(:, 1:3) = fseg(:, 1:3) * rotMatrix;
+    fseg(:, 4:6) = fseg(:, 4:6) * rotMatrix;
+    links(:, 3:5) = links(:, 3:5) * rotMatrix;
+    links(:, 6:8) = links(:, 6:8) * rotMatrix;
+end
 
-        for i = 1:L2
-            connumb = conlist(i, 1);
-            conlist(i, 2:connumb + 1) = linspace(1, connumb, connumb);
-        end
+%numerical tolerance
+eps = 1e-10;
 
+% length of the nodelist for which the velocity will be calculated
+L1 = size(nodelist, 1);
+% if no nodelist is given then the nodelist becomes the whole node population
[…]

### 2021-02-14 src/plotSimulation.m

@@ -1,4 +1,4 @@
-function plotSimulation(Usim, Fsim, rn, links, plim, vertices, plotFreq, viewangle, plotForceDisp, amag, mumag, curstep, plotFlags)
+function plotSimulation(Usim, Fsim, rn, links, plim, vertices, plotFreq, viewangle, plotForceDisp, amag, mumag, curstep, plotFlags, args)
 
     figNum = 0;
     
@@ -14,7 +14,7 @@ function plotSimulation(Usim, Fsim, rn, links, plim, vertices, plotFreq, viewang
         if plotFlags.secondary
             figNum = figNum + 1;
             figure(figNum)
-            plotForceDisp(Usim, Fsim, amag, mumag, curstep);
+            plotForceDisp(Usim, Fsim, amag, mumag, curstep, args);
         end
     end
 

### 2021-02-14 src/plotnodes.m

@@ -12,9 +12,9 @@ function [output] = plotnodes(rn, links, plim, vertices)
         n0 = links(i, 1);
         n1 = links(i, 2);
         %to skip external nodes...
-        %     if rn(n0,end)==67||rn(n1,end)==67
-        %        continue;
-        %     end
+%             if rn(n0,end)==67||rn(n1,end)==67
+%                continue;
+%             end
         lvec = amag * (rn(n1, 1:3) - rn(n0, 1:3));
         plane_n = links(i, 6:8);
         bvec = links(i, 3:5);

### 2021-02-14 src/remesh.m

@@ -1,6 +1,6 @@
 function [rn, links, connectivity, linksinconnect, fseg] = remesh(rn, links, ...
         connectivity, linksinconnect, fseg, lmin, lmax, areamin, areamax, MU, ...
-        NU, a, Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, ...
+        NU, a, Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, my, mz, ...
         w, h, d, CUDA_flag, Bcoeff)
     % first coarsen the parts of the mesh than can be coarsened
     % then refine the parts of the mesh that need it
@@ -8,16 +8,16 @@ function [rn, links, connectivity, linksinconnect, fseg] = remesh(rn, links, ...
     % do not change the order of these two subroutines
     [rn, links, connectivity, linksinconnect, fseg] = meshcoarsen(rn, links, connectivity, ...
         linksinconnect, fseg, lmin, lmax, areamin, MU, NU, a, Ec, mobility, vertices, rotMatrix, ...
-        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff);
+        uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag, Bcoeff);
 
     [rn, links, connectivity, linksinconnect, fseg] = meshrefine(rn, links, connectivity, ...
         linksinconnect, fseg, lmin, lmax, areamax, MU, NU, a, Ec, mobility, vertices, rotMatrix, ...
-        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff);
+        uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag, Bcoeff);
 end
 
 function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = meshcoarsen(...
         rn, links, connectivity, linksinconnect, fseg, lmin, lmax, areamin, MU, NU, a, ...
-        Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff)
+        Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag, Bcoeff)
     rnnew = rn;
     [~, lrn2] = size(rn);
     linksnew = links;
[…]

### 2021-02-14 src/remeshPreCollision.m

@@ -1,6 +1,6 @@
 function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = remeshPreCollision(rnnew, linksnew, ...
         connectivitynew, linksinconnectnew, fsegnew, lmin, lmax, areamin, areamax, MU, NU, a, Ec, ...
-        mobility, rotMatrix, doremesh, dovirtmesh, vertices, u_hat, nc, xnodes, D, mx, mz, w, h, d, ...
+        mobility, rotMatrix, doremesh, dovirtmesh, vertices, u_hat, nc, xnodes, D, mx, my, mz, w, h, d, ...
         TriangleCentroids, TriangleNormals, CUDA_flag, Bcoeff)
 
     if doremesh% do virtual re-meshing first
@@ -13,7 +13,7 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = remesh
         %remeshing internal dislocation structures
         [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = remesh_all(rnnew, linksnew, ...
             connectivitynew, linksinconnectnew, fsegnew, lmin, lmax, areamin, areamax, MU, NU, a, Ec, ...
-            mobility, rotMatrix, doremesh, dovirtmesh, vertices, u_hat, nc, xnodes, D, mx, mz, w, h, d, ...
+            mobility, rotMatrix, doremesh, dovirtmesh, vertices, u_hat, nc, xnodes, D, mx, my, mz, w, h, d, ...
             TriangleCentroids, TriangleNormals, CUDA_flag, Bcoeff);
     end
 

### 2021-02-14 src/remesh_all.m

@@ -12,7 +12,7 @@
 
 function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = remesh_all(rn, links, ...
         connectivity, linksinconnect, fseg, lmin, lmax, areamin, areamax, MU, NU, a, Ec, mobility, rotMatrix, ...
-        doremesh, dovirtmesh, vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, P, fn, CUDA_flag, Bcoeff)
+        doremesh, dovirtmesh, vertices, uhat, nc, xnodes, D, mx, my, mz, w, h, d, P, fn, CUDA_flag, Bcoeff)
 
     if dovirtmesh
         % Beginning of surface remeshing for surface node.
@@ -29,7 +29,7 @@ function [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = remesh
     if doremesh
         [rnnew, linksnew, connectivitynew, linksinconnectnew, fsegnew] = remesh(rnnew, linksnew, ...
             connectivitynew, linksinconnectnew, fsegnew, lmin, lmax, areamin, areamax, MU, NU, a, ...
-            Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff);
+            Ec, mobility, vertices, rotMatrix, uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag, Bcoeff);
     end
 
 end

### 2021-02-14 src/segforcevec.m

@@ -1,5 +1,5 @@
 function [fseg_tot] = segforcevec(MU, NU, a, Ec, rn, links, linkid, ~, ...
-        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag)
+        uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag)
     %compute nodal driving force of dislocation network by stress formula
     %(vectorized version)
     %rn: nodal position
@@ -37,7 +37,7 @@ function [fseg_tot] = segforcevec(MU, NU, a, Ec, rn, links, linkid, ~, ...
     if linkid == 0%calculate forces on all segments
         %PK force due to applied stress
 
-        fpk = pkforcevec(uhat, nc, xnodes, D, mx, mz, w, h, d, segments);
+        fpk = pkforcevec(uhat, nc, xnodes, D, mx, my, mz, w, h, d, segments);
 
         %self force due to self stress
         [fs0, fs1] = selfforcevec(MU, NU, a, Ec, segments);
@@ -73,7 +73,7 @@ function [fseg_tot] = segforcevec(MU, NU, a, Ec, rn, links, linkid, ~, ...
         end
 
         %PK force due to applied stress
-        fpk = pkforcevec(uhat, nc, xnodes, D, mx, mz, w, h, d, segments(linkid, :));
+        fpk = pkforcevec(uhat, nc, xnodes, D, mx, my, mz, w, h, d, segments(linkid, :));
 
         %self force due to self stress
         [fs0, fs1] = selfforcevec(MU, NU, a, Ec, segments(linkid, :));
@@ -97,7 +97,7 @@ end
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-function f = pkforcevec(uhat, nc, xnodes, D, mx, mz, w, h, d, segments)
+function f = pkforcevec(uhat, nc, xnodes, D, mx, my, mz, w, h, d, segments)
     %nodal force on dislocation segments due to applied stress sigext
     %(vectorized version)
     %format of segments array:
@@ -119,7 +119,7 @@ function f = pkforcevec(uhat, nc, xnodes, D, mx, mz, w, h, d, segments)
             pause;
         end
 
[…]

### 2021-02-14 src/separation.m

@@ -1,6 +1,6 @@
 function [rn, links, connectivity, linksinconnect, fseg] = separation(doseparation, rn, ...
         links, connectivity, linksinconnect, fseg, mobility, rotMatrix, MU, NU, a, Ec, mindist, ...
-        vertices, uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag, Bcoeff)
+        vertices, uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag, Bcoeff)
 
     if ~doseparation
         return
@@ -124,14 +124,14 @@ function [rn, links, connectivity, linksinconnect, fseg] = separation(doseparati
                 for k = 1:connectivity(i, 1)
                     linkid1 = connectivity(i, 2 * k);
                     fseg(linkid1, :) = segforcevec(MU, NU, a, Ec, rn(:, [1 2 3 lrn2]), links, linkid1, vertices, ...
-                        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag);
+                        uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag);
                 end
 
                 % calculate the segment forces connected to the new node
                 for k = 1:connectivity(lastnode, 1)
                     linkid2 = connectivity(lastnode, 2 * k);
                     fseg(linkid2, :) = segforcevec(MU, NU, a, Ec, rn(:, [1 2 3 lrn2]), links, linkid2, vertices, ...
-                        uhat, nc, xnodes, D, mx, mz, w, h, d, CUDA_flag);
+                        uhat, nc, xnodes, D, mx, my, mz, w, h, d, CUDA_flag);
                 end
 
                 % evaluate the power dissipated by this splitting configuration

### 2021-02-14 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/Input_HeadVsFEM_ReactionForce.m

@@ -16,14 +16,14 @@ a = 5;
 
 % No rotation matrix.
 % bVec = [1 1 1];
-% nVec = [-1 1 0];
+% nVec = [1 -1 0];
 
 % With rotation matrix.
-n1 = [1 0 0]; e1 = [1;1;1]; e1 = e1/norm(e1);
-n2 = [0 1 0]; e2 = [1;-1;0]; e2 = e2/norm(e2);
-n3 = cross(n1,n2); e3 = cross(e1,e2); e3 = e3/norm(e3);
+n1 = [1 0 0]; e1 = [1; 1; 1]; e1 = e1 / norm(e1);
+n2 = [0 1 0]; e2 = [1; -1; 0]; e2 = e2 / norm(e2);
+n3 = cross(n1, n2); e3 = cross(e1, e2); e3 = e3 / norm(e3);
 rotMatrix = [e1 e2 e3]';
-bVec = [1 0 0]*sqrt(3)/2;
+bVec = [1 0 0] * sqrt(3) / 2;
 nVec = [0 1 0];
 
 bVec * rotMatrix
@@ -79,7 +79,7 @@ xcoord = dx / 32; % eigth of the domain.
 %%
 ycoord = dy / 2; % middle of the domain
 % ycoord = ycoord(2)/2; % middle of first element
-simName = strcat(simName, 'corner');
+% simName = strcat(simName, 'corner');
 x = linspace(xcoord, xcoord, len);
 y = linspace(ycoord, ycoord, len);
 z = linspace(0, dz, len);
@@ -92,13 +92,14 @@ rn(:, 1) = x;
 rn(:, 2) = y;
 rn(:, 3) = z;
 links = zeros(len - 1, 8);
-rn(1, 4) = 6;%61
-rn(end, 4) = 6;%61
-rn = [rn; x(1) y(1) -1000*dz 67; x(1) y(1) 1000*dz 67];
+rn(1, 4) = 6; %61
+rn(end, 4) = 6; %61
+rn = [rn; x(1) y(1) -1000 * dz 67; x(1) y(1) 1000 * dz 67];
 
 for i = 1:len - 1
     links(i, :) = [i, i + 1, bVec, nVec];
 end
+
 links = [links; len + 1, 1, bVec, nVec; len + 2, len, bVec, nVec];
 % rntol = 45;
 
[…]

### 2021-02-14 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/simulationGifs.m

@@ -1,0 +1,149 @@
+clear all
+
+nameAIni = '../../../../output/initial_analytic_11-Jan-2021_bb_0';
+nameA = '../../../../output/analytic_11-Jan-2021_bb_';
+nameNIni = '../../../../output/initial_numeric_11-Jan-2021_bb_0';
+nameN = '../../../../output/numeric_11-Jan-2021_bb_';
+addpath '../../../'
+
+%%
+axis tight manual % this ensures that getframe() returns a consistent size
+load(nameAIni);
+counter = 0;
+outputname = './paper/images/analytic.gif';
+while counter < 66
+    filename = strcat(nameA, sprintf('%d', counter));
+    load(filename)
+    view([0 0])
+%     view([-15 15])
+    plotnodes(rn,links,plim,vertices);
+    % Capture the plot as an image
+    frame = getframe(gcf);
+    im = frame2im(frame);
+    [imind,cm] = rgb2ind(im,256);
+    % Write to the GIF File
+    if counter == 0
+        imwrite(imind,cm,outputname,'gif', 'Loopcount',inf);
+    else
+        imwrite(imind,cm,outputname,'gif','WriteMode','append');
+    end
+    counter = counter + 1;
+end
+
+%%
+axis tight manual
+load(nameAIni)
+counter = 0;
+outputname = './paper/images/analytic_';
+filename = strcat(nameA, sprintf('%d', counter));
+outputname = strcat(outputname, sprintf('%d', counter));
+load(filename)
+plotnodes(rn,links,plim,vertices);
+set(gcf, 'Units', 'Inches');
+pos = get(gcf, 'Position');
+set(gcf, 'PaperPositionMode', 'Auto', 'PaperUnits', 'Inches', 'PaperSize', [pos(3), pos(4)])
+print(gcf, sprintf('%s.pdf', outputname), '-dpdf', '-r300')
+
+counter = 30;
+outputname = './paper/images/analytic_';
+filename = strcat(nameA, sprintf('%d', counter));
+outputname = strcat(outputname, sprintf('%d', counter));
+load(filename)
+plotnodes(rn,links,plim,vertices);
+set(gcf, 'Units', 'Inches');
+pos = get(gcf, 'Position');
+set(gcf, 'PaperPositionMode', 'Auto', 'PaperUnits', 'Inches', 'PaperSize', [pos(3), pos(4)])
[…]

### 2021-03-05 docs/EasyDD_Startup_Guide/EasyDD Startup Guide.tex

%%%%%%%%%%

%%% Document type

\documentclass[a4paper,12pt]{article}

%%% Packages and formatting

%% Symbolic maths
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{tabu}

%% Algorithms
\usepackage[ruled,vlined]{algorithm2e}
\SetKw{KwBy}{by} % for loop
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}} % comment colours?
\SetCommentSty{mycommfont} % algorithm comments

%% Theorems and definitions
\newtheorem{definition}{Definition}[section]

%% Figure graphics
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{wrapfig}

%% Comments
\usepackage{comment}

%% Margins and spacing
\usepackage[left=3.5cm, right=3cm, top=3cm, bottom=3cm]{geometry}
\usepackage{setspace}
%\intextsep the space between text and floats in the running text
%\textfloatsep the space between a float at the top of the page and the text, also the space below text and a float at the bottom of the page
%\floatsep the space between to consecutive floats
\setlength{\intextsep}{1cm}
\setlength{\textfloatsep}{1cm}
\setlength{\parskip}{0.2cm}

%% Highlighting
\usepackage{soul}
\usepackage{color}
\usepackage{xcolor}

%% Language and quotes
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

%% Fonts
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault} % Use after title page

%% Paths
\graphicspath{ {./figures/} }

%% Bibliography
\usepackage{natbib}
\usepackage[
backend=biber,
style=nature,
citestyle=numeric,
sorting=ynt,
natbib=true
]{biblatex}
\addbibresource{bibliography.bib}

%% Hyperlinks
\usepackage{hyperref} % WARNING: import this last!
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=violet,
    citecolor=magenta,
    menucolor=blue,
%    allcolors=blue, % Sets all colours equal
%    pdftitle={Sharelatex Example},
%    bookmarks=true,
%    pdfpagemode=FullScreen
}
\urlstyle{same}
%\href{http://www.sharelatex.com}{Something Linky}
%\url{http://www.sharelatex.com}
%\href{run:./file.txt}{File.txt}

%% Referencing
\usepackage{cleveref}
\newcommand{\crefrangeconjunction}{--} % Get an en-dash instead of the word "to"

%%%

%%%%%%%%%%

\begin{document}

%%% Document spacing

% In mathematics DPhil thesis template:
%\baselineskip=18pt plus1pt
% Instead you can try double spacing:
\doublespacing

%%%

\begin{titlepage}
    \begin{center}
        \vspace*{3cm}

        \Huge
        EasyDD Startup Guide

 	\vfill

        \vspace{3cm}

        \includegraphics[width=0.35\textwidth]{ox_brand_cmyk_pos_crop1.pdf}

 	\vspace{1cm}

 	\LARGE
    Oxford Materials \\
    \Large
    March 5, 2021

    \end{center}
\end{titlepage}

\renewcommand{\familydefault}{\sfdefault} % Font!

\pagenumbering{roman}

\tableofcontents
\newpage

\pagenumbering{arabic}

\section{Getting EasyDD}

EasyDD is a MATLAB-based discrete dislocation plasticity code developed in Oxford based on DDLab. The official build is publicly available to be downloaded from \href{https://github.com/TarletonGroup/EasyDD}{GitHub}. To begin working on this code without affecting the original repository, you may \href{https://docs.github.com/en/free-pro-team@latest/github/getting-started-with-github/fork-a-repo}{fork} it to your own repository. As you make modifications in your repository, the original repository may change; to update these changes in your own repository, you must \href{https://docs.github.com/en/free-pro-team@latest/github/collaborating-with-issues-and-pull-requests/syncing-a-fork}{sync the fork}.

\section{Input file}

To run a simulation, you must first specify and run an input file. This generates all of the material-specific parameters and specifies subprocesses which EasyDD will use to run the simulation. Subprocesses are defined as function handles and may be custom-made by the user. If a mandatory parameter is failed to be defined in the input file, a default value will be used so that the simulation can run anyways.

\subsection{Input variables}

\subsubsection*{Material parameters}

\begin{itemize}
  \item \texttt{rn}: $N \times 4$ matrix designating the positions and \texttt{flag}s of all $N$ nodes
  \begin{equation*}
  \texttt{rn} = 
  \begin{bmatrix}
  x_1 & y_1 & z_1 & \texttt{flag}_1 \\
  x_2 & y_2 & z_2 & \texttt{flag}_2 \\
  \vdots & \vdots & \vdots & \vdots \\
  x_N & y_N & z_N & \texttt{flag}_N
  \end{bmatrix}
  \end{equation*}
  \texttt{flag} = 0: mobile node; \texttt{flag} = 7: immobile node; \texttt{flag} = 6: node only allowed to move on its surface; \texttt{flag} = 67: virtual node at pseudo-infinity
  \item \texttt{links}: $M \times 8$ matrix designating the start and end node \texttt{id}'s, the normalised burgers vector $(b_{xi},b_{yi},b_{zi})$, and slip plane normal $(n_{xi},n_{yi},n_{zi})$ for each of the $M$ segments
  \begin{equation*}
  \texttt{links} = 
  \begin{bmatrix}
  \alpha & \beta & b_{x1} & b_{y1} & b_{z1} & n_{x1} & n_{y1} & n_{z1}\\
  \beta & \gamma & b_{x2} & b_{y2} & b_{z2} & n_{x2} & n_{y2} & n_{z2}\\
  \vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots\\
  \delta & \epsilon & b_{xM} & b_{yM} & b_{zM} & n_{xM} & n_{yM} & n_{zM}\\
  \end{bmatrix}
  \end{equation*}
  \item \texttt{MU}: material's shear modulus
  \item \texttt{NU}: material's Poisson's ratio
  \item \texttt{a}: dislocation core isotropic spreading radius
  \item \texttt{Ec}: energy per unit length of the elastic contribution of the core of a screw dislocation
  \item \texttt{Bcoeff}: drag coefficients corresponding to different dislocation orientations; definition depends on mobility law
  \item \texttt{rotMatrix}: rotation matrix which rotates crystal slip system axes in mobility law
  \item \texttt{amag}: lattice parameter in units of $\mu$m
  \item \texttt{mumag}: material's shear modulus in units of MPa
\end{itemize}

\subsubsection*{Nodal network hyper-parameters}

\begin{itemize}
  \item \texttt{maxconnections}: total number of segments permitted to be connected to one node
  \item \texttt{lmax}: maximum length permitted for any segment
  \item \texttt{lmin}: minimum length permitted for any segment
  \item \texttt{areamax}: maximum area preferred between three consecutive nodes in a dislocation
  \item \texttt{areamin}: minimum area preferred between three consecutive nodes in a dislocation
  \item \texttt{rmax}: maximum distance any node may move during a given time increment
  \item \texttt{rann}: maximum distance two non-consecutive segments or nodes can be from each other in order to interact
  \item \texttt{rntol}: error tolerance for the integrator in order to adjust the time increment
  \item \texttt{dt0}: maximum permitted absolute time increment
  \item \texttt{dt}: current absolute time increment
  \item \texttt{totalSimTime}: absolute maximum time duration of simulation
  \item \texttt{holdingTime}: absolute time duration before any loading is applied
\end{itemize}

\subsubsection*{Geometry \& boundary condition variables}

\begin{itemize}
  \item \texttt{dx}, \texttt{dy}, \texttt{dz}: cantilever (cuboid) beam size in $x$,$y$,$z$ directions
  \item \texttt{mx}, \texttt{my}, \texttt{mz}: number of finite elements along $x$,$y$,$z$ directions
  \item \texttt{u\_dot}, \texttt{sign\_u\_dot}, \texttt{u\_bar}, \texttt{u\_tilde}, \ldots: boundary condition for nodal displacement
  \item \texttt{f\_dot}, \texttt{sign\_f\_dot}, \texttt{f\_bar}, \texttt{f\_tilde}, \ldots: boundary condition for nodal force
  \item \texttt{r\_hat}: boundary condition for nodal reaction force
  \item \texttt{calculateLoadingFunctionArgs}: struct containing variables for loading conditions
\end{itemize}

\subsubsection*{Post-processing parameters}

\begin{itemize}
  \item \texttt{printfreq}: frequency per time-step that nodal information is printed
  \item \texttt{saveFreq}: frequency per time-step that workspace variables are saved
  \item \texttt{plotFreq}: frequency per time-step that the nodal positions are plotted
  \item \texttt{plim}: maximum permitted value for any of the $x$, $y$ and $z$ values plotted
  \item \texttt{viewangle}: angle orientation of plot display [\texttt{azimuth},\texttt{elevation}]
  \item \texttt{plotArgs}: struct containing variables for plotting
  \item \texttt{plotFlags}: struct containing flags to enable plotting
\end{itemize}

\subsubsection*{Parallelisation \& flags}

\begin{itemize}
  \item \texttt{n\_threads}: number of threads per GPU block
  \item \texttt{para\_scheme}: parallelisation scheme for traction calculations (\texttt{para\_scheme} = 0: none; \texttt{para\_scheme} = 1: over dislocations; \texttt{para\_scheme} = 2: over surface elements)
  \item \texttt{CUDA\_flag}: enables compiling of CUDA code
  \item \texttt{CUDA\_segseg\_flag}: enables seg-seg force computation parallelisation
  \item \texttt{doremesh}: enables remesh phase for each time-step
  \item \texttt{docollision}: enables collision phase for each time-step
  \item \texttt{doseparation}: enables separation phase for each time-step
  \item \texttt{dovirtmesh}: enables virtual remeshing phase for each time-step
\end{itemize}

\subsubsection*{Subprocesses}

\begin{itemize}
  \item \texttt{mobility}: specifies mobility law function subprocess (e.g. \texttt{@mobfcc0})
  \item \texttt{integrator}: specifies integrator function subprocess (e.g. \texttt{@int\_trapezoid})
  \item \texttt{simType}: specifies simulation geometry and assigns types of boundary conditions to degrees of freedom (e.g. \texttt{@cantileverBending})
  \item \texttt{calculateLoading}: specifies general loading conditions (e.g. \texttt{@constantLoading})
  \item \texttt{loading}: calculates time-dependent boundary conditions at degrees of freedom (e.g. \texttt{@displacementControl})
  \item \texttt{calculateTractions}: specifies how the tractions on surface nodes are calculated (e.g. \texttt{@calculateAnalyticTractions})
\end{itemize}

\subsection{Parameter constraints}

It is important that the input parameters fulfill a set of logical constraints which are imposed by the simulation geometry and nodal network. Poorly defined parameters may result in the simulation generating numerical instabilities and nonphysical results. In the following, some recommended constraints for higher accuracy simulations are listed.
\begin{gather}
2*\texttt{lmin} < \texttt{lmax} \\
0 \leq 4*\texttt{areamin} < 4*\frac{1}{2}*\texttt{lmin}^2 < \texttt{areamax} \leq \frac{\sqrt{3}}{2}*\frac{1}{2}*\texttt{lmax}^2 \\
2*\texttt{a} \leq \texttt{rann} < \texttt{lmin} \\
\texttt{rntol} \sim \texttt{rmax} < \texttt{rann} \\
\texttt{areamin} = 2*\texttt{rntol}*\texttt{lmax}
\end{gather}

\subsection{Parameter units}

Material parameters must be defined with consistent units to avoid a large disparity in scales. In the following table, simulation units in SI are listed for different physical dimensions. Let $\alpha$ and $\mu$ respectively be the lattice parameter and the shear modulus of the material in SI units. Let $B = 1 \left[\text{Pa} \cdot \text{s}\right]$ represent the scaling of drag units.
\begin{center}
\begin{tabular}{ m{4cm}  m{4cm} }
 \hline
 \textbf{Dimension} & \textbf{Simulation units} \\
 \hline\hline
 \text{Length} $\left[\text{m}\right]$ & $\alpha$ \\ 
 \hline
 \text{Pressure} $\left[\text{Pa}\right]$ & $\mu$ \\
 \hline
 \text{Drag} $\left[\text{Pa} \cdot \text{s}\right]$ & $B$ \\
 \hline
 \text{Time} $\left[\text{s}\right]$ & $B / \mu$ \\
 \hline
 \text{Velocity} $\left[\text{m} \cdot \text{s}^{-1}\right]$ & $\alpha \cdot \mu / B$ \\
 \hline
 \text{Force} $\left[\text{Pa} \cdot \text{m}^2\right]$ & $\mu \cdot \alpha^2$ \\
 \hline
 \text{Nodal force} $\left[\text{Pa} \cdot \text{m}\right]$ & $\mu \cdot \alpha$ \\
 \hline
\end{tabular}
\end{center}
Note that $\texttt{amag}$ and $\texttt{mumag}$ are respectively the lattice parameter in units of $\mu \text{m}$ and the shear modulus in units of $\text{MPa}$. As an example, consider Zirconium; its lattice parameter and shear modulus are respectively $\alpha = 3.233 \times 10^{-10} \left[\text{m}\right]$ and $\mu = 3.71 \times 10^{10} \left[\text{Pa}\right]$. In the following table, assignment values are converted to the corresponding physical values in SI units.
\begin{center}
\begin{tabular}{ m{5cm}  m{8cm} }
 \multicolumn{2}{c}{\textbf{Example: Zirconium}} \\
 \hline
 \textbf{Assignment value} & \textbf{Physical value}\\
 \hline\hline
 $\texttt{MU} = 1$ & $\texttt{MU} \cdot \mu = 3.71 \times 10^{10} \left[\text{Pa}\right]$ \\
 \hline
 $\texttt{Bcoeff} = 180\text{E}{-6}$ & $\texttt{Bcoeff} \cdot B = 180 \times 10^{-6} \left[\text{Pa} \cdot \text{s}\right]$ \\
 \hline
 $\texttt{dt} = 37.1$ & $\texttt{dt} \cdot B / \mu = 1 \times 10^{-9} \left[\text{s}\right]$ \\
 \hline
 $\texttt{a} = 90$ & $90 \cdot \alpha = 2.91 \times 10^{-8} \left[\text{m}\right]$ \\
 \hline
 $\texttt{f\_dot} = 0.1$ & $\texttt{f\_dot} \cdot \mu^2 \cdot \alpha^2 / B  = 14.387 \left[\text{Pa} \cdot \text{m}^2 \cdot \text{s}^{-1}\right]$ \\
 \hline
 $\texttt{amag} = 3.233 \text{E}{-4}$ & $3.233 \times 10^{-4} \left[\mu \text{m}\right]$ \\
 \hline
 $\texttt{mumag} = 3.71 \text{E}{4}$ & $3.71 \times 10^{4} \left[\text{MPa}\right]$ \\
 \hline
\end{tabular}
\end{center}
Suppose that we wish to set the length of dimension $x$ of the cuboid geometry to $10 \left[\mu \text{m} \right]$. This can be done by performing the assignment $\texttt{dx} = 10 / \texttt{amag}$. Expressing the physical units of \texttt{dx} explicitly yields
\begin{equation*}
\texttt{dx} = \frac{10}{\texttt{amag}} \cdot \alpha = \frac{10}{3.233 \times 10^{-4}} \cdot 3.233 \times 10^{-10} \left[\text{m}\right] = 10 \cdot 10^{-6} \left[\text{m}\right] = 10 \left[\mu \text{m}\right]
\end{equation*}

\newpage
%\printbibliography

\end{document}

### 2021-03-05 input/Thesis_Ni_110_tensile.m
Segsegforces now use cuda.

@@ -44,10 +44,10 @@ MU = 1.0;
 NU = 0.31;
 
 % x = <110>, y = <1-10>, z = <001>
-dz = 8.711 / amag; % 8.711 microns
-dx = 3 * dz;
+dz = 12 / amag; % 8.711 microns
+dx = 3.5 * dz;
 dy = dz;
-mx = 30;
+mx = 35;
 my = 10;
 mz = 10;
 
@@ -63,10 +63,13 @@ vertices = [0, 0, 0; ...
 % mumag*1e6 converts the meters to micrometers in the units.
 % The experimental displacement rate is 5 nm = 5e-3 micrometers.
 % The cantilever is dx micrometers long.
-timeUnit = 5e-3*(mumag*1e6);%/dx;
-u_dot = dx/timeUnit;
-% u_dot = 5e-3;
-% u_dot = dx/mumag;
+simDisp = 5e-3/amag; % 5 nanometers
+timeSim = 1 * (mumag*1e6)/1e-4; % timeSim = timeReal * ||mu|| / B
+u_dotSimFromReal = simDisp/timeSim;
+tmpScale = 1e9;% 5*1e8
+
+u_dot = u_dotSimFromReal*tmpScale;
+timeUnit = timeSim/tmpScale*1000;
 
 % This is the proper plotting function.
 % plot(Usim(1:curstep-1)/mumag/1e6,Fsim(1:curstep-1)*amag^2*mumag/1e6/1e6)
@@ -86,12 +89,12 @@ simType = @micropillarTensile;
 run fccLoops
 prismbVec(:, :) = prismbVec(:, :) / max(abs(prismbVec(1, :)));
 prismbVec(:, :) = prismbVec(:, :) * norm(prismbVec(1, :));
-segLen = 0.1 / amag;
+segLen = 0.2 / amag;
 lmin = 0.1 / amag;
 lmax = 0.4 / amag;
 
 a = lmin/20;
-rann = 2*a;%lmin/2;
+rann = lmin;%lmin/2;
 rntol = 3*lmin^2;
 rmax = 3*lmin^2;%lmin/2;
 
@@ -177,7 +180,7 @@ totalSimTime = timeUnit*1e4;
 mobility = @mobfcc0_110;
 % rotMatrix = rotMatrix';
 % mobility = @mobfcc0;
-saveFreq = 5;
+saveFreq = 1e9;
 plotFreq = 5;
 
[…]
